### 2022-10-12 src/tex/ms.tex
[showyourwork] first commit

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}

% Begin!
\begin{document}

% Title
\title{An open source scientific article}

% Author list
\author{@tomas-cabrera}

% Abstract with filler text
\begin{abstract}
    Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
    Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis.
    Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna.
    Donec vehicula augue eu neque, morbi tristique senectus et netus et.
    Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum.
    Phasellus eu tellus sit amet tortor gravida placerat.
    Integer sapien est, iaculis in, pretium quis, viverra ac, nunc.
    Praesent eget sem vel leo ultrices bibendum.
    Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac.
    Curabitur auctor semper nulla donec varius orci eget risus.
    Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
    Duis eget orci sit amet orci dignissim rutrum.
\end{abstract}

% Main body with filler text
\section{Introduction}
\label{sec:intro}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis.
Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna.
Donec vehicula augue eu neque, morbi tristique senectus et netus et.
Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum.
Phasellus eu tellus sit amet tortor gravida placerat.
Integer sapien est, iaculis in, pretium quis, viverra ac, nunc.
Praesent eget sem vel leo ultrices bibendum.
Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac.
Curabitur auctor semper nulla donec varius orci eget risus.
Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
Duis eget orci sit amet orci dignissim rutrum.

Nam dui ligula, fringilla a, euismod sodales, sollici- tudin vel, wisi.
Morbi auctor lorem non justo, nam lacus libero, pretium at, lobortis vitae.
Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna.
Morbi ac orci et nisl hendrerit mollis, suspendisse ut massa, cras nec ante.
Pellentesque a nulla cum sociis natoque penatibus et magnis dis parturient.
Aliquam tincidunt urna, nulla ullamcorper vestibulum turpis.
Pellentesque cursus luctus mauris \citep{Luger2021}.

\bibliography{bib}

\end{document}

### 2022-10-12 src/scripts/random_numbers.py
Added a new figure

@@ -1,0 +1,13 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import paths
+
+# Generate some data
+random_numbers = np.random.randn(100, 10)
+
+# Plot and save
+fig = plt.figure(figsize=(7, 6))
+plt.plot(random_numbers)
+plt.xlabel("x")
+plt.ylabel("y")
+fig.savefig(paths.figures / "random_numbers.pdf", bbox_inches="tight", dpi=300)

### 2022-10-12 src/tex/ms.tex
Added a new figure
First hvss figure

@@
 
+\begin{figure}[ht!]
+    \script{random_numbers.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/random_numbers.pdf}
+        \caption{
+            Plot showing a bunch of random numbers.
+        }
+        \label{fig:random_numbers}
+    \end{centering}
+\end{figure}
+
+\begin{figure*}
+    \script{cmc_single_clusters.py}
+    \gridline{
+        \fig{figures/cmc_single_clusters_vout-N8e5-rv0.5-rg8-Z0.0002.pdf}{0.49\textwidth}{}
+        \fig{figures/cmc_single_clusters_vout-N4e5-rv0.5-rg8-Z0.0002.pdf}{0.49\textwidth}{}
+    }
+    \gridline{
+        \fig{figures/cmc_single_clusters_vout-N8e5-rv2-rg8-Z0.0002.pdf}{0.49\textwidth}{}
+        \fig{figures/cmc_single_clusters_vout-N8e5-rv0.5-rg8-Z0.02.pdf}{0.49\textwidth}{}
+    }
+    \caption{
+        Scatter plots of the cluster ejection velocity $V_{rm out}$ versus encounter time $t$ for every escaping object from the integrated encounters for the four sample CMC models (see the beginning of \S\ref{subsec:single_clusters} for details).
+        The histograms show the same data in 1D.
+        The different types of encounters are color-coded: encounters between a binary star and a CO are in red,
+        encounters between a mixed binary (1 star and 1 CO) and a CO are in blue, encounters between a mixed binary and a star are in yellow, and encounters between a CO binary and a star are in purple.
+        The $N$-body core radius $r_{c, NB}$ \citep{1985ApJ...298...80C} of the model is plotted in maroon over the timewise histogram.
+    }
+    \label{fig:cmc_single_clusters}
+\end{figure*}
+
 Nam dui ligula, fringilla a, euismod sodales, sollici- tudin vel, wisi.

### 2022-10-12 src/scripts/cmc_single_clusters.py

@@ -1,0 +1,245 @@
+import sys
+import os
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+from matplotlib.colors import ListedColormap
+from matplotlib import cm
+from matplotlib.legend_handler import HandlerTuple
+
+import rustics
+import paths
+
+################################################################################
+
+#plt.style.use("./matplotlibrc")
+
+# Get cluster names
+cmc_cluster_list = [
+    "N8e5_rv0.5_rg8_Z0.0002",
+    "N8e5_rv2_rg8_Z0.0002",
+    "N8e5_rv0.5_rg8_Z0.02",
+    "N4e5_rv0.5_rg8_Z0.0002",
+]
+#cmc_cluster_list = rustics.DF_MODELS[(rustics.DF_MODELS.N == 4) & (rustics.DF_MODELS.rv == 0.5)].fname
+
+for ci, cmc_cluster in enumerate(cmc_cluster_list):
+    print("{}, N_REALZ={}".format(cmc_cluster, rustics.N_REALZ))
+
+    # File names and directory creation
+    path_to_ejections = paths.data_cmc / cmc_cluster / rustics.FILE_EJECTIONS
+
+    # Read saved data file
+    ejdf = rustics.EjectionDf(path_to_ejections)
+
+    # Convert to physical units
+    ejdf.convert_from_fewbody()
+
+    # Filter out mergers
+    ejdf.df = ejdf.df[ejdf.df["type_f"] > 0]
+
+    # Calculate vout (velocity from cluster)
+    ejdf.df["vout"] = ejdf.calc_vout()
+    ejdf.df["mx"] = ejdf.df[["m0", "m10", "m11"]].max(axis=1)
+
+    # Load times and core radii from initial.dyn.dat
+    df_dyn = pd.read_csv(
+        paths.data_cmc / cmc_cluster / "initial.dyn.dat",
+        #"/".join((paths.data, "cmc", cmc_cluster, "initial.dyn.dat")),
+        names=["t", "N", "rc_nb"],
+        usecols=[0, 3, 24],  # 0 for t, 3 for N, 24 for rc_nb
+        skiprows=2,
+        delim_whitespace=True,
+    )
+
+    # Load intial.conv.sh (for converting TotalTime to Myr and core radius to pcs)
+    # Copied from cmctools/cmctoolkit.py
+    conv_path = paths.data_cmc / cmc_cluster / "initial.conv.sh"
[…]

### 2022-10-12 src/scripts/paths.py

@@ -13,6 +13,12 @@ src = root / "src"
 # Absolute path to the `src/data` folder (contains datasets)
 data = src / "data"
 
+# Absolute path to the `src/data/cmc` folder (CMC model data)
+data_cmc = data / "cmc"
+
+# Absolute path to the `src/data/mwgcs` folder (MW GC data (observational catalogs))
+data_mwgcs = data / "mwgcs"
+
 # Absolute path to the `src/static` folder (contains static images)
 static = src / "static"
 

### 2022-10-12 src/scripts/rustics.py

@@ -1,0 +1,922 @@
+# RUnaway STars In Cluster Simulations
+###############################################################################
+
+
+import numpy as np
+import pandas as pd
+import multiprocessing as mp
+import parmap
+from tqdm import tqdm
+
+import paths
+
+###############################################################################
+
+
+# Physical constants
+
+
+# Unit conversions
+YR_TO_S = 365.2425 * 24 * 3600
+PC_TO_M = 3.0857e16
+
+# Number of realizations per CMC encounter
+N_REALZ = 10
+
+
+# Filename of realization data
+FILE_REALZ = "output_N-%d.txt" % N_REALZ
+
+
+# File suffix for ejection data
+SUFFIX_EJECTIONS = "_ejections"
+
+
+# Filename of ejection data
+FILE_EJECTIONS = (SUFFIX_EJECTIONS + ".").join(FILE_REALZ.rsplit(".", 1))
+
+
+## Path to project
+#PATH_TO_PROJECT = "/home/tomas/Documents/cmu/research/hvss"
+#
+#
+## Path to data
+#PATH_TO_DATA = "/".join((PATH_TO_PROJECT, "data"))
+#
+#
+## Path to figures
+#PATH_TO_FIGURES = "/".join((PATH_TO_PROJECT, "rustics/figures"))
+#
+#
+## Path to CMC data
+#PATH_TO_CMC_DATA = PATH_TO_DATA
+#
+#
+## Path to matplotlib_style_file
+#PATH_TO_MPLRC = "/home/tomas/Documents/cmu/research/matplotlib_style_file"
+
+
+# Table of CMC catalog models, received from Kyle Kremer via. e-mail 07/27/2021 and supplemented with cmc_core_collapsed.py and gcs_mw-cmc.ipynb
+# Also obtainable from Table A1 in Kremer et al. 2020 (catalog paper)
+DF_MODELS = pd.read_csv(
+    paths.data_cmc / "Catalog_models_ccw.dat",
+)
+# Old version, reads directly from Kyle's Catalog_models.dat
+# DF_MODELS = pd.read_table(
+#    "/".join((PATH_TO_PROJECT, "Catalog_models_ccw.dat")),
+#    names=["N", "rv", "rg", "Z", "N_BH", "status"],
+#    skiprows=2,
+#    delimiter=" ",
+# )
[…]

### 2022-10-12 src/scripts/cmc_orbits_cdf.py
Added prelimiary vlos cdf

@@ -1,0 +1,186 @@
+import os
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import matplotlib.ticker as mplticker
+from matplotlib.patches import Patch
+
+import rustics
+import paths
+
+################################################################################
+
+# TODO: add functionality to calculate vlos for object
+#       Currently fails at creating SkyCoord object in rustics.py
+
+################################################################################
+
+#plt.style.use(rustics.PATH_TO_MPLRC)
+
+# Get model info
+path_to_data = paths.data_mwgcs
+df_mwgcs = pd.DataFrame(os.listdir(path_to_data), columns=["fname"]) 
+
+# Iterables
+columns = ["vlos", "mf"]
+
+# Specify kgroup
+kgroup = None
+kgroup = rustics.INFO_BSE_K_GROUPS.iloc[0]
+
+# Make subplot mosiac
+plot_size = 2.3
+fig, axd = plt.subplot_mosaic(
+    [columns],
+    sharey=True,
+    figsize=(plot_size * len(columns), plot_size),
+    gridspec_kw={
+        "wspace": 0,
+        "hspace": 0,
+    },
+)
+
+# Iterate over columns (each should have an entry in rustics.BINS)
+for ci, c in enumerate(columns):
+    print("column=%s" % c)
+
+    # Initialize hist. generator
+    bins = rustics.BINS_CDF[c]
+    if c == "mf":
+        # Bin by pre-/post-core collapse for mass histograms
+        hg = rustics.HistogramGenerator(c, bins, nprocs=4, kgroup=kgroup)#, cc=True)
+    else:
+        hg = rustics.HistogramGenerator(c, bins, nprocs=4, kgroup=kgroup)
+
+    # Generate histograms
+    df_mwgcs["hists"] = hg.generate_catalog_histograms(df_mwgcs, pm_pbar=True, path_to_data=path_to_data)
+
+    # Choose axis
+    ax = axd[c]
+
+    # Plot
+    if 0:#c == "mf":
+        for cci, cc_row in rustics.INFO_CC_GROUPS.iterrows():
+            # Plot histogram
+            weights = df_mwgcs["hists"].sum()[cci]
+            ax.hist(
+                bins[:-1],
+                bins=bins,
+                weights=np.cumsum(weights) / np.sum(weights),
+                label="CMC",
[…]

### 2022-10-12 src/scripts/rustics.py

@@ -4,6 +4,8 @@
 
 import numpy as np
 import pandas as pd
+from astropy.coordinates import SkyCoord, ICRS, Galactic, Galactocentric
+from astropy import units as u
 import multiprocessing as mp
 import parmap
 from tqdm import tqdm
@@ -59,7 +61,7 @@ FILE_EJECTIONS = (SUFFIX_EJECTIONS + ".").join(FILE_REALZ.rsplit(".", 1))
 # Table of CMC catalog models, received from Kyle Kremer via. e-mail 07/27/2021 and supplemented with cmc_core_collapsed.py and gcs_mw-cmc.ipynb
 # Also obtainable from Table A1 in Kremer et al. 2020 (catalog paper)
 DF_MODELS = pd.read_csv(
-    paths.data_cmc / "Catalog_models_ccw.dat",
+    paths.data / "Catalog_models_ccw.dat",
 )
 # Old version, reads directly from Kyle's Catalog_models.dat
 # DF_MODELS = pd.read_table(
@@ -240,6 +242,7 @@ HEADERS_TO_LABELS = {
     "dist": r"$d [{\rm kpc}]$",
     "vesc/rho_0": r"$v_{\rm esc}/\rho_0 [{\rm km~s^{-1}/something}]$",
     "v_radial": r"$v_r [{\rm km~s}^{-1}]$",
+    "vlos": r"$v_{\rm los} [{\rm km~s}^{-1}]$",
     "mx": r"$m_{\rm max} (M_\odot)$",
     "M": r"$M~[M_\odot]$",
     "rc_spitzer/r_h": r"$r_{\rm core} / r_{h,m}$",
@@ -303,6 +306,7 @@ AXES_LIMS = {
     "mf": [5e-2, 55],
     "dist": [1e-3, 1e5],
     "v_radial": [-1e3, 1e3],
+    "vlos": [-1e3, 1e3],
 }
 
 
@@ -313,6 +317,7 @@ HIST_LIMS = {
     "Nej": [0, 14],
     "dist": [5e-4, 1e3],
     "v_radial": [5e-4, 1e3],
+    "vlos": [5e-4, 1e3],
 }
 
 
@@ -324,6 +329,7 @@ BINS = {
     "dist": np.logspace(*np.log10(AXES_LIMS["dist"]), 60),
     # "v_radial": np.linspace(*AXES_LIMS["v_radial"], 120),
[…]

### 2022-10-12 src/tex/ms.tex
Added prelimiary vlos cdf
Added catalog histograms

@@
 \usepackage{showyourwork}
+
+% My commands
+\newcommand{\CMC}{\texttt{CMC}}
+\newcommand{\CMCcat}{\texttt{CMC Cluster Catalog}}
+\newcommand{\fewbody}{\texttt{Fewbody}}
 
@@
     \caption{
-        Scatter plots of the cluster ejection velocity $V_{rm out}$ versus encounter time $t$ for every escaping object from the integrated encounters for the four sample CMC models (see the beginning of \S\ref{subsec:single_clusters} for details).
+        Scatter plots of the cluster ejection velocity $V_{rm out}$ versus encounter time $t$ for every escaping object from the integrated encounters for the four sample \CMC\ models (see the beginning of \S\ref{subsec:single_clusters} for details).
         The histograms show the same data in 1D.
@@
     \label{fig:cmc_single_clusters}
+\end{figure*}
+
+\begin{figure}[ht!]
+    \script{cmc_orbits_cdf.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/cmc_orbits_cdf_S.pdf}
+        \caption{
+            Plot showing orbit cdf.
+        }
+        \label{fig:cmc_orbits_cdf}
+    \end{centering}
+\end{figure}
+
+\begin{figure*}
+    \script{cmc_catalog.py}
+    \centering
+    \includegraphics[width=\textwidth]{figures/cmc_catalog_S.pdf}
+    \caption{
+        Histograms for all MS stars ejected from the \CMCcat\ models as a result of BSCO encounters.
+        The three columns display the cluster ejection velocities $v_{\rm out}$, the present-day straight-line travel distances $d$, and the masses $m$ of the ejected objects, respectively.
+        Each row divides the data across the values for the \CMC\ model parameters size $N$ (number of objects), initial virial radius $r_{\rm vir}$ (parsecs), or metallicity $Z$.
+        Each histogram is averaged over all models computed with the respective model parameter.
+        In the right column (the mass plots), the data are further divided by whether the ejection occurred before or after the BH-ejection core collapse of the cluster, if one occurred within the integration time.
+    }
+    \label{fig:cmc_catalog}
 \end{figure*}

### 2022-10-12 src/scripts/cmc_catalog.py

@@ -1,0 +1,165 @@
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import matplotlib.ticker as mplticker
+from matplotlib.patches import Patch
+
+import rustics
+import paths
+
+################################################################################
+
+#plt.style.use(rustics.PATH_TO_MPLRC)
+
+# Get model info
+df_models = rustics.DF_MODELS
+
+# Iterables
+columns = ["vout", "dist", "mf"]
+params = ["N", "rv", "Z"]
+
+# Specify kgroup
+kgroup = None
+kgroup = rustics.INFO_BSE_K_GROUPS.iloc[0]
+
+# Toggle weighting by MW GCs
+weight_mw = False
+
+# Make subplot mosiac
+plot_size = 2.3
+mosaic = [["_".join((p, c)) for c in columns] for p in params]
+fig, axd = plt.subplot_mosaic(
+    mosaic,
+    sharey=True,
+    figsize=(plot_size * len(columns), plot_size * len(params)),
+    gridspec_kw={
+        "wspace": 0,
+        "hspace": 0,
+    },
+)
+
+# Iterate over columns (each should have an entry in rustics.BINS)
+for ci, c in enumerate(columns):
+    print("column=%s" % c)
+
+    # Initialize hist. generator
+    bins = rustics.BINS[c]
+    if c == "mf":
+        # Bin by pre-/post-core collapse for mass histograms
+        hg = rustics.HistogramGenerator(c, bins, nprocs=4, kgroup=kgroup, cc=True)
+    else:
+        hg = rustics.HistogramGenerator(c, bins, nprocs=4, kgroup=kgroup)
+
+    # Generate histograms
+    df_models["hists"] = hg.generate_catalog_histograms(df_models, pm_pbar=True)
+
+    # Weight by MW GCs
+    if weight_mw:
+        df_models["hists"] *= df_models["weights_mw"]
+
+    # Iterate over parameters
+    for pi, p in enumerate(params):
+        print("\tparam=%s" % p)
+
+        # Choose axis
+        ax = axd["_".join((p, c))]
+
+        # Iterate over unique values of the parameter
+        for xi, x in enumerate(np.sort(df_models[p].unique())):
+            if c == "mf":
+                for cci, cc_row in rustics.INFO_CC_GROUPS.iterrows():
+                    # Plot histogram
+                    mask = df_models[p] == x
+                    nclusters = mask.sum()
[…]

### 2022-10-12 src/scripts/cmc_orbits_cdf.py

@@ -10,9 +10,6 @@ import paths
 
 ################################################################################
 
-# TODO: add functionality to calculate vlos for object
-#       Currently fails at creating SkyCoord object in rustics.py
-
 ################################################################################
 
 #plt.style.use(rustics.PATH_TO_MPLRC)

### 2022-10-12 src/scripts/cmc_single_clusters_vesc.py
Addes vesc plot

@@ -1,0 +1,176 @@
+import sys
+import os
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+from matplotlib.colors import ListedColormap
+from matplotlib import cm
+from matplotlib.legend_handler import HandlerTuple
+import matplotlib.ticker as mplticker
+
+import rustics
+import paths
+
+################################################################################
+
+#plt.style.use(rustics.PATH_TO_MPLRC)
+
+# Get cluster names
+cmc_cluster_list = [
+    "N8e5_rv0.5_rg8_Z0.0002",
+    "N4e5_rv0.5_rg8_Z0.0002",
+    "N8e5_rv2_rg8_Z0.0002",
+    "N8e5_rv0.5_rg8_Z0.02",
+]
+
+mosaic = np.reshape(cmc_cluster_list, (4,1))
+figheight = 1.5 
+figwidth = 4
+fig, axd = plt.subplot_mosaic(
+    mosaic,
+    figsize=(mosaic.shape[1]*figwidth, mosaic.shape[0]*figheight),
+    sharex=True,
+    gridspec_kw={
+        "hspace": 0,
+        "wspace": 0,
+    },
+)
+for ci, cmc_cluster in enumerate(cmc_cluster_list):
+    print("{}, N_REALZ={}".format(cmc_cluster, rustics.N_REALZ))
+
+    # File names and directory creation
+    path_to_ejections = paths.data_cmc / cmc_cluster / rustics.FILE_EJECTIONS
+
+    # Read saved data file
+    ejdf = rustics.EjectionDf(path_to_ejections)
+    ejdf.df = ejdf.df
+
+    # Convert to physical units
+    ejdf.convert_from_fewbody()
+
+    # Filter out mergers
+    ejdf.df = ejdf.df[ejdf.df["type_f"] > 0]
+
+    # Load times and core radii from initial.dyn.dat
+    df_dyn = pd.read_csv(
+        paths.data_cmc / cmc_cluster / "initial.dyn.dat",
+        # names=["t", "rc_nb"],
+        # usecols=[0, 24],  # 0 for t, 24 for rc_nb
+        names=["t", "Dt", "rho_0", "rc_nb"],
+        usecols=[0, 1, 21, 24],  # 0 for t, 1 for Dt, 24 for rho_0
+        skiprows=2,
+        delim_whitespace=True,
+    )
+
[…]

### 2022-10-12 src/tex/ms.tex
Addes vesc plot (ms.tex)

@@
 
+\begin{figure}
+    \script{cmc_single_clusters_vesc.py}
+    \centering
+    \includegraphics[width=0.49\textwidth]{figures/cmc_single_clusters_vesc.pdf}
+    \caption{
+        The local escape velocities $v_{\rm esc}$ of all BSCO encounters generated from the four sample \CMC\ models (colored points), plotted alongside the central density $\rho_c$ of the model (maroon), that latter of which is divided by the initial central density of the model.
+        See Figure \ref{fig:cmc_single_clusters_vesc} for an explanation of the color scheme.
+    }
+    \label{fig:cmc_single_clusters_vesc}
+\end{figure}
+
 \begin{figure*}

### 2022-10-12 src/tex/ms.tex
Copied article content from Overleaf

@@
 % My commands
+\newcommand{\kms}{${\rm km \times s^{-1}}$}
+\newcommand{\Msun}{$M_\sun$}
 \newcommand{\CMC}{\texttt{CMC}}
@@
 \newcommand{\fewbody}{\texttt{Fewbody}}
+
+\shorttitle{Runaway \& hypervelocity stars from globular clusters}
+\shortauthors{Cabrera et al.}
 
@@
 % Title
-\title{An open source scientific article}
+\title{Runaway and hypervelocity stars from binary-single encounters in globular clusters}
 
 % Author list
-\author{@tomas-cabrera}
+\author[0000-0002-1270-7666]{Tom\'as Cabrera}
+\affiliation{McWilliams Center for Cosmology,
+    Department of Physics,
+    Carnegie Mellon University,
+    5000 Forbes Avenue, Pittsburgh, PA 15213
+}
+
+\author[0000-0003-4175-8881]{Carl L. Rodriguez}
+\affiliation{McWilliams Center for Cosmology,
+    Department of Physics,
+    Carnegie Mellon University,
+    5000 Forbes Avenue, Pittsburgh, PA 15213
+}
 
@@
 \begin{abstract}
-    Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
-    Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis.
-    Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna.
-    Donec vehicula augue eu neque, morbi tristique senectus et netus et.
-    Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum.
-    Phasellus eu tellus sit amet tortor gravida placerat.
-    Integer sapien est, iaculis in, pretium quis, viverra ac, nunc.
-    Praesent eget sem vel leo ultrices bibendum.
-    Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac.
-    Curabitur auctor semper nulla donec varius orci eget risus.
-    Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
-    Duis eget orci sit amet orci dignissim rutrum.
+    An abstract.
 \end{abstract}
@@
 
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
-Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis.
-Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna.
-Donec vehicula augue eu neque, morbi tristique senectus et netus et.
-Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum.
-Phasellus eu tellus sit amet tortor gravida placerat.
-Integer sapien est, iaculis in, pretium quis, viverra ac, nunc.
-Praesent eget sem vel leo ultrices bibendum.
-Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac.
-Curabitur auctor semper nulla donec varius orci eget risus.
-Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
-Duis eget orci sit amet orci dignissim rutrum.
+Hypervelocity stars (HVSs) are stars that have been accelerated beyond the local galactic escape speed, that is, to the point of becoming unbound from the galactic potential.
+Theorized by \citealt{1988Natur.331..687H}, the classical origin of HVSs is the dynamical disruption of a stellar binary by a super massive black hole (SMBH); this ``Hills mechanism" is believed to be capable of accelerating stars to speeds up to 4000 km s$^{-1}$.
+Since the first HVS discovery \citep{2005ApJ...622L..33B}, a handful of candidate objects have been identified in the Milky Way (MW) (e.g.
+\citealt{2014ApJ...787...89B}), including the object S5-HVS1, with a measured speed of $\sim$1700 km s$^{-1}$ \citep{2020MNRAS.491.2465K}.
+While S5-HVS1 is believed to have originated from the galactic center, for which there is overwhelming evidence for an SMBH (\citealt{1998ApJ...509..678G}, \citealt{2018A&A...615L..15G}, \citealt{2022ApJ...930L..12E}), data from Gaia DR2 have been used to eliminate the galactic center origin case for most former HVS candidates \citep{2018MNRAS.479.2789B}.
+Stars may also be accelerated if their binary companion goes supernova, but HVSs produced through this mechanism are generally ejected with relatively modest speeds of a few hundred km s$^{-1}$ \citep{2019A&A...624A..66R}, with exceptionally light companions potentially receiving velocities around 1000 km s$^{-1}$ \citep{2015MNRAS.448L...6T}.
 
-\begin{figure}[ht!]
-    \script{random_numbers.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/random_numbers.pdf}
-        \caption{
-            Plot showing a bunch of random numbers.
-        }
-        \label{fig:random_numbers}
-    \end{centering}
-\end{figure}
+Another process that produces HVSs is dynamical interaction among stellar-mass objects.
+The long-term stability of binaries opens the door to 3- and 4-body encounters, which have a greater ability to accelerate stars than 2-body interactions.
+\citet{1991AJ....101..562L} studied these encounters with numerical methods, and found that the upper speed limit for products of these encounters was approximately the escape speed from the surface of the most massive star; for a sun-like star, this escape speed is $\sim$620 km s$^{-1}$, while for a 60 $M_\odot$ late main-sequence star it is $\sim$1400 km s$^{-1}$.
+However, such a velocity limit has not been examined for encounters involving compact objects such as white dwarfs (WDs), neutron stars (NSs), and black holes (BHs) whose small physical radius permits stronger encounters without collisions among objects.
+
+Dynamical encounters among stellar-mass objects occur frequently in globular clusters (GCs), due to the high densities therein.
+Furthermore, the efficient formation of binary black holes (BBHs) in the cores of evolved GCs \citep{2005MNRAS.358..572I} encourages multi-body encounters among these compact objects and stars in the enclosing shell as the BBHs are themselves ejected from the core due to strong dynamical encounters.
+With around 150 GCs identified in the MW today (e.g.
+\citealt{2018MNRAS.478.1520B}), it is possible that the dynamics of these systems account for some of the HVSs that are inconsistent with the galactic center origin model.
+
+This work investigates the capacity of GCs to produce HVSs through dynamical encounters between binaries and single objects through numerical modeling of realistic encounter populations, building upon the existing knowledge base by performing the first direct $N$-body analysis of binary-single encounters composed of a mixture of stars and compact objects.
+The the inclusion of compact objects is expected to yield an upper speed limit distinct from that presented by \citealt{1991AJ....101..562L}.
+A realistic population of binary-single encounters from star clusters is then assembled by extracting the appropriate events from the catalog of cluster models provided by the {\tt\string Cluster Monte Carlo} (\CMC) group \citep{2020ApJS..247...48K}.
+Each encounter is multiplied over randomized spatial configurations and integrated to estimate the properties of the HVS star population generated by three-body encounters in GCs.
+This analysis concludes that GCs are possible generators of HVSs in all velocity regimes thus observed, beyond the previously established limit for star-only encounters, albeit the rate at which these objects are produced from GCs is significantly lower than that for the galactic center.
+
+\section{Methods} \label{sec:methods}
+
+\subsection{Binary-single encounter population} \label{subsec:binsingle_pop}
+
+To establish realistic binary-single encounter populations for clusters of various parameters, we take the 148 cluster models from the \CMCcat\ and extract the initial conditions of all of the binary-single encounters that involve at least one luminous object (star, WD, or NS) and one compact object.
+On average, the number of encounters satisfying these criteria per cluster model is in the mid ten thousands.
+We then realize each encounter in isolation with the small-$N$-body code \fewbody\ \citep{2004MNRAS.352....1F}.
+We compute 10 realizations of each encounter - varying the random seed used to specify the geometry of the encounter - to obtain a better statistical representation of the binary-single encounter population.
+
+The resulting objects that leave the cluster to become runaway or HVSs are identified as follows.
+\fewbody\ terminates integration before the resulting objects are far from each other's gravitational influence; therefore, the final velocity of an object after an encounter $v_{\rm fin}$ is calculated as the hyperbolic excess velocity
+\begin{equation}
+    v_{\rm fin} = v \sqrt{\frac{U + K}{K}},
+\end{equation}
+where $v$ is the velocity of the object, and $U$ and $K$ are the Keplerian potential and kinetic energies of the top-level binary-single system (all of these quantities are evaluated at the termination of integration).
+The local escape velocity of the star cluster $v_{\rm esc}$ is provided by \CMC\ with the other encounter parameters; any object with $v_{\rm fin} \ge v_{\rm esc}$ is considered to escape the cluster.
+The velocity of an ejected object once it has left the cluster is therefore
+\begin{equation}
+    v_{\rm out} = \sqrt{v_{\rm fin}^2 - v_{\rm esc}^2}.
+\end{equation}
+
+It is worth noting that the encounter initial conditions recorded in the \CMCcat\ contain velocities calculated in the center-of-mass frame of the encounter.
+A more rigorous calculation of $v_{\rm out}$ would therefore utilize the velocity dispersion $\sigma$ to determine how $v_{\rm fin}$ translates to a velocity in the reference frame of the star cluster model.
+Assuming that the distribution of the 3D object velocity $\vec{v}_{\rm fin}$ is independent of the center-of-mass velocity $\vec{v}_{\rm cm}$ of the encounter it originated from, we find that the average ratio of speed after to speed before the transformation to the cluster reference frame $v'_{\rm fin} / v_{\rm fin}$ is a maximum of $\sim$1.3 in the case $v_{\rm fin} \approx \sigma$, and a minimum of 1 in the case $v_{\rm fin} \gg \sigma$.
+As $v_{\rm cm} \sim \sigma$, and $\sigma \lesssim v_{\rm esc}$ [CITATIONS?], we estimate that neglecting a transformation to the cluster reference frame after center-of-mass encounter integration slightly reduces the resulting ejection population in a manner that does not significantly affect the following analysis.
+% Stackedbar plot of resulting encounters?
+
+\subsection{Core collapse and ejecta} \label{subsec:cc}
+
+The core collapses of star clusters due to dynamical heat flow from the center to the outer regions of a system are well-documented processes (e.g.
+\citealt{1968MNRAS.138..495L}, \citealt{2020IAUS..351..357K}).
+One kind of core collapse occurs when the population of BHs in cluster (localized to the center via.
+mass segregation) is depleted through fewbody encounters in this region; the dynamically less energetic core is no longer able to fuel the dynamics of the rest of the cluster, and the cluster contracts.
+Many of these core encounters are between a binary and a single, contain compact objects, and can impart large accelerations on the participants, and accordingly are of particular interest here.
+
+In this analysis, we label a cluster as core collapsed when its population of BHs has been reduced to less than 10 members.
+By this metric, 69 of the 148 \CMCcat\ models achieve core collapse by the end of the 14 Gyr integration time, and small cluster mass and spatial size are good indicators of systems that evolve to this point the fastest.
+
+\subsection{Estimating a MW-like population} \label{subsec:est_MW-like}
+
+% Plot idea: the log(M) vs. rr vs. r_hm diagnostic plots in gcs_mw-cmc.ipynb, with top/bottom//left/right axes showing the physical and normalized values of each variable
+
+In the interest of predicting realistic statistics and rates for a MW-like GC population, we assign representative \CMC\ models to each of the GCs in an aggregate observational catalog.
+The 148 models in the \CMCcat\ are specified by cluster initial size $N$ (number of stellar objects), initial virial radius $r_{\rm vir}$ (parsecs), distance from the galactic center $r_{\rm gc}$ (kiloparsecs, used in \CMC\ to calculate tidal effects from the galactic potential), and metallicity $Z$ (used to prescribe star evolution), with values chosen to span much of the MW GC parameter space; see \citet{2020IAUS..351..357K} for more details.
+After the same paper we use cluster mass $M$ and core radius to half-mass radius ratio $r_{\rm core} / r_{h,m}$ to relate \CMC\ models to MW GCs, and in this study we also include metallicity $Z$ to help distinguish otherwise similar systems.
+We use the definition of core radius from [CITATION, the Spitzer book?]:
+\begin{equation}
+    r_{\rm core} = \sqrt{\frac{3 \sigma_c^2}{4 \pi \rho_c}},
+\end{equation}
+where $\sigma_c$ is the central velocity dispersion and $\rho_c$ is the central density for the cluster.
+
+To assemble a set of MW GCs we combine the catalogs of \citet{2010arXiv1012.3224H} and \citet{2018MNRAS.478.1520B}, as the latter provides $M$ and $r_{\rm core} / r_{h,m}$ measurements and the former $Z$ measurements for the observed systems.
+We use 149 GCs from the conjunction of the two catalogs, after vetting the 15 GCs that lack a measurement for any of the three parameters of interest.
+These MW GCs and the \CMC\ models are shown in Figure \ref{fig:mw-cmc}.
+The quantities for the \CMC\ models are computed from the final timesteps.
+
+%\begin{figure*}
+%    \script{mw-cmc.py}
+%    \centering
+%    \includegraphics[width=\textwidth]{figures/mw-cmc.pdf}
+%    \caption{
+%        The clusters and models used in this work.
+%        Galactic GCs are represented by black dots, and CMC models by red dots.
+%        The sample \CMC\ models used in \S\ref{subsec:single_clusters} are shown as blue stars.
+%        M3 and its \CMC\ counterpart relevant to \S\ref{} are shown as purple triangles.
+%        Cluster mass $M_{\rm cluster}$ is shown on the $y$-axis, and the core radius/half-mass radius ratio $r_{\rm core}/r_{h,m}$ (metallicity $[{\rm Fe/H}]$) on the left (right) $x$-axis.
+%        The opposing axes along the top and right of the figure display the normalized parameters $[x]_{\rm norm}$, as defined in \S\ref{subsec:est_MW-like}.
+%    }
+%    \label{fig:mw-cmc}
+%\end{figure*}
+
+We use a simple nearest neighbor algorithm to assign a representative \CMC\ model to each of the MW GCs, where the \CMC\ model with the shortest Euclidean distance to the MW GC is taken as its representative.
+Each of the three parameters $\log_{10}(M)$, $r_{\rm core} / r_{h,m}$, and $[{\rm Fe/H}]$ are more equally weighted by computing the distance in the respective standard normalized space, where each parameter is normalized by taking its $Z$-score in the context of the \CMC\ clusters:
+\begin{equation}
+    [x]_{\rm norm} = \frac{x - \bar{x}_{\rm \CMC}}{\sigma_{\rm x, \CMC}},
+\end{equation}
+where $\bar{x}_{\rm CMC}$ and $\sigma_{\rm x,CMC}$ are respectively the mean and standard deviation of the parameter $x$ over the set of \CMC\ models.
+
+While the \CMCcat\ has fairly representative models for most of the MW GCs, there are a number of larger-cored GCs (right side of the left pane of Figure \ref{fig:mw-cmc}) that are relatively distant from the nearest \CMC\ model.
+In our nearest-neighbors pairing, this means that a single \CMC\ model can be chosen to represent a disproportionate number of MW GCs.
+In the pairing we define, 61 \CMC\ models end up being used to characterize the MW GCs, with the most used model paired to 21 GCs.
+With these disclosures, we consider our representation of the galactic population of GCs to be adequate for this analysis.
+
+\section{Results} \label{sec:results}
+
+\subsection{Ejections from single clusters} \label{subsec:single_clusters}
+
+Here we study the BSCO ejections produced by individual \CMC\ cluster models.
+\CMC\ model N8e5\_rv0.5\_rg8\_Z0.0002 is taken as a sample as it represents a typical MW GC, and models N4e5\_rv0.5\_rg8\_Z0.0002, N8e5\_rv0.5\_rg8\_Z0.0002, and N8e5\_rv2\_rg8\_Z0.02 are included to examine the effects parameter variation has on the population of ejected objects (all four of these models are represented by blue stars in Figure \ref{fig:mw-cmc}).
+For simpler reference, we name the first sample model the ``base" model, and the remaining three the ``low-mass", ``bigger", and ``high-metallicity" models, respectively.
+
+It is relevant to note a strong correlation between BSCO encounters and the evolution of the cluster core.
+Figure \ref{fig:cmc_single_clusters_vesc} plots the local escape velocities $v_{\rm esc}$ for all BSCO encounters from the sample models, along with the central density $\rho_c$ \citep{1985ApJ...298...80C}, scaled to the initial density of the model $\rho_{c,0}$.
+Within any small interval of time, the respective BSCO encounters are well-localized around a particular escape velocity, indicating that throughout the evolution of the cluster contemporary encounters are similarly localized to the same cluster radii.
+Furthermore, the variation of this ``particular escape velocity" is quite parallel to the variation of the core density of the cluster.
+Naturally one would expect the densest part of a system to facilitate the highest rates of few-body encounters; in this case the dominance is extreme enough to characterize the encounter statistics as a whole.
 
@@
 \end{figure}
+
+Figure \ref{fig:cmc_single_clusters} shows the ejection velocity $v_{\rm out}$ for every MS star ejected via.
+a BSCO encounter in these clusters, plotted at the time of encounter since the cluster's formation $t$.
+By comparing the scatter plot to the evolution of the $N$-body core radius $r_{c, NB}$ \citep{1985ApJ...298...80C}, it is clear how the BSCO encounters and ejections are linked to the dynamical evolution of the cluster.
+Whenever a cluster undergoes a core collapse, the heightened densities lead to predictably high encounter rates.
 
@@
 
-\begin{figure}[ht!]
-    \script{cmc_orbits_cdf.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/cmc_orbits_cdf_S.pdf}
-        \caption{
-            Plot showing orbit cdf.
-        }
-        \label{fig:cmc_orbits_cdf}
-    \end{centering}
-\end{figure}
+An interplay between stellar evolution and cluster dynamics is revealed in the kinds of BSCO encounters that occur at certain times.
+The most massive stars in a cluster are both the first to form binaries and the first to evolve into COs; hence, in general encounters between a mixed binary (composed of a MS star and a CO) and a single MS star dominate the first generations of BSCO encounters.
+This dominance usually continues until the first core collapse after CO formation, where the heightened densities facilitate a rise in encounters involving 2 COs.
+There is a stark difference in the ejection velocities produced by these encounters in comparison to the previous mixed binary-single MS star encounters, and the fastest ejections over the cluster's lifetime are produced in the first tens of Myr after the respective core collapse.
+This regime lasts for a few to tens of Gyr, during which the COs in the core (predominantly BHs) preferentially form CO-CO binaries, as evidenced in the drop of mixed binary-single CO encounters during this phase.
+
+For cluster models that evolve to a BH-ejection core collapse, the corresponding increase in BSCO encounters is dominated by stellar binary-single CO encounters.
+The coupling between core evolution and BSCO encounter localization appears to weaken in this phase, as the rapid increase(decrease) in core density(radius) does not translate to a similarly strong increase in escape velocity, though an increase still occurs (cf.
+Fig.
+\ref{fig:cmc_single_clusters_vesc}).
+We also find that the majority of these encounters do not involve BHs, but rather a WD (or in some cases a NS).
+These behaviors are consistent with the picture of the remaining COs migrating inwards to the core after the ejection of nearly all BHs.
+
+This general evolution varies with model parameters, as can be observed by comparing different panels of Fig. \ref{fig:cmc_single_clusters}.
+The low-mass model lacks an energetic core to sustain a larger spatial profile, and the resulting strong contraction of the core leads to an ejection of 5\% of the cluster mass via BSCO encounters in the first 100 Myr.
+This model does reach a BH-ejection core collapse by the end of the integration time, but this collapse is much less sudden that that for the base model.
+
+The bigger model evolves slower, and so it does not reach the same core collapse phase as the previous two.
+The lower densities prevent the initial dominance of mixed binary-single star encounters, as the frequency of BSCO encounters is relatively low until the initial core collapse.
+On the other hand, this first core collapse is not associated with an abundance of BSCO encounters in the high-metallicity model, which sees a roughly monotonic rise in BSCO encounters throughout its evolution.
+% Talk to Carl about interpretation of high metallicity model
+
+Figure \ref{fig:cmc_catalog} shows average histograms for cluster ejection velocities $v_{\rm out}$, present-day straight-line travel distances $d$, and masses $m$ of all stars ejected by BSCO encounters in all \CMCcat\ models, binned by model parameters $N$, $r_{\rm vir}$, and $Z$.
+The number of \CMC\ models corresponding to each parameter value varies, and so each histogram is an averaged over the respective models.
+The travel distances $d$ are the distances an object would move in a straight line between ejection and the present day, that is, the product of the ejection velocity and the time interval between the time of ejection and 14 Gyr.
+It is worth noting the prominence of the $N = 4\times10^5$, $r_{\rm vir} = 0.5$ pc, $Z = 0.0002$ models in these averaged histograms: they are the cause of the peaks above the other distributions, as the three (one for each value of $r_{\rm gc} \in \{2, 8, 20\}$ kpc) produce significantly more ejections than the other models ($\sim$2.9, 2.0, and $1.4 \times 10^4$, respectively, versus the average rate of $1-2 \times 10^3$ for the catalog).
+
+% Play with this figure placement after text is done:
+%   figure* will let it span over both columns
+%   placing the \fig commands in the same gridline will place them in the same horizontal row
 
@@
 
-Nam dui ligula, fringilla a, euismod sodales, sollici- tudin vel, wisi.
-Morbi auctor lorem non justo, nam lacus libero, pretium at, lobortis vitae.
-Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna.
-Morbi ac orci et nisl hendrerit mollis, suspendisse ut massa, cras nec ante.
-Pellentesque a nulla cum sociis natoque penatibus et magnis dis parturient.
-Aliquam tincidunt urna, nulla ullamcorper vestibulum turpis.
-Pellentesque cursus luctus mauris \citep{Luger2021}.
+Acknowledging these especially fecund models, predicable trends are visible in these histograms: increasing mass and decreasing size are both associated with higher ejection velocities and accordingly higher travel distances.
+However, while the smallest clusters produce the most ejections, the most massive clusters produce the \textit{fewest} ejections.
+The $N = 4 \times 10^5$ models consistently produce the most ejections in comparison with otherwise identical models of different population sizes, suggesting that at this mass there are not enough massive objects to prevent a severe initial core collapse through binary burning, but there are enough to facilitate a high number of BSCO encounters (the number of few-body encounters in general is also maximized in the $N = 4 \times 10^5$ models).
+
+The most noticeable distinction among models of different metallicities is the number of ejections, which decreases with increasing metallicity.
+This is understandable, as higher metallicities lead to lower-mass objects, which in turn leads to weaker few-body encounters.
+This does not have a strong effect on the mass spectrum of ejected objects above 1 $M_\odot$, but below this cutoff mass the different metallicity-binned models diverge significantly, and only in the ejections that occur before the BH-ejection core collapse of the model.
+This same phenomenon is visible in Fig. \ref{fig:cmc_single_clusters}, wherein it was previously noted that the high-metallicity model did not produce many ejections during its initial core collapse.
+The low-metallicity model is able to produce many ejections because 1) its core collapse is deeper, and 2) there are roughly $1.2 \times$ as many BHs present at core collapse, and 3) the BHs in the low-metallicity model are up to $2 \times$ as massive as those in the high-metallicity model.
+
+\subsection{Galactic population} \label{subsec:res_MW-like}
+
+We now consider the MW-like population of BSCO encounters, assembled from the \CMCcat\ models as described in section \S\ref{subsec:est_MW-like}.
+
+Figure \ref{fig:encio_stackedbar} shows the encounter types and results for BSCO encounters from a MW-like population of GCs, with the top plot including all encounters and the bottom including only those that result in an ejection.
+The majority of BSCO encounters are between a mixed binary and a star, and the bulk of the remaining encounters involve two COs.
+Interactions between COs and stellar binaries are relatively rare, and mostly occur after a secondary core collapse in which COs (esp.
+BHs) are ejected from the cluster core (c.f.
+Fig.
+\ref{fig:cmc_single_clusters}).
+
+%\begin{figure}
+%    \scripts{encio_stackebar.py}
+%    \centering
+%    \includegraphics[width=0.49\textwidth]{encio_stackedbar_catalog_wmw_dej.pdf}
+%    \caption{
+%        Results of all BSCO encounters from the MW-weighted cluster population.
+%        The x-axis shows the encounter type, the colors denote the result of the encounter, and the color saturation and hatch indicates whether the encounter ejected an object from the host cluster or not.
+%        The black percentages show what part of the encounter type bar is filled by the respective result.
+%    }
+%    \label{fig:encio_stackedbar}
+%\end{figure}
+
+Of all BSCO encounters, $\sim3\%$ eject at least one of the interacting bodies out of the host cluster.
+Most star-ejecting encounters are between a single star and a binary.
+In comparison, when a CO interacts with a binary containing at least one star, generally the star remains in the binary, and when the star is ejected from the binary it is more likely for all three objects to depart as singles with smaller velocities than for a single star to carry away enough of the encounter's energy to overcome the local escape velocity (c.f.
+\citet{1983ApJ...268..319H}).
+We conclude that the most characteristic star-ejecting BSCO encounters in the galaxy (in terms of maximum velocities and abundance) occur shortly after the formations of COs and multiple-CO systems, the latter of which we have demonstrated is strongly linked to the core collapse timescale of galactic GCs.
+
+Using our synthetic MW-like BSCO encounter population, we estimate the galactic rate of stellar ejections from GCs to be $\sim2 \times 10^4~{\rm Gyr}^{-1}$, averaged over the age of the universe.
+Most stars are ejected with velocities in the tens of kilometers per second.
+In the absence of any other forces, these velocities translate to potential wanderings of tens of kiloparsecs over 1-10 Gyr time frames.
+As the galactic escape speed is on the order of hundreds of kilometers per second [CITATION], we estimate that the destiny of most stars ejected from GCs by BSCO encounters is one of being scattering throughout the galaxy, to distances far enough away from the generating GC to appear unrelated.
+% GC formation ages?
+
+% \begin{equation}
+%     R_{GC,ej}
+%     \sim \frac{\sum_i N_{MW,i} \frac{N_{ej,i}}{10}}{13.8~{\rm Gyr}}
+%     \approx 0.02~{\rm Gyr}^{-1},
+% \end{equation}
+% where $i$ indexes over the \CMC\ models, $N_{MW,i}$ is the number of MW GCs that have the $i^{th}$ model as their nearest \CMC\ neighbor, and $N_{ej,i}$ is the number of single objects from the integrated encounters with a hyperbolic excess velocity greater than the local GC escape speed for the $i^{th}$ model (the division by 10 accounts for the multiplication of encounters described in section \ref{sec:methods}).
+
+% \subsubsection{Ejection velocities}
+%
+% Of the 148 clusters, 51 clusters have a maximum ejection velocity $v_{\rm out,max}>1000~{\rm km~s}^{-1}$, 23 clusters with $v_{\rm out,max}>1500~{\rm km~s}^{-1}$, and 3 clusters with $v_{\rm out,max}>2000~{\rm km~s}^{-1}$.
+% The fastest ejection velocity is found in the realizations of the $N=8\times10^5,\ r_{\rm vir}=0.5~{\rm pc},\ r_{\rm gc}=20~{\rm kpc}, Z=0.01~Z_\odot$ cluster, where a single $31~M_\odot$ mass BH replaces a $0.15~M_\odot$ mass star in a binary with a $69~M_\odot$ mass BH to accelerate the star to a speed of $\sim$2160~\kms.
+% This is noticeably greater than the surface escape velocity of a 69~$M_\odot$ star ($\sim$1500~\kms, assuming a radius of $R_*\approx12~R_\odot$), the theoretical limit given by the method of \citet{1991AJ....101..562L}.
+
+\section{Discussion \& Conclusions} \label{sec:disccon}
+
+%BSCO encs are ~<10% of all 3-/4-body encounters
+In this work we have studied the population of binary-single encounters involving at least one compact object and one luminous object in galactic globular clusters with synthetic methods utilizing the \CMCcat\ of star-by-star models of the same.
+Taking the object parameters and velocities for the literal BSCO encounters, we amplified the group through repeated realizations with the small-$N$-body code \fewbody\ for different encounter geometries.
+We used observational catalogs of galactic GCs to translate the collection of cluster model results into a representative population of BSCO encounters for the Milky Way.
+
+BSCO ejections were found to be closely linked to the dynamics of the cluster core, where the closest encounters among the densest stellar objects occur.
+GCs lose mass, and generally expand as they evolve; accordingly, the majority of and the fastest BSCO ejecta were produced in the early stages of the models.
+High-metallicity models had overall weaker ejection mechanisms, due to smaller stellar masses.
+
+%P on rate comparison to other mechanisms (Brown 2015)
+%P on Leonard comparison
+%P on comparison to Hill's mechanism products
+
+This work shows that dynamic binary-single interactions among stars and stellar-mass BHs are capable of producing HVSs with speeds comparable to those of HVSs produced by encounters involving SMBHs.
+
+One caveat is the estimated rate at which GCs produce HVSs.
+Among all realizations, 448 stars are ejected with $v_{\rm out}>1000~{\rm km~s}^{-1}$, meaning that a population of clusters identical to the \CMC\ models are expected to produce about 45 HVSs per 12 Gyr, equating to a rate of $\sim 4 \times 10^{-9}~{\rm yr}^{-1}$.
+The MW has 150 observed GCs (e.g.
+\citealt{2018MNRAS.478.1520B}) compared to the 148 models of the \CMCcat, so this rate is roughly representative of the galactic HVSs production rate via.
+binary-single encounters in GCs (weighting each cluster model's contribution to the rate by abundance of galactic GCs with similar parameters is one way of improving this estimate).
+Considering the HVS production rate for the galactic center of $\sim 10^{-4}~{\rm yr}^{-1}$ \citep{2015ARA&A..53...15B}, it is apparent that the binary-single process is significantly less fecund.
+This analysis does not investigate HVSs produced via binary-binary encounters, which tend to produce HVSs at higher efficiencies and with greater velocities compared to binary-single encounters \citep{1991AJ....101..562L}; a possible avenue of exploration is how these kinds of encounters contribute to the GC HVS production rate.
+
+While we find that compact objects do allow the velocity limit of \citet{1991AJ....101..562L} to be exceeded, at the moment we do not have a strong suggestion for a new limit.
+If the escape velocity definition remains, one idea is to calculate the quantity at the tidal radius of the star with respect to the most massive compact object in the encounter.
+The escape velocity at this distance is approximately 2400 \kms\ for the $m_{\rm s}\approx0.15~M_\odot$, $m_{\rm BH}\approx69~M_\odot$ pair from the \CMC\ realizations.
+In the intermediate steps of this work, an encounter similar to this one produced a HVS with a velocity of $\sim$6300~\kms; investigation into where this encounter lies with respect to the others is still underway.
+
+% Multiple stellar populations --> multiple BH/CO formation epochs?
+
+\begin{figure}[ht!]
+    \script{cmc_orbits_cdf.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/cmc_orbits_cdf_S.pdf}
+        \caption{
+            Plot showing orbit cdf.
+        }
+        \label{fig:cmc_orbits_cdf}
+    \end{centering}
+\end{figure}
 

### 2022-10-12 src/scripts/random_numbers.py

@@ -1,13 +1,0 @@
-import matplotlib.pyplot as plt
-import numpy as np
-import paths
-
-# Generate some data
-random_numbers = np.random.randn(100, 10)
-
-# Plot and save
-fig = plt.figure(figsize=(7, 6))
-plt.plot(random_numbers)
-plt.xlabel("x")
-plt.ylabel("y")
-fig.savefig(paths.figures / "random_numbers.pdf", bbox_inches="tight", dpi=300)

### 2022-10-12 src/scripts/test.py

@@ -1,0 +1,32 @@
+from astropy.coordinates import SkyCoord, ICRS, Galactic, Galactocentric
+from astropy import units as u
+
+import rustics
+import paths
+
+# Load ejections data, while only loading the column that matters
+# Column loading is problematic with unit conversions
+# Special cases for columns that are functions of the ejections columns
+path = paths.data_mwgcs / "NGC_6388" / "output_N-10_ejections.txt" 
+# Specify columns to load, and add "kf" if kgroup filtering is enabled
+usecols = ["X", "Y", "Z", "U", "V", "W"]
+# Load, and convert units
+ejdf = rustics.EjectionDf(path, usecols=usecols)
+ejdf.convert_from_fewbody()
+print(ejdf.df)
+
+# Create coordinate object; convert to ICRS
+sc_ejs = {
+    "x": ejdf.df.X * u.kpc,
+    "y": ejdf.df.Y * u.kpc,
+    "z": ejdf.df.Z * u.kpc,
+    "v_x": ejdf.df.U * u.km / u.s,
+    "v_y": ejdf.df.V * u.km / u.s,
+    "v_z": ejdf.df.W * u.km / u.s,
+}
+print(sc_ejs)
+sc_ejs = SkyCoord(frame=Galactocentric, **sc_ejs)
+sc_ejs = sc_ejs.transform_to(Galactic)
+print(sc_ejs)
+ejdf.df["vlos"] = sc_ejs.radial_velocity.value
+print(ejdf.df)

### 2022-10-13 src/scripts/cmc_orbits_cdf.py
Updated vlos calculation for Brown/Hattori cdf to consistently use line-of-sight velocity measured in Galactic frame

@@ -10,6 +10,23 @@ import paths
 
 ################################################################################
 
+# Notes on velocity definitions
+# Galactic: position from earth, velocity from galactic center
+# Galactocentric: position+velocity from galactic center
+# Brown+18:
+#   Brown+14 gives SDSS Catalog identifiers for stars
+#   v_\odot (v_helio in eq. 1?): heliocentric radial velocity
+#   v_rf: "Heliocentric radial velocity transformed to the Galactic frame"
+# Hattori+18:
+#   Gives Gaia source_ids for stars
+#   v_los: Gaia radial_velocity = "Spectroscopic radial velocity in Solar system barycentric rest frame"
+#       Reminder: "barycentric" is about CoM of system (i.e. ~CoM of Sun+earth), so ICRS is the relevant frame
+#   v_tan: Tangetial motion measured from Earth in Galactic rest frame (see eq. 1) 
+#   v_r: Galactocentric radial velocity (radial velocity from galactic center)
+#   v_total: Presumably (v_tan**2 + v_rf(v_los)**2)**0.5, where v_rf is the radial velocity transformed to the Galactic rest frame
+# This work:
+#   compare Brown v_rf with Hattori v_rf(l, b, v_los) (after Brown+18 eq.1, with additional things for barycentrism) and radial_velocity in Galactic frame in this work
+
 ################################################################################
 
 #plt.style.use(rustics.PATH_TO_MPLRC)
@@ -86,18 +103,6 @@ for ci, c in enumerate(columns):
         )
     if (c == "vout") or (c == "v_radial") or (c == "vlos"):
 
-        # Crude figure-measurement
-        ebins = np.arange(275,2000,53)
-        eweights = [0] * (len(ebins)-1)
-        eweights[0] = 10
-        eweights[1] = 4
-        eweights[2] = 6
-        eweights[3] = 2
-        eweights[4] = 3
-        eweights[5] = 1
-        eweights[6] = 0
-        eweights[7] = 2
-
         # Actually using radial velocities from Brown+18
         ebins=bins
         eweights, _ = np.histogram(
@@ -119,14 +124,105 @@ for ci, c in enumerate(columns):
 
         # And the velocities from Hattori+18
         ebins=bins
-        np.random.RandomState(123456)
-        # v_r
[…]

### 2022-10-13 src/scripts/rustics.py

@@ -16,11 +16,13 @@ import paths
 
 
 # Physical constants
+Usun_gc = np.array([11.1, 247.24, 7.25]) # From Brown+18
 
 
 # Unit conversions
 YR_TO_S = 365.2425 * 24 * 3600
 PC_TO_M = 3.0857e16
+
 
 # Number of realizations per CMC encounter
 N_REALZ = 10
@@ -720,8 +722,11 @@ class HistogramGenerator:
                 "v_z": ejdf.df.W.to_numpy() * u.km / u.s,
             }
             sc_ejs = SkyCoord(frame=Galactocentric, **sc_ejs)
-            sc_ejs = sc_ejs.transform_to(Galactic) # TODO: verify that this is the right frame
-            ejdf.df["vlos"] = sc_ejs.radial_velocity.value
+            sc_ejs = sc_ejs.transform_to(Galactic)
+            ls = sc_ejs.l.value
+            bs = sc_ejs.b.value
+            rvs = sc_ejs.radial_velocity.value
+            ejdf.df["vlos"] = rvs + Usun_gc[0] * np.cos(ls) * np.cos(bs) + Usun_gc[1] *  np.sin(ls) * np.cos(bs) + Usun_gc[2] * np.sin(bs)
 
         # If kgroup is given, filter
         if type(self.kgroup) != type(None):

### 2022-10-13 src/scripts/cmc_orbits_pdf.py
Refined v_los cdf, and added pdf.  Also made all scripts dependent on rustics.py

@@ -1,0 +1,275 @@
+import os
+
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import matplotlib.ticker as mplticker
+from matplotlib.patches import Patch
+
+import rustics
+import paths
+
+################################################################################
+
+# Notes on velocity definitions
+# Galactic: position from earth, velocity from galactic center
+# Galactocentric: position+velocity from galactic center
+# Brown+18:
+#   Brown+14 gives SDSS Catalog identifiers for stars
+#   v_\odot (v_helio in eq. 1?): heliocentric radial velocity
+#   v_rf: "Heliocentric radial velocity transformed to the Galactic frame"
+# Hattori+18:
+#   Gives Gaia source_ids for stars
+#   v_los: Gaia radial_velocity = "Spectroscopic radial velocity in Solar system barycentric rest frame"
+#       Reminder: "barycentric" is about CoM of system (i.e. ~CoM of Sun+earth), so ICRS is the relevant frame
+#   v_tan: Tangetial motion measured from Earth in Galactic rest frame (see eq. 1) 
+#   v_r: Galactocentric radial velocity (radial velocity from galactic center)
+#   v_total: Presumably (v_tan**2 + v_rf(v_los)**2)**0.5, where v_rf is the radial velocity transformed to the Galactic rest frame
+# This work:
+#   compare Brown v_rf with Hattori v_rf(l, b, v_los) (after Brown+18 eq.1, with additional things for barycentrism) and radial_velocity in Galactic frame in this work
+
+################################################################################
+
+#plt.style.use(rustics.PATH_TO_MPLRC)
+
+# Get model info
+path_to_data = paths.data_mwgcs
+df_mwgcs = pd.DataFrame(os.listdir(path_to_data), columns=["fname"]) 
+
+# Iterables
+columns = ["vlos", "mf"]
+
+# Specify kgroup
+kgroup = None
+kgroup = rustics.INFO_BSE_K_GROUPS.iloc[0]
+
+# Make subplot mosiac
+plot_size = 2.3
+fig, axd = plt.subplot_mosaic(
+    [columns],
+    figsize=(plot_size * len(columns), plot_size),
+    gridspec_kw={
+        "hspace": 0,
+    },
+)
+
+# Iterate over columns (each should have an entry in rustics.BINS)
+for ci, c in enumerate(columns):
+    print("column=%s" % c)
+
+    # Initialize hist. generator
+    bins = rustics.BINS[c]
+    if c == "mf":
[…]

### 2022-10-13 src/scripts/rustics.py

@@ -308,7 +308,7 @@ AXES_LIMS = {
     "mf": [5e-2, 55],
     "dist": [1e-3, 1e5],
     "v_radial": [-1e3, 1e3],
-    "vlos": [-1e3, 1e3],
+    "vlos": [275, 2e3],
 }
 
 
@@ -331,7 +331,7 @@ BINS = {
     "dist": np.logspace(*np.log10(AXES_LIMS["dist"]), 60),
     # "v_radial": np.linspace(*AXES_LIMS["v_radial"], 120),
     "v_radial": np.arange(*AXES_LIMS["v_radial"], 10),
-    "vlos": np.arange(*AXES_LIMS["v_radial"], 10),
+    "vlos": np.logspace(*np.log10(AXES_LIMS["vlos"]), 20),
 }
 
 # Dictionary of standard bins for CDF
@@ -342,7 +342,7 @@ BINS_CDF = {
     "dist": np.logspace(*np.log10(AXES_LIMS["dist"]), 60),
     # "v_radial": np.linspace(*AXES_LIMS["v_radial"], 120),
     "v_radial": np.linspace(275,2600,30),
-    "vlos": np.linspace(275,2600,30),
+    "vlos": np.linspace(275,1200,30),
 }
 
 # Dictionary of limits for CC plots
@@ -712,6 +712,11 @@ class HistogramGenerator:
             ejdf.df["v_radial"] = ejdf.df["vout"] * ejdf.df["proj"]
             print("%24s %g" % (model["fname"], ejdf.df["v_radial"].max()))
         elif self.column == "vlos":
+            # Throw out -1's
+            ejdf.df = ejdf.df[
+                (ejdf.df.X != -1)
+                & (ejdf.df.Y != -1)
+            ]
             # Create coordinate object; convert to ICRS
             sc_ejs = {
                 "x": ejdf.df.X.to_numpy() * u.kpc,

### 2022-10-14 src/tex/ms.tex
Refined v_los cdf, and added pdf.  Also made all scripts dependent on rustics.py
Added Spitzer reference.

@@
 After the same paper we use cluster mass $M$ and core radius to half-mass radius ratio $r_{\rm core} / r_{h,m}$ to relate \CMC\ models to MW GCs, and in this study we also include metallicity $Z$ to help distinguish otherwise similar systems.
-We use the definition of core radius from [CITATION, the Spitzer book?]:
+We use the definition of core radius from \citet{1987degc.book.....S}:
 \begin{equation}
@@
 \begin{figure}[ht!]
+    \script{cmc_orbits_pdf.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/cmc_orbits_pdf_S.pdf}
+        \caption{
+            Plot showing orbit pdf.  $v_{\rm los}$ is the radial velocity measured on earth transformed to the galactic rest frame.
+        }
+        \label{fig:cmc_orbits_pdf}
+    \end{centering}
+\end{figure}
+
+\begin{figure}[ht!]
     \script{cmc_orbits_cdf.py}

### 2022-10-18 src/scripts/gc_orbit_ejections.py
Added rgc/Z histograms/vtoday-quantile plots

@@ -1,0 +1,318 @@
+import os
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import multiprocessing as mp
+import parmap
+from tqdm import tqdm
+from galpy.orbit import Orbit
+from galpy.potential import MWPotential2014
+from astropy.coordinates import SkyCoord, Galactocentric
+from astropy import units as u
+
+import rustics
+import paths
+import mywheels.cmcutils.readoutput as ro
+import mywheels.gccatalogs.aggregate as ag
+
+###############################################################################
+
+helio_baumgardt = {
+    "galcen_distance": 8.1 * u.kpc,
+    "galcen_v_sun": np.array([11.1, 12.24 + 240, 7.25]) * u.km / u.s,
+    "z_sun": 0.0 * u.pc,
+}
+
+plt.style.use("./matplotlibrc")
+
+###############################################################################
+
+def integrate_cmc_ejections(
+    cmc_fname,
+    mwgc_catalog,
+    cmc_path=paths.data_cmc,
+    ejections_fname="output_N-10_ejections.txt",
+):
+    """! A function to parallelize the integration of encounters, s.t. the CMC data only have to be loaded once."""
+
+    print(cmc_fname)
+
+    ##############################
+    ###   Load CMC ejections   ###
+    ##############################
+    # Make path to and load CMC ejections
+    path = "/".join((cmc_path, cmc_fname, ejections_fname))
+    cmc = rustics.EjectionDf(
+        path,
+        usecols=[
+            "time",
+            "v_crit",
+            "vesc",
+            "vfin",
+            "mf",
+            "k0",
+            "k10",
+            "k11",
+            "type_f",
+            "kf",
+        ],
+    )
+    cmc.convert_from_fewbody()
+    cmc.df["vout"] = cmc.calc_vout()
+    #cmc.df = cmc.df[-100:]
+
+    ##############################
+    ###    Loop through GCs    ###
+    ##############################
+    # Preliminary things
+    # NOTE: There are three time coordiate systems:
+    #       ts: ranges from present (t=0) to beginning of universe (t=-t_int)
+    #       cmc.df.time: ranges from beginning of universe (time=0) to present (time=t_int); t_ejs is in this convention
[…]

### 2022-10-18 src/scripts/rgc-z_hists.py

@@ -1,0 +1,188 @@
+import os
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import matplotlib.ticker as mplticker
+import multiprocessing as mp
+import parmap
+
+import rustics
+import paths
+
+###############################################################################
+
+#helio_baumgardt = {
+#    "galcen_distance": 8.1 * u.kpc,
+#    "galcen_v_sun": np.array([11.1, 12.24 + 240, 7.25]) * u.km / u.s,
+#    "z_sun": 0.0 * u.pc,
+#}
+
+###############################################################################
+
+def generate_rgc_hist(
+    gc_fname,
+    path=paths.data_mwgcs,
+    bins=np.linspace(0,1e5,50),
+    ej_fname="output_N-10_ejections.txt",
+    #kgroup=None,
+    kgroup=rustics.INFO_BSE_K_GROUPS.loc[0],
+):
+    """ Function to make a single rgc histogram, for parallelization. """
+    # Define path, load ejections with relevant columns
+    path = path / gc_fname / ej_fname
+    ejdf = rustics.EjectionDf(path, usecols=["X","Y","kf"])
+    # Filter with BSE k's if specified
+    if type(kgroup) != type(None):
+        ejdf.df = ejdf.df[
+            (ejdf.df.kf >= kgroup.lo) & (ejdf.df.kf < kgroup.hi)
+        ]
+    # Throw out -1's
+    ejdf.df = ejdf.df[
+        (ejdf.df.X != -1)
+        & (ejdf.df.Y != -1)
+    ]
+    # Calculate rgc and make histogram
+    ejdf.df["rgc"] = (ejdf.df.X**2 + ejdf.df.Y**2)**0.5
+    hist, _ = np.histogram(ejdf.df.rgc, bins=bins)
+    return hist
+
+def generate_Z_hist(
+    gc_fname,
+    path=paths.data_mwgcs,
+    bins=np.linspace(0,1e5,50),
+    ej_fname="output_N-10_ejections.txt",
+    #kgroup=None,
+    kgroup=rustics.INFO_BSE_K_GROUPS.loc[0],
+):
+    """ Function to make a single rgc histogram, for parallelization. """
+    # Define path, load ejections with relevant columns
+    path = path / gc_fname / ej_fname
+    ejdf = rustics.EjectionDf(path, usecols=["Z","kf"])
[…]

### 2022-10-18 src/scripts/rgc-z_master.py

@@ -1,0 +1,97 @@
+import os
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import multiprocessing as mp
+import parmap
+from tqdm import tqdm
+from galpy.orbit import Orbit
+from galpy.potential import MWPotential2014
+from astropy.coordinates import SkyCoord, Galactocentric
+from astropy import units as u
+
+import rustics
+
+###############################################################################
+
+helio_baumgardt = {
+    "galcen_distance": 8.1 * u.kpc,
+    "galcen_v_sun": np.array([11.1, 12.24 + 240, 7.25]) * u.km / u.s,
+    "z_sun": 0.0 * u.pc,
+}
+
+plt.style.use(rustics.PATH_TO_MPLRC)
+
+###############################################################################
+
+df = pd.read_csv("/home/tomas/Documents/cmu/research/hvss/data/mwgcs/NGC_104/output_N-10_ejections.txt", index_col=0)
+df["rgc"] = (df.X**2 + df.Y**2)**0.5
+df["vtoday"] = (df.U**2 + df.V**2 + df.W**2)**0.5
+print(df.columns)
+
+# Histograms
+for p in ["Z", "rgc"]:
+    d = df[p]
+    if p == "Z":
+        bins = np.logspace(np.log10(d[d>0].min()), np.log10(d[d>0].max()), 50)
+    else:
+        bins = np.logspace(np.log10(d.min()), np.log10(d.max()), 50)
+    plt.hist(d, bins=bins, histtype="step", label=r"$%s > 0$" % p)
+    plt.hist(-1 * d, bins=bins, histtype="step", label=r"$%s < 0$" % p)
+    if p == "Z":
+        plt.xscale("symlog")
+    else:
+        plt.xscale("log")
+    plt.yscale("log")
+    plt.xlabel(r"$|%s| {\rm [kpc]}$" % p)
+    plt.ylabel(r"$N$")
+    plt.legend(title="NGC_104")
+    plt.tight_layout()
+    plt.savefig("hist_%s.pdf" % p)
+    plt.close()
+
+# Velocity quartiles
+for p in ["Z", "rgc"]:
+    dx = df[p]
+    if p == "Z":
+        bins = np.logspace(np.log10(dx[dx>0].min()), np.log10(dx[dx>0].max()), 30)
+    else:
+        bins = np.logspace(np.log10(dx.min()), np.log10(dx.max()), 20)
+    quants = [0.01, 0.1, 0.5, 0.9, 0.99][::-1]
[…]

### 2022-10-18 src/scripts/rgc-z_quants.py

@@ -1,0 +1,309 @@
+import os
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import matplotlib.ticker as mplticker
+import multiprocessing as mp
+import parmap
+
+import rustics
+import paths
+
+###############################################################################
+
+#helio_baumgardt = {
+#    "galcen_distance": 8.1 * u.kpc,
+#    "galcen_v_sun": np.array([11.1, 12.24 + 240, 7.25]) * u.km / u.s,
+#    "z_sun": 0.0 * u.pc,
+#}
+
+###############################################################################
+
+def fetch_vtodays_rgc(
+    gc_fname,
+    path=paths.data_mwgcs,
+    ej_fname="output_N-10_ejections.txt",
+    #kgroup=None,
+    kgroup=rustics.INFO_BSE_K_GROUPS.loc[0],
+):
+    """ Function to make a single rgc histogram, for parallelization. """
+    # Define path, load ejections with relevant columns
+    path = path / gc_fname / ej_fname
+    ejdf = rustics.EjectionDf(path, usecols=["X","Y","U","V","W","kf"])
+    # Filter with BSE k's if specified
+    if type(kgroup) != type(None):
+        ejdf.df = ejdf.df[
+            (ejdf.df.kf >= kgroup.lo) & (ejdf.df.kf < kgroup.hi)
+        ]
+    # Throw out -1's
+    ejdf.df = ejdf.df[
+        (ejdf.df.X != -1)
+        & (ejdf.df.Y != -1)
+    ]
+    # Calculate rgc and make histogram
+    ejdf.df["rgc"] = (ejdf.df.X**2 + ejdf.df.Y**2)**0.5
+    ejdf.df["vtoday"] = (ejdf.df.U**2 + ejdf.df.V**2 + ejdf.df.W**2)**0.5
+    return ejdf.df[["rgc", "vtoday"]] 
+
+def fetch_vtodays_Z(
+    gc_fname,
+    path=paths.data_mwgcs,
+    ej_fname="output_N-10_ejections.txt",
+    #kgroup=None,
+    kgroup=rustics.INFO_BSE_K_GROUPS.loc[0],
+):
+    """ Function to make a single rgc histogram, for parallelization. """
+    # Define path, load ejections with relevant columns
+    path = path / gc_fname / ej_fname
+    ejdf = rustics.EjectionDf(path, usecols=["Z","U","V","W","kf"])
[…]

### 2022-10-18 src/scripts/rustics.py

@@ -1,7 +1,6 @@
 # RUnaway STars In Cluster Simulations
 ###############################################################################
 
-
 import numpy as np
 import pandas as pd
 from astropy.coordinates import SkyCoord, ICRS, Galactic, Galactocentric
@@ -252,6 +251,7 @@ HEADERS_TO_LABELS = {
     "M_norm": r"$\big[\log_{10} M\big]_{\rm norm}$",
     "rc_spitzer/r_h_norm": r"$\big[r_{\rm core} / r_{h,m}\big]_{\rm norm}$",
     "[Fe/H]_norm": r"$\big[[{\rm Fe/H}]\big]_{\rm norm}$",
+    "rgc": r"$r_{\rm GC}~[{\rm kpc}]$",
 }
 
 
@@ -681,6 +681,8 @@ class HistogramGenerator:
             usecols = ["vfin", "vesc", "v_crit"]
         elif self.column == "vlos":
             usecols = ["X", "Y", "Z", "U", "V", "W"]
+        elif self.columns == "rgc":
+            usecols = ["X", "Y"]
         else:
             usecols = [self.column]
         if type(self.kgroup) != type(None):
@@ -690,6 +692,12 @@ class HistogramGenerator:
         # Load, and convert units
         ejdf = EjectionDf(path, usecols=usecols)
         ejdf.convert_from_fewbody()
+        if ("X" in ejdf.df.columns) & ("Y" in ejdf.df.columns):
+            # Throw out -1's
+            ejdf.df = ejdf.df[
+                (ejdf.df.X != -1)
+                & (ejdf.df.Y != -1)
+            ]
         # Calculate additional things if needed
         if self.column == "vout":
             ejdf.df["vout"] = ejdf.calc_vout()
@@ -712,11 +720,6 @@ class HistogramGenerator:
             ejdf.df["v_radial"] = ejdf.df["vout"] * ejdf.df["proj"]
             print("%24s %g" % (model["fname"], ejdf.df["v_radial"].max()))
         elif self.column == "vlos":
-            # Throw out -1's
-            ejdf.df = ejdf.df[
-                (ejdf.df.X != -1)
-                & (ejdf.df.Y != -1)
-            ]
             # Create coordinate object; convert to ICRS
             sc_ejs = {
                 "x": ejdf.df.X.to_numpy() * u.kpc,
@@ -732,6 +735,9 @@ class HistogramGenerator:
[…]

### 2022-10-18 src/scripts/test.py

@@ -26,7 +26,10 @@ sc_ejs = {
 }
 print(sc_ejs)
 sc_ejs = SkyCoord(frame=Galactocentric, **sc_ejs)
+print("Galactocentric:\n", sc_ejs)
+sc_ejs = sc_ejs.transform_to(ICRS)
+print("ICRS:\n", sc_ejs)
 sc_ejs = sc_ejs.transform_to(Galactic)
-print(sc_ejs)
+print("Galactic:\n", sc_ejs)
 ejdf.df["vlos"] = sc_ejs.radial_velocity.value
 print(ejdf.df)

### 2022-10-19 src/scripts/gcej_today.py
Added present-day coordinate plots

@@ -1,0 +1,179 @@
+#! For generating ra-dec and mu-mu plots of GCs and their ejecta
+###############################################################################
+
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+from astropy.coordinates import SkyCoord, Galactocentric, Galactic, ICRS
+from astropy import units as u
+from galpy.orbit import Orbit
+from galpy.potential import MWPotential2014
+
+import rustics
+import paths
+
+###############################################################################
+
+# Load GC data
+path = paths.data / "baumgardt_orbits_table_clean.txt"
+gcdf = pd.read_csv(
+    path,
+    usecols=["Cluster", "X", "Y", "Z", "U", "V", "W"],
+    index_col="Cluster",
+    delim_whitespace=True,
+)
+
+# Iterate over sample GCs
+for gc in rustics.SAMPLE_GCS:
+    # Get GC data
+    gcrow = gcdf.loc[gc]
+    scgc = SkyCoord(
+        frame=Galactocentric,
+        x=gcrow.X * u.kpc,
+        y=gcrow.Y * u.kpc,
+        z=gcrow.Z * u.kpc,
+        v_x=gcrow.U * u.km / u.s,
+        v_y=gcrow.V * u.km / u.s,
+        v_z=gcrow.W * u.km / u.s,
+    )
+    scgc = scgc.transform_to(Galactic)
+    ogc = Orbit(scgc)
+    ts = np.linspace(0,-14000,100000) * u.Myr
+    ogc.integrate(ts, MWPotential2014, method="dop853_c", progressbar=False)
+    scgc_orbit = ogc.SkyCoord(ts)
+    scgc_orbit = scgc_orbit.transform_to(Galactic)
+
+    # Get ejections data
+    ejdf = rustics.EjectionDf(
+        paths.data_mwgcs / gc / "output_N-10_ejections.txt",
+        usecols=["time", "X", "Y", "Z", "U", "V", "W"],
+    )
+    ejdf.df = ejdf.df[
+        (ejdf.df.X != -1)
+        & (ejdf.df.Y != -1)
+    ]
+
+    # Convert units
+    scej = SkyCoord(
+        frame=Galactocentric,
+        x=ejdf.df.X.to_numpy() * u.kpc,
+        y=ejdf.df.Y.to_numpy() * u.kpc,
[…]

### 2022-10-19 src/scripts/rustics.py

@@ -99,6 +99,13 @@ MODEL_NAMES_V2 = [
     "N2e5_rv0.5_rg20_Z0.002",
 ]
 
+# List of sample GCs to use for orbit, mu-mu plots
+SAMPLE_GCS = [
+    "NGC_104",
+    "NGC_5139",
+    "NGC_6205",
+    "NGC_7089",
+]
 
 # Headers for realization dataframes
 HEADERS_REALZ = [
@@ -681,7 +688,7 @@ class HistogramGenerator:
             usecols = ["vfin", "vesc", "v_crit"]
         elif self.column == "vlos":
             usecols = ["X", "Y", "Z", "U", "V", "W"]
-        elif self.columns == "rgc":
+        elif self.column == "rgc":
             usecols = ["X", "Y"]
         else:
             usecols = [self.column]
@@ -935,26 +942,144 @@ class StackedBarGenerator:
 ###############################################################################
 
 
-def collect_dat_timesteps(path, dat_file, tmin=0., tmax=14000., tnum=50, cmccat_kwargs={}, dat_kwargs={},):
-    """! Collects timesteps in specified range for all models in the catalog, from the specifed dat file.
+class GCCatalog:
+    def __init__(self, paths, pd_kwargs={}):
+        """! Basic things for now."""
 
-    @param  cmccatalog      mywheels.cmcutils.readoutput.CMCCatalog-type, i.e. a composite of the path to the catalog and the model names (parameters optional).
-    @param  dat_file        Name of the dat file to read, e.g. "initial.dyn.dat".
-                            Should be the same for all models in the catalog.
-    @param  tmin            See tnum.
-    @param  tmax            See tnum.
-    @param  tnum            Number of timesteps to include for each model.
-                            Timesteps selected are those closest to the times in np.linspace(tmin, tmax, tnum).
-                            dat_times[np.abs(np.subtract.outer(dat_times, times_to_match)).argmin(axis=0)]
-    @param  cmccat_kwargs   Dictionary of kwargs for CMCCatalog class initialization.
-    @param  dat_kwargs      Dictionary of kwargs for _dat_file class initialization.
+        # If a single path is specified, assume it is a loadable csv
+        if type(paths) == str:
+            self.df = pd.read_csv(paths, **pd_kwargs)
 
-    @return df_cat_dat      pandas df of the specified timesteps.
+        # If a list of paths is specified, assume they are baumgardt and harris catalogs 
+        elif type(paths) == list:
[…]

### 2022-10-21 src/scripts/gcej_today.py
Refined gcej_today (scatter colors)

@@ -15,13 +15,32 @@ import paths
 ###############################################################################
 
 # Load GC data
-path = paths.data / "baumgardt_orbits_table_clean.txt"
-gcdf = pd.read_csv(
-    path,
-    usecols=["Cluster", "X", "Y", "Z", "U", "V", "W"],
-    index_col="Cluster",
-    delim_whitespace=True,
+cat = rustics.GCCatalog(
+    str(paths.data / "mwgcs-cmc.dat"),
+    pd_kwargs={"index_col": "Cluster"},
 )
+cat.df.fname = [n.replace("_v2", "").replace(".tar.gz", "") for n in cat.df.fname]
+
+# Load orbital parameters
+cat_orbit = rustics.GCCatalog(
+    str(paths.data / "baumgardt_orbits_table_clean.txt"),
+    pd_kwargs={
+        "index_col": "Cluster",
+        "delim_whitespace": True,
+        "usecols": [
+            "Cluster",
+            "X",
+            "Y",
+            "Z",
+            "U",
+            "V",
+            "W",
+        ],
+    },
+)
+
+# Join the two dfs
+gcdf = cat.df.join(cat_orbit.df)
 
 # Iterate over sample GCs
 for gc in rustics.SAMPLE_GCS:
@@ -52,6 +71,8 @@ for gc in rustics.SAMPLE_GCS:
         (ejdf.df.X != -1)
         & (ejdf.df.Y != -1)
     ]
+    # Downsample by 1/10
+    ejdf.df = ejdf.df.sample(frac=0.1, random_state=int(gcrow.X * 1e3))
 
     # Convert units
     scej = SkyCoord(
@@ -68,43 +89,59 @@ for gc in rustics.SAMPLE_GCS:
     # Set up figure
     nrows = 2
     ncols = 1
-    fig = plt.figure(figsize=(3.286 * ncols, 2 * nrows))
+    fig = plt.figure(figsize=(2.5*1.618 * ncols, 2.5*1 * nrows))
     axx = fig.add_subplot(*(nrows,ncols,1), projection="aitoff")
     axx.grid(True, c="gray", alpha=0.5, zorder=0, lw=0.5)
     axv = fig.add_subplot(*(nrows,ncols,2))
+    # Color scale
+    cs = (ejdf.df.time + 14000. - gcrow.t) / 14000.
+    # kwargs for ejecta scatterpoints
+    kw_ej = {
+        "c": (ejdf.df.time + 14000. - gcrow.t) / 14000.,
[…]

### 2022-10-21 src/scripts/gc_orbit_ejections.py
Updated colors in gc_orbits to match those in gceg

@@ -170,7 +170,8 @@ def integrate_cmc_ejections(
             o_gc.x(t_ejs),
             o_gc.y(t_ejs),
             #c="k",
-            c=t_ejs,
+            c = (t_ejs.value + 14000.) / 14000.,
+            #c=t_ejs,
             s=1.,
             lw=0,
             rasterized=True,

### 2022-10-21 src/scripts/gcej_today.py

@@ -94,7 +94,6 @@ for gc in rustics.SAMPLE_GCS:
     axx.grid(True, c="gray", alpha=0.5, zorder=0, lw=0.5)
     axv = fig.add_subplot(*(nrows,ncols,2))
     # Color scale
-    cs = (ejdf.df.time + 14000. - gcrow.t) / 14000.
     # kwargs for ejecta scatterpoints
     kw_ej = {
         "c": (ejdf.df.time + 14000. - gcrow.t) / 14000.,

### 2022-10-21 src/tex/ms.tex
Added rgc/Z histograms/vtoday-quantile plots
Started editing methods-matchign section

@@
 
-In the interest of predicting realistic statistics and rates for a MW-like GC population, we assign representative \CMC\ models to each of the GCs in an aggregate observational catalog.
-The 148 models in the \CMCcat\ are specified by cluster initial size $N$ (number of stellar objects), initial virial radius $r_{\rm vir}$ (parsecs), distance from the galactic center $r_{\rm gc}$ (kiloparsecs, used in \CMC\ to calculate tidal effects from the galactic potential), and metallicity $Z$ (used to prescribe star evolution), with values chosen to span much of the MW GC parameter space; see \citet{2020IAUS..351..357K} for more details.
-After the same paper we use cluster mass $M$ and core radius to half-mass radius ratio $r_{\rm core} / r_{h,m}$ to relate \CMC\ models to MW GCs, and in this study we also include metallicity $Z$ to help distinguish otherwise similar systems.
+In the interest of predicting realistic statistics and rates for a MW-like GC population, we seek to assemble a synthetic MW-like population of GCs out of the \CMCcat.
+These 148 models are designated by cluster initial size $N$ (number of stellar objects), initial virial radius $r_{\rm vir}$ (parsecs), distance from the galactic center $r_{\rm gc}$ (kiloparsecs, used in \CMC\ to calculate tidal effects from the galactic potential), and metallicity $Z$ (used to prescribe star evolution), with values chosen to span much of the MW GC parameter space; see \citet{2020IAUS..351..357K} for more details.
+
+We predominantly use the observational catalog of \citet{2018MNRAS.478.1520B} to obtain parameters for MW GCs, though this source lacks metallicity measurements for the objects.
+Therefore we supplement this catalog with that of \citet{2010arXiv1012.3224H}, which has this information for all but 12 of the GCs in the former work; this leaves us with the 149 GCs we use in this analysis.
+
+We choose a representative \CMC\ model for each MW GC in the following manner.
+For each GC, after \citet{2021ApJ...912..102R} we first find the values of $r_{\rm gc}$ and $Z$ in the \CMCcat\ model grid closest to the measurements of these parameters for the GC (in linear and log space, respectively) and select the models with the respective values as candidate representatives.
+We choose 11 times linearly spaced between 10 and 13.5 Gyr (c.f. \citet{2013ApJ...775..134V}), and find the \CMC\ timesteps closest to the chosen times for the candidate models.
+
+The representative model is chosen by finding the model timestep closest to the GC in normalized $\log M$-$r_{\rm core} / r_{h,m}$ space by Euclidean distance.
 We use the definition of core radius from \citet{1987degc.book.....S}:
@@
 where $\sigma_c$ is the central velocity dispersion and $\rho_c$ is the central density for the cluster.
+We normalize the two dimensions in the \CMC\ space, i.e. the parameters actually used to compute the distance are
+\begin{equation}
+    x_{\rm norm} = \frac{x - \bar{x}_{\rm \CMC}}{\sigma_{\rm x, \CMC}},
+\end{equation}
+where $\bar{x}_{\rm CMC}$ and $\sigma_{\rm x,CMC}$ are respectively the mean and standard deviation of the parameter $x$ over the set of \CMC\ models.
 
-To assemble a set of MW GCs we combine the catalogs of \citet{2010arXiv1012.3224H} and \citet{2018MNRAS.478.1520B}, as the latter provides $M$ and $r_{\rm core} / r_{h,m}$ measurements and the former $Z$ measurements for the observed systems.
-We use 149 GCs from the conjunction of the two catalogs, after vetting the 15 GCs that lack a measurement for any of the three parameters of interest.
 These MW GCs and the \CMC\ models are shown in Figure \ref{fig:mw-cmc}.
@@
 
-\begin{figure}[ht!]
+\begin{figure}
     \script{cmc_orbits_pdf.py}
@@
         \caption{
-            Plot showing orbit pdf.  $v_{\rm los}$ is the radial velocity measured on earth transformed to the galactic rest frame.
+            Plot showing orbit pdf.
+            $v_{\rm los}$ is the radial velocity measured on earth transformed to the galactic rest frame.
         }
@@
 
-\begin{figure}[ht!]
+\begin{figure}
     \script{cmc_orbits_cdf.py}
@@
 
+\begin{figure}
+    \script{rgc-z_hists.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/rgc-z_hists.pdf}
+        \caption{
+            Plot showing $r_{\rm GC},\ Z$ (distance from galactic center, distance from galactic plane) histograms for galactic population.
+        }
+        \label{fig:rgc-z_hists}
+    \end{centering}
+\end{figure}
+
+\begin{figure}
+    \script{rgc-z_quants.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/rgc-z_quants.pdf}
+        \caption{
+            Plot showing $r_{\rm GC},\ Z$ quantiles for galactic population.
+        }
+        \label{fig:rgc-z_quants}
+    \end{centering}
+\end{figure}
+
+\begin{figure*}
+    \script{gc_orbit_ejections.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/gc_orbit_ejections_NGC_104.pdf}
+        \caption{
+            Plot showing GC orbits.
+        }
+        \label{fig:gc_orbit_ejections_NGC_104}
+    \end{centering}
+\end{figure*}
+
+\begin{figure*}
+    \script{gc_orbit_ejections.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/gc_orbit_ejections_NGC_5139.pdf}
+        \caption{
+            Plot showing GC orbits.
+        }
+        \label{fig:gc_orbit_ejections_NGC_5139}
+    \end{centering}
+\end{figure*}
+
+\begin{figure*}
+    \script{gc_orbit_ejections.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/gc_orbit_ejections_NGC_6205.pdf}
+        \caption{
+            Plot showing GC orbits.
+        }
+        \label{fig:gc_orbit_ejections_NGC_6205}
+    \end{centering}
+\end{figure*}
+
+\begin{figure*}
+    \script{gc_orbit_ejections.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/gc_orbit_ejections_NGC_7089.pdf}
+        \caption{
+            Plot showing GC orbits.
+        }
+        \label{fig:gc_orbit_ejections_NGC_7089}
+    \end{centering}
+\end{figure*}
+
+\begin{figure*}
+    \script{gcej_today.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/gcej_today_NGC_104.pdf}
+        \caption{
+            Plot showing present-day coords.
+        }
+        \label{fig:gcej_today_NGC_104}
+    \end{centering}
+\end{figure*}
+
+\begin{figure*}
+    \script{gcej_today.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/gcej_today_NGC_5139.pdf}
+        \caption{
+            Plot showing present-day coords.
+        }
+        \label{fig:gcej_today_NGC_5139}
+    \end{centering}
+\end{figure*}
+
+\begin{figure*}
+    \script{gcej_today.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/gcej_today_NGC_6205.pdf}
+        \caption{
+            Plot showing present-day coords.
+        }
+        \label{fig:gcej_today_NGC_6205}
+    \end{centering}
+\end{figure*}
+
+\begin{figure*}
+    \script{gcej_today.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/gcej_today_NGC_7089.pdf}
+        \caption{
+            Plot showing present-day coords.
+        }
+        \label{fig:gcej_today_NGC_7089}
+    \end{centering}
+\end{figure*}
+
 \bibliography{bib}

### 2022-10-25 src/tex/ms.tex
Added CMC/MWGC plot

@@
 
-These MW GCs and the \CMC\ models are shown in Figure \ref{fig:mw-cmc}.
+These MW GCs and the \CMC\ models are shown in Figure \ref{fig:cmcs-mwgcs_scatter}.
 The quantities for the \CMC\ models are computed from the final timesteps.
 
-%\begin{figure*}
-%    \script{mw-cmc.py}
-%    \centering
-%    \includegraphics[width=\textwidth]{figures/mw-cmc.pdf}
-%    \caption{
-%        The clusters and models used in this work.
-%        Galactic GCs are represented by black dots, and CMC models by red dots.
-%        The sample \CMC\ models used in \S\ref{subsec:single_clusters} are shown as blue stars.
-%        M3 and its \CMC\ counterpart relevant to \S\ref{} are shown as purple triangles.
-%        Cluster mass $M_{\rm cluster}$ is shown on the $y$-axis, and the core radius/half-mass radius ratio $r_{\rm core}/r_{h,m}$ (metallicity $[{\rm Fe/H}]$) on the left (right) $x$-axis.
-%        The opposing axes along the top and right of the figure display the normalized parameters $[x]_{\rm norm}$, as defined in \S\ref{subsec:est_MW-like}.
-%    }
-%    \label{fig:mw-cmc}
-%\end{figure*}
+\begin{figure}
+    \script{cmcs-mwgcs_scatter.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/cmcs-mwgcs_scatter.pdf}
+        \caption{
+        The clusters and models used in this work.
+        Galactic GCs are represented by black dots, and CMC models by red dots.
+        The sample \CMC\ models used in \S\ref{subsec:single_clusters} are shown as blue stars.
+        M3 and its \CMC\ counterpart relevant to \S\ref{} are shown as purple triangles.
+        Cluster mass $M_{\rm cluster}$ is shown on the $y$-axis, and the core radius/half-mass radius ratio $r_c/r_h$ (metallicity $[{\rm Fe/H}]$) on the left (right) $x$-axis.
+        The opposing axes along the top and right of the figure display the normalized parameters $[x]_{\rm norm}$, as defined in \S\ref{subsec:est_MW-like}.
+        }
+        \label{fig:cmcs-mwgcs_scatter}
+    \end{centering}
+\end{figure}
 
@@
 
-While the \CMCcat\ has fairly representative models for most of the MW GCs, there are a number of larger-cored GCs (right side of the left pane of Figure \ref{fig:mw-cmc}) that are relatively distant from the nearest \CMC\ model.
+While the \CMCcat\ has fairly representative models for most of the MW GCs, there are a number of larger-cored GCs (right side of the left pane of Figure \ref{fig:cmcs-mwgcs_scatter}) that are relatively distant from the nearest \CMC\ model.
 In our nearest-neighbors pairing, this means that a single \CMC\ model can be chosen to represent a disproportionate number of MW GCs.
@@
 Here we study the BSCO ejections produced by individual \CMC\ cluster models.
-\CMC\ model N8e5\_rv0.5\_rg8\_Z0.0002 is taken as a sample as it represents a typical MW GC, and models N4e5\_rv0.5\_rg8\_Z0.0002, N8e5\_rv0.5\_rg8\_Z0.0002, and N8e5\_rv2\_rg8\_Z0.02 are included to examine the effects parameter variation has on the population of ejected objects (all four of these models are represented by blue stars in Figure \ref{fig:mw-cmc}).
+\CMC\ model N8e5\_rv0.5\_rg8\_Z0.0002 is taken as a sample as it represents a typical MW GC, and models N4e5\_rv0.5\_rg8\_Z0.0002, N8e5\_rv0.5\_rg8\_Z0.0002, and N8e5\_rv2\_rg8\_Z0.02 are included to examine the effects parameter variation has on the population of ejected objects (all four of these models are represented by blue stars in Figure \ref{fig:cmcs-mwgcs_scatter}).
 For simpler reference, we name the first sample model the ``base" model, and the remaining three the ``low-mass", ``bigger", and ``high-metallicity" models, respectively.

### 2022-10-25 src/scripts/cmcs-mwgcs_scatter.py

@@ -1,0 +1,70 @@
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+
+import rustics
+import paths
+
+###############################################################################
+
+# Plot settings
+kw_mwgcs = {
+    "c": "k",
+    "s": 10,
+    "lw": 0,
+    "marker": "^",
+    "label": "MW GCs",
+}
+kw_cmcs = {
+    "c": "xkcd:azure",
+    "s": 10,
+    "lw": 0,
+    "label": r"\texttt{CMC} models",
+}
+
+# Load data
+cmcs = pd.read_csv(paths.data / "cmcs.dat")
+cmcs["R_GC"] = cmcs.rg
+mwgcs = pd.read_csv(paths.data / "mwgcs.dat")
+
+# Setup figure
+mosaic = np.array([["logM-rc/rh"], ["R_GC-[Fe/H]"]])
+fs = 2.25
+fig, axd = plt.subplot_mosaic(
+    mosaic,
+    figsize=(fs * 1.618 * mosaic.shape[1], fs * 1 * mosaic.shape[0]),
+)
+
+# Plot data
+for ai in axd:
+    ax = axd[ai]
+    y,x = ai.split("-")
+
+    # cmcs
+    ax.scatter(
+        cmcs[x],
+        cmcs[y],
+        **kw_cmcs,
+    )
+
+    # mwgcs
+    ax.scatter(
+        mwgcs[x],
+        mwgcs[y],
+        **kw_mwgcs,
+    )
+
+    # Extra things
+    ax.set_xlabel(rustics.HEADERS_TO_LABELS[x])
+    ax.set_ylabel(rustics.HEADERS_TO_LABELS[y])
+    ax.legend(
+        frameon=True,
+        shadow=False,
+        scatterpoints=1,
+        facecolor="w",
+    )
+
+# Cleanup and save
+plt.tight_layout()
+plt.savefig(paths.figures / __file__.split("/")[-1].replace(".py",".pdf"))
+plt.close()

### 2022-10-25 src/scripts/rustics.py

@@ -259,6 +259,9 @@ HEADERS_TO_LABELS = {
     "rc_spitzer/r_h_norm": r"$\big[r_{\rm core} / r_{h,m}\big]_{\rm norm}$",
     "[Fe/H]_norm": r"$\big[[{\rm Fe/H}]\big]_{\rm norm}$",
     "rgc": r"$r_{\rm GC}~[{\rm kpc}]$",
+    "R_GC": r"$r_{\rm GC}~[{\rm kpc}]$",
+    "rc/rh": r"$r_c / r_h$",
+    "logM": r"$\log(M~[M_\odot])$",
 }
 
 

### 2022-10-25 src/tex/ms.tex
Consolidated orbits into one figure; added orbit info to methods section; started writing about results for orbits

@@
 
+In the interest of predicting realistic statistics and rates for a MW-like GC population, we seek to assemble a synthetic MW-like population of GC-runaways from BSCO encounters.
+The two steps involved here are 1) selecting representative \CMC\ models for galactic GCs, and 2) integrating the post-ejection orbits to the present day.
+
+\subsubsection{Pairing \CMC\ models to MW GCs} \label{subsubsec:pairing}
 % Plot idea: the log(M) vs. rr vs. r_hm diagnostic plots in gcs_mw-cmc.ipynb, with top/bottom//left/right axes showing the physical and normalized values of each variable
 
-In the interest of predicting realistic statistics and rates for a MW-like GC population, we seek to assemble a synthetic MW-like population of GCs out of the \CMCcat.
-These 148 models are designated by cluster initial size $N$ (number of stellar objects), initial virial radius $r_{\rm vir}$ (parsecs), distance from the galactic center $r_{\rm gc}$ (kiloparsecs, used in \CMC\ to calculate tidal effects from the galactic potential), and metallicity $Z$ (used to prescribe star evolution), with values chosen to span much of the MW GC parameter space; see \citet{2020IAUS..351..357K} for more details.
+The 148 \CMC\ models are designated by cluster initial size $N$ (number of stellar objects), initial virial radius $r_{\rm vir}$ (parsecs), distance from the galactic center $r_{\rm gc}$ (kiloparsecs, used in \CMC\ to calculate tidal effects from the galactic potential), and metallicity $Z$ (used to prescribe star evolution), with values chosen to span much of the MW GC parameter space; see \citet{2020IAUS..351..357K} for more details.
 
@@
 For each GC, after \citet{2021ApJ...912..102R} we first find the values of $r_{\rm gc}$ and $Z$ in the \CMCcat\ model grid closest to the measurements of these parameters for the GC (in linear and log space, respectively) and select the models with the respective values as candidate representatives.
-We choose 11 times linearly spaced between 10 and 13.5 Gyr (c.f. \citet{2013ApJ...775..134V}), and find the \CMC\ timesteps closest to the chosen times for the candidate models.
+We choose 11 linearly spaced times between 10 and 13.5 Gyr (c.f. \citet{2013ApJ...775..134V}), and find the \CMC\ timesteps closest to the chosen times for the candidate models.
+The MW GCs and the \CMC\ models are shown in Figure \ref{fig:cmcs-mwgcs_scatter}.
 
-The representative model is chosen by finding the model timestep closest to the GC in normalized $\log M$-$r_{\rm core} / r_{h,m}$ space by Euclidean distance.
-We use the definition of core radius from \citet{1987degc.book.....S}:
+The representative model is chosen by finding the model timestep closest to the GC in normalized $\log M$-$r_c / r_h$ space by Euclidean distance.
+We use the 3D half-mass radius for $r_h$, and the definition of core radius from \citet{1987degc.book.....S}:
 \begin{equation}
-    r_{\rm core} = \sqrt{\frac{3 \sigma_c^2}{4 \pi \rho_c}},
+    r_c = \sqrt{\frac{3 \sigma_c^2}{4 \pi \rho_c}},
 \end{equation}
@@
 
-These MW GCs and the \CMC\ models are shown in Figure \ref{fig:cmcs-mwgcs_scatter}.
-The quantities for the \CMC\ models are computed from the final timesteps.
-
 \begin{figure}
@@
         The clusters and models used in this work.
-        Galactic GCs are represented by black dots, and CMC models by red dots.
-        The sample \CMC\ models used in \S\ref{subsec:single_clusters} are shown as blue stars.
-        M3 and its \CMC\ counterpart relevant to \S\ref{} are shown as purple triangles.
+        Galactic GCs are represented by black triangles, and CMC models by blue dots.
+        %The sample \CMC\ models used in \S\ref{subsec:single_clusters} are shown as blue stars.
+        %M3 and its \CMC\ counterpart relevant to \S\ref{} are shown as purple triangles.
         Cluster mass $M_{\rm cluster}$ is shown on the $y$-axis, and the core radius/half-mass radius ratio $r_c/r_h$ (metallicity $[{\rm Fe/H}]$) on the left (right) $x$-axis.
-        The opposing axes along the top and right of the figure display the normalized parameters $[x]_{\rm norm}$, as defined in \S\ref{subsec:est_MW-like}.
         }
@@
 
-We use a simple nearest neighbor algorithm to assign a representative \CMC\ model to each of the MW GCs, where the \CMC\ model with the shortest Euclidean distance to the MW GC is taken as its representative.
-Each of the three parameters $\log_{10}(M)$, $r_{\rm core} / r_{h,m}$, and $[{\rm Fe/H}]$ are more equally weighted by computing the distance in the respective standard normalized space, where each parameter is normalized by taking its $Z$-score in the context of the \CMC\ clusters:
-\begin{equation}
-    [x]_{\rm norm} = \frac{x - \bar{x}_{\rm \CMC}}{\sigma_{\rm x, \CMC}},
-\end{equation}
-where $\bar{x}_{\rm CMC}$ and $\sigma_{\rm x,CMC}$ are respectively the mean and standard deviation of the parameter $x$ over the set of \CMC\ models.
+While the \CMCcat\ has fairly representative models for most of the MW GCs, there are a number of larger-cored GCs (right side of the left pane of Figure \ref{fig:cmcs-mwgcs_scatter}) that are relatively distant from the nearest \CMC\ model; in practice, this means that a single \CMC\ model can be chosen to represent a disproportionate number of MW GCs.
+Our pairing algorithm ends up using 57 of the 148 \CMC\ models to build the sythetic population, and the most utilized model is matched to 14 MWGCs, or $\lesssim10\%$ of the population.
+Furthermore, the most used models are typical in terms of number of ejections and cluster evolution, and so the more extreme models are not expected to have an excessive effect on the sythetic population we compose.
 
-While the \CMCcat\ has fairly representative models for most of the MW GCs, there are a number of larger-cored GCs (right side of the left pane of Figure \ref{fig:cmcs-mwgcs_scatter}) that are relatively distant from the nearest \CMC\ model.
-In our nearest-neighbors pairing, this means that a single \CMC\ model can be chosen to represent a disproportionate number of MW GCs.
-In the pairing we define, 61 \CMC\ models end up being used to characterize the MW GCs, with the most used model paired to 21 GCs.
-With these disclosures, we consider our representation of the galactic population of GCs to be adequate for this analysis.
+\subsubsection{Integrating runaways to the present day} \label{subsubsec:galpy}
+
+We now produce a present-day picture of these runaways by evolving their trajectories to the present day, using \texttt{galpy}\footnote{http://github.com/jobovy/galpy} \citep{2015ApJS..216...29B} to perform the necessary integrations.
+For each MW GC, we consider the matched \CMC\ model timestep as the present-day representation of the system, and pair it with the present-day orbital position and velocity from \citet{2018MNRAS.478.1520B}.
+We integrate the orbit backwards through time, and place the ejected objects at the appropriate points in the trajectory.
+The ejection velocity $v_{\rm out}$ from the model is assigned a random direction\footnote{The generator is seeded with an integer expression of the ejection velocity for reproducability.} and boosted to the galactic rest frame, and this trajectory is evolved to the present day.
 
@@
 
+Figure \ref{fig:gc_orbit_ejections} shows the integrated orbits for a selection of GCs, and the points at which objects are ejected from the cluster.
+As was seen earlier, ejections occur much more frequently in the early stages of the cluster, and here the slower velocities at larger distances from the galactic center leads to a higher percentage of objects being ejected far away from this focus.
+
+\begin{figure*}
+    \script{gc_orbit_ejections.py}
+    \gridline{
+        \fig{figures/gc_orbit_ejections_NGC_104.pdf}{0.49\textwidth}{}
+        \fig{figures/gc_orbit_ejections_NGC_5139.pdf}{0.49\textwidth}{}
+    }
+    \gridline{
+        \fig{figures/gc_orbit_ejections_NGC_6205.pdf}{0.49\textwidth}{}
+        \fig{figures/gc_orbit_ejections_NGC_7089.pdf}{0.49\textwidth}{}
+    }
+    \caption{
+        Plots showing the back-integrated orbits for some MW GCs, and the points in the orbit where an object is ejected from the GC.
+        The color scale of the points indicates the time of ejection, measured backward from the present day; from the partial monochromism of the data and the density of points for portions of the orbit it can be seen how the ejections are more concentrated earlier in the cluster's evolution and farther away from the galactic center.
+    }
+    \label{fig:gc_orbit_ejections}
+\end{figure*}
+
+The present-day sythetic populations of runaways for the same sample CMC/GC pairings are shown in Figure \ref{fig:gcej_today}.
+While it is clear how the GC orbits influence the distribution of ejected objects, the ejecta wander to a broad enough spread that any one object loses most of the information of its cluster of origin by the present day.
+The proper motion distribution is less affected in this way (especially for more circular GC orbits), which is coherent with previous work in using these velocities to study the origins of such objects.
+What is important to note here is that the current proper motion of the cluster is not necessarily the best locus to use when comparing stellar proper motions: a well-informed back-integration of the orbit can reveal that the cluster might have spent its time in a region with a center distinct from the present-day propor motion.
+
+\begin{figure*}
+    \script{gcej_today.py}
+    \gridline{
+        \fig{figures/gcej_today_NGC_104.pdf}{0.49\textwidth}{}
+        \fig{figures/gcej_today_NGC_5139.pdf}{0.49\textwidth}{}
+    }
+    \gridline{
+        \fig{figures/gcej_today_NGC_6205.pdf}{0.49\textwidth}{}
+        \fig{figures/gcej_today_NGC_7089.pdf}{0.49\textwidth}{}
+    }
+    \caption{
+        Present-day positions (galactic longitude/latitude) and velocities (projected onto the galactic longitude/latitude directions) for the runaway objects from the sample GCs.
+        The color scale again denotes the time of ejection.
+        The back-integrated orbits are shown as the light gray trajectories, and the blue "x" is the position/velocity of the GC as measured by \citet{2018MNRAS.478.1520B}.
+    }
+    \label{fig:gcej_today}
+\end{figure*}
+
 % \begin{equation}
@@
 
-\begin{figure*}
-    \script{gc_orbit_ejections.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/gc_orbit_ejections_NGC_104.pdf}
-        \caption{
-            Plot showing GC orbits.
-        }
-        \label{fig:gc_orbit_ejections_NGC_104}
-    \end{centering}
-\end{figure*}
-
-\begin{figure*}
-    \script{gc_orbit_ejections.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/gc_orbit_ejections_NGC_5139.pdf}
-        \caption{
-            Plot showing GC orbits.
-        }
-        \label{fig:gc_orbit_ejections_NGC_5139}
-    \end{centering}
-\end{figure*}
-
-\begin{figure*}
-    \script{gc_orbit_ejections.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/gc_orbit_ejections_NGC_6205.pdf}
-        \caption{
-            Plot showing GC orbits.
-        }
-        \label{fig:gc_orbit_ejections_NGC_6205}
-    \end{centering}
-\end{figure*}
-
-\begin{figure*}
-    \script{gc_orbit_ejections.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/gc_orbit_ejections_NGC_7089.pdf}
-        \caption{
-            Plot showing GC orbits.
-        }
-        \label{fig:gc_orbit_ejections_NGC_7089}
-    \end{centering}
-\end{figure*}
-
-\begin{figure*}
-    \script{gcej_today.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/gcej_today_NGC_104.pdf}
-        \caption{
-            Plot showing present-day coords.
-        }
-        \label{fig:gcej_today_NGC_104}
-    \end{centering}
-\end{figure*}
-
-\begin{figure*}
-    \script{gcej_today.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/gcej_today_NGC_5139.pdf}
-        \caption{
-            Plot showing present-day coords.
-        }
-        \label{fig:gcej_today_NGC_5139}
-    \end{centering}
-\end{figure*}
-
-\begin{figure*}
-    \script{gcej_today.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/gcej_today_NGC_6205.pdf}
-        \caption{
-            Plot showing present-day coords.
-        }
-        \label{fig:gcej_today_NGC_6205}
-    \end{centering}
-\end{figure*}
-
-\begin{figure*}
-    \script{gcej_today.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/gcej_today_NGC_7089.pdf}
-        \caption{
-            Plot showing present-day coords.
-        }
-        \label{fig:gcej_today_NGC_7089}
-    \end{centering}
-\end{figure*}
-
 \bibliography{bib}

### 2022-10-26 src/scripts/gcej_today.py
Removed tick labels from gcej l-b plots

@@ -142,6 +142,9 @@ for gc in rustics.SAMPLE_GCS:
         scgc_orbit.b.radian,
         **kw_o,
     )
+    # Remove axes labels
+    axx.set_xticklabels([])
+    axx.set_yticklabels([])
 
     ## Plot mu_ra_cosdec-mu_dec
     #scej = scej.transform_to(ICRS)

### 2022-10-27 src/tex/ms.tex
Added rate plot, and added to maintext

@@
 % My commands
-\newcommand{\kms}{${\rm km \times s^{-1}}$}
+\newcommand{\kms}{${\rm km~s^{-1}}$}
 \newcommand{\Msun}{$M_\sun$}
@@
 
-We now consider the MW-like population of BSCO encounters, assembled from the \CMCcat\ models as described in section \S\ref{subsec:est_MW-like}.
+We now consider the MW-like population of BSCO runaways, assembled from the \CMCcat\ models as described in section \S\ref{subsec:est_MW-like}.
 
@@
 
+% Either use showyourwork \variable here,
+%   or make a new plot showing the rate as a function of time
+%   Could plot two rates on the same axes (if the scale works): one for the runaway rate, and one for the hypervelocity rate
 Using our synthetic MW-like BSCO encounter population, we estimate the galactic rate of stellar ejections from GCs to be $\sim2 \times 10^4~{\rm Gyr}^{-1}$, averaged over the age of the universe.
@@
 The proper motion distribution is less affected in this way (especially for more circular GC orbits), which is coherent with previous work in using these velocities to study the origins of such objects.
-What is important to note here is that the current proper motion of the cluster is not necessarily the best locus to use when comparing stellar proper motions: a well-informed back-integration of the orbit can reveal that the cluster might have spent its time in a region with a center distinct from the present-day propor motion.
+What is important to note here is that the current proper motion of the cluster is not necessarily the best locus to use when comparing stellar proper motions: a well-informed back-integration of the orbit can reveal the average proper motion of the cluster, which may be distiguishable from its present-day proper motion.
 
@@
         The back-integrated orbits are shown as the light gray trajectories, and the blue "x" is the position/velocity of the GC as measured by \citet{2018MNRAS.478.1520B}.
+        The set of sythetic ejecta shown here is the result of downsampling the total set by a factor of ten, to account for the repeated-realizations method described in \S\ref{subsec:binsingle_pop}
     }
@@
 \end{figure*}
+
+From a galactocentric perspective, the population of runaways is fairly isotropic in position, as can be seen in Figures \ref{fig:rgc-z_hists} and  \ref{fig:rgc-z_quants}.
+The distributions of distance from the galactic origin, and the local distributions of galactocentric velocity are similar when distributing over radius $r_{\rm gc}$ versus distance from the galactic plane $Z_{\rm gc}$.
+Most runaways end up at a distance on the order of 10 pc from the galactic center, and with a velocity on the order of 100-300~\kms.
+Few runaways make it past the $\sim$100 pc mark, but those that do naturally retain the highest velocities, reaching upwards of 1000~\kms.
+% So this indicates that hypervelocity stars are likely to come from other sources, since the fastest BSCO runaways will have had plenty of time to leave the galaxy?
+
+% Combine these plots into 2x2 grid (hists. on top, either column: r or Z)
+% Make the same plots for all ejecta w/ v_rf > 275?
+% Change the plots to be based on v_rf instead of v_esc?
+\begin{figure}
+    \script{rgc-z_hists.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/rgc-z_hists.pdf}
+        \caption{
+            Plot showing $r_{\rm GC},\ Z$ (distance from galactic center, distance from galactic plane) histograms for galactic population.
+        }
+        \label{fig:rgc-z_hists}
+    \end{centering}
+\end{figure}
+
+\begin{figure}
+    \script{rgc-z_quants.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/rgc-z_quants.pdf}
+        \caption{
+            Plot showing $r_{\rm GC},\ Z$ quantiles for galactic population.
+        }
+        \label{fig:rgc-z_quants}
+    \end{centering}
+\end{figure}
+
+One final result of note is that of the heliocentric radial velocity $v_{\rm rf}$ distribution of the synthetic population.
+\citet{2021arXiv211213864G} in part studied the galactic center origin of HVSs, and found that there is an apparent tension between the observed and predicted runaway populations; specifically, the predicted number of stars with velocities $\gtrsim 700~{\rm km~s^{-1}}$ was much higher than the observed rate from the HVS sample of \citet{2018ApJ...866...39B}.
+The same work found that a decreasing star formation rate over last millions of years would reduce the recent (and thus more likely to be observed) HVS production rate enough to overcome the discrepency.
+As noted in \S\ref{subsec:single_clusters}, the BSCO runaways studied here are produced at much higher rates when the models are young, and few HVSs are produced in the later stages of the cluster.
+The resulting $v_{\rm rf}$ distribution is much closer to the observed distribution than that for the galactic center origin case, albeit skewed towards slightly smaller velocities (Figure \ref{fig:cmc_orbits_cdf}).
+This latter difference grows when comparing to the HVS sample of \citet{2018ApJ...866..121H}, who focused on metal-poor stars, which are more akin to the objects that populate GCs.
+
+\begin{figure}
+    \script{cmc_orbits_cdf.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/cmc_orbits_cdf_S.pdf}
+        \caption{
+            Velocity distributions for our sythetic and some previous observational HVS catalogs.
+            $v_{\rm rf}$ is the heliocentric radial velocity of the star as measured in the galactic rest frame.
+        }
+        \label{fig:cmc_orbits_cdf}
+    \end{centering}
+\end{figure}
 
@@
 \begin{figure}
-    \script{cmc_orbits_cdf.py}
+    \script{mwej_rates.py}
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/cmc_orbits_cdf_S.pdf}
+        \includegraphics[width=\linewidth]{figures/mwej_rates.pdf}
         \caption{
-            Plot showing orbit cdf.
+            Plot showing ejection rates through time.
         }
-        \label{fig:cmc_orbits_cdf}
-    \end{centering}
-\end{figure}
-
-\begin{figure}
-    \script{rgc-z_hists.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/rgc-z_hists.pdf}
-        \caption{
-            Plot showing $r_{\rm GC},\ Z$ (distance from galactic center, distance from galactic plane) histograms for galactic population.
-        }
-        \label{fig:rgc-z_hists}
-    \end{centering}
-\end{figure}
-
-\begin{figure}
-    \script{rgc-z_quants.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/rgc-z_quants.pdf}
-        \caption{
-            Plot showing $r_{\rm GC},\ Z$ quantiles for galactic population.
-        }
-        \label{fig:rgc-z_quants}
+        \label{fig:mwej_rates}
     \end{centering}

### 2022-10-27 src/scripts/mwej_rates.py

@@ -1,0 +1,148 @@
+import numpy as np
+from numba import njit
+import pandas as pd
+import multiprocessing as mp
+import parmap
+import matplotlib.pyplot as plt
+
+import rustics
+import paths
+
+###############################################################################
+
+# Tested this code with and without njit, and with and without multiprocessing
+# Only ran once each so no averaging, but there's enough to see nonetheless
+# window_step = 1, window_width = 10
+#      nprocs     |   1   |   4
+# ---------------------------------
+#  time w/o @njit |  85s  |  37s
+#  time w/ @njit  |  50s  |  24s
+
+###############################################################################
+
+@njit
+def _rolling_window_count(data, window_centers, window_width):
+    """! A function to count the number of instances in a rolling window.
+    Should all be numpy to take full advantage of numba.njit.
+    Atm. automatically trims the domain s.t. only full windows are included.
+
+    @param  data                Data to count, as a 1D numpy array
+    @param  window_centers      Centers of windows
+    @param  window_width        Width of rolling window
+    """
+    # Loop through windows
+    window_counts = []
+    for wc in window_centers:
+        wmin = wc - window_width / 2.
+        wmax = wc + window_width / 2.
+        mask = (data >= wmin) & (data < wmax)
+        window_counts.append(mask.sum())
+    return window_counts
+        
+
+def calc_rolling_rate(mwrow, window_centers, window_width=10, vlim=(0.,np.inf)):
+    """! Function for parallelizing rolling rate calculation.
+
+    @param  mwrow               mwdf row for a certain GC
+    @param  vlim                Limits of velocities to include
+    @param  window_step         Step size of rolling window, in Myr
+    @param  window_width        Width of rolling window, in Myr
+    """
+
+    # Load CMC ejections
+    gcdf = pd.read_csv(
+        paths.data_mwgcs / mwrow.Cluster / "output_N-10_ejections.txt",
+        usecols=["time","U","V","W"],
+    )
+
+    # Filter -1's (post-present-day ejections)
[…]

### 2022-10-31 src/tex/ms.tex
Small edits to ms.tex

@@
 Hypervelocity stars (HVSs) are stars that have been accelerated beyond the local galactic escape speed, that is, to the point of becoming unbound from the galactic potential.
-Theorized by \citealt{1988Natur.331..687H}, the classical origin of HVSs is the dynamical disruption of a stellar binary by a super massive black hole (SMBH); this ``Hills mechanism" is believed to be capable of accelerating stars to speeds up to 4000 km s$^{-1}$.
+Theorized by \citealt{1988Natur.331..687H}, the classical origin of HVSs is the dynamical disruption of a stellar binary by a super massive black hole (SMBH); this ``Hills mechanism" is believed to be capable of accelerating stars to speeds up to 4000 km s$^{-1}$, and naturally makes HVSs potential probes of the galactic center.
 Since the first HVS discovery \citep{2005ApJ...622L..33B}, a handful of candidate objects have been identified in the Milky Way (MW) (e.g.
 \citealt{2014ApJ...787...89B}), including the object S5-HVS1, with a measured speed of $\sim$1700 km s$^{-1}$ \citep{2020MNRAS.491.2465K}.
-While S5-HVS1 is believed to have originated from the galactic center, for which there is overwhelming evidence for an SMBH (\citealt{1998ApJ...509..678G}, \citealt{2018A&A...615L..15G}, \citealt{2022ApJ...930L..12E}), data from Gaia DR2 have been used to eliminate the galactic center origin case for most former HVS candidates \citep{2018MNRAS.479.2789B}.
-Stars may also be accelerated if their binary companion goes supernova, but HVSs produced through this mechanism are generally ejected with relatively modest speeds of a few hundred km s$^{-1}$ \citep{2019A&A...624A..66R}, with exceptionally light companions potentially receiving velocities around 1000 km s$^{-1}$ \citep{2015MNRAS.448L...6T}.
+While S5-HVS1, along with several others, is well-explained by accepting an origin from the galactic center, for which there is overwhelming evidence for an SMBH (\citealt{1998ApJ...509..678G}, \citealt{2018A&A...615L..15G}, \citealt{2022ApJ...930L..12E}), recent studies have found examples of high-velocity stars that are not so easily read \citep[e.g.][]{2018MNRAS.479.2789B, 2019MNRAS.483.2007E, 2021A&A...646L...4I}.
+Two consistent results from these lines of work are that many stars previously classified as HV are nonetheless bound to the galactic potential, and many of these ``runaways" are more likely to have been ejected from the disk or a satellite as opposed to the galactic center.
+Altogether, the identification of systems of origin for HV and runaway stars is a necessary threshold problem to unlocking the full potential of observations of these objects.
 
-Another process that produces HVSs is dynamical interaction among stellar-mass objects.
-The long-term stability of binaries opens the door to 3- and 4-body encounters, which have a greater ability to accelerate stars than 2-body interactions.
-\citet{1991AJ....101..562L} studied these encounters with numerical methods, and found that the upper speed limit for products of these encounters was approximately the escape speed from the surface of the most massive star; for a sun-like star, this escape speed is $\sim$620 km s$^{-1}$, while for a 60 $M_\odot$ late main-sequence star it is $\sim$1400 km s$^{-1}$.
-However, such a velocity limit has not been examined for encounters involving compact objects such as white dwarfs (WDs), neutron stars (NSs), and black holes (BHs) whose small physical radius permits stronger encounters without collisions among objects.
+Alternate acceleration mechanisms capable of producing high-velocity stars include the binary supernova and dynamical ejection scenarios (BSS \citep{1967BOTT....4...86P} and DES \citep{1961BAN....15..265B}, respectively).
+The BSS has been predicted to accelerate stars to speeds of a few hundred \kms \citep{2019A&A...624A..66R}, with exceptionally light companions potentially receiving velocities in excess of 1000 \kms \citep{2015MNRAS.448L...6T}.
+The DES has been associated with higher speed limits: \citet{1991AJ....101..562L} studied these encounters with numerical methods, and found that the upper limit for products of these encounters was approximately the escape speed from the surface of the most massive star involved; for a sun-like star, this escape speed is $\sim$620 \kms, while for a 60 $M_\odot$ late main-sequence star it is $\sim$1400 \kms.
 
-Dynamical encounters among stellar-mass objects occur frequently in globular clusters (GCs), due to the high densities therein.
-Furthermore, the efficient formation of binary black holes (BBHs) in the cores of evolved GCs \citep{2005MNRAS.358..572I} encourages multi-body encounters among these compact objects and stars in the enclosing shell as the BBHs are themselves ejected from the core due to strong dynamical encounters.
-With around 150 GCs identified in the MW today (e.g.
-\citealt{2018MNRAS.478.1520B}), it is possible that the dynamics of these systems account for some of the HVSs that are inconsistent with the galactic center origin model.
+Globular clusters (GCs) are obvious candidate matrices for both of these events due to their high stellar densities, but the DES might be exceptionally amplified due to the combined effects of mass segregation and stellar evolution.
+This process is characterized as the migration of the most massive objects to the center of a self-gravitating system due to dynamical friction \citep{2008gady.book.....B}, which in turn leads to efficient formation of binaries in the core \citep{2005MNRAS.358..572I}.
+This central population of binaries is highly influential on the evolution of the cluster, primarily serving as a heat source as binaries form and shrink through dynamical encounters, undergoing one kind of ``core collapse" in the process \citep[e.g.][]{2007ApJ...658.1047F, 2013MNRAS.429.2881C}.
+In a realistic cluster, these dynamical phases occur after stars have started collapsing into black holes (BHs), and such objects dominate the core population \citep{2020IAUS..351..357K}.
+The resulting abundance of black hole binaries (BBHs) characterizes GCs as one of the favorable progenitors of gravitional wave sources \citep{2000ApJ...528L..17P, 2015PhRvL.115e1101R}, and in the context of this paper motivates the investigation of whether the population of GCs in the Milky Way (MW) can be considered a significant source of high-velocity stars.
 
-This work investigates the capacity of GCs to produce HVSs through dynamical encounters between binaries and single objects through numerical modeling of realistic encounter populations, building upon the existing knowledge base by performing the first direct $N$-body analysis of binary-single encounters composed of a mixture of stars and compact objects.
-The the inclusion of compact objects is expected to yield an upper speed limit distinct from that presented by \citealt{1991AJ....101..562L}.
-A realistic population of binary-single encounters from star clusters is then assembled by extracting the appropriate events from the catalog of cluster models provided by the {\tt\string Cluster Monte Carlo} (\CMC) group \citep{2020ApJS..247...48K}.
-Each encounter is multiplied over randomized spatial configurations and integrated to estimate the properties of the HVS star population generated by three-body encounters in GCs.
+This work investigates the capacity of GCs to produce HVSs through the DES, particularly in encounters between binaries and single objects, which may include compact objects (COs, a category that includes BHs, white dwarfs (WDs), and neutron stars (NSs)).
+We compose a realistic set of these binary-single compact object (BSCO) encounters by pulling initial conditions from the \CMCcat\ of MW-like GC models \citep{2020ApJS..247...48K}.
+\CMC\ is a H\'enon-style Monte Carlo code for $N$-body simulations of star clusters, and has the relevant features of stellar evolution implementation and direct integration of strong encounters between stars and stellar multiples; the referenced catalog consists of 148 models which span much of the parameter space of MW GCs.
 This analysis concludes that GCs are possible generators of HVSs in all velocity regimes thus observed, beyond the previously established limit for star-only encounters, albeit the rate at which these objects are produced from GCs is significantly lower than that for the galactic center.
@@
 
-To establish realistic binary-single encounter populations for clusters of various parameters, we take the 148 cluster models from the \CMCcat\ and extract the initial conditions of all of the binary-single encounters that involve at least one luminous object (star, WD, or NS) and one compact object.
-On average, the number of encounters satisfying these criteria per cluster model is in the mid ten thousands.
+\CMC\ records all strong encounters that required direct integration during a cluster model run.
+To establish realistic binary-single encounter populations for clusters of various parameters, we take the 148 models from the \CMCcat\ and extract the initial conditions of all strong binary-single encounters that involve at least one luminous object (star, WD, or NS) and one compact object.
+These criteria on the constituents are applied in order to ensure that each encounter has a change of producing an observable object, and to focus on the effects COs have on this population.
+Over the entire catalog, our encounter sample makes up about half of all strong encounters that occur in the models, with each model contributing a few ten thousand BSCO encounters on average.
 We then realize each encounter in isolation with the small-$N$-body code \fewbody\ \citep{2004MNRAS.352....1F}.
-We compute 10 realizations of each encounter - varying the random seed used to specify the geometry of the encounter - to obtain a better statistical representation of the binary-single encounter population.
+We compute 10 realizations of each encounter, varying the encounter angles for each realization, to obtain a better statistical representation of the binary-single encounter population.
 
@@
 where $v$ is the velocity of the object, and $U$ and $K$ are the Keplerian potential and kinetic energies of the top-level binary-single system (all of these quantities are evaluated at the termination of integration).
-The local escape velocity of the star cluster $v_{\rm esc}$ is provided by \CMC\ with the other encounter parameters; any object with $v_{\rm fin} \ge v_{\rm esc}$ is considered to escape the cluster.
+The local escape velocity of the star cluster $v_{\rm esc}$ is provided by \CMC\ with the other encounter parameters; any object with $v_{\rm fin} \ge v_{\rm esc}$ is considered to escape the cluster, suspending the possibility of subsequent encounters.
 The velocity of an ejected object once it has left the cluster is therefore
@@
 It is worth noting that the encounter initial conditions recorded in the \CMCcat\ contain velocities calculated in the center-of-mass frame of the encounter.
-A more rigorous calculation of $v_{\rm out}$ would therefore utilize the velocity dispersion $\sigma$ to determine how $v_{\rm fin}$ translates to a velocity in the reference frame of the star cluster model.
+A more rigorous calculation of $v_{\rm out}$ would utilizes the velocity dispersion $\sigma$ to determine how $v_{\rm fin}$ translates to a velocity in the reference frame of the star cluster model.
 Assuming that the distribution of the 3D object velocity $\vec{v}_{\rm fin}$ is independent of the center-of-mass velocity $\vec{v}_{\rm cm}$ of the encounter it originated from, we find that the average ratio of speed after to speed before the transformation to the cluster reference frame $v'_{\rm fin} / v_{\rm fin}$ is a maximum of $\sim$1.3 in the case $v_{\rm fin} \approx \sigma$, and a minimum of 1 in the case $v_{\rm fin} \gg \sigma$.
-As $v_{\rm cm} \sim \sigma$, and $\sigma \lesssim v_{\rm esc}$ [CITATIONS?], we estimate that neglecting a transformation to the cluster reference frame after center-of-mass encounter integration slightly reduces the resulting ejection population in a manner that does not significantly affect the following analysis.
-% Stackedbar plot of resulting encounters?
+As $v_{\rm cm} \sim \sigma$ and $\sigma \lesssim v_{\rm esc}$ [CITATIONS?], we estimate that neglecting a transformation to the cluster reference frame after center-of-mass encounter integration shrinks the resulting ejection populationoverall, but not in a manner that significantly affects the following analysis.
 
@@
 
-In this analysis, we label a cluster as core collapsed when its population of BHs has been reduced to less than 10 members.
-By this metric, 69 of the 148 \CMCcat\ models achieve core collapse by the end of the 14 Gyr integration time, and small cluster mass and spatial size are good indicators of systems that evolve to this point the fastest.
+In this analysis, we label a cluster as core collapsed when its population of BHs has been reduced to less than 10 members \citep{2020IAUS..351..357K}.
+By this metric, 69 of the 148 \CMCcat\ models achieve core collapse by the end of the 14 Gyr integration time, and small cluster mass and size are good predictors of systems that evolve to this point the fastest.
 
@@
 In the interest of predicting realistic statistics and rates for a MW-like GC population, we seek to assemble a synthetic MW-like population of GC-runaways from BSCO encounters.
-The two steps involved here are 1) selecting representative \CMC\ models for galactic GCs, and 2) integrating the post-ejection orbits to the present day.
+The two steps involved here are 1) selecting representative \CMC\ models for galactic GCs, and 2) integrating the post-ejection orbits to the present day in the context of the MW.
 
@@
 
-We predominantly use the observational catalog of \citet{2018MNRAS.478.1520B} to obtain parameters for MW GCs, though this source lacks metallicity measurements for the objects.
-Therefore we supplement this catalog with that of \citet{2010arXiv1012.3224H}, which has this information for all but 12 of the GCs in the former work; this leaves us with the 149 GCs we use in this analysis.
+We predominantly use the observational catalog of \citet{2018MNRAS.478.1520B} to obtain parameters for MW GCs.
+This catalog lacks metallicity measurements for the objects; therefore we supplement with that of \citet{2010arXiv1012.3224H}.
+12 of the GCs in the former catalog do not have metallicity measurements in the latter, leaving us with the 149 Mw GCs we use in this analysis.
 
@@
 The representative model is chosen by finding the model timestep closest to the GC in normalized $\log M$-$r_c / r_h$ space by Euclidean distance.
+We choose these parameters as in this context of GC population synthesis they are reasonable proxies for respectively the scale and evolutionary state of the cluster.
 We use the 3D half-mass radius for $r_h$, and the definition of core radius from \citet{1987degc.book.....S}:
@@
 \end{equation}
-where $\bar{x}_{\rm CMC}$ and $\sigma_{\rm x,CMC}$ are respectively the mean and standard deviation of the parameter $x$ over the set of \CMC\ models.
+where $\bar{x}_{\rm CMC}$ and $\sigma_{\rm x,CMC}$ are respectively the mean and standard deviation of the parameter $x$ over the total set of \CMC\ models.
 
@@
 Our pairing algorithm ends up using 57 of the 148 \CMC\ models to build the sythetic population, and the most utilized model is matched to 14 MWGCs, or $\lesssim10\%$ of the population.
-Furthermore, the most used models are typical in terms of number of ejections and cluster evolution, and so the more extreme models are not expected to have an excessive effect on the sythetic population we compose.
+The most used models are typical in terms of number of ejections and cluster evolution, and so while the more extreme GCs might be misrepresented, they are being represented by average models nonetheless.
 
@@
 For each MW GC, we consider the matched \CMC\ model timestep as the present-day representation of the system, and pair it with the present-day orbital position and velocity from \citet{2018MNRAS.478.1520B}.
-We integrate the orbit backwards through time, and place the ejected objects at the appropriate points in the trajectory.
-The ejection velocity $v_{\rm out}$ from the model is assigned a random direction\footnote{The generator is seeded with an integer expression of the ejection velocity for reproducability.} and boosted to the galactic rest frame, and this trajectory is evolved to the present day.
+We integrate the orbit backwards through time, and place the ejected objects at the appropriate times in the trajectory.
+The ejection velocity $v_{\rm out}$ from the model is assigned a random direction and boosted to the galactic rest frame, and this trajectory is evolved to the present day.
 
@@
 Here we study the BSCO ejections produced by individual \CMC\ cluster models.
-\CMC\ model N8e5\_rv0.5\_rg8\_Z0.0002 is taken as a sample as it represents a typical MW GC, and models N4e5\_rv0.5\_rg8\_Z0.0002, N8e5\_rv0.5\_rg8\_Z0.0002, and N8e5\_rv2\_rg8\_Z0.02 are included to examine the effects parameter variation has on the population of ejected objects (all four of these models are represented by blue stars in Figure \ref{fig:cmcs-mwgcs_scatter}).
+\CMC\ model N8e5\_rv0.5\_rg8\_Z0.0002 is taken as a sample as it represents a typical MW GC, and models N4e5\_rv0.5\_rg8\_Z0.0002, N8e5\_rv0.5\_rg8\_Z0.0002, and N8e5\_rv2\_rg8\_Z0.02 are included to examine the effects parameter variation has on the population of ejected objects.
 For simpler reference, we name the first sample model the ``base" model, and the remaining three the ``low-mass", ``bigger", and ``high-metallicity" models, respectively.
@@
 It is relevant to note a strong correlation between BSCO encounters and the evolution of the cluster core.
-Figure \ref{fig:cmc_single_clusters_vesc} plots the local escape velocities $v_{\rm esc}$ for all BSCO encounters from the sample models, along with the central density $\rho_c$ \citep{1985ApJ...298...80C}, scaled to the initial density of the model $\rho_{c,0}$.
+Figure \ref{fig:cmc_single_clusters_vesc} plots the local escape velocities $v_{\rm esc}$\footnote{$v_{\rm esc}$ here is to be considered as a proxy for the distance from the center of the cluster.} for all BSCO encounters from the sample models, along with the central density $\rho_c$ \citep{1985ApJ...298...80C}, scaled to the initial density of the model $\rho_{c,0}$.
 Within any small interval of time, the respective BSCO encounters are well-localized around a particular escape velocity, indicating that throughout the evolution of the cluster contemporary encounters are similarly localized to the same cluster radii.
-Furthermore, the variation of this ``particular escape velocity" is quite parallel to the variation of the core density of the cluster.
+Furthermore, the variation of this ``particular escape velocity" mimics the variation of the core density of the cluster.
 Naturally one would expect the densest part of a system to facilitate the highest rates of few-body encounters; in this case the dominance is extreme enough to characterize the encounter statistics as a whole.
@@
         The local escape velocities $v_{\rm esc}$ of all BSCO encounters generated from the four sample \CMC\ models (colored points), plotted alongside the central density $\rho_c$ of the model (maroon), that latter of which is divided by the initial central density of the model.
-        See Figure \ref{fig:cmc_single_clusters_vesc} for an explanation of the color scheme.
+        See Figure \ref{fig:cmc_single_clusters} for an explanation of the color scheme.
     }
@@
 a BSCO encounter in these clusters, plotted at the time of encounter since the cluster's formation $t$.
-By comparing the scatter plot to the evolution of the $N$-body core radius $r_{c, NB}$ \citep{1985ApJ...298...80C}, it is clear how the BSCO encounters and ejections are linked to the dynamical evolution of the cluster.
-Whenever a cluster undergoes a core collapse, the heightened densities lead to predictably high encounter rates.
+By comparing the scatter plot to the evolution of the $N$-body core radius $r_{c, NB}$ \citep{1985ApJ...298...80C}, it is clear how the BSCO encounters and ejections are linked to the dynamical evolution of the cluste: whenever a cluster undergoes a core collapse, the heightened densities lead to predictably high encounter rates.
 
@@
 This dominance usually continues until the first core collapse after CO formation, where the heightened densities facilitate a rise in encounters involving 2 COs.
-There is a stark difference in the ejection velocities produced by these encounters in comparison to the previous mixed binary-single MS star encounters, and the fastest ejections over the cluster's lifetime are produced in the first tens of Myr after the respective core collapse.
+There is a stark difference in the ejection velocities produced by these encounters in comparison to the previous mixed binary-single MS star encounters, and the fastest ejections over the cluster's lifetime are produced in the first tens of Myr after the associated core collapse.
 This regime lasts for a few to tens of Gyr, during which the COs in the core (predominantly BHs) preferentially form CO-CO binaries, as evidenced in the drop of mixed binary-single CO encounters during this phase.
 
-For cluster models that evolve to a BH-ejection core collapse, the corresponding increase in BSCO encounters is dominated by stellar binary-single CO encounters.
+For cluster models that evolve to a BH-ejection core collapse (in our sample, all but the large model), the corresponding increase in BSCO encounters is dominated by stellar binary-single CO encounters.
 The coupling between core evolution and BSCO encounter localization appears to weaken in this phase, as the rapid increase(decrease) in core density(radius) does not translate to a similarly strong increase in escape velocity, though an increase still occurs (cf.
@@
 \ref{fig:cmc_single_clusters_vesc}).
-We also find that the majority of these encounters do not involve BHs, but rather a WD (or in some cases a NS).
+We also find that the majority of these encounters do not involve BHs, but rather WDs (or in some cases a NSs).
 These behaviors are consistent with the picture of the remaining COs migrating inwards to the core after the ejection of nearly all BHs.
@@
 This general evolution varies with model parameters, as can be observed by comparing different panels of Fig. \ref{fig:cmc_single_clusters}.
-The low-mass model lacks an energetic core to sustain a larger spatial profile, and the resulting strong contraction of the core leads to an ejection of 5\% of the cluster mass via BSCO encounters in the first 100 Myr.
-This model does reach a BH-ejection core collapse by the end of the integration time, but this collapse is much less sudden that that for the base model.
+The low-mass model lacks a core energetic enough to sustain a larger spatial profile, and the resulting strong contraction of the core leads to an ejection of 5\% of the cluster mass via BSCO encounters in the first 100 Myr.
+This model does reach a BH-ejection core collapse by the end of the integration time, but this collapse is slower than that for the base model.
 
@@
 
-Figure \ref{fig:cmc_catalog} shows average histograms for cluster ejection velocities $v_{\rm out}$, present-day straight-line travel distances $d$, and masses $m$ of all stars ejected by BSCO encounters in all \CMCcat\ models, binned by model parameters $N$, $r_{\rm vir}$, and $Z$.
-The number of \CMC\ models corresponding to each parameter value varies, and so each histogram is an averaged over the respective models.
+Figure \ref{fig:cmc_catalog} shows histograms for cluster ejection velocities $v_{\rm out}$ and masses $m$ of all stars ejected by BSCO encounters in all \CMCcat\ models, binned by model parameters $N$, $r_{\rm vir}$, and $Z$.
+The number of \CMC\ models corresponding to each parameter value varies, and so each histogram is averaged over the respective models, in addition to being divided by the factor of 10 in encounter multiplication.
 The travel distances $d$ are the distances an object would move in a straight line between ejection and the present day, that is, the product of the ejection velocity and the time interval between the time of ejection and 14 Gyr.
-It is worth noting the prominence of the $N = 4\times10^5$, $r_{\rm vir} = 0.5$ pc, $Z = 0.0002$ models in these averaged histograms: they are the cause of the peaks above the other distributions, as the three (one for each value of $r_{\rm gc} \in \{2, 8, 20\}$ kpc) produce significantly more ejections than the other models ($\sim$2.9, 2.0, and $1.4 \times 10^4$, respectively, versus the average rate of $1-2 \times 10^3$ for the catalog).
+It is worth noting the prominence of the $N = 4\times10^5$, $r_{\rm vir} = 0.5$ pc, $Z = 0.0002$ models in these averaged histograms: they are the cause of the peaks above the other distributions, as the three (one for each value of $r_{\rm gc} \in \{2, 8, 20\}$ kpc) produce significantly more ejections than the other models ($\sim$2.9, 2.0, and $1.4 \times 10^4$, respectively, versus the average number of $1-2 \times 10^3$ for the catalog).
 
@@
 The most noticeable distinction among models of different metallicities is the number of ejections, which decreases with increasing metallicity.
-This is understandable, as higher metallicities lead to lower-mass objects, which in turn leads to weaker few-body encounters.
-This does not have a strong effect on the mass spectrum of ejected objects above 1 $M_\odot$, but below this cutoff mass the different metallicity-binned models diverge significantly, and only in the ejections that occur before the BH-ejection core collapse of the model.
+This is understandable, as higher metallicities lead to lower-mass objects, which in turn lead to weaker few-body encounters.
+This has a slight effect on the mass spectrum of ejected objects above 1 $M_\odot$, but a much stronger one for the objects below this cutoff mass.
+Tthe different metallicity-binned models diverge significantly, and only in the ejections that occur before the BH-ejection core collapse of the model.
 This same phenomenon is visible in Fig. \ref{fig:cmc_single_clusters}, wherein it was previously noted that the high-metallicity model did not produce many ejections during its initial core collapse.
-The low-metallicity model is able to produce many ejections because 1) its core collapse is deeper, and 2) there are roughly $1.2 \times$ as many BHs present at core collapse, and 3) the BHs in the low-metallicity model are up to $2 \times$ as massive as those in the high-metallicity model.
+The low-metallicity model is able to produce many ejections primarily because of the higher stellar masses, which lead to a greater population of black holes in number and average mass, enabling stronger dynamics.
+%because 1) its core collapse is deeper, and 2) there are roughly $1.2 \times$ as many BHs present at core collapse, and 3) the BHs in the low-metallicity model are up to $2 \times$ as massive as those in the high-metallicity model.
 
@@
 
-Of all BSCO encounters, $\sim3\%$ eject at least one of the interacting bodies out of the host cluster.
+Of all BSCO encounters in our synthetic MW population, $\sim3\%$ eject at least one of the interacting bodies out of the host cluster.
 Most star-ejecting encounters are between a single star and a binary.
@@
 We conclude that the most characteristic star-ejecting BSCO encounters in the galaxy (in terms of maximum velocities and abundance) occur shortly after the formations of COs and multiple-CO systems, the latter of which we have demonstrated is strongly linked to the core collapse timescale of galactic GCs.
-
-% Either use showyourwork \variable here,
-%   or make a new plot showing the rate as a function of time
-%   Could plot two rates on the same axes (if the scale works): one for the runaway rate, and one for the hypervelocity rate
-Using our synthetic MW-like BSCO encounter population, we estimate the galactic rate of stellar ejections from GCs to be $\sim2 \times 10^4~{\rm Gyr}^{-1}$, averaged over the age of the universe.
-Most stars are ejected with velocities in the tens of kilometers per second.
-In the absence of any other forces, these velocities translate to potential wanderings of tens of kiloparsecs over 1-10 Gyr time frames.
-As the galactic escape speed is on the order of hundreds of kilometers per second [CITATION], we estimate that the destiny of most stars ejected from GCs by BSCO encounters is one of being scattering throughout the galaxy, to distances far enough away from the generating GC to appear unrelated.
-% GC formation ages?
 
@@
 The present-day sythetic populations of runaways for the same sample CMC/GC pairings are shown in Figure \ref{fig:gcej_today}.
-While it is clear how the GC orbits influence the distribution of ejected objects, the ejecta wander to a broad enough spread that any one object loses most of the information of its cluster of origin by the present day.
-The proper motion distribution is less affected in this way (especially for more circular GC orbits), which is coherent with previous work in using these velocities to study the origins of such objects.
+While it is clear how the GC orbits influence the distribution of ejected objects, the ejecta wander to a broad enough spread that any one object loses some of the information of its cluster of origin by the present day.
+The proper motion distribution is less affected in this way (especially for more circular GC orbits), which is coherent with previous works that use these velocities to study the origins of such objects.
 What is important to note here is that the current proper motion of the cluster is not necessarily the best locus to use when comparing stellar proper motions: a well-informed back-integration of the orbit can reveal the average proper motion of the cluster, which may be distiguishable from its present-day proper motion.
@@
 The same work found that a decreasing star formation rate over last millions of years would reduce the recent (and thus more likely to be observed) HVS production rate enough to overcome the discrepency.
-As noted in \S\ref{subsec:single_clusters}, the BSCO runaways studied here are produced at much higher rates when the models are young, and few HVSs are produced in the later stages of the cluster.
+GCs natural follow this pattern (c.f.
+S\ref{subsec:single_clusters}), as the BSCO runaways studied here are produced at much higher rates when the models are young, and few HVSs are produced in the later stages of the cluster.
 The resulting $v_{\rm rf}$ distribution is much closer to the observed distribution than that for the galactic center origin case, albeit skewed towards slightly smaller velocities (Figure \ref{fig:cmc_orbits_cdf}).
@@
         \label{fig:cmc_orbits_cdf}
+    \end{centering}
+\end{figure}
+
+Figure \ref{fig:mwej_rates} shows the rate of HVS/runaway production for our sythetic population, along with some base values from the literature.
+In both cases, the GC ejection rate is smaller than the observed rate, especially at the present day.
+However, runaways from GCs could make up an appreciable fraction of runaways in the early universe.
+It is also of note that GCs are able to produce any HVSs at all, at velocities previously associated entirely with the galactic center.
+
+\begin{figure}
+    \script{mwej_rates.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/mwej_rates.pdf}
+        \caption{
+            The ejection rate for the synthetic MW GC population.
+            The red dashed line represents the HVS rate for the galactic center, and the blue dashed line the runaway rate for the disk proposed by \citep{2015ARA&A..53...15B}.
+        }
+        \label{fig:mwej_rates}
     \end{centering}
@@
 
-\begin{figure}
-    \script{cmc_orbits_pdf.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/cmc_orbits_pdf_S.pdf}
-        \caption{
-            Plot showing orbit pdf.
-            $v_{\rm los}$ is the radial velocity measured on earth transformed to the galactic rest frame.
-        }
-        \label{fig:cmc_orbits_pdf}
-    \end{centering}
-\end{figure}
-
-\begin{figure}
-    \script{mwej_rates.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/mwej_rates.pdf}
-        \caption{
-            Plot showing ejection rates through time.
-        }
-        \label{fig:mwej_rates}
-    \end{centering}
-\end{figure}
+%\begin{figure}
+%    \script{cmc_orbits_pdf.py}
+%    \begin{centering}
+%        \includegraphics[width=\linewidth]{figures/cmc_orbits_pdf_S.pdf}
+%        \caption{
+%            Plot showing orbit pdf.
+%            $v_{\rm los}$ is the radial velocity measured on earth transformed to the galactic rest frame.
+%        }
+%        \label{fig:cmc_orbits_pdf}
+%    \end{centering}
+%\end{figure}
 

### 2022-10-31 src/scripts/mwej_rates.py
Update after restoring P50s; should include environment.yml

@@ -144,5 +144,5 @@ ax.legend()
 
 # Make neat and save
 plt.tight_layout()
-plt.savefig(paths.figures / __file__.replace(".py", ".pdf"))
+plt.savefig(paths.figures / __file__.split("/")[-1].replace(".py", ".pdf"))
 plt.close()

### 2022-11-04 src/tex/ms.tex
Cleaned up some figures; made it easier to do star/WD plots.

@@
     \gridline{
-        \fig{figures/cmc_single_clusters_vout-N8e5-rv0.5-rg8-Z0.0002.pdf}{0.49\textwidth}{}
-        \fig{figures/cmc_single_clusters_vout-N4e5-rv0.5-rg8-Z0.0002.pdf}{0.49\textwidth}{}
+        \fig{figures/cmc_single_clusters_vout-N8e5-rv0.5-rg8-Z0.0002_S.pdf}{0.49\textwidth}{}
+        \fig{figures/cmc_single_clusters_vout-N4e5-rv0.5-rg8-Z0.0002_S.pdf}{0.49\textwidth}{}
     }
     \gridline{
-        \fig{figures/cmc_single_clusters_vout-N8e5-rv2-rg8-Z0.0002.pdf}{0.49\textwidth}{}
-        \fig{figures/cmc_single_clusters_vout-N8e5-rv0.5-rg8-Z0.02.pdf}{0.49\textwidth}{}
+        \fig{figures/cmc_single_clusters_vout-N8e5-rv2-rg8-Z0.0002_S.pdf}{0.49\textwidth}{}
+        \fig{figures/cmc_single_clusters_vout-N8e5-rv0.5-rg8-Z0.02_S.pdf}{0.49\textwidth}{}
     }
@@
 
-From a galactocentric perspective, the population of runaways is fairly isotropic in position, as can be seen in Figures \ref{fig:rgc-z_hists} and  \ref{fig:rgc-z_quants}.
+From a galactocentric perspective, the population of runaways is fairly isotropic in position, as can be seen in Figure \ref{fig:rgc-z}.
 The distributions of distance from the galactic origin, and the local distributions of galactocentric velocity are similar when distributing over radius $r_{\rm gc}$ versus distance from the galactic plane $Z_{\rm gc}$.
@@
 % Change the plots to be based on v_rf instead of v_esc?
-\begin{figure}
-    \script{rgc-z_hists.py}
+\begin{figure*}
+    \script{rgc-z.py}
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/rgc-z_hists.pdf}
+        \includegraphics[width=\linewidth]{figures/rgc-z_S.pdf}
         \caption{
@@
     \end{centering}
-\end{figure}
-
-\begin{figure}
-    \script{rgc-z_quants.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/rgc-z_quants.pdf}
-        \caption{
-            Plot showing $r_{\rm GC},\ Z$ quantiles for galactic population.
-        }
-        \label{fig:rgc-z_quants}
-    \end{centering}
-\end{figure}
+\end{figure*}
 

### 2022-11-04 src/scripts/cmc_catalog_3x3.py

@@ -1,3 +1,5 @@
+# Backup of old cmc_catalog, where the three parameters were v_out, d, and m (new 2x3 throws out d)
+###############################################################################
 import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
@@ -15,25 +17,26 @@ import paths
 df_models = rustics.DF_MODELS
 
 # Iterables
-columns = ["vout", "mf"]
+columns = ["vout", "dist", "mf"]
 params = ["N", "rv", "Z"]
 
 # Specify kgroup
 kgroup = None
-kgroup = rustics.INFO_BSE_K_GROUPS.iloc[0]
+kgroup = rustics.INFO_BSE_K_GROUPS.iloc[1]
 
 # Toggle weighting by MW GCs
 weight_mw = False
 
 # Make subplot mosiac
 plot_size = 2.3
-mosaic = [["_".join((p, c)) for p in params] for c in columns]
+mosaic = [["_".join((p, c)) for c in columns] for p in params]
 fig, axd = plt.subplot_mosaic(
     mosaic,
     sharey=True,
-    figsize=(plot_size * len(params), plot_size * len(columns)),
+    figsize=(plot_size * len(columns), plot_size * len(params)),
     gridspec_kw={
         "wspace": 0,
+        "hspace": 0,
     },
 )
 
@@ -115,18 +118,22 @@ for ci, c in enumerate(columns):
         ax.xaxis.set_minor_formatter(mplticker.NullFormatter())
 
         # Adjust x-axis labels and ticks; add legend to top row
-        ax.set_xlabel(rustics.HEADERS_TO_LABELS[c])
+        if p == params[0]:
+            ax.tick_params(labeltop=True)
+        elif p == params[-1]:
+            ax.set_xlabel(rustics.HEADERS_TO_LABELS[c])
+        else:
+            ax.set_xticklabels([])
+
+        # Adjust y-axis labels and ticks
         if c == columns[0]:
+            ax.set_ylabel(r"Counts/$N_{\rm models}$")
             ax.legend(
                 title=rustics.HEADERS_TO_LABELS[p],
                 loc=rustics.LOC_LEGEND[c],
                 frameon=False,
             )
-
-        # Adjust y-axis labels and ticks
-        if p == params[0]:
-            ax.set_ylabel(r"Counts/$N_{\rm models}$")
-        elif p == params[-1]:
+        elif c == columns[-1]:
             ax.tick_params(labelright=True)
         else:
             ax.set_yticklabels([])

### 2022-11-04 src/scripts/cmc_single_clusters.py

@@ -234,7 +234,8 @@ for ci, cmc_cluster in enumerate(cmc_cluster_list):
     # hvss_utils.grid_selfmade(axd["scatter"])
     Nstr, rvstr, rgstr, Zstr = cmc_cluster.split("_")
     lstr = "-".join((y, Nstr, rvstr, rgstr, Zstr))
-    plt.savefig(paths.figures / lstr.join(("cmc_single_clusters_", ".pdf")))
+    #plt.savefig(paths.figures / lstr.join(("cmc_single_clusters_", ".pdf")))
+    plt.savefig(paths.figures / lstr.join(("cmc_single_clusters_", "_%s.pdf" % kgroup["initials"])))
     #    "/".join(
     #        (
     #            paths.figures,

### 2022-11-04 src/scripts/rgc-z.py

@@ -1,0 +1,251 @@
+import os
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import matplotlib.ticker as mplticker
+import matplotlib.scale as mplscale
+import multiprocessing as mp
+import parmap
+
+import rustics
+import paths
+
+###############################################################################
+
+#helio_baumgardt = {
+#    "galcen_distance": 8.1 * u.kpc,
+#    "galcen_v_sun": np.array([11.1, 12.24 + 240, 7.25]) * u.km / u.s,
+#    "z_sun": 0.0 * u.pc,
+#}
+
+###############################################################################
+
+def fetch_rgc_Zgc_vtodays(
+    gc_fname,
+    path=paths.data_mwgcs,
+    ej_fname="output_N-10_ejections.txt",
+    kgroup=None,
+):
+    """ Function to make a single rgc histogram, for parallelization. """
+    # Define path, load ejections with relevant columns
+    path = path / gc_fname / ej_fname
+    ejdf = rustics.EjectionDf(path, usecols=["X","Y","Z","U","V","W","kf"])
+    # Filter with BSE k's if specified
+    if type(kgroup) != type(None):
+        ejdf.df = ejdf.df[
+            (ejdf.df.kf >= kgroup.lo) & (ejdf.df.kf < kgroup.hi)
+        ]
+    # Throw out -1's (after present day)
+    ejdf.df = ejdf.df[
+        (ejdf.df.X != -1)
+        & (ejdf.df.Y != -1)
+    ]
+    # Calculate rgcs and vtodays; rename Z to Zgc to avoid overlap with metallicity settings
+    ejdf.df["rgc"] = (ejdf.df.X**2 + ejdf.df.Y**2)**0.5
+    ejdf.df["vtoday"] = (ejdf.df.U**2 + ejdf.df.V**2 + ejdf.df.W**2)**0.5
+    ejdf.df.rename(columns={"Z": "Zgc"}, inplace=True)
+    return ejdf.df[["rgc", "Zgc", "vtoday"]]
+
+def add_minor_labels(axis):
+    """ Utility to add minor labels to axis."""
+    lim = axis.get_view_interval()
+    if lim[0] > 0:
+        numticks = np.ceil(np.log10(lim[1] / lim[0])) + 2
+        locmin = mplticker.LogLocator(
+            base=10, subs=np.arange(0, 1, 0.1), numticks=numticks
+        )
+    else:
[…]

### 2022-11-04 src/scripts/rgc-z_hists.py

@@ -24,8 +24,7 @@ def generate_rgc_hist(
     path=paths.data_mwgcs,
     bins=np.linspace(0,1e5,50),
     ej_fname="output_N-10_ejections.txt",
-    #kgroup=None,
-    kgroup=rustics.INFO_BSE_K_GROUPS.loc[0],
+    kgroup=None,
 ):
     """ Function to make a single rgc histogram, for parallelization. """
     # Define path, load ejections with relevant columns
@@ -51,8 +50,7 @@ def generate_Z_hist(
     path=paths.data_mwgcs,
     bins=np.linspace(0,1e5,50),
     ej_fname="output_N-10_ejections.txt",
-    #kgroup=None,
-    kgroup=rustics.INFO_BSE_K_GROUPS.loc[0],
+    kgroup=None,
 ):
     """ Function to make a single rgc histogram, for parallelization. """
     # Define path, load ejections with relevant columns
@@ -111,16 +109,20 @@ bins = np.logspace(-3, 4, 50)
 ax = axd["rgc"]
 
 # Read data + generate histograms
+kw_function = {
+    "bins": bins,
+    "kgroup": rustics.INFO_BSE_K_GROUPS.loc[1],
+}
 if nprocs == 1:
     # Don't run in parallel
     hists = parmap.map(
-        generate_rgc_hist, model_fnames, bins=bins, pm_parallel=False, pm_pbar=True,
+        generate_rgc_hist, model_fnames, **kw_function, m_parallel=False, pm_pbar=True,
     )
 else:
     # Run in parallel
     pool = mp.Pool(nprocs)
     hists = parmap.map(
-        generate_rgc_hist, model_fnames, bins=bins, pm_parallel=True, pm_pbar=True,
+        generate_rgc_hist, model_fnames, **kw_function, pm_parallel=True, pm_pbar=True,
     )
 hists = np.array(hists)
 
@@ -145,21 +147,21 @@ add_minor_labels(ax.xaxis)
 ##############################
 
 # Set bins, axes
-bins = np.logspace(-3, 4, 50)
 bins = np.array([-1 * bins[::-1], bins]).flatten()
 ax = axd["Z"]
 
 # Read data + generate histograms
+kw_function["bins"] = bins
 if nprocs == 1:
     # Don't run in parallel
     hists = parmap.map(
-        generate_Z_hist, model_fnames, bins=bins, pm_parallel=False, pm_pbar=True,
[…]

### 2022-11-04 src/scripts/rgc-z_quants.py

@@ -23,8 +23,7 @@ def fetch_vtodays_rgc(
     gc_fname,
     path=paths.data_mwgcs,
     ej_fname="output_N-10_ejections.txt",
-    #kgroup=None,
-    kgroup=rustics.INFO_BSE_K_GROUPS.loc[0],
+    kgroup=None,
 ):
     """ Function to make a single rgc histogram, for parallelization. """
     # Define path, load ejections with relevant columns
@@ -49,8 +48,7 @@ def fetch_vtodays_Z(
     gc_fname,
     path=paths.data_mwgcs,
     ej_fname="output_N-10_ejections.txt",
-    #kgroup=None,
-    kgroup=rustics.INFO_BSE_K_GROUPS.loc[0],
+    kgroup=None,
 ):
     """ Function to make a single rgc histogram, for parallelization. """
     # Define path, load ejections with relevant columns
@@ -100,6 +98,9 @@ icolors = dict(zip(intervals, ["xkcd:azure", "xkcd:azure"]))
 quantiles = [0.5]
 for i in intervals:
     quantiles += [(1-i)/2, (1+i)/2]
+kw_function = {
+    "kgroup": rustics.INFO_BSE_K_GROUPS.loc[1],
+}
 
 # Setup figure
 fig, axd = plt.subplot_mosaic(
@@ -119,13 +120,13 @@ ax = axd["rgc"]
 if nprocs == 1:
     # Don't run in parallel
     data = parmap.map(
-        fetch_vtodays_rgc, model_fnames, pm_parallel=False, pm_pbar=True,
+        fetch_vtodays_rgc, model_fnames, **kw_function, pm_parallel=False, pm_pbar=True,
     )
 else:
     # Run in parallel
     pool = mp.Pool(nprocs)
     data = parmap.map(
-        fetch_vtodays_rgc, model_fnames, pm_parallel=True, pm_pbar=True,
+        fetch_vtodays_rgc, model_fnames, **kw_function, pm_parallel=True, pm_pbar=True,
     )
 data = pd.concat(data, ignore_index=True)
 
@@ -216,13 +217,13 @@ ax = axd["Z"]
 if nprocs == 1:
     # Don't run in parallel
     data = parmap.map(
-        fetch_vtodays_Z, model_fnames, pm_parallel=False, pm_pbar=True,
+        fetch_vtodays_Z, model_fnames, **kw_function, pm_parallel=False, pm_pbar=True,
     )
 else:
[…]

### 2022-11-04 src/scripts/rustics.py

@@ -258,10 +258,12 @@ HEADERS_TO_LABELS = {
     "M_norm": r"$\big[\log_{10} M\big]_{\rm norm}$",
     "rc_spitzer/r_h_norm": r"$\big[r_{\rm core} / r_{h,m}\big]_{\rm norm}$",
     "[Fe/H]_norm": r"$\big[[{\rm Fe/H}]\big]_{\rm norm}$",
-    "rgc": r"$r_{\rm GC}~[{\rm kpc}]$",
-    "R_GC": r"$r_{\rm GC}~[{\rm kpc}]$",
+    "rgc": r"$r_{\rm gc}~[{\rm kpc}]$",
+    "Zgc": r"$Z~[{\rm kpc}]$",
+    "R_GC": r"$r_{\rm gc}~[{\rm kpc}]$",
     "rc/rh": r"$r_c / r_h$",
     "logM": r"$\log(M~[M_\odot])$",
+    "vtoday": r"$v_{\rm today} [{\rm km~s}^{-1}]$",
 }
 
 

### 2022-11-04 src/tex/ms.tex
Updated Conclusion

@@
         \caption{
-            Plot showing $r_{\rm GC},\ Z$ (distance from galactic center, distance from galactic plane) histograms for galactic population.
+            Histograms and velocity quantiles for the synthetic ejecta.
+            The left (right) plots show the profile over radial distance from the galactic center $r_{\rm gc}$ (distance from the galactic plane $Z$).
+            The quantiles in the lower plots are calculated from the present-day velocities of our population.
         }
-        \label{fig:rgc-z_hists}
+        \label{fig:rgc-z}
     \end{centering}
@@
 
-%BSCO encs are ~<10% of all 3-/4-body encounters
-In this work we have studied the population of binary-single encounters involving at least one compact object and one luminous object in galactic globular clusters with synthetic methods utilizing the \CMCcat\ of star-by-star models of the same.
-Taking the object parameters and velocities for the literal BSCO encounters, we amplified the group through repeated realizations with the small-$N$-body code \fewbody\ for different encounter geometries.
-We used observational catalogs of galactic GCs to translate the collection of cluster model results into a representative population of BSCO encounters for the Milky Way.
+In this work we have studied fewbody encounters in GCs as means of producing stellar runaways.
+We composed a synthetic MW-like population of ejecta by matching observed GCs to realistic $N$-body models of these systems and embedding the models in the orbits of their real counterparts.
+In particular we considered binary-single encounters involving at least one compact object; this selection retained about half of all fewbody encounters in the catalog of models.
 
@@
 GCs lose mass, and generally expand as they evolve; accordingly, the majority of and the fastest BSCO ejecta were produced in the early stages of the models.
-High-metallicity models had overall weaker ejection mechanisms, due to smaller stellar masses.
+High-metallicity models had overall weaker ejection mechanisms (in frequency and maximum velocity), due to smaller stellar masses.
+BSCO encounters occurring in realistic GCs are capable of accelerating stars to velocities in excess of 2000 \kms, which means that this source of runaways cannot be entirely ruled out by a simple velocity cut.
+We also note that these velocities appear to pass the speed limit on star-only fewbody encounters set by \citet{1991AJ....101..562L}; further study is needed to confirm if this is cause by the inclusion of compact objects or another factor.
 
-%P on rate comparison to other mechanisms (Brown 2015)
-%P on Leonard comparison
-%P on comparison to Hill's mechanism products
+While ejected objects evolve to be largly indistinguishable from other MW stars in terms of position, they were found capable of retaining some information about the motion of their GC of origin, particularly in the case of GCs with near-circular orbits.
+The overall population of ejecta was usually concentrated around the average proper motion of the GC throughout its orbit.
+It is important to realize that the present-day proper motion of a GC may not reflect this average proper motion, and that in general a better kinematic picture is possible if the orbit is back-integrated.
 
-This work shows that dynamic binary-single interactions among stars and stellar-mass BHs are capable of producing HVSs with speeds comparable to those of HVSs produced by encounters involving SMBHs.
-
-One caveat is the estimated rate at which GCs produce HVSs.
-Among all realizations, 448 stars are ejected with $v_{\rm out}>1000~{\rm km~s}^{-1}$, meaning that a population of clusters identical to the \CMC\ models are expected to produce about 45 HVSs per 12 Gyr, equating to a rate of $\sim 4 \times 10^{-9}~{\rm yr}^{-1}$.
-The MW has 150 observed GCs (e.g.
-\citealt{2018MNRAS.478.1520B}) compared to the 148 models of the \CMCcat, so this rate is roughly representative of the galactic HVSs production rate via.
-binary-single encounters in GCs (weighting each cluster model's contribution to the rate by abundance of galactic GCs with similar parameters is one way of improving this estimate).
-Considering the HVS production rate for the galactic center of $\sim 10^{-4}~{\rm yr}^{-1}$ \citep{2015ARA&A..53...15B}, it is apparent that the binary-single process is significantly less fecund.
-This analysis does not investigate HVSs produced via binary-binary encounters, which tend to produce HVSs at higher efficiencies and with greater velocities compared to binary-single encounters \citep{1991AJ....101..562L}; a possible avenue of exploration is how these kinds of encounters contribute to the GC HVS production rate.
-
-While we find that compact objects do allow the velocity limit of \citet{1991AJ....101..562L} to be exceeded, at the moment we do not have a strong suggestion for a new limit.
-If the escape velocity definition remains, one idea is to calculate the quantity at the tidal radius of the star with respect to the most massive compact object in the encounter.
-The escape velocity at this distance is approximately 2400 \kms\ for the $m_{\rm s}\approx0.15~M_\odot$, $m_{\rm BH}\approx69~M_\odot$ pair from the \CMC\ realizations.
-In the intermediate steps of this work, an encounter similar to this one produced a HVS with a velocity of $\sim$6300~\kms; investigation into where this encounter lies with respect to the others is still underway.
-
-% Multiple stellar populations --> multiple BH/CO formation epochs?
-
-%\begin{figure}
-%    \script{cmc_orbits_pdf.py}
-%    \begin{centering}
-%        \includegraphics[width=\linewidth]{figures/cmc_orbits_pdf_S.pdf}
-%        \caption{
-%            Plot showing orbit pdf.
-%            $v_{\rm los}$ is the radial velocity measured on earth transformed to the galactic rest frame.
-%        }
-%        \label{fig:cmc_orbits_pdf}
-%    \end{centering}
-%\end{figure}
+In the galactic context, the velocity distribution of the synthetic ejecta was found to be similar to that of HVS observations at relatively low velocities; specifically, out population was skewed towards these velocities with respect to observations.
+With galactic-center origin studies finding distributions skewed towards higher velocities in the same respect, it is possible that a mixture of the two could be used to more accurately model the real population of these objects.
+Such a calculation must be done in light of the relative rates of the two mechanisms: our study concludes that the GC BSCO runaway rate might have been a few 10\% of the overall rate in the first few Gyr of the universe, but today is no more than 10\%.
 

### 2022-11-04 src/scripts/rgc-z.py

@@ -73,7 +73,7 @@ def add_minor_labels(axis):
 nprocs=4
 model_fnames = os.listdir(paths.data_mwgcs)
 # Set bins, Zgc by reflecting rgc across 0
-bins = {"rgc": np.logspace(-3, 4, 50)}
+bins = {"rgc": np.logspace(-3, 4.6, 50)}
 bins["Zgc"] = np.array([-1 * bins["rgc"][::-1], bins["rgc"]]).flatten()
 
 # Load data
@@ -229,6 +229,7 @@ for p in params:
     axh = axd["%s-hist" % p]
     ax.set_xlim(axh.get_xlim())
     if p == "rgc":
+        ax.legend(loc="upper left")
         ax.set_xscale(axh.get_xscale())
         axrgc = ax
     elif p == "Zgc":

### 2022-11-04 src/scripts/rgc-z_hists.py

@@ -1,190 +1,0 @@
-import os
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as plt
-import matplotlib.ticker as mplticker
-import multiprocessing as mp
-import parmap
-
-import rustics
-import paths
-
-###############################################################################
-
-#helio_baumgardt = {
-#    "galcen_distance": 8.1 * u.kpc,
-#    "galcen_v_sun": np.array([11.1, 12.24 + 240, 7.25]) * u.km / u.s,
-#    "z_sun": 0.0 * u.pc,
-#}
-
-###############################################################################
-
-def generate_rgc_hist(
-    gc_fname,
-    path=paths.data_mwgcs,
-    bins=np.linspace(0,1e5,50),
-    ej_fname="output_N-10_ejections.txt",
-    kgroup=None,
-):
-    """ Function to make a single rgc histogram, for parallelization. """
-    # Define path, load ejections with relevant columns
-    path = path / gc_fname / ej_fname
-    ejdf = rustics.EjectionDf(path, usecols=["X","Y","kf"])
-    # Filter with BSE k's if specified
-    if type(kgroup) != type(None):
-        ejdf.df = ejdf.df[
-            (ejdf.df.kf >= kgroup.lo) & (ejdf.df.kf < kgroup.hi)
-        ]
-    # Throw out -1's
-    ejdf.df = ejdf.df[
-        (ejdf.df.X != -1)
-        & (ejdf.df.Y != -1)
-    ]
-    # Calculate rgc and make histogram
-    ejdf.df["rgc"] = (ejdf.df.X**2 + ejdf.df.Y**2)**0.5
-    hist, _ = np.histogram(ejdf.df.rgc, bins=bins)
-    return hist
-
-def generate_Z_hist(
-    gc_fname,
-    path=paths.data_mwgcs,
-    bins=np.linspace(0,1e5,50),
-    ej_fname="output_N-10_ejections.txt",
-    kgroup=None,
-):
-    """ Function to make a single rgc histogram, for parallelization. """
-    # Define path, load ejections with relevant columns
-    path = path / gc_fname / ej_fname
-    ejdf = rustics.EjectionDf(path, usecols=["Z","kf"])
-    # Filter with BSE k's if specified
-    if type(kgroup) != type(None):
-        ejdf.df = ejdf.df[
[…]

### 2022-11-04 src/scripts/rgc-z_master.py

@@ -1,97 +1,0 @@
-import os
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as plt
-import multiprocessing as mp
-import parmap
-from tqdm import tqdm
-from galpy.orbit import Orbit
-from galpy.potential import MWPotential2014
-from astropy.coordinates import SkyCoord, Galactocentric
-from astropy import units as u
-
-import rustics
-
-###############################################################################
-
-helio_baumgardt = {
-    "galcen_distance": 8.1 * u.kpc,
-    "galcen_v_sun": np.array([11.1, 12.24 + 240, 7.25]) * u.km / u.s,
-    "z_sun": 0.0 * u.pc,
-}
-
-plt.style.use(rustics.PATH_TO_MPLRC)
-
-###############################################################################
-
-df = pd.read_csv("/home/tomas/Documents/cmu/research/hvss/data/mwgcs/NGC_104/output_N-10_ejections.txt", index_col=0)
-df["rgc"] = (df.X**2 + df.Y**2)**0.5
-df["vtoday"] = (df.U**2 + df.V**2 + df.W**2)**0.5
-print(df.columns)
-
-# Histograms
-for p in ["Z", "rgc"]:
-    d = df[p]
-    if p == "Z":
-        bins = np.logspace(np.log10(d[d>0].min()), np.log10(d[d>0].max()), 50)
-    else:
-        bins = np.logspace(np.log10(d.min()), np.log10(d.max()), 50)
-    plt.hist(d, bins=bins, histtype="step", label=r"$%s > 0$" % p)
-    plt.hist(-1 * d, bins=bins, histtype="step", label=r"$%s < 0$" % p)
-    if p == "Z":
-        plt.xscale("symlog")
-    else:
-        plt.xscale("log")
-    plt.yscale("log")
-    plt.xlabel(r"$|%s| {\rm [kpc]}$" % p)
-    plt.ylabel(r"$N$")
-    plt.legend(title="NGC_104")
-    plt.tight_layout()
-    plt.savefig("hist_%s.pdf" % p)
-    plt.close()
-
-# Velocity quartiles
-for p in ["Z", "rgc"]:
-    dx = df[p]
-    if p == "Z":
-        bins = np.logspace(np.log10(dx[dx>0].min()), np.log10(dx[dx>0].max()), 30)
-    else:
-        bins = np.logspace(np.log10(dx.min()), np.log10(dx.max()), 20)
-    quants = [0.01, 0.1, 0.5, 0.9, 0.99][::-1]
[…]

### 2022-11-04 src/scripts/rgc-z_quants.py

@@ -1,310 +1,0 @@
-import os
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as plt
-import matplotlib.ticker as mplticker
-import multiprocessing as mp
-import parmap
-
-import rustics
-import paths
-
-###############################################################################
-
-#helio_baumgardt = {
-#    "galcen_distance": 8.1 * u.kpc,
-#    "galcen_v_sun": np.array([11.1, 12.24 + 240, 7.25]) * u.km / u.s,
-#    "z_sun": 0.0 * u.pc,
-#}
-
-###############################################################################
-
-def fetch_vtodays_rgc(
-    gc_fname,
-    path=paths.data_mwgcs,
-    ej_fname="output_N-10_ejections.txt",
-    kgroup=None,
-):
-    """ Function to make a single rgc histogram, for parallelization. """
-    # Define path, load ejections with relevant columns
-    path = path / gc_fname / ej_fname
-    ejdf = rustics.EjectionDf(path, usecols=["X","Y","U","V","W","kf"])
-    # Filter with BSE k's if specified
-    if type(kgroup) != type(None):
-        ejdf.df = ejdf.df[
-            (ejdf.df.kf >= kgroup.lo) & (ejdf.df.kf < kgroup.hi)
-        ]
-    # Throw out -1's
-    ejdf.df = ejdf.df[
-        (ejdf.df.X != -1)
-        & (ejdf.df.Y != -1)
-    ]
-    # Calculate rgc and make histogram
-    ejdf.df["rgc"] = (ejdf.df.X**2 + ejdf.df.Y**2)**0.5
-    ejdf.df["vtoday"] = (ejdf.df.U**2 + ejdf.df.V**2 + ejdf.df.W**2)**0.5
-    return ejdf.df[["rgc", "vtoday"]] 
-
-def fetch_vtodays_Z(
-    gc_fname,
-    path=paths.data_mwgcs,
-    ej_fname="output_N-10_ejections.txt",
-    kgroup=None,
-):
-    """ Function to make a single rgc histogram, for parallelization. """
-    # Define path, load ejections with relevant columns
-    path = path / gc_fname / ej_fname
-    ejdf = rustics.EjectionDf(path, usecols=["Z","U","V","W","kf"])
-    # Filter with BSE k's if specified
-    if type(kgroup) != type(None):
-        ejdf.df = ejdf.df[
[…]

### 2022-12-19 src/scripts/cmc_single_clusters.py
Added initial script to generate the credible regions.  Environment fixed to work with healpy (conda-forge used for all).  Also confirmed some rasterizations.

@@ -189,6 +189,7 @@ for ci, cmc_cluster in enumerate(cmc_cluster_list):
 #            alpha=0.7,
 #            lw=0.75,
 #            zorder=0,
+#            rasterized=True,
 #        )
 
     axd["scatter"].set_xlabel(rustics.HEADERS_TO_LABELS[x])

### 2022-12-19 src/scripts/gc_orbit_ejections.py

@@ -164,6 +164,7 @@ def integrate_cmc_ejections(
             c="gray",
             alpha=0.5,
             lw=0.25,
+            rasterized=True,
         )
         # Ejection points
         scats=ax.scatter(
@@ -185,7 +186,8 @@ def integrate_cmc_ejections(
         plt.savefig(paths.figures / __file__.split("/")[-1].replace(".py","_%s.pdf" % cluster))
         plt.close()
 
-        ### This section contains the code for integrating ejection orbits 
+        ### This section contains the code that was used to integrate the ejection orbits;
+        ### no fancy "integrate if GC ejections file does not exist", just plain old commenting to avoid running this everytime the figure is generated
         ############################################################
         ## The first option here is faster by >2x, despite not using galpy parallelization
         ######################################## 

### 2022-12-19 src/scripts/gcej_today.py

@@ -110,6 +110,7 @@ for gc in rustics.SAMPLE_GCS:
         "s": 20,
         "lw": 0.5,
         "marker": "X",
+        "rasterized": True,
     }
     # kwargs for GC orbit
     kw_o = {
@@ -117,6 +118,7 @@ for gc in rustics.SAMPLE_GCS:
         "alpha": 0.5,
         "lw": 0.25,
         "zorder": 0,
+        "rasterized": True,
     }
 
     # Plot locations (matplotlib aitoff wants coordinates in radians)

### 2022-12-19 src/scripts/generate_credible_regions.py

@@ -1,0 +1,169 @@
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import multiprocessing as mp
+import parmap
+from astropy.coordinates import SkyCoord, Galactocentric, ICRS
+from astropy import units as u
+import healpy as hp
+
+import paths
+import rustics
+
+###############################################################################
+
+
+def calc_credible_indices(probs, intervals):
+    """! Return an array of indices that compose the specified credible intervals.
+
+    @type   probs:      np.array
+    @param  probs:      Array of probabilities
+
+    @type   intervals:  list
+    @param  intervals:  List of credible regions to calculate.
+
+    @rtype:             np.array
+    @return:            Boolean array that can be used to mask probabilities to credible region.
+
+    """
+
+    # Get sort indices, sort probabilities
+    argsort_inds = np.argsort(probs)[::-1]
+    probs_sorted = probs[argsort_inds]
+    print("probs_sorted:", probs_sorted)
+
+    # Get cumulative probabilities, and find indices of intervals
+    probs_cumsum = np.cumsum(probs_sorted)
+    ss_inds = np.searchsorted(probs_cumsum, intervals, side="right")
+    print("ss_inds:", ss_inds)
+
+    # Generate boolean masks for credible regions
+    masks = np.full((len(intervals), probs.shape[0]), False)
+    for ii, i in enumerate(ss_inds):
+        masks[ii, argsort_inds[:i]] = True
+    print("masks:", masks)
+    print("probs[masks[0,:]]:", probs[masks[0, :]])
+
+    return masks
+
+
+def calc_ej_credible_regions(
+    gc_name,
+    intervals=[0.5, 0.9],
+    dir_path=paths.data_mwgcs,
+    ej_fname="output_N-10_ejections.txt",
+    hp_level=5,
+    hp_fname="hp_probs.fits",
+    pm_fname="pm_probs.fits",
+    overwrite=True,
+):
+    """! Calculate the credible regions for the ejections from one GC.
+
+    @type   gc_name:    string
+    @param  gc_name:    Name of globular cluster
+
+    @type   intervals:  list
+    @param  intervals:  List of floats of credible regions to calculate.
+
+    @type   dir_path:   string
+    @param  dir_path:   path/to/directory containing GC folders
+
+    @type   ej_fname:   string
[…]

### 2023-01-07 src/tex/ms.tex
Added initial script to generate the credible regions.  Environment fixed to work with healpy (conda-forge used for all).  Also confirmed some rasterizations.
Updated single_clusters, ms.tex.  This might also include the final version of credible_regions, if it wasn't committed previously.

@@
 \usepackage{showyourwork}
+\usepackage{amsmath}
 
@@
 
+\newcommand{\carl}[1]{\textcolor{red}{carl: #1}}
+
 \shorttitle{Runaway \& hypervelocity stars from globular clusters}
@@
 % Title
-\title{Runaway and hypervelocity stars from binary-single encounters in globular clusters}
+\title{Runaway and Hypervelocity Stars from  Compact-Object Encounters in Globular Clusters}
 
@@
 \begin{abstract}
-    An abstract.
+    The dense environments in the cores of globular clusters (GCs) facilitate many fewbody encounters among stellar objects.
+ 	Mass segregation ensures that the most massive stars sink into the core first, and subsequently that the core becomes populated with black holes as the same stars evolve; these compact objects are expected to enable stronger dynamics than star-only encounters.
+ 	We study the capacity of these systems to produce high speed stellar ejecta through a synthetic population of binary-single encounters, the latter of which we construct from realistic $N$-body models of GCs.
+ 	We pair our model-discriminated populations with observational catalogs of Milky Way GCs to compose a present-day galactic population of ejecta.
+ 	We find that these kinds of encounters can accelerate stars to velocities in excess of 2000 \kms, to speeds beyond the previously predicted limits for ejecta from star-only encounters and in the same regime of galactic center ejections.
+	However, the same ejections can only account for 1.5-10\% of the total population of stellar runaways, and only 0.01-1\% of hypervelocity stars, with similar relative rates found for white dwarf ejections.
+	We also provide credible regions for ejecta from 149 Milky Way GCs, which we hope will be useful as supplementary evidence when pairing runaway stars with origin GCs.
 \end{abstract}
@@
 Hypervelocity stars (HVSs) are stars that have been accelerated beyond the local galactic escape speed, that is, to the point of becoming unbound from the galactic potential.
-Theorized by \citealt{1988Natur.331..687H}, the classical origin of HVSs is the dynamical disruption of a stellar binary by a super massive black hole (SMBH); this ``Hills mechanism" is believed to be capable of accelerating stars to speeds up to 4000 km s$^{-1}$, and naturally makes HVSs potential probes of the galactic center.
+Theorized by \citealt{1988Natur.331..687H}, the classical origin of HVSs is the dynamical disruption of a stellar binary by a super massive black hole (SMBH); this ``Hills mechanism" is believed to be capable of accelerating stars to speeds up to 4000 km s$^{-1}$, and naturally makes HVSs a potential probe of the galactic center.
 Since the first HVS discovery \citep{2005ApJ...622L..33B}, a handful of candidate objects have been identified in the Milky Way (MW) (e.g.
@@
 Alternate acceleration mechanisms capable of producing high-velocity stars include the binary supernova and dynamical ejection scenarios (BSS \citep{1967BOTT....4...86P} and DES \citep{1961BAN....15..265B}, respectively).
-The BSS has been predicted to accelerate stars to speeds of a few hundred \kms \citep{2019A&A...624A..66R}, with exceptionally light companions potentially receiving velocities in excess of 1000 \kms \citep{2015MNRAS.448L...6T}.
+The BSS has been predicted to accelerate stars to speeds of a few hundred \kms \citep{2019A&A...624A..66R, 2022MNRAS.tmp.3236I}, with exceptionally light companions potentially receiving velocities in excess of 1000 \kms \citep{2015MNRAS.448L...6T}.
 The DES has been associated with higher speed limits: \citet{1991AJ....101..562L} studied these encounters with numerical methods, and found that the upper limit for products of these encounters was approximately the escape speed from the surface of the most massive star involved; for a sun-like star, this escape speed is $\sim$620 \kms, while for a 60 $M_\odot$ late main-sequence star it is $\sim$1400 \kms.
 
-Globular clusters (GCs) are obvious candidate matrices for both of these events due to their high stellar densities, but the DES might be exceptionally amplified due to the combined effects of mass segregation and stellar evolution.
-This process is characterized as the migration of the most massive objects to the center of a self-gravitating system due to dynamical friction \citep{2008gady.book.....B}, which in turn leads to efficient formation of binaries in the core \citep{2005MNRAS.358..572I}.
+Globular clusters (GCs) are obvious candidate matrices \carl{odd phrasing, but fine if you want} for both of these events due to their high stellar densities, but the DES might be exceptionally amplified due to the combined effects of mass segregation and stellar evolution.
+This process is characterized as the migration of the most massive objects to the center of a self-gravitating system due to dynamical friction \citep[e.g.,][]{2008gady.book.....B}, which in turn leads to efficient formation of binaries in the core \citep{2005MNRAS.358..572I}.
 This central population of binaries is highly influential on the evolution of the cluster, primarily serving as a heat source as binaries form and shrink through dynamical encounters, undergoing one kind of ``core collapse" in the process \citep[e.g.][]{2007ApJ...658.1047F, 2013MNRAS.429.2881C}.
 In a realistic cluster, these dynamical phases occur after stars have started collapsing into black holes (BHs), and such objects dominate the core population \citep{2020IAUS..351..357K}.
-The resulting abundance of black hole binaries (BBHs) characterizes GCs as one of the favorable progenitors of gravitional wave sources \citep{2000ApJ...528L..17P, 2015PhRvL.115e1101R}, and in the context of this paper motivates the investigation of whether the population of GCs in the Milky Way (MW) can be considered a significant source of high-velocity stars.
+The resulting abundance of black hole binaries (BBHs) characterizes GCs as one of the favorable progenitors of gravitational-wave sources \citep{2000ApJ...528L..17P, 2015PhRvL.115e1101R}, and in the context of this paper motivates the investigation of whether the population of GCs in the Milky Way (MW) can be considered a significant source of high-velocity stars.
 
-This work investigates the capacity of GCs to produce HVSs through the DES, particularly in encounters between binaries and single objects, which may include compact objects (COs, a category that includes BHs, white dwarfs (WDs), and neutron stars (NSs)).
-We compose a realistic set of these binary-single compact object (BSCO) encounters by pulling initial conditions from the \CMCcat\ of MW-like GC models \citep{2020ApJS..247...48K}.
-\CMC\ is a H\'enon-style Monte Carlo code for $N$-body simulations of star clusters, and has the relevant features of stellar evolution implementation and direct integration of strong encounters between stars and stellar multiples; the referenced catalog consists of 148 models which span much of the parameter space of MW GCs.
-This analysis concludes that GCs are possible generators of HVSs in all velocity regimes thus observed, beyond the previously established limit for star-only encounters, albeit the rate at which these objects are produced from GCs is significantly lower than that for the galactic center.
+This work investigates the capacity of GCs to produce HVSs through the DES, particularly in encounters between binaries and single objects, which may include compact objects (COs) such as BHs, white dwarfs (WDs), and neutron stars (NSs).
+We compose a realistic set of GC binary-single compact object (BSCO) encounters using the initial conditions self-consistently pulling initial conditions from the 148 models of the \CMCcat\, a collection of $N$-body GC models covering the space of MW-like GCs \citep{2020ApJS..247...48K} generated with the Cluster Monte Carlo code \cite[\texttt{CMC}][]{Rodriguez2022}.
+In section II \carl{instead of a 1-sentence punch line, we typically write In section III we..., in section III we..., followed by your nice conclusion sentence below.}
+We conclude that GCs are possible generators of HVSs in all velocity regimes thus observed, beyond the previously established limit for star-only encounters, albeit the rate at which these objects are produced from GCs is significantly lower than that for the galactic center.
 
-\section{Methods} \label{sec:methods}
+\section{Methods: Sampling \& Integrating BSCO encounters} \label{sec:methods}
 
-\subsection{Binary-single encounter population} \label{subsec:binsingle_pop}
+The \CMCcat\ was generated using \CMC, a H\'enon-style $N$-body code for collisional stellar dynamics.
+Developed over two decades \citep{2000ApJ...540..969J,2013ApJS..204...15P,Rodriguez2022}, \CMC\ relies upon the technique originally developed by \cite{1971Ap&SS..13..284H,1971Ap&SS..14..151H}, where the cumulative effect of two-body encounters is modeled as an ``effective'' encounter between neighboring particles (in a radially sorted, spherically symmetric  potential).
+Because these neighboring particles are individual stars (or binaries), the H\'enon method allows detailed stellar and strong dynamical encounters to be considered as well.
+To that end \CMC~includes prescriptions for three-body binary formation from single BHs \cite{2013ApJ...763L..15M}, binary-single and binary-binary gravitational encounters using the \texttt{Fewbody} small-$N$ scattering package \cite{2004MNRAS.352....1F,2007ApJ...658.1047F}, and galactic tidal fields \cite{2013MNRAS.429.2881C} \carl{CARL CHECK THAT}.
+The version of \CMC~used to create the \CMCcat\citep[which used identical physics to the public version described in][]{Rodriguez2022} treats single and binary stellar evolution for stars with  the \texttt{COSMIC} code for population synthesis \citep{2020ApJ...898...71B}.
+\texttt{COSMIC} is based upon the original Binary Stellar Evolution (BSE) code \citep{2000MNRAS.315..543H,2002MNRAS.329..897H}, but with updated prescriptions for compact-object formation and massive star evolution; see \cite{2020ApJ...898...71B} and \cite{Rodriguez2022} for details.
 
-\CMC\ records all strong encounters that required direct integration during a cluster model run.
+When one of the two neighboring particles in a cluster is a binary, \CMC\ calculates whether to perform a strong dynamical encounter by calculating the probably $P_{\rm BS}$ for an encounter to occur within a single timestep $\Delta T$ as
+
+\begin{equation}
+P_{\rm BS} = n \Sigma w \Delta T~,
+\label{eqn:pbs}
+\end{equation}
+
+\noindent where $n$ is the local density of stars, $w$ is the relative velocity between the neighboring star and binary, and $\Sigma$ is the cross section for encounters to occur, given by
+
+\begin{equation}
+\Sigma = \pi r_p^2 \left(1+\frac{2 G M}{r_p w^2}\right),
+\label{eqn:sigma}
+\end{equation}
+
+\noindent where $M$ is the total mass of the system and $r_p$ is the radius within which a strong encounter is assumed to occur (equal to twice the binary semi-major axis by default).  
+During each timestep, \CMC\ determines whether to perform a strong three-body encounter between a neighboring star and binary by computing the probability from \ref{eqn:pbs} and comparing it to a random variable drawn from [0,1], $X$.
+If $X < P_{\rm BS}$, an encounter is performed with an impact parameter, $b$, selected from a distribution proportional to $b db$ out to a maximum integrated area set by \ref{eqn:sigma}.
+All other parameters, such as the phase of the binary and the orientation of the angular momentum and Runge-Lenz vectors are randomly selected.
+Of course, this means that any encounter produced in a single \CMC\ integration is only a single realization of all the possible encounters that could have occurred in the cluster at that time.
+%While \CMC\ will produce HVSs naturally during a cluster integration, we want to increase records all strong encounters that required direct integration during a cluster model run.
+
 To establish realistic binary-single encounter populations for clusters of various parameters, we take the 148 models from the \CMCcat\ and extract the initial conditions of all strong binary-single encounters that involve at least one luminous object (star, WD, or NS) and one compact object.
@@
 Over the entire catalog, our encounter sample makes up about half of all strong encounters that occur in the models, with each model contributing a few ten thousand BSCO encounters on average.
-We then realize each encounter in isolation with the small-$N$-body code \fewbody\ \citep{2004MNRAS.352....1F}.
+We then realize each encounter in isolation with the same \fewbody\ package used in \CMC.
 We compute 10 realizations of each encounter, varying the encounter angles for each realization, to obtain a better statistical representation of the binary-single encounter population.
@@
 The resulting objects that leave the cluster to become runaway or HVSs are identified as follows.
-\fewbody\ terminates integration before the resulting objects are far from each other's gravitational influence; therefore, the final velocity of an object after an encounter $v_{\rm fin}$ is calculated as the hyperbolic excess velocity
+To save computational resources, \fewbody\ terminates its integration once the relevant encounter products have positive energy and are moving away from one another.
+In other words, the encounters are terminated before the resulting objects are far from each other's gravitational influence.
+To account for this, we calculate the final velocity of an object after an encounter $v_{\rm fin}$ as the hyperbolic excess velocity
 \begin{equation}
@@
 \end{equation}
-where $v$ is the velocity of the object, and $U$ and $K$ are the Keplerian potential and kinetic energies of the top-level binary-single system (all of these quantities are evaluated at the termination of integration).
-The local escape velocity of the star cluster $v_{\rm esc}$ is provided by \CMC\ with the other encounter parameters; any object with $v_{\rm fin} \ge v_{\rm esc}$ is considered to escape the cluster, suspending the possibility of subsequent encounters.
+\noindent where $v$ is the velocity of the object leaving the encounter, and $U$ and $K$ are the Keplerian potential and kinetic energies of the top-level binary-single system (all of these quantities are evaluated at the termination of integration).
+The local escape velocity of the star cluster $v_{\rm esc}$ is provided by \CMC\ with the other encounter parameters; any object with $v_{\rm fin} \ge v_{\rm esc}$ is considered to escape the cluster.
 The velocity of an ejected object once it has left the cluster is therefore
@@
 
+{\color{blue} New version:
+The initial conditions used for these encounters are calculated in the center-of-mass rest frame of the encounter, i.e.
+they do not contain information about the center-of-mass velocity of the encounter in the frame of the GC model.
+We do not attempt to correct for this, which leads to an underestimation of final velocities for encountering objects and subsequently ejection rates; we justify this in Appendix \ref{app:restframe}.
+}
+
+{\color{magenta} Old version:
 It is worth noting that the encounter initial conditions recorded in the \CMCcat\ contain velocities calculated in the center-of-mass frame of the encounter.
-A more rigorous calculation of $v_{\rm out}$ would utilizes the velocity dispersion $\sigma$ to determine how $v_{\rm fin}$ translates to a velocity in the reference frame of the star cluster model.
+A more rigorous calculation of $v_{\rm out}$ would utilize the velocity dispersion $\sigma$ to determine how $v_{\rm fin}$ translates to a velocity in the reference frame of the star cluster.
 Assuming that the distribution of the 3D object velocity $\vec{v}_{\rm fin}$ is independent of the center-of-mass velocity $\vec{v}_{\rm cm}$ of the encounter it originated from, we find that the average ratio of speed after to speed before the transformation to the cluster reference frame $v'_{\rm fin} / v_{\rm fin}$ is a maximum of $\sim$1.3 in the case $v_{\rm fin} \approx \sigma$, and a minimum of 1 in the case $v_{\rm fin} \gg \sigma$.
-As $v_{\rm cm} \sim \sigma$ and $\sigma \lesssim v_{\rm esc}$ [CITATIONS?], we estimate that neglecting a transformation to the cluster reference frame after center-of-mass encounter integration shrinks the resulting ejection populationoverall, but not in a manner that significantly affects the following analysis.
+As $v_{\rm cm} \sim \sigma$ and $\sigma \lesssim v_{\rm esc}$ \carl{I don't really follow this calculation; need to clarify it}, we estimate that neglecting a transformation to the cluster reference frame after center-of-mass encounter integration shrinks the resulting ejection population overall, but not in a manner that significantly affects the following analysis.
+}
 
-\subsection{Core collapse and ejecta} \label{subsec:cc}
+\section{Results} \label{sec:results}
 
+\subsection{GC dynamics and BSCO ejections} \label{subsec:gcdyns}
+
+\subsubsection{GC core collapses} \label{subsubsec:cc}
+
+As the fewbody encounter rate is highly dependent on the density of stellar objects, we 
 The core collapses of star clusters due to dynamical heat flow from the center to the outer regions of a system are well-documented processes (e.g.
-\citealt{1968MNRAS.138..495L}, \citealt{2020IAUS..351..357K}).
+\citealt{1968MNRAS.138..495L}, \citealt{2020IAUS..351..357K} \carl{steal a few more citations from the CMC code paper}).
+\carl{ the following text needs some clarification as well.
+Core collapse is a well-defined process that occurs even in equal-mass clusters.
+What you're trying to distinguish between is the first core collapse.
+Take a quick look at (and cite) the following papers (commented in the tex)}
+%https://ui.adsabs.harvard.edu/abs/2013MNRAS.432.2779B/abstract
+%https://ui.adsabs.harvard.edu/abs/2014MNRAS.445.3435H/abstract
+\carl{also distinguish everywhere between \texttt{Fewbody} the code (which should look like that) and fewbody gravitational encounters}
 One kind of core collapse occurs when the population of BHs in cluster (localized to the center via.
@@
 
-In this analysis, we label a cluster as core collapsed when its population of BHs has been reduced to less than 10 members \citep{2020IAUS..351..357K}.
-By this metric, 69 of the 148 \CMCcat\ models achieve core collapse by the end of the 14 Gyr integration time, and small cluster mass and size are good predictors of systems that evolve to this point the fastest.
+In this analysis, we label a cluster as core collapsed when its population of BHs has been reduced to less than 10 members \citep[following][]{2020IAUS..351..357K}.
+By this metric, 69 of the 148 \CMCcat\ models achieve core collapse by the end of the 14 Gyr integration time, and small cluster mass and size are good predictors of systems that evolve to this point the fastest \carl{add comparison to number of CC clusters in MW (count the number in the Harris catalog and cite it)}.
 
-\subsection{Estimating a MW-like population} \label{subsec:est_MW-like}
+\subsubsection{Ejections from single clusters} \label{subsubsec:single_clusters}
 
-In the interest of predicting realistic statistics and rates for a MW-like GC population, we seek to assemble a synthetic MW-like population of GC-runaways from BSCO encounters.
-The two steps involved here are 1) selecting representative \CMC\ models for galactic GCs, and 2) integrating the post-ejection orbits to the present day in the context of the MW.
-
-\subsubsection{Pairing \CMC\ models to MW GCs} \label{subsubsec:pairing}
-% Plot idea: the log(M) vs. rr vs. r_hm diagnostic plots in gcs_mw-cmc.ipynb, with top/bottom//left/right axes showing the physical and normalized values of each variable
-
-The 148 \CMC\ models are designated by cluster initial size $N$ (number of stellar objects), initial virial radius $r_{\rm vir}$ (parsecs), distance from the galactic center $r_{\rm gc}$ (kiloparsecs, used in \CMC\ to calculate tidal effects from the galactic potential), and metallicity $Z$ (used to prescribe star evolution), with values chosen to span much of the MW GC parameter space; see \citet{2020IAUS..351..357K} for more details.
-
-We predominantly use the observational catalog of \citet{2018MNRAS.478.1520B} to obtain parameters for MW GCs.
-This catalog lacks metallicity measurements for the objects; therefore we supplement with that of \citet{2010arXiv1012.3224H}.
-12 of the GCs in the former catalog do not have metallicity measurements in the latter, leaving us with the 149 Mw GCs we use in this analysis.
-
-We choose a representative \CMC\ model for each MW GC in the following manner.
-For each GC, after \citet{2021ApJ...912..102R} we first find the values of $r_{\rm gc}$ and $Z$ in the \CMCcat\ model grid closest to the measurements of these parameters for the GC (in linear and log space, respectively) and select the models with the respective values as candidate representatives.
-We choose 11 linearly spaced times between 10 and 13.5 Gyr (c.f. \citet{2013ApJ...775..134V}), and find the \CMC\ timesteps closest to the chosen times for the candidate models.
-The MW GCs and the \CMC\ models are shown in Figure \ref{fig:cmcs-mwgcs_scatter}.
-
-The representative model is chosen by finding the model timestep closest to the GC in normalized $\log M$-$r_c / r_h$ space by Euclidean distance.
-We choose these parameters as in this context of GC population synthesis they are reasonable proxies for respectively the scale and evolutionary state of the cluster.
-We use the 3D half-mass radius for $r_h$, and the definition of core radius from \citet{1987degc.book.....S}:
-\begin{equation}
-    r_c = \sqrt{\frac{3 \sigma_c^2}{4 \pi \rho_c}},
-\end{equation}
-where $\sigma_c$ is the central velocity dispersion and $\rho_c$ is the central density for the cluster.
-We normalize the two dimensions in the \CMC\ space, i.e. the parameters actually used to compute the distance are
-\begin{equation}
-    x_{\rm norm} = \frac{x - \bar{x}_{\rm \CMC}}{\sigma_{\rm x, \CMC}},
-\end{equation}
-where $\bar{x}_{\rm CMC}$ and $\sigma_{\rm x,CMC}$ are respectively the mean and standard deviation of the parameter $x$ over the total set of \CMC\ models.
-
-\begin{figure}
-    \script{cmcs-mwgcs_scatter.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/cmcs-mwgcs_scatter.pdf}
-        \caption{
-        The clusters and models used in this work.
-        Galactic GCs are represented by black triangles, and CMC models by blue dots.
-        %The sample \CMC\ models used in \S\ref{subsec:single_clusters} are shown as blue stars.
-        %M3 and its \CMC\ counterpart relevant to \S\ref{} are shown as purple triangles.
-        Cluster mass $M_{\rm cluster}$ is shown on the $y$-axis, and the core radius/half-mass radius ratio $r_c/r_h$ (metallicity $[{\rm Fe/H}]$) on the left (right) $x$-axis.
-        }
-        \label{fig:cmcs-mwgcs_scatter}
-    \end{centering}
-\end{figure}
-
-While the \CMCcat\ has fairly representative models for most of the MW GCs, there are a number of larger-cored GCs (right side of the left pane of Figure \ref{fig:cmcs-mwgcs_scatter}) that are relatively distant from the nearest \CMC\ model; in practice, this means that a single \CMC\ model can be chosen to represent a disproportionate number of MW GCs.
-Our pairing algorithm ends up using 57 of the 148 \CMC\ models to build the sythetic population, and the most utilized model is matched to 14 MWGCs, or $\lesssim10\%$ of the population.
-The most used models are typical in terms of number of ejections and cluster evolution, and so while the more extreme GCs might be misrepresented, they are being represented by average models nonetheless.
-
-\subsubsection{Integrating runaways to the present day} \label{subsubsec:galpy}
-
-We now produce a present-day picture of these runaways by evolving their trajectories to the present day, using \texttt{galpy}\footnote{http://github.com/jobovy/galpy} \citep{2015ApJS..216...29B} to perform the necessary integrations.
-For each MW GC, we consider the matched \CMC\ model timestep as the present-day representation of the system, and pair it with the present-day orbital position and velocity from \citet{2018MNRAS.478.1520B}.
-We integrate the orbit backwards through time, and place the ejected objects at the appropriate times in the trajectory.
-The ejection velocity $v_{\rm out}$ from the model is assigned a random direction and boosted to the galactic rest frame, and this trajectory is evolved to the present day.
-
-\section{Results} \label{sec:results}
-
-\subsection{Ejections from single clusters} \label{subsec:single_clusters}
-
-Here we study the BSCO ejections produced by individual \CMC\ cluster models.
+\carl{No need to announce what we're doing it, better to motivate why, e.g.: To get a clear idea of the production of HVSs from our clusters, we examine two representative cases with $N=10^8$ initial particles ( final masses of $\sim 2\times10^5M_{\odot}$, near the median of the GC mass function in the MW )}Here we study the BSCO ejections produced by individual \CMC\ cluster models.
 \CMC\ model N8e5\_rv0.5\_rg8\_Z0.0002 is taken as a sample as it represents a typical MW GC, and models N4e5\_rv0.5\_rg8\_Z0.0002, N8e5\_rv0.5\_rg8\_Z0.0002, and N8e5\_rv2\_rg8\_Z0.02 are included to examine the effects parameter variation has on the population of ejected objects.
+\carl{Wait, careful here.
+I'd say rv1 or rv2 is much more representative of MW clusters, rv0.5 is pretty compact (at least in terms of the clusters it produces).
+We want a rv0.5 and rv2 model to explore what core collapse looks like, but I'd use rv1 as the base model for futzing with the  metallicity}
 For simpler reference, we name the first sample model the ``base" model, and the remaining three the ``low-mass", ``bigger", and ``high-metallicity" models, respectively.
 
-It is relevant to note a strong correlation between BSCO encounters and the evolution of the cluster core.
-Figure \ref{fig:cmc_single_clusters_vesc} plots the local escape velocities $v_{\rm esc}$\footnote{$v_{\rm esc}$ here is to be considered as a proxy for the distance from the center of the cluster.} for all BSCO encounters from the sample models, along with the central density $\rho_c$ \citep{1985ApJ...298...80C}, scaled to the initial density of the model $\rho_{c,0}$.
+What is immediately apparent from these single cluster models is a strong correlation between BSCO encounters and the evolution of the cluster core.
+Figure \ref{fig:cmc_single_clusters_vesc} plots the local escape velocities $v_{\rm esc}$\footnote{$v_{\rm esc}$ here is to be considered as a proxy for the distance from the center of the cluster.} at the location of all BSCO encounters from the four models, along with the central density $\rho_c$ \citep{1985ApJ...298...80C}, scaled to the initial density of the model $\rho_{c,0}$.
 Within any small interval of time, the respective BSCO encounters are well-localized around a particular escape velocity, indicating that throughout the evolution of the cluster contemporary encounters are similarly localized to the same cluster radii.
@@
 Naturally one would expect the densest part of a system to facilitate the highest rates of few-body encounters; in this case the dominance is extreme enough to characterize the encounter statistics as a whole.
+
+\carl{Ok, the particular escape velocity is almost certainly the escape speed from the core (or rather is limited by/slightly below it).
+let's try the following: you can calculate the central escape speed directly from the .dyn.dat file (it has central potential and potential at the tidal boundary, the difference of which gives you the central escape speed (well the energy needed to escape)).
+I think it might make more sense to try plotting that in each figure using the velocity ticks, eliminate the central density, then just have one small plot that compares rc,rh,rho, and central escape speed for one (or two) of the models (maybe the rv0.5 and rv2 models)}
+
+\carl{honestly, I think figures 2 and 3 are somewhat redundant; let's take a look at what happens if we put the central escape speed in figure 3, and making that our figure 2.
+Then we have a new figure 3 that is just the comparison beteween $v_{esc}$, rc, rho for the four models.}
+% figure 2 = escape velocity; figure 3 = scatterplots
 
@@
     \caption{
-        Scatter plots of the cluster ejection velocity $V_{rm out}$ versus encounter time $t$ for every escaping object from the integrated encounters for the four sample \CMC\ models (see the beginning of \S\ref{subsec:single_clusters} for details).
+        Scatter plots of the cluster ejection velocity $V_{rm out}$ versus encounter time $t$ for every escaping object from the integrated encounters for the four sample \CMC\ models (see the beginning of \S\ref{subsubsec:single_clusters} for details).
         The histograms show the same data in 1D.
@@
 
+\subsection{Estimating a MW-like population} \label{subsec:est_MW-like}
+
+In the interest of predicting realistic statistics and rates for a MW-like GC population, we seek to assemble a synthetic MW-like population of GC-runaways from BSCO encounters.
+The two steps involved here are 1) selecting representative \CMC\ models for galactic GCs, and 2) integrating the post-ejection orbits to the present day in the context of the MW.
+
+\subsubsection{Pairing \CMC\ models to MW GCs} \label{subsubsec:pairing}
+% Plot idea: the log(M) vs. rr vs. r_hm diagnostic plots in gcs_mw-cmc.ipynb, with top/bottom//left/right axes showing the physical and normalized values of each variable
+
+The 148 \CMC\ models are designated by cluster initial size $N$ (number of stellar objects), initial virial radius $r_{\rm vir}$ (parsecs), distance from the galactic center $r_{\rm gc}$ (kiloparsecs, used in \CMC\ to calculate tidal effects from the galactic potential), and metallicity $Z$ (used to prescribe star evolution), with values chosen to span much of the MW GC parameter space; see \citet{2020IAUS..351..357K} for more details.
+\carl{As an example, model...
+represents a cluster...}
+
+We predominantly use the observational catalog of \citet{2018MNRAS.478.1520B} to obtain parameters for MW GCs.
+This catalog lacks metallicity measurements for the objects; therefore we supplement with that of \citet{2010arXiv1012.3224H}.
+12 of the GCs in the former catalog do not have metallicity measurements in the latter, leaving us with the 149 MW GCs we use in this analysis.
+
+We choose a representative \CMC\ model for each MW GC in the following manner.
+For each GC \carl{model}, \sout{after} \carl{following} \citet{2021ApJ...912..102R} we first find the values of $r_{\rm gc}$ and $Z$ in the \CMCcat\ model grid closest to the measurements of these parameters for the GC (in linear and log space, respectively) and select the models with the respective values as candidate representatives.
+We choose 11 linearly spaced times between 10 and 13.5 Gyr (c.f.
+\citet{2013ApJ...775..134V}), and find the \CMC\ timesteps closest to the chosen times for the candidate models.
+\carl{wait, are the ages for the clusters specified in the Baumgardt catalog?
+Where are those coming from}
+The MW GCs and the \CMC\ models are shown in Figure \ref{fig:cmcs-mwgcs_scatter}.
+
+\carl{Once we have identified a cluster time, metallicity, and galactocentric distance, we identify a single} representative model by finding the timestep closest to the MW GC in normalized $\log M$-$r_c / r_h$ space by Euclidean distance.
+\carl{be careful to specific MW or model GC when saying GC here.}
+We choose these parameters as in this context of GC population synthesis they are reasonable proxies for respectively the scale and evolutionary state of the cluster.
+We use the 3D half-mass radius for $r_h$, \carl{cite the specific baumgardt paper here; 3d half-mass radius is a pretty odd thing to get from a catalog so people may be confused} and the definition of core radius from \citet{1987degc.book.....S}:
+\begin{equation}
+    r_c = \sqrt{\frac{3 \sigma_c^2}{4 \pi \rho_c}},
+\end{equation}
+where $\sigma_c$ is the central velocity dispersion and $\rho_c$ is the central density for the cluster \carl{make sure we're using the same core radius definition too}.
+We normalize the two dimensions in the \CMC\ space, i.e.~the parameters actually used to compute the distance are
+\begin{equation}
+    x_{\rm norm} = \frac{x - \bar{x}_{\rm \CMC}}{\sigma_{\rm x, \CMC}},
+\end{equation}
+where $\bar{x}_{\rm CMC}$ and $\sigma_{\rm x,CMC}$ are respectively the mean and standard deviation of the parameter $x$ over the total set of \CMC\ models.
+\carl{this should go above where you're describing finding the closest model}
+
+\begin{figure}
+    \script{cmcs-mwgcs_scatter.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/cmcs-mwgcs_scatter.pdf}
+        \caption{
+        The clusters and models used in this work.
+        Galactic GCs are represented by black triangles, and CMC models by blue dots.
+        %The sample \CMC\ models used in \S\ref{subsec:single_clusters} are shown as blue stars.
+        %M3 and its \CMC\ counterpart relevant to \S\ref{} are shown as purple triangles.
+        Cluster mass $M_{\rm cluster}$ is shown on the $y$-axis, and the core radius/half-mass radius ratio $r_c/r_h$ (metallicity $[{\rm Fe/H}]$) on the left (right) $x$-axis.
+\carl{need to distinguish between top and bottom.
+Also I would say "vertical and horizontal" more than x and y, or better yet just say "plot this v that".
+Also don't need units of dex for metallicity (that's common enough to be understood)}
+        }
+        \label{fig:cmcs-mwgcs_scatter}
+    \end{centering}
+\end{figure}
+
+While the \CMCcat\ has fairly representative models for most of the MW GCs, there are a number of larger-cored GCs (right side of the left pane of Figure \ref{fig:cmcs-mwgcs_scatter}) that are relatively distant from the nearest \CMC\ model; in practice, this means that a single \CMC\ model can be chosen to represent a disproportionate number of MW GCs.
+Our pairing algorithm ends up using 57 of the 148 \CMC\ models to build the sythetic population, and the most utilized model is matched to 14 MWGCs, or $\lesssim10\%$ of the population.
+The most used models are typical in terms of number of ejections and cluster evolution, and so while the more extreme GCs might be misrepresented, they are being represented by average models nonetheless.
+
+\subsubsection{Integrating runaways to the present day} \label{subsubsec:galpy}
+
+We now produce a present-day picture of these runaways by evolving their trajectories to the present day, using \texttt{galpy}\footnote{http://github.com/jobovy/galpy} \citep{2015ApJS..216...29B} to perform the necessary integrations.
+For each MW GC, we consider the matched \CMC\ model timestep as the present-day representation of the system, and pair it with the present-day orbital position and velocity from \citet{2018MNRAS.478.1520B}.
+We integrate the orbit backwards through time, and place the ejected objects at the appropriate times in the trajectory.
+The ejection velocity $v_{\rm out}$ from the model is assigned a random direction and boosted to the galactic rest frame, and this trajectory is evolved to the present day.
+
 \subsection{Galactic population} \label{subsec:res_MW-like}
@@
 %\begin{figure}
-%    \scripts{encio_stackebar.py}
+%    %\scripts{encio_stackebar.py}
 %    \centering
@@
 
+\appendix
+
+\section{Ejecta credible regions} \label{app:credreg}
+
+We include with this publication phase credible regions in phase space for ejecta populations from the MW GCs considered, which may be accessed at [LINK].
+We intend these constructions to be used as secondary evidence for cluster membership of runaway stars, and to encourage further studies into understanding the respective phase space distributions.
+The 2D position and proper motion distributions are separated into two different files, the conventions of which are described below.
+
+The distribution of ejecta on the sky is quantified by discretizing the sphere with an order 4 nested HEALPix map [CITE], binning the sky into 3072 equal-area tiles.
+We choose this resolution to enable identification of interesting credible regions while minimizing the apparent effect of isolated points whose exact location is dependent on the RNG seeds used.
+We create the respective histogram by counting the number of synthetic ejecta that are found in each tile in the present day, and normalize by the total number of ejecta for the GC.
+The resulting probability histogram is stored in the first column (\texttt{PROBS}) of the \texttt{hp\_probs.fits} file for each GC; the \texttt{NEJECT} field in the header of the same file contains the number of ejections for the GC.
+We calculate our credible regions by cumulatively adding the highest probability bins until the target percentage is reached.
+The last two columns (\texttt{CR50} and \texttt{CR90}) are boolean masks of the same convection as the HEALPix probability histogram corresponding to the credible regions (50\% and 90\%, respectively), where bins with entries of 1 are included in the region.
+Figure \ref{fig:check_credible_regions_x} shows the histogram and 50\% and 90\% credible regions for E3, as an example (the script used to generate this plot is \texttt{check\_credible\_regions.py} in the GitHub repository; click on the icon by the caption to be taken directly to the file).
+
+\begin{figure}
+    \script{check_credible_regions.py}
+    \centering
+    \includegraphics[width=0.9\textwidth]{figures/check_credible_regions_x.pdf}
+    \caption{
+        The HEALPix histogram for a sample GC (E3), with the 50\% and 90\% credible regions in the right subplot.
+        Galactic coordinates are used.
+    }
+    \label{fig:check_credible_regions_x}
+\end{figure}
+
+We construct proper motion histograms and credible regions in a similar manner.
+We use a domain of $-30 \le \mu_\alpha \cos \delta~{\rm [km~s^{-1}]} \le 30$, $-45 \le \mu_\delta~{\rm [km~s^{-1}]} \le 15$ divided into a 50 $\times$ 50 grid.
+These bounds and resolution are included in the headers of the \texttt{pm\_prob.fits} files for each GC, where calling \texttt{np.linspace(PM[D/RCD]MIN, PM[D/RCD]MAX, PMNUM)} will return the bin edges used for the appropriate dimension.
+The header also includes a \texttt{COVERAGE} field containing the fraction of ejecta that lie in the specified domain; for all GCs this fraction is at least 0.98, and in most cases is greater than 0.999.
+The total number of ejected objects (including those outside of the domain) is stored in the \texttt{NEJECT} field, as for the HEALPix histograms.
+The proper motion histogram and respective masks for the 50\% and 90\% credible regions are stored in the \texttt{pm\_prob.fits} files as separate HDUs; these items for the same example GC as the HEALPix plot is show in Figure \ref{fig:check_credible_regions_v}, and the same \texttt{check\_credible\_regions.py} script contains the generating code.
+
+\begin{figure}
+    \script{check_credible_regions.py}
+    \centering
+    \includegraphics[width=0.7\textwidth]{figures/check_credible_regions_v.pdf}
+    \caption{
+        The proper motion histogram and credible regions for the same sample GC.
+    }
+    \label{fig:check_credible_regions_v}
+\end{figure}
+
+\section{Velocities in encounter rest frames versus the GC rest frame} \label{app:restframe}
+
+We justify here our claim that in neglecting the transformation from the encounter rest frame to the GC model rest frame we obtain slower - and subsequently fewer - ejections.
+
+H\'enon's Monte Carlo method tracks the dynamical state of objects by their energy and angular momentum, which makes the technique inherently spherically symmetric.
+When drawing a radial and tangential velocity from an object's orbit, the sign of the radial velocity is randomly chosen as positive or negative with equal weighting, and when setting up a fewbody encounter an angle $0 \le \phi \le 2\pi$ between the tangential velocities of the two objects is chosen from a uniform distribution.
+These two features ensure isotropy of either velocity with respect to the other, and of the center-of-mass velocity of the encounter with respect to the GC model rest frame $\vec{v}_{\rm cm|GC}$.
+Note that the speed $v_{\rm cm|GC}$ cannot be greater than the maximum speed between the two objects.
+
+If we assume that the direction of the post-encounter object velocity in the center-of-mass rest frame $\vec{v}_{\rm f|cm}$ is isotropic with respect to $\vec{v}_{\rm cm|GC}$, then the average speed after boosting back to the model rest frame is
+\begin{equation}
+    \langle v_{\rm f|GC} \rangle
+    = \int_0^{2\pi} \frac{d\phi}{2\pi} \sqrt{(v_{\rm f|cm} + v_{\rm cm} \cos \phi)^2 + (v_{\rm cm} \sin \phi)^2}.
+\end{equation}
+Naturally, for $v_{\rm cm|GC} \ll v_{\rm f|cm}$ this average post-boost speed approaches $v_{\rm f|cm}$, and in the limit $v_{\rm cm|GC} \gg v_{\rm f|cm}$ it approaches $v_{\rm cm|GC}$, which recall must be less than the initial speed of the other object in the encounter: in either of these cases, the speed augmentation caused by the boost does not favor faster or slower post-encounter velocities.
+The maximum average ``acceleration" resulting from the boost occurs at the limit $v_{\rm cm|GC} = v_{\rm f|cm}$, where $\langle v_{\rm f|GC} \rangle \sim 1.3 v_{\rm f|cm} = 1.3 v_{\rm cm|GC}$.
+
+The assumption of isotropy in calculating $\langle v_{\rm f|GC} \rangle$ is appropriate for resonant encounters wherein the dynamics are chaotic.
+For flyby encounters where the objects travel on roughly hyperbolic trajectories, there is a preference for post-encounter velocities in the same direction as the initial velocity, if the impact parameter distribution is sufficiently expansive and weighted by the square of the parameter and the final velocities are marginalized over the angle that orients the plane of the ``2-body" encounter.
+The isotropic case is therefore a conservative limit on this flyby case, and predicts a greater boost-propagated speedup than if the calculation was done in full detail.
+
+In summary, neglecting to return to the model rest frame after the \fewbody\ step for strong encounters is found to not favor faster or slower post-encounter speeds when the final speed of an object is much greater than or much less than the center-of-mass speed of the encounter.
+There is an average speedup of 30\% when the two speeds are comparable, but this latter condition means that the speeds themselves are less than the maximum initial speed of the objects, which limits the extent to which the boost itself reveals speeds in excess of the escape velocity.
+
 \bibliography{bib}

### 2023-01-07 src/scripts/check_credible_regions.py

@@ -18,7 +18,7 @@ def hist2d_hpx_to_mollweide(
     xsize=1000,
     longitude_grid_spacing=60,
     latitude_grid_spacing=30,
-    graticule_labels=False,
+    graticule_labels=True,
     kw_rotator={},
     kw_pcolormesh={},
 ):
@@ -90,10 +90,10 @@ def hist2d_hpx_to_mollweide(
 
 # Get ejections data
 gc = "NGC_104"
-# gc = "NGC_5139"
-# gc = "NGC_6205"
+gc = "NGC_5139"
+gc = "NGC_6205"
 gc = "NGC_7089"
-# gc = "Pyxis"
+gc = "Pyxis"
 gc = "E_3"
 gc_path = paths.data_mwgcs / gc
 ejdf = rustics.EjectionDf(
@@ -144,10 +144,11 @@ ml, h = hp.fitsfunc.read_map(gc_path / "hp_probs.fits", h=True, field=None)
 
 # Set up figure
 fig, axd = plt.subplot_mosaic(
-    [["hist"], ["cred"]],
+    [["hist", "cred"]],
     subplot_kw={
         "projection": "mollweide",
     },
+    figsize=(6, 2),
 )
 for ax in axd.values():
     ax.grid(True, c="gray", alpha=0.5, zorder=0, lw=0.5)
@@ -199,10 +200,10 @@ hist2d_hpx_to_mollweide(
 # axcb.set_label(r"$m~(M_\odot)$")
 
 # Clean and show
+fig.suptitle(gc)
 plt.tight_layout()
-plt.show()
-plt.close("all")
-# print(cow)
+plt.savefig(paths.figures / __file__.split("/")[-1].replace(".py", "_x.pdf"))
+plt.close()
 
 ##############################
 ###     Proper Motions     ###
@@ -210,12 +211,13 @@ plt.close("all")
 
 # Set up figure
 fig, axd = plt.subplot_mosaic(
-    [["hist"], ["cred"]],
+    [["hist", "cred"]],
     sharex=True,
     sharey=True,
     gridspec_kw={
-        "hspace": 0,
+        "wspace": 0,
     },
+    figsize=(6, 4),
 )
 
 # Transform to mu_ra_cosdec-mu_dec
@@ -240,7 +242,9 @@ ax.hist2d(
[…]

### 2023-01-07 src/scripts/cmc_single_clusters.py

@@ -12,7 +12,7 @@ import paths
 
 ################################################################################
 
-#plt.style.use("./matplotlibrc")
+# plt.style.use("./matplotlibrc")
 
 # Get cluster names
 cmc_cluster_list = [
@@ -21,7 +21,7 @@ cmc_cluster_list = [
     "N8e5_rv0.5_rg8_Z0.02",
     "N4e5_rv0.5_rg8_Z0.0002",
 ]
-#cmc_cluster_list = rustics.DF_MODELS[(rustics.DF_MODELS.N == 4) & (rustics.DF_MODELS.rv == 0.5)].fname
+# cmc_cluster_list = rustics.DF_MODELS[(rustics.DF_MODELS.N == 4) & (rustics.DF_MODELS.rv == 0.5)].fname
 
 for ci, cmc_cluster in enumerate(cmc_cluster_list):
     print("{}, N_REALZ={}".format(cmc_cluster, rustics.N_REALZ))
@@ -45,7 +45,7 @@ for ci, cmc_cluster in enumerate(cmc_cluster_list):
     # Load times and core radii from initial.dyn.dat
     df_dyn = pd.read_csv(
         paths.data_cmc / cmc_cluster / "initial.dyn.dat",
-        #"/".join((paths.data, "cmc", cmc_cluster, "initial.dyn.dat")),
+        # "/".join((paths.data, "cmc", cmc_cluster, "initial.dyn.dat")),
         names=["t", "N", "rc_nb"],
         usecols=[0, 3, 24],  # 0 for t, 3 for N, 24 for rc_nb
         skiprows=2,
@@ -55,7 +55,7 @@ for ci, cmc_cluster in enumerate(cmc_cluster_list):
     # Load intial.conv.sh (for converting TotalTime to Myr and core radius to pcs)
     # Copied from cmctools/cmctoolkit.py
     conv_path = paths.data_cmc / cmc_cluster / "initial.conv.sh"
-    #conv_path = "/".join((paths.data, "cmc", cmc_cluster, "initial.conv.sh"))
+    # conv_path = "/".join((paths.data, "cmc", cmc_cluster, "initial.conv.sh"))
     f = open(conv_path, "r")
     convfile = f.read().split("\n")
     f.close()
@@ -91,17 +91,19 @@ for ci, cmc_cluster in enumerate(cmc_cluster_list):
         },
         figsize=(4, 4),
     )
-    axd["scatter"].set_xscale("log", subs=[2, 3, 4, 5, 6, 7, 8, 9])
[…]

### 2023-01-07 src/scripts/cmc_single_clusters_vesc.py

@@ -13,7 +13,7 @@ import paths
 
 ################################################################################
 
-#plt.style.use(rustics.PATH_TO_MPLRC)
+# plt.style.use(rustics.PATH_TO_MPLRC)
 
 # Get cluster names
 cmc_cluster_list = [
@@ -23,12 +23,12 @@ cmc_cluster_list = [
     "N8e5_rv0.5_rg8_Z0.02",
 ]
 
-mosaic = np.reshape(cmc_cluster_list, (4,1))
-figheight = 1.5 
+mosaic = np.reshape(cmc_cluster_list, (4, 1))
+figheight = 1.5
 figwidth = 4
 fig, axd = plt.subplot_mosaic(
     mosaic,
-    figsize=(mosaic.shape[1]*figwidth, mosaic.shape[0]*figheight),
+    figsize=(mosaic.shape[1] * figwidth, mosaic.shape[0] * figheight),
     sharex=True,
     gridspec_kw={
         "hspace": 0,
@@ -117,7 +117,7 @@ for ci, cmc_cluster in enumerate(cmc_cluster_list):
     colorr = "xkcd:crimson"
     axr = ax.twinx()
     axr.set_xlim(ax.get_xlim())
-    axr.set_yscale("log", subs=[2, 3, 4, 5, 6, 7, 8, 9])
+    axr.set_yscale("log")  # , subs=[2, 3, 4, 5, 6, 7, 8, 9])
     tsample = [
         int(i)
         for i in np.logspace(
@@ -145,11 +145,11 @@ for ci, cmc_cluster in enumerate(cmc_cluster_list):
 
     # Expand ylim if not large enough
     ylim = ax.get_ylim()
-    if np.floor(np.log10(ylim[1]))==np.floor(np.log10(ylim[0])):
-        ax.set_ylim((0.5*ylim[0], 2*ylim[1]))
+    if np.floor(np.log10(ylim[1])) == np.floor(np.log10(ylim[0])):
+        ax.set_ylim((0.5 * ylim[0], 2 * ylim[1]))
 
     # Add cluster label
-    axr.annotate(cmc_cluster, (0.025,0.0525), xycoords="axes fraction")
+    axr.annotate(cmc_cluster, (0.025, 0.0525), xycoords="axes fraction")
 
     # Add minor ticks
     xlim = ax.get_xlim()
[…]

### 2023-01-07 src/scripts/gc_orbit_ejections.py

@@ -21,9 +21,10 @@ helio_baumgardt = {
     "z_sun": 0.0 * u.pc,
 }
 
-#plt.style.use("./matplotlibrc")
+# plt.style.use("./matplotlibrc")
 
 ###############################################################################
+
 
 def integrate_cmc_ejections(
     cmc_fname,
@@ -33,14 +34,13 @@ def integrate_cmc_ejections(
 ):
     """! A function to parallelize the integration of encounters, s.t. the CMC data only have to be loaded once."""
 
-    #print(cmc_fname)
+    # print(cmc_fname)
     keep_going = 0
     for cluster in mwgc_catalog.df[mwgc_catalog.df.fname == cmc_fname].index:
         if cluster in rustics.SAMPLE_GCS:
             keep_going = 1
     if not keep_going:
-        return 1 
-        
+        return 1
 
     ##############################
     ###   Load CMC ejections   ###
@@ -64,7 +64,7 @@ def integrate_cmc_ejections(
     )
     cmc.convert_from_fewbody()
     cmc.df["vout"] = cmc.calc_vout()
-    #cmc.df = cmc.df[-100:]
+    # cmc.df = cmc.df[-100:]
 
     ##############################
     ###    Loop through GCs    ###
@@ -110,8 +110,9 @@ def integrate_cmc_ejections(
 
         # Integrate GC orbit, and save
         o_gc.integrate(ts, MWPotential2014, method="dop853_c", progressbar=False)
-        path = "/".join((cmc_path, "mwgcs", cluster, "gc_orbit.dat"))
-        os.makedirs("/".join((path.split("/")[:-1])), exist_ok=True)
+        path = paths.data_mwgcs / cluster
+        os.makedirs(path, exist_ok=True)
+        path = path / "gc_orbit.dat"
         pd.DataFrame(
             {
                 "t": ts,
@@ -152,10 +153,14 @@ def integrate_cmc_ejections(
         ###       Plot orbits      ###
         ##############################
         fig, axd = plt.subplot_mosaic(
-            [["xy",],],
-            figsize=(4,4),
+            [
+                [
+                    "xy",
+                ],
+            ],
+            figsize=(4, 4),
         )
-        
+
         ax = axd["xy"]
         # GC trajectory
         ax.plot(
@@ -167,13 +172,13 @@ def integrate_cmc_ejections(
             rasterized=True,
         )
         # Ejection points
-        scats=ax.scatter(
[…]

### 2023-01-07 src/scripts/generate_credible_regions.py

@@ -80,7 +80,7 @@ def calc_ej_credible_regions(
     gc_path,
     intervals=[0.5, 0.9],
     ej_fname="output_N-10_ejections.txt",
-    hp_level=5,
+    hp_level=3,
     hp_fname="hp_probs.fits",
     pm_fname="pm_probs.fits",
     overwrite=True,

### 2023-01-23 src/tex/ms.tex
Fixed orbit plots, final edits to text.

@@
 % Title
-\title{Runaway and Hypervelocity Stars from  Compact-Object Encounters in Globular Clusters}
+\title{Runaway and Hypervelocity Stars from Compact Object Encounters in Globular Clusters}
 
@@
 While S5-HVS1, along with several others, is well-explained by accepting an origin from the galactic center, for which there is overwhelming evidence for an SMBH (\citealt{1998ApJ...509..678G}, \citealt{2018A&A...615L..15G}, \citealt{2022ApJ...930L..12E}), recent studies have found examples of high-velocity stars that are not so easily read \citep[e.g.][]{2018MNRAS.479.2789B, 2019MNRAS.483.2007E, 2021A&A...646L...4I}.
-Two consistent results from these lines of work are that many stars previously classified as HV are nonetheless bound to the galactic potential, and many of these ``runaways" are more likely to have been ejected from the disk or a satellite as opposed to the galactic center.
-Altogether, the identification of systems of origin for HV and runaway stars is a necessary threshold problem to unlocking the full potential of observations of these objects.
+Two consistent results from these lines of work are that many stars previously classified as HVSs are nonetheless bound to the galactic potential, and many of these ``runaways" are more likely to have been ejected from the disk or a satellite as opposed to the galactic center.
+Altogether, the identification of systems of origin for HVSs and runaway stars is a necessary threshold problem to unlocking the full potential of observations of these objects.
 
@@
 The BSS has been predicted to accelerate stars to speeds of a few hundred \kms \citep{2019A&A...624A..66R, 2022MNRAS.tmp.3236I}, with exceptionally light companions potentially receiving velocities in excess of 1000 \kms \citep{2015MNRAS.448L...6T}.
-The DES has been associated with higher speed limits: \citet{1991AJ....101..562L} studied these encounters with numerical methods, and found that the upper limit for products of these encounters was approximately the escape speed from the surface of the most massive star involved; for a sun-like star, this escape speed is $\sim$620 \kms, while for a 60 $M_\odot$ late main-sequence star it is $\sim$1400 \kms.
+The DES has been associated with higher speed limits: \citet{1991AJ....101..562L} studied these encounters with numerical methods, and found that the upper limit for products of these encounters was approximately the escape speed from the surface of the most massive star involved.
+For a sun-like star, this escape speed is $\sim$620 \kms, while for a 60 $M_\odot$ late main-sequence star it is $\sim$1400 \kms.
 
-Globular clusters (GCs) are obvious candidate matrices \carl{odd phrasing, but fine if you want} for both of these events due to their high stellar densities, but the DES might be exceptionally amplified due to the combined effects of mass segregation and stellar evolution.
-This process is characterized as the migration of the most massive objects to the center of a self-gravitating system due to dynamical friction \citep[e.g.,][]{2008gady.book.....B}, which in turn leads to efficient formation of binaries in the core \citep{2005MNRAS.358..572I}.
+Globular clusters (GCs) are obvious candidate matrices for both of these events due to their high stellar densities, but the DES might be exceptionally amplified due to the combined effects of mass segregation and stellar evolution.
+The former process is characterized as the migration of the most massive objects to the center of a self-gravitating system due to dynamical friction \citep[e.g.,][]{2008gady.book.....B}, which in turn leads to efficient formation of binaries in the core \citep{2005MNRAS.358..572I}.
 This central population of binaries is highly influential on the evolution of the cluster, primarily serving as a heat source as binaries form and shrink through dynamical encounters, undergoing one kind of ``core collapse" in the process \citep[e.g.][]{2007ApJ...658.1047F, 2013MNRAS.429.2881C}.
@@
 
-This work investigates the capacity of GCs to produce HVSs through the DES, particularly in encounters between binaries and single objects, which may include compact objects (COs) such as BHs, white dwarfs (WDs), and neutron stars (NSs).
-We compose a realistic set of GC binary-single compact object (BSCO) encounters using the initial conditions self-consistently pulling initial conditions from the 148 models of the \CMCcat\, a collection of $N$-body GC models covering the space of MW-like GCs \citep{2020ApJS..247...48K} generated with the Cluster Monte Carlo code \cite[\texttt{CMC}][]{Rodriguez2022}.
-In section II \carl{instead of a 1-sentence punch line, we typically write In section III we..., in section III we..., followed by your nice conclusion sentence below.}
+Several recent and ongoing studies seek investigate these phenomena and the broader question of extra-tidal stars from GCs, in part encouraged by the continual improvement of astrometric measurements through efforts such as \textit{Gaia} \citet{2022A&A...667A.148G}.
+\citet{2023MNRAS.518.4249G} developed and used a particle spray code to model ejections from GC cores and demonstrate that kinematic cuts can be too aggressive when searching for ejecta, preferring the use of chemical abundances alone.
+\citet{2023arXiv230105166F} presented a comprehensive catalog of extra-tidal features of MWGCs, produced by simulating tidal stripping of known MWGCs in the context of the MW potential.
+Of particular proximity to our work, \citet{2022arXiv221116523W} used the same GC model catalog we employ to holistically examine stellar ejections from GCs and identify key mechanisms.
+The latter two of of these works are explicitly presented as the first in a series of papers seeking to compose a more complete picture of their respective objects.
+
+This work investigates the capacity of GCs to produce HVSs through the DES.
+We focus on encounter between binary and single objects, as they are the most abundant kind of fewbody encounter, and specifically those that involve compact objects (COs, meaning BHs, a white dwarfs (WDs), and neutron stars (NSs)).
+In \S\ref{sec:methods}, we describe our method of generating binary-single compact object (BSCO) ejecta populations from realistic simulations of GCs.
+In \S\ref{sec:gcdyns}, we examine these populations as functions of GC parameters, and the relationship they have to GC evolution.
+In \S\ref{sec:est_MW-like}, we combine our synthetic populations with observational MWGC catalogs to produce a MW-like population of ejecta, along with predicting rates and phase space distributions for these objects.
 We conclude that GCs are possible generators of HVSs in all velocity regimes thus observed, beyond the previously established limit for star-only encounters, albeit the rate at which these objects are produced from GCs is significantly lower than that for the galactic center.
@@
 The \CMCcat\ was generated using \CMC, a H\'enon-style $N$-body code for collisional stellar dynamics.
-Developed over two decades \citep{2000ApJ...540..969J,2013ApJS..204...15P,Rodriguez2022}, \CMC\ relies upon the technique originally developed by \cite{1971Ap&SS..13..284H,1971Ap&SS..14..151H}, where the cumulative effect of two-body encounters is modeled as an ``effective'' encounter between neighboring particles (in a radially sorted, spherically symmetric  potential).
+Developed over two decades \citep{2000ApJ...540..969J,2013ApJS..204...15P,Rodriguez2022}, \CMC\ relies upon the technique originally developed by \citet{1971Ap&SS..13..284H,1971Ap&SS..14..151H}, where the cumulative effect of two-body encounters is modeled as an ``effective'' encounter between neighboring particles (in a radially sorted, spherically symmetric  potential).
 Because these neighboring particles are individual stars (or binaries), the H\'enon method allows detailed stellar and strong dynamical encounters to be considered as well.
-To that end \CMC~includes prescriptions for three-body binary formation from single BHs \cite{2013ApJ...763L..15M}, binary-single and binary-binary gravitational encounters using the \texttt{Fewbody} small-$N$ scattering package \cite{2004MNRAS.352....1F,2007ApJ...658.1047F}, and galactic tidal fields \cite{2013MNRAS.429.2881C} \carl{CARL CHECK THAT}.
-The version of \CMC~used to create the \CMCcat\citep[which used identical physics to the public version described in][]{Rodriguez2022} treats single and binary stellar evolution for stars with  the \texttt{COSMIC} code for population synthesis \citep{2020ApJ...898...71B}.
-\texttt{COSMIC} is based upon the original Binary Stellar Evolution (BSE) code \citep{2000MNRAS.315..543H,2002MNRAS.329..897H}, but with updated prescriptions for compact-object formation and massive star evolution; see \cite{2020ApJ...898...71B} and \cite{Rodriguez2022} for details.
+To that end \CMC~includes prescriptions for three-body binary formation from single BHs \citep{2013ApJ...763L..15M}, binary-single and binary-binary gravitational encounters using the \texttt{Fewbody} small-$N$ scattering package \citep{2004MNRAS.352....1F,2007ApJ...658.1047F}, and galactic tidal fields \citep{2013MNRAS.429.2881C} \carl{CARL CHECK THAT}.
+The version of \CMC\ used to create the \CMCcat\citep[which used identical physics to the public version described in][]{Rodriguez2022} treats single and binary stellar evolution for stars with  the \texttt{COSMIC} code for population synthesis \citep{2020ApJ...898...71B}.
+\texttt{COSMIC} is based upon the original Binary Stellar Evolution (BSE) code \citep{2000MNRAS.315..543H,2002MNRAS.329..897H}, but with updated prescriptions for compact-object formation and massive star evolution; see \citet{2020ApJ...898...71B} and \citet{Rodriguez2022} for details.
 
 When one of the two neighboring particles in a cluster is a binary, \CMC\ calculates whether to perform a strong dynamical encounter by calculating the probably $P_{\rm BS}$ for an encounter to occur within a single timestep $\Delta T$ as
-
 \begin{equation}
@@
 \end{equation}
-
-\noindent where $n$ is the local density of stars, $w$ is the relative velocity between the neighboring star and binary, and $\Sigma$ is the cross section for encounters to occur, given by
-
+where $n$ is the local density of stars, $w$ is the relative velocity between the neighboring star and binary, and $\Sigma$ is the cross section for encounters to occur, given by
 \begin{equation}
@@
 \end{equation}
-
-\noindent where $M$ is the total mass of the system and $r_p$ is the radius within which a strong encounter is assumed to occur (equal to twice the binary semi-major axis by default).  
+where $M$ is the total mass of the system and $r_p$ is the radius within which a strong encounter is assumed to occur (equal to twice the binary semi-major axis by default).  
 During each timestep, \CMC\ determines whether to perform a strong three-body encounter between a neighboring star and binary by computing the probability from \ref{eqn:pbs} and comparing it to a random variable drawn from [0,1], $X$.
@@
 Of course, this means that any encounter produced in a single \CMC\ integration is only a single realization of all the possible encounters that could have occurred in the cluster at that time.
-%While \CMC\ will produce HVSs naturally during a cluster integration, we want to increase records all strong encounters that required direct integration during a cluster model run.
 
-To establish realistic binary-single encounter populations for clusters of various parameters, we take the 148 models from the \CMCcat\ and extract the initial conditions of all strong binary-single encounters that involve at least one luminous object (star, WD, or NS) and one compact object.
-These criteria on the constituents are applied in order to ensure that each encounter has a change of producing an observable object, and to focus on the effects COs have on this population.
+To establish realistic binary-single encounter populations for clusters of various parameters, we take the 148 models from the \CMCcat\ and extract the initial conditions of all strong binary-single encounters that involve at least one luminous object (star, WD, or NS; to limit the focus to encounters that can produce observable ejecta) and one CO.
 Over the entire catalog, our encounter sample makes up about half of all strong encounters that occur in the models, with each model contributing a few ten thousand BSCO encounters on average.
-We then realize each encounter in isolation with the same \fewbody\ package used in \CMC.
-We compute 10 realizations of each encounter, varying the encounter angles for each realization, to obtain a better statistical representation of the binary-single encounter population.
+We then realize each encounter in isolation with the same \fewbody\ package used in \CMC, computing 10 realizations of each encounter while re-drawing the randomly selected parameters (e.g.
+binary phase) to obtain a better statistical representation of the binary-single encounter population.
 
-The resulting objects that leave the cluster to become runaway or HVSs are identified as follows.
-To save computational resources, \fewbody\ terminates its integration once the relevant encounter products have positive energy and are moving away from one another.
-In other words, the encounters are terminated before the resulting objects are far from each other's gravitational influence.
+The resulting objects that leave the model to become runaway stars or HVSs are identified as follows.
+To save computational resources, \fewbody\ terminates its integration once the relevant encounter products have positive energy and are moving away from one another; this means that encounters are generally terminated before the resulting objects are far from each other's gravitational influence.
 To account for this, we calculate the final velocity of an object after an encounter $v_{\rm fin}$ as the hyperbolic excess velocity
@@
 
-{\color{blue} New version:
 The initial conditions used for these encounters are calculated in the center-of-mass rest frame of the encounter, i.e.
 they do not contain information about the center-of-mass velocity of the encounter in the frame of the GC model.
-We do not attempt to correct for this, which leads to an underestimation of final velocities for encountering objects and subsequently ejection rates; we justify this in Appendix \ref{app:restframe}.
-}
+We do not attempt to correct for this, which leads to a minor underestimation of final velocities for encountering objects and subsequently ejection rates; we justify this in Appendix \ref{app:restframe}.
 
-{\color{magenta} Old version:
-It is worth noting that the encounter initial conditions recorded in the \CMCcat\ contain velocities calculated in the center-of-mass frame of the encounter.
-A more rigorous calculation of $v_{\rm out}$ would utilize the velocity dispersion $\sigma$ to determine how $v_{\rm fin}$ translates to a velocity in the reference frame of the star cluster.
-Assuming that the distribution of the 3D object velocity $\vec{v}_{\rm fin}$ is independent of the center-of-mass velocity $\vec{v}_{\rm cm}$ of the encounter it originated from, we find that the average ratio of speed after to speed before the transformation to the cluster reference frame $v'_{\rm fin} / v_{\rm fin}$ is a maximum of $\sim$1.3 in the case $v_{\rm fin} \approx \sigma$, and a minimum of 1 in the case $v_{\rm fin} \gg \sigma$.
-As $v_{\rm cm} \sim \sigma$ and $\sigma \lesssim v_{\rm esc}$ \carl{I don't really follow this calculation; need to clarify it}, we estimate that neglecting a transformation to the cluster reference frame after center-of-mass encounter integration shrinks the resulting ejection population overall, but not in a manner that significantly affects the following analysis.
-}
+\section{GC dynamics and BSCO ejections} \label{sec:gcdyns}
 
-\section{Results} \label{sec:results}
+\subsection{GC core collapses} \label{subsec:cc}
 
-\subsection{GC dynamics and BSCO ejections} \label{subsec:gcdyns}
+Core collapse is a well-documented feature of GC evolution (e.g.
+\citealt{1968MNRAS.138..495L}, \citealt{2001A&A...375..711F}, \citealt{2006MNRAS.368..121F}, \citealt{2008gady.book.....B}, \citealt{2020IAUS..351..357K}), and as will be seen is a significant factor in the ejection of stars from these systems.
+In general, a core collapse occurs when gravitational potential energy is rapidly liberated from the central region of a GC through dynamical encounters, causing the core to contract while energizing and potentially expanding the surrounding envelope of stars.
+Binaries play an important role in these processes, as their formation and hardening through fewbody encounters accelerate the other interacting stars, which subsequently travel to the more extended regions of the GC and potentially escape it entirely.
+The first core collapse of a GC tends to be propagated by these dynamics, causing the GC to puff up over the following Gyrs as the central binaries continue to shrink and the stellar density increases.
 
-\subsubsection{GC core collapses} \label{subsubsec:cc}
+Mass segregation causes the core to be populated by the most massive objects in the GC, which also are those that first evolve into BHs.
+As the core contracts, successively stronger encounters eject all but a small handful of the initially 10s-100s of BHs; this reduced subsystem is unable to support the GC to the same extent as its predecessor, and so the interior of the GC contracts until a sufficiently strong replacement is composed.
+After \citet{2020IAUS..351..357K}, we employ this characteristic of BH ejection as a metric of whether a GC model has undergone this second kind of core collapse: once there are less than 10 BHs remaining in the model, we label it as core collapsed from that time onward.
 
-As the fewbody encounter rate is highly dependent on the density of stellar objects, we 
-The core collapses of star clusters due to dynamical heat flow from the center to the outer regions of a system are well-documented processes (e.g.
-\citealt{1968MNRAS.138..495L}, \citealt{2020IAUS..351..357K} \carl{steal a few more citations from the CMC code paper}).
-\carl{ the following text needs some clarification as well.
-Core collapse is a well-defined process that occurs even in equal-mass clusters.
-What you're trying to distinguish between is the first core collapse.
-Take a quick look at (and cite) the following papers (commented in the tex)}
-%https://ui.adsabs.harvard.edu/abs/2013MNRAS.432.2779B/abstract
-%https://ui.adsabs.harvard.edu/abs/2014MNRAS.445.3435H/abstract
-\carl{also distinguish everywhere between \texttt{Fewbody} the code (which should look like that) and fewbody gravitational encounters}
-One kind of core collapse occurs when the population of BHs in cluster (localized to the center via.
-mass segregation) is depleted through fewbody encounters in this region; the dynamically less energetic core is no longer able to fuel the dynamics of the rest of the cluster, and the cluster contracts.
-Many of these core encounters are between a binary and a single, contain compact objects, and can impart large accelerations on the participants, and accordingly are of particular interest here.
+\subsection{Ejections from individual clusters} \label{subsec:single_clusters}
 
-In this analysis, we label a cluster as core collapsed when its population of BHs has been reduced to less than 10 members \citep[following][]{2020IAUS..351..357K}.
-By this metric, 69 of the 148 \CMCcat\ models achieve core collapse by the end of the 14 Gyr integration time, and small cluster mass and size are good predictors of systems that evolve to this point the fastest \carl{add comparison to number of CC clusters in MW (count the number in the Harris catalog and cite it)}.
+The 148 \CMC\ models are designated by cluster initial size $N$ (number of stellar objects), initial virial radius $r_{\rm vir}$ (parsecs), distance from the galactic center $r_{\rm gc}$ (kiloparsecs, used in \CMC\ to calculate tidal effects from the galactic potential), and metallicity $Z$ (used to prescribe star evolution), with values chosen to span much of the MWGC parameter space; see \citet{2020IAUS..351..357K} for more details.
+To get a clear idea of how cluster evolution is linked to BSCO ejections, we examine four sample models; our base \CMCcat\ model has initial conditions
+\begin{itemize}
+    \item $N = 8 \times 10^5$
+    \item $r_{\rm vir} = 0.5~{\rm pc}$
+    \item $r_{\rm gc} = 8~{\rm kpc}$
+    \item $Z = 0.01Z_\odot$,
+\end{itemize}
+which, except for the compact virial radius, are near the typical values for the MWGC population (the small virial radius model is chosen for its shorter relaxation time, promising a greater dynamical age for a given physical time).
+Each of the other three sample models vary one of these parameters (either $N \to 4 \times 10^5$, $r_{\rm vir} \to 2~{\rm pc}$, or $Z \to Z_\odot$) to promote understanding of the effects of each.
 
-\subsubsection{Ejections from single clusters} \label{subsubsec:single_clusters}
-
-\carl{No need to announce what we're doing it, better to motivate why, e.g.: To get a clear idea of the production of HVSs from our clusters, we examine two representative cases with $N=10^8$ initial particles ( final masses of $\sim 2\times10^5M_{\odot}$, near the median of the GC mass function in the MW )}Here we study the BSCO ejections produced by individual \CMC\ cluster models.
-\CMC\ model N8e5\_rv0.5\_rg8\_Z0.0002 is taken as a sample as it represents a typical MW GC, and models N4e5\_rv0.5\_rg8\_Z0.0002, N8e5\_rv0.5\_rg8\_Z0.0002, and N8e5\_rv2\_rg8\_Z0.02 are included to examine the effects parameter variation has on the population of ejected objects.
-\carl{Wait, careful here.
-I'd say rv1 or rv2 is much more representative of MW clusters, rv0.5 is pretty compact (at least in terms of the clusters it produces).
-We want a rv0.5 and rv2 model to explore what core collapse looks like, but I'd use rv1 as the base model for futzing with the  metallicity}
-For simpler reference, we name the first sample model the ``base" model, and the remaining three the ``low-mass", ``bigger", and ``high-metallicity" models, respectively.
-
-What is immediately apparent from these single cluster models is a strong correlation between BSCO encounters and the evolution of the cluster core.
-Figure \ref{fig:cmc_single_clusters_vesc} plots the local escape velocities $v_{\rm esc}$\footnote{$v_{\rm esc}$ here is to be considered as a proxy for the distance from the center of the cluster.} at the location of all BSCO encounters from the four models, along with the central density $\rho_c$ \citep{1985ApJ...298...80C}, scaled to the initial density of the model $\rho_{c,0}$.
-Within any small interval of time, the respective BSCO encounters are well-localized around a particular escape velocity, indicating that throughout the evolution of the cluster contemporary encounters are similarly localized to the same cluster radii.
-Furthermore, the variation of this ``particular escape velocity" mimics the variation of the core density of the cluster.
-Naturally one would expect the densest part of a system to facilitate the highest rates of few-body encounters; in this case the dominance is extreme enough to characterize the encounter statistics as a whole.
-
-\carl{Ok, the particular escape velocity is almost certainly the escape speed from the core (or rather is limited by/slightly below it).
-let's try the following: you can calculate the central escape speed directly from the .dyn.dat file (it has central potential and potential at the tidal boundary, the difference of which gives you the central escape speed (well the energy needed to escape)).
-I think it might make more sense to try plotting that in each figure using the velocity ticks, eliminate the central density, then just have one small plot that compares rc,rh,rho, and central escape speed for one (or two) of the models (maybe the rv0.5 and rv2 models)}
-
-\carl{honestly, I think figures 2 and 3 are somewhat redundant; let's take a look at what happens if we put the central escape speed in figure 3, and making that our figure 2.
-Then we have a new figure 3 that is just the comparison beteween $v_{esc}$, rc, rho for the four models.}
-% figure 2 = escape velocity; figure 3 = scatterplots
-
-\begin{figure}
-    \script{cmc_single_clusters_vesc.py}
-    \centering
-    \includegraphics[width=0.49\textwidth]{figures/cmc_single_clusters_vesc.pdf}
-    \caption{
-        The local escape velocities $v_{\rm esc}$ of all BSCO encounters generated from the four sample \CMC\ models (colored points), plotted alongside the central density $\rho_c$ of the model (maroon), that latter of which is divided by the initial central density of the model.
-        See Figure \ref{fig:cmc_single_clusters} for an explanation of the color scheme.
-    }
-    \label{fig:cmc_single_clusters_vesc}
-\end{figure}
-
-Figure \ref{fig:cmc_single_clusters} shows the ejection velocity $v_{\rm out}$ for every MS star ejected via.
-a BSCO encounter in these clusters, plotted at the time of encounter since the cluster's formation $t$.
-By comparing the scatter plot to the evolution of the $N$-body core radius $r_{c, NB}$ \citep{1985ApJ...298...80C}, it is clear how the BSCO encounters and ejections are linked to the dynamical evolution of the cluste: whenever a cluster undergoes a core collapse, the heightened densities lead to predictably high encounter rates.
+Figure \ref{fig:cmc_single_clusters} shows the ejection velocity $v_{\rm out}$ for every MS star ejected via.~a BSCO encounter in these models, plotted at the time of encounter from initialization $t$.
+What is immediately apparent from these single cluster models is a strong correlation between BSCO encounters and the evolution of the cluster core: whenever a cluster undergoes a core collapse, the heightened densities lead to predictably high encounter rates.
 
@@
     \caption{
-        Scatter plots of the cluster ejection velocity $V_{rm out}$ versus encounter time $t$ for every escaping object from the integrated encounters for the four sample \CMC\ models (see the beginning of \S\ref{subsubsec:single_clusters} for details).
-        The histograms show the same data in 1D.
-        The different types of encounters are color-coded: encounters between a binary star and a CO are in red,
-        encounters between a mixed binary (1 star and 1 CO) and a CO are in blue, encounters between a mixed binary and a star are in yellow, and encounters between a CO binary and a star are in purple.
-        The $N$-body core radius $r_{c, NB}$ \citep{1985ApJ...298...80C} of the model is plotted in maroon over the timewise histogram.
+        Scatter plots of the cluster ejection velocity $v_{\rm out}$ versus encounter time $t$ for every escaping object from the integrated encounters for the four sample \CMC\ models (see the beginning of \S\ref{subsec:single_clusters} for details); the histograms show the distribution of velocities.
+        The points are color-coded by the kind of encounter they originated from: encounters between a binary star and a CO are in red, encounters between a mixed binary (1 star and 1 CO) and a CO are in blue, encounters between a mixed binary and a star are in yellow, and encounters between a CO binary and a star are in purple.
+        The core density (in code units) is plotted in above the scatter plot.
     }
@@
 An interplay between stellar evolution and cluster dynamics is revealed in the kinds of BSCO encounters that occur at certain times.
-The most massive stars in a cluster are both the first to form binaries and the first to evolve into COs; hence, in general encounters between a mixed binary (composed of a MS star and a CO) and a single MS star dominate the first generations of BSCO encounters.
-This dominance usually continues until the first core collapse after CO formation, where the heightened densities facilitate a rise in encounters involving 2 COs.
-There is a stark difference in the ejection velocities produced by these encounters in comparison to the previous mixed binary-single MS star encounters, and the fastest ejections over the cluster's lifetime are produced in the first tens of Myr after the associated core collapse.
+The most massive stars in a cluster are both the first to form binaries and the first to evolve into COs; hence, encounters between a mixed binary (composed of a MS star and a CO) and a single MS star tend to dominate the first generations of BSCO encounters.
+This dominance usually continues until the first core collapse after CO formation, where the heightened densities facilitate a rise in encounters involving multiple COs.
+There is a stark difference in the ejection velocities produced by these encounters in comparison to the previous mixed binary-single MS star encounters, and the fastest ejections over the cluster's lifetime are produced in the first tens of Myr after the associated ``first" core collapse.
 This regime lasts for a few to tens of Gyr, during which the COs in the core (predominantly BHs) preferentially form CO-CO binaries, as evidenced in the drop of mixed binary-single CO encounters during this phase.
 
-For cluster models that evolve to a BH-ejection core collapse (in our sample, all but the large model), the corresponding increase in BSCO encounters is dominated by stellar binary-single CO encounters.
-The coupling between core evolution and BSCO encounter localization appears to weaken in this phase, as the rapid increase(decrease) in core density(radius) does not translate to a similarly strong increase in escape velocity, though an increase still occurs (cf.
-Fig.
-\ref{fig:cmc_single_clusters_vesc}).
+For cluster models that evolve to BH-depletion ``second" core collapse (in our sample, all but the large model), the corresponding increase in BSCO encounters is dominated by stellar binary-single CO encounters.
 We also find that the majority of these encounters do not involve BHs, but rather WDs (or in some cases a NSs).
-These behaviors are consistent with the picture of the remaining COs migrating inwards to the core after the ejection of nearly all BHs.
+These behaviors are consistent with mass segregation, where it is only after the higher-mass BHs are ejected that these lower-mass COs can migrate into the core.
 
 This general evolution varies with model parameters, as can be observed by comparing different panels of Fig. \ref{fig:cmc_single_clusters}.
-The low-mass model lacks a core energetic enough to sustain a larger spatial profile, and the resulting strong contraction of the core leads to an ejection of 5\% of the cluster mass via BSCO encounters in the first 100 Myr.
-This model does reach a BH-ejection core collapse by the end of the integration time, but this collapse is slower than that for the base model.
+The $N = 4 \times 10^5$ model lacks a core energetic enough to sustain a larger spatial profile, and the resulting contraction of the core leads to an ejection of 5\% of the cluster mass via BSCO encounters in the first 100 Myr.
+This model does reach a BH-ejection core collapse by the end of the integration time, but this collapse is less pronounced than that for the base model.
 
-The bigger model evolves slower, and so it does not reach the same core collapse phase as the previous two.
+The $r_{\rm vir} = 2 {\rm pc}$ model evolves to ``first" core collapse later than the previous two, and noticeably lacks the pre-core collapse abundance of mixed binary-single star encounters seen above.
+When ``first" core collapse does occur, the distribution of encounters is similar to the respective distributions for the base model.
+
+The difference between the solar metallicity model and the others is striking.
+This model does not evolve to ``first" core collapse until $\sim$200 Myr (by far the latest out of the four), but still reaches ``second" core collapse near 7 Gyr.
+Furthermore, the lower stellar masses make the first core collapse much less severe, delaying the maximum ejecta production rate until the second core collapse; this rate increases roughly monotonically throughout the model's evolution.
+
+The $r_{\rm vir} = 2 pc$ model evolves slower, and so it does not reach the same core collapse phase as the previous two.
 The lower densities prevent the initial dominance of mixed binary-single star encounters, as the frequency of BSCO encounters is relatively low until the initial core collapse.
 On the other hand, this first core collapse is not associated with an abundance of BSCO encounters in the high-metallicity model, which sees a roughly monotonic rise in BSCO encounters throughout its evolution.
-% Talk to Carl about interpretation of high metallicity model
+
+The dominance of the core in overall BSCO encounter production is even more clear when considering the radial localization of the encounters.
+\CMC\ does not record the radius where each strong encounter occurred, but it does record the local escape velocity.
+For comparison, the escape velocity from the center of the model can be computed from the central and tidal boundary potentials, which are recorded throughout the evolution of the cluster.\footnote{These potentials can be found in the standard \CMC\ output file \texttt{initial.esc.dat}, which records data pertaining to stars that become unbound to the model for any reason.
+The escape rate is high enough that the time domain is well-resolved by these data.}
+Figure \ref{fig:cmc_single_clusters_vesc} plots these data for the same sample clusters, where the distribution of encounter escape velocities is strikingly correlated to the central escape velocity, indicating the degree to which the core dominates these dynamics.
+
+\begin{figure}
+    \script{cmc_single_clusters_vesc.py}
+    \centering
+    \includegraphics[width=0.49\textwidth]{figures/cmc_single_clusters_vesc.pdf}
+    \caption{
+        The local escape velocities $v_{\rm esc}$ of all BSCO encounters generated from the four sample \CMC\ models (colored points), plotted alongside the central escape velocity of the model (maroon).
+        See Figure \ref{fig:cmc_single_clusters} for an explanation of the color scheme.
+    }
+    \label{fig:cmc_single_clusters_vesc}
+\end{figure}
 
@@
 The number of \CMC\ models corresponding to each parameter value varies, and so each histogram is averaged over the respective models, in addition to being divided by the factor of 10 in encounter multiplication.
-The travel distances $d$ are the distances an object would move in a straight line between ejection and the present day, that is, the product of the ejection velocity and the time interval between the time of ejection and 14 Gyr.
 It is worth noting the prominence of the $N = 4\times10^5$, $r_{\rm vir} = 0.5$ pc, $Z = 0.0002$ models in these averaged histograms: they are the cause of the peaks above the other distributions, as the three (one for each value of $r_{\rm gc} \in \{2, 8, 20\}$ kpc) produce significantly more ejections than the other models ($\sim$2.9, 2.0, and $1.4 \times 10^4$, respectively, versus the average number of $1-2 \times 10^3$ for the catalog).
-
-% Play with this figure placement after text is done:
-%   figure* will let it span over both columns
-%   placing the \fig commands in the same gridline will place them in the same horizontal row
 
@@
         Histograms for all MS stars ejected from the \CMCcat\ models as a result of BSCO encounters.
-        The three columns display the cluster ejection velocities $v_{\rm out}$, the present-day straight-line travel distances $d$, and the masses $m$ of the ejected objects, respectively.
-        Each row divides the data across the values for the \CMC\ model parameters size $N$ (number of objects), initial virial radius $r_{\rm vir}$ (parsecs), or metallicity $Z$.
-        Each histogram is averaged over all models computed with the respective model parameter.
-        In the right column (the mass plots), the data are further divided by whether the ejection occurred before or after the BH-ejection core collapse of the cluster, if one occurred within the integration time.
+        The top (bottom) row displays the distribution of ejection velocities from the models $v_{\rm out}$ (masses $m$ of the ejected objects).
+        Each each separates the data by different \CMC\ model parameters: either size $N$ (number of objects), initial virial radius $r_{\rm vir}$ (parsecs), or metallicity $Z$.
+        Each histogram is averaged over all models computed with the respective value of model parameter.
+        In the the mass histograms, the data are further divided by whether the ejection occurred before or after the ``second," BH-depletion core collapse of the cluster, if one occurred within the integration time.
     }
@@
 
-Acknowledging these especially fecund models, predicable trends are visible in these histograms: increasing mass and decreasing size are both associated with higher ejection velocities and accordingly higher travel distances.
-However, while the smallest clusters produce the most ejections, the most massive clusters produce the \textit{fewest} ejections.
-The $N = 4 \times 10^5$ models consistently produce the most ejections in comparison with otherwise identical models of different population sizes, suggesting that at this mass there are not enough massive objects to prevent a severe initial core collapse through binary burning, but there are enough to facilitate a high number of BSCO encounters (the number of few-body encounters in general is also maximized in the $N = 4 \times 10^5$ models).
+Acknowledging these especially fecund models, predicable trends are visible in these histograms: increasing mass and decreasing size are both associated with higher ejection velocities.
+However, while the number of ejections increases as the models become more compact, increasing the number of particles/mass of the model leads to a slight \textit{decrease} in ejecta.
+The $N = 4 \times 10^5$ models consistently produce the most ejections in comparison with otherwise identical models of different population sizes, suggesting that at this mass there are not enough massive objects to prevent a severe initial core collapse through binary burning, but there are enough to facilitate a high number of BSCO encounters (the number of fewbody encounters in general is also maximized in the $N = 4 \times 10^5$ models).
 
 The most noticeable distinction among models of different metallicities is the number of ejections, which decreases with increasing metallicity.
-This is understandable, as higher metallicities lead to lower-mass objects, which in turn lead to weaker few-body encounters.
-This has a slight effect on the mass spectrum of ejected objects above 1 $M_\odot$, but a much stronger one for the objects below this cutoff mass.
-Tthe different metallicity-binned models diverge significantly, and only in the ejections that occur before the BH-ejection core collapse of the model.
-This same phenomenon is visible in Fig. \ref{fig:cmc_single_clusters}, wherein it was previously noted that the high-metallicity model did not produce many ejections during its initial core collapse.
-The low-metallicity model is able to produce many ejections primarily because of the higher stellar masses, which lead to a greater population of black holes in number and average mass, enabling stronger dynamics.
-%because 1) its core collapse is deeper, and 2) there are roughly $1.2 \times$ as many BHs present at core collapse, and 3) the BHs in the low-metallicity model are up to $2 \times$ as massive as those in the high-metallicity model.
+This is understandable, as in practice the lower metallicity models have greater BH populations than the higher metallicity models; quantitatively, the 1\% solar models have about $1.2 \times$ as many BHs at the time of ``first" core collapse as the solar models, and maximum BH masses about $2 \times$ those of the same.
+This weakens BSCO dynamics before and during ``first" core collapse, as was first made visible in Figure \ref{fig:cmc_single_clusters}.
+Because this effect takes place in the earlier stages of model evolution - namely, when mass segregation has had less time to separate lighter objects from the strong dynamics of heavier objects - this has the most significant effect of reducing the number of ejecta with $m < M_\odot$.
+Notably, the different metallicity models have quite similar ejecta mass distributions after ``second" core collapse, as the effect of metallicity on the masses of the remaining WDs and NSs is much less pronounced than on the now-ejected BHs.
 
-\subsection{Estimating a MW-like population} \label{subsec:est_MW-like}
+\section{A MW-like population of BSCO ejecta} \label{sec:est_MW-like}
 
 In the interest of predicting realistic statistics and rates for a MW-like GC population, we seek to assemble a synthetic MW-like population of GC-runaways from BSCO encounters.
-The two steps involved here are 1) selecting representative \CMC\ models for galactic GCs, and 2) integrating the post-ejection orbits to the present day in the context of the MW.
+The two steps involved here are 1) selecting representative \CMC\ models for galactic GCs, and 2) integrating the post-ejection orbits in the context of the MW to produce a present-day picture.
 
-\subsubsection{Pairing \CMC\ models to MW GCs} \label{subsubsec:pairing}
-% Plot idea: the log(M) vs. rr vs. r_hm diagnostic plots in gcs_mw-cmc.ipynb, with top/bottom//left/right axes showing the physical and normalized values of each variable
+\subsection{Pairing \CMC\ models to MWGCs} \label{subsec:pairing}
 
-The 148 \CMC\ models are designated by cluster initial size $N$ (number of stellar objects), initial virial radius $r_{\rm vir}$ (parsecs), distance from the galactic center $r_{\rm gc}$ (kiloparsecs, used in \CMC\ to calculate tidal effects from the galactic potential), and metallicity $Z$ (used to prescribe star evolution), with values chosen to span much of the MW GC parameter space; see \citet{2020IAUS..351..357K} for more details.
-\carl{As an example, model...
-represents a cluster...}
+We predominantly use the observational catalog of \citet{2018MNRAS.478.1520B} to obtain parameters for MWGCs.
+This catalog lacks metallicity measurements for the objects; therefore we supplement with that of \citet{2010arXiv1012.3224H}.
+12 of the GCs in the former catalog do not have metallicity measurements in the latter, leaving us with the 149 MWGCs we use in this analysis.
 
-We predominantly use the observational catalog of \citet{2018MNRAS.478.1520B} to obtain parameters for MW GCs.
-This catalog lacks metallicity measurements for the objects; therefore we supplement with that of \citet{2010arXiv1012.3224H}.
-12 of the GCs in the former catalog do not have metallicity measurements in the latter, leaving us with the 149 MW GCs we use in this analysis.
+Assigning a representative model to each MWGC is nontrivial.
+While many GCs are expected to be older than 12 Gyr, some could be as young as 9 Gyr \citep{2013ApJ...775..134V}; to reflect this, we find 11 timesteps as evenly spaced as possible between 10 and 13.5 Gyr for each \CMC\ model, yielding a set of model snapshots spanning the different \CMC\ initial conditions and sampling the models at different evolutionary stages.
 
-We choose a representative \CMC\ model for each MW GC in the following manner.
-For each GC \carl{model}, \sout{after} \carl{following} \citet{2021ApJ...912..102R} we first find the values of $r_{\rm gc}$ and $Z$ in the \CMCcat\ model grid closest to the measurements of these parameters for the GC (in linear and log space, respectively) and select the models with the respective values as candidate representatives.
-We choose 11 linearly spaced times between 10 and 13.5 Gyr (c.f.
-\citet{2013ApJ...775..134V}), and find the \CMC\ timesteps closest to the chosen times for the candidate models.
-\carl{wait, are the ages for the clusters specified in the Baumgardt catalog?
-Where are those coming from}
-The MW GCs and the \CMC\ models are shown in Figure \ref{fig:cmcs-mwgcs_scatter}.
+These snapshots are plotted with our composite catalog of MWGCs in Figure \ref{fig:cmcs-mwgcs_scatter}.
+The upper plot shows the models/GCs in $r_{\rm gc}$ - [Fe/H] space; note the discretization of the \CMC\ models, as the respective parameters are held constant over integration, and so each blue point represents the $\sim 15$ \CMC\ models that are initiated with those particular values.
+When choosing a representative snapshot for each GC, we effectively follow \citet{2021ApJ...912..102R} by first finding the blue point closest to the GC in this space and constrain our search to the respective snapshots.
 
-\carl{Once we have identified a cluster time, metallicity, and galactocentric distance, we identify a single} representative model by finding the timestep closest to the MW GC in normalized $\log M$-$r_c / r_h$ space by Euclidean distance.
-\carl{be careful to specific MW or model GC when saying GC here.}
-We choose these parameters as in this context of GC population synthesis they are reasonable proxies for respectively the scale and evolutionary state of the cluster.
-We use the 3D half-mass radius for $r_h$, \carl{cite the specific baumgardt paper here; 3d half-mass radius is a pretty odd thing to get from a catalog so people may be confused} and the definition of core radius from \citet{1987degc.book.....S}:
+Having constrained the snapshots by $r_{\rm gc}$ and metallicity, we then choose one of an appropriate size and evolutionary state by comparing the snapshots with the model in normalized $\log M$ - $r_c / r_h$ space, where $M$ is the mass of the cluster in $M_\odot$, $r_c$ is the Spitzer core radius \citep{1987degc.book.....S}
 \begin{equation}
@@
 \end{equation}
-where $\sigma_c$ is the central velocity dispersion and $\rho_c$ is the central density for the cluster \carl{make sure we're using the same core radius definition too}.
-We normalize the two dimensions in the \CMC\ space, i.e.~the parameters actually used to compute the distance are
+(where $\sigma_c$ is the central velocity dispersion and $\rho_c$ is the central density) and $r_h$ is the 3D half-mass radius of the snapshot (the latter two parameters are used because both are immediately accessible in the \citet{2018MNRAS.478.1520B} catalog and standard \CMC\ output).
+The models and GCs are plotted in the non-normalized space of these parameters in the bottom plot of Figure \ref{fig:cmcs-mwgcs_scatter}.
+The transformation to the normalized space is simply
 \begin{equation}
@@
 \end{equation}
-where $\bar{x}_{\rm CMC}$ and $\sigma_{\rm x,CMC}$ are respectively the mean and standard deviation of the parameter $x$ over the total set of \CMC\ models.
-\carl{this should go above where you're describing finding the closest model}
+where $\bar{x}_{\rm CMC}$ and $\sigma_{\rm x,CMC}$ are respectively the mean and standard deviation of the parameter $x$ over the complete set of \CMC\ snapshots.
+The snapshot from the $r_{\rm gc}$ - [Fe/H] subset that is closest to the MWGC in the normalized $\log M$ - $r_c / r_h$ space is chosen to represent the GC; as an example, 47 Tuc ($r_{\rm gc} = 7.52$ kpc, $Z = 0.0019$; $\log M = 5.95$, $r_c / r_h,m = 0.125$) is represented by a snapshot from model \texttt{N1.6e6\_rv2\_rg8\_Z0.002}, which at the 10.8 Gyr time of the snapshot has $\log M = 5.91$ and $r_c / r_h = 0.126$.
 
@@
         The clusters and models used in this work.
-        Galactic GCs are represented by black triangles, and CMC models by blue dots.
-        %The sample \CMC\ models used in \S\ref{subsec:single_clusters} are shown as blue stars.
-        %M3 and its \CMC\ counterpart relevant to \S\ref{} are shown as purple triangles.
-        Cluster mass $M_{\rm cluster}$ is shown on the $y$-axis, and the core radius/half-mass radius ratio $r_c/r_h$ (metallicity $[{\rm Fe/H}]$) on the left (right) $x$-axis.
-\carl{need to distinguish between top and bottom.
-Also I would say "vertical and horizontal" more than x and y, or better yet just say "plot this v that".
-Also don't need units of dex for metallicity (that's common enough to be understood)}
+        Galactic GCs are represented by black triangles, and CMC model snapshots by blue dots.
+        The top (bottom) plot shows the systems in $r_{\rm gc}$ v. [Fe/H] ($\log M$ v. $r_c / r_h$) space.
         }
@@
 
-While the \CMCcat\ has fairly representative models for most of the MW GCs, there are a number of larger-cored GCs (right side of the left pane of Figure \ref{fig:cmcs-mwgcs_scatter}) that are relatively distant from the nearest \CMC\ model; in practice, this means that a single \CMC\ model can be chosen to represent a disproportionate number of MW GCs.
-Our pairing algorithm ends up using 57 of the 148 \CMC\ models to build the sythetic population, and the most utilized model is matched to 14 MWGCs, or $\lesssim10\%$ of the population.
-The most used models are typical in terms of number of ejections and cluster evolution, and so while the more extreme GCs might be misrepresented, they are being represented by average models nonetheless.
+While the \CMCcat\ has fairly representative models for most of the MWGCs, there are a number of larger-cored GCs (right side of the bottom plot of Figure \ref{fig:cmcs-mwgcs_scatter}) that are relatively distant from the nearest \CMC\ model; in practice, this means that a single \CMC\ model can be used to represent several MWGCs.
+In practice, we find that the models that are chosen for several MWGCs are average models for the \CMCcat, and so we expect that while characteristics of more extreme GCs are not necessarily well-represented, they are replaced by typical models nonetheless.
 
-\subsubsection{Integrating runaways to the present day} \label{subsubsec:galpy}
+\subsection{Integrating runaways to the present day} \label{subsec:galpy}
 
-We now produce a present-day picture of these runaways by evolving their trajectories to the present day, using \texttt{galpy}\footnote{http://github.com/jobovy/galpy} \citep{2015ApJS..216...29B} to perform the necessary integrations.
-For each MW GC, we consider the matched \CMC\ model timestep as the present-day representation of the system, and pair it with the present-day orbital position and velocity from \citet{2018MNRAS.478.1520B}.
-We integrate the orbit backwards through time, and place the ejected objects at the appropriate times in the trajectory.
-The ejection velocity $v_{\rm out}$ from the model is assigned a random direction and boosted to the galactic rest frame, and this trajectory is evolved to the present day.
+Having chosen representative snapshots for all MWGCs, we now use our synthetic ejecta populations to compose a MW-like population of BSCO ejecta from GCs.
+All orbit integrations in the galactic frame are done with \texttt{galpy}\footnote{http://github.com/jobovy/galpy} \citep{2015ApJS..216...29B}.
 
-\subsection{Galactic population} \label{subsec:res_MW-like}
-
-We now consider the MW-like population of BSCO runaways, assembled from the \CMCcat\ models as described in section \S\ref{subsec:est_MW-like}.
-
-Figure \ref{fig:encio_stackedbar} shows the encounter types and results for BSCO encounters from a MW-like population of GCs, with the top plot including all encounters and the bottom including only those that result in an ejection.
-The majority of BSCO encounters are between a mixed binary and a star, and the bulk of the remaining encounters involve two COs.
-Interactions between COs and stellar binaries are relatively rare, and mostly occur after a secondary core collapse in which COs (esp.
-BHs) are ejected from the cluster core (c.f.
-Fig.
-\ref{fig:cmc_single_clusters}).
-
-%\begin{figure}
-%    %\scripts{encio_stackebar.py}
-%    \centering
-%    \includegraphics[width=0.49\textwidth]{encio_stackedbar_catalog_wmw_dej.pdf}
-%    \caption{
-%        Results of all BSCO encounters from the MW-weighted cluster population.
-%        The x-axis shows the encounter type, the colors denote the result of the encounter, and the color saturation and hatch indicates whether the encounter ejected an object from the host cluster or not.
-%        The black percentages show what part of the encounter type bar is filled by the respective result.
-%    }
-%    \label{fig:encio_stackedbar}
-%\end{figure}
-
-Of all BSCO encounters in our synthetic MW population, $\sim3\%$ eject at least one of the interacting bodies out of the host cluster.
-Most star-ejecting encounters are between a single star and a binary.
-In comparison, when a CO interacts with a binary containing at least one star, generally the star remains in the binary, and when the star is ejected from the binary it is more likely for all three objects to depart as singles with smaller velocities than for a single star to carry away enough of the encounter's energy to overcome the local escape velocity (c.f.
-\citet{1983ApJ...268..319H}).
-We conclude that the most characteristic star-ejecting BSCO encounters in the galaxy (in terms of maximum velocities and abundance) occur shortly after the formations of COs and multiple-CO systems, the latter of which we have demonstrated is strongly linked to the core collapse timescale of galactic GCs.
+Setting the snapshot to the present-day galactic orbital parameters from \citet{2018MNRAS.478.1520B}, we back-integrate the orbit of each GC in the \texttt{galpy}\texttt{MWPotential2014} potential to the initialization time of the respective model.
+We then locate each ejected object at the appropriate place in the GC orbit, using the time of BSCO encounter (naturally ignoring any ejections that occurred after the time of the chosen snapshot).
+A random ejection direction is chosen in the GC rest frame for each object, and the velocities are then transformed to the galactic rest frame.
+Finally, the orbits of all ejecta are then integrated to the present day in the same galactic potential.
 
@@
     \caption{
-        Plots showing the back-integrated orbits for some MW GCs, and the points in the orbit where an object is ejected from the GC.
-        The color scale of the points indicates the time of ejection, measured backward from the present day; from the partial monochromism of the data and the density of points for portions of the orbit it can be seen how the ejections are more concentrated earlier in the cluster's evolution and farther away from the galactic center.
+        Plots showing the back-integrated orbits for some sample MWGCs (gray curves), and the points in the orbit where an object is ejected from the GC (scatter points).
+        The color scale communicates the mass of the ejected star.
+        The concentration of ejections in the first few orbits is clear, and an increased density of ejections when clusters are farther away from the galactic center is visible as well.
+        Viewing the figure electronically makes it easier to find the few high-mass ejecta amid the abundance of lower mass objects.
     }
@@
 
-The present-day sythetic populations of runaways for the same sample CMC/GC pairings are shown in Figure \ref{fig:gcej_today}.
+The present-day synthetic populations of runaways for the same sample CMC/GC pairings are shown in Figure \ref{fig:gcej_today}.
 While it is clear how the GC orbits influence the distribution of ejected objects, the ejecta wander to a broad enough spread that any one object loses some of the information of its cluster of origin by the present day.
 The proper motion distribution is less affected in this way (especially for more circular GC orbits), which is coherent with previous works that use these velocities to study the origins of such objects.
-What is important to note here is that the current proper motion of the cluster is not necessarily the best locus to use when comparing stellar proper motions: a well-informed back-integration of the orbit can reveal the average proper motion of the cluster, which may be distiguishable from its present-day proper motion.
+What is important to note here is that the current proper motion of the cluster is not necessarily the best locus to use when comparing stellar proper motions: a well-informed back-integration of the orbit can reveal the average proper motion of the cluster, which may be distinguishable from its present-day proper motion.
+We include histograms, and 50\% and 90\% credible regions in sky area and proper motion space as a product of this work, for use as evidence when assigning runaway stars to GC origins; see Appendix \ref{app:credreg} for a description of these products.
 
@@
     \gridline{
-        \fig{figures/gcej_today_NGC_104.pdf}{0.49\textwidth}{}
-        \fig{figures/gcej_today_NGC_5139.pdf}{0.49\textwidth}{}
+        \fig{figures/gcej_today_NGC_104.pdf}{0.45\textwidth}{}
+        \fig{figures/gcej_today_NGC_5139.pdf}{0.45\textwidth}{}
     }
     \gridline{
-        \fig{figures/gcej_today_NGC_6205.pdf}{0.49\textwidth}{}
-        \fig{figures/gcej_today_NGC_7089.pdf}{0.49\textwidth}{}
+        \fig{figures/gcej_today_NGC_6205.pdf}{0.45\textwidth}{}
+        \fig{figures/gcej_today_NGC_7089.pdf}{0.45\textwidth}{}
     }
@@
         Present-day positions (galactic longitude/latitude) and velocities (projected onto the galactic longitude/latitude directions) for the runaway objects from the sample GCs.
-        The color scale again denotes the time of ejection.
-        The back-integrated orbits are shown as the light gray trajectories, and the blue "x" is the position/velocity of the GC as measured by \citet{2018MNRAS.478.1520B}.
-        The set of sythetic ejecta shown here is the result of downsampling the total set by a factor of ten, to account for the repeated-realizations method described in \S\ref{subsec:binsingle_pop}
+        The color scale is the same as in Figure \ref{fig:gc_orbit_ejections}, depicting the eject masses.
+        The back-integrated orbits are shown as the gray trajectories, and the blue "x" is the position/velocity of the GC as measured by \citet{2018MNRAS.478.1520B}.
+        The set of synthetic ejecta shown here is the result of downsampling the total set by a factor of ten, to account for the repeated-realizations method described in \S\ref{sec:methods}. 
     }
@@
 Few runaways make it past the $\sim$100 pc mark, but those that do naturally retain the highest velocities, reaching upwards of 1000~\kms.
-% So this indicates that hypervelocity stars are likely to come from other sources, since the fastest BSCO runaways will have had plenty of time to leave the galaxy?
 
-% Combine these plots into 2x2 grid (hists. on top, either column: r or Z)
-% Make the same plots for all ejecta w/ v_rf > 275?
-% Change the plots to be based on v_rf instead of v_esc?
 \begin{figure*}
@@
 
-One final result of note is that of the heliocentric radial velocity $v_{\rm rf}$ distribution of the synthetic population.
+One result of note is that of the heliocentric radial velocity $v_{\rm rf}$ distribution of the synthetic population.
 \citet{2021arXiv211213864G} in part studied the galactic center origin of HVSs, and found that there is an apparent tension between the observed and predicted runaway populations; specifically, the predicted number of stars with velocities $\gtrsim 700~{\rm km~s^{-1}}$ was much higher than the observed rate from the HVS sample of \citet{2018ApJ...866...39B}.
-The same work found that a decreasing star formation rate over last millions of years would reduce the recent (and thus more likely to be observed) HVS production rate enough to overcome the discrepency.
-GCs natural follow this pattern (c.f.
-S\ref{subsec:single_clusters}), as the BSCO runaways studied here are produced at much higher rates when the models are young, and few HVSs are produced in the later stages of the cluster.
+The same work found that a decreasing star formation rate over last millions of years would reduce the recent (and thus more likely to be observed) HVS production rate enough to overcome the discrepancy.
+GCs naturally follow this pattern (c.f.
+\S\ref{sec:gcdyns}), as the BSCO runaways studied here are produced at much higher rates when the models are young, and few HVSs are produced in the later stages of the cluster.
 The resulting $v_{\rm rf}$ distribution is much closer to the observed distribution than that for the galactic center origin case, albeit skewed towards slightly smaller velocities (Figure \ref{fig:cmc_orbits_cdf}).
@@
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/cmc_orbits_cdf_S.pdf}
+        \includegraphics[width=0.99\linewidth]{figures/cmc_orbits_cdf_S.pdf}
         \caption{
@@
 
-Figure \ref{fig:mwej_rates} shows the rate of HVS/runaway production for our sythetic population, along with some base values from the literature.
+Figure \ref{fig:mwej_rates} shows the rate of HVS/runaway production for our synthetic population, along with some base values from the literature.
 In both cases, the GC ejection rate is smaller than the observed rate, especially at the present day.
@@
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/mwej_rates.pdf}
+        \includegraphics[width=0.99\linewidth]{figures/mwej_rates.pdf}
         \caption{
-            The ejection rate for the synthetic MW GC population.
+            The ejection rate for the synthetic MWGC population.
             The red dashed line represents the HVS rate for the galactic center, and the blue dashed line the runaway rate for the disk proposed by \citep{2015ARA&A..53...15B}.
@@
 
-% \begin{equation}
-%     R_{GC,ej}
-%     \sim \frac{\sum_i N_{MW,i} \frac{N_{ej,i}}{10}}{13.8~{\rm Gyr}}
-%     \approx 0.02~{\rm Gyr}^{-1},
-% \end{equation}
-% where $i$ indexes over the \CMC\ models, $N_{MW,i}$ is the number of MW GCs that have the $i^{th}$ model as their nearest \CMC\ neighbor, and $N_{ej,i}$ is the number of single objects from the integrated encounters with a hyperbolic excess velocity greater than the local GC escape speed for the $i^{th}$ model (the division by 10 accounts for the multiplication of encounters described in section \ref{sec:methods}).
-
-% \subsubsection{Ejection velocities}
-%
-% Of the 148 clusters, 51 clusters have a maximum ejection velocity $v_{\rm out,max}>1000~{\rm km~s}^{-1}$, 23 clusters with $v_{\rm out,max}>1500~{\rm km~s}^{-1}$, and 3 clusters with $v_{\rm out,max}>2000~{\rm km~s}^{-1}$.
-% The fastest ejection velocity is found in the realizations of the $N=8\times10^5,\ r_{\rm vir}=0.5~{\rm pc},\ r_{\rm gc}=20~{\rm kpc}, Z=0.01~Z_\odot$ cluster, where a single $31~M_\odot$ mass BH replaces a $0.15~M_\odot$ mass star in a binary with a $69~M_\odot$ mass BH to accelerate the star to a speed of $\sim$2160~\kms.
-% This is noticeably greater than the surface escape velocity of a 69~$M_\odot$ star ($\sim$1500~\kms, assuming a radius of $R_*\approx12~R_\odot$), the theoretical limit given by the method of \citet{1991AJ....101..562L}.
-
 \section{Discussion \& Conclusions} \label{sec:disccon}
@@
 We composed a synthetic MW-like population of ejecta by matching observed GCs to realistic $N$-body models of these systems and embedding the models in the orbits of their real counterparts.
-In particular we considered binary-single encounters involving at least one compact object; this selection retained about half of all fewbody encounters in the catalog of models.
+In particular we considered binary-single encounters involving at least one compact object; this selection includes about half of all fewbody encounters in the catalog of models.
 
-BSCO ejections were found to be closely linked to the dynamics of the cluster core, where the closest encounters among the densest stellar objects occur.
+BSCO ejections were found to be closely linked to the evolution of the cluster core, where the closest encounters among the densest stellar objects occur.
 GCs lose mass, and generally expand as they evolve; accordingly, the majority of and the fastest BSCO ejecta were produced in the early stages of the models.
 High-metallicity models had overall weaker ejection mechanisms (in frequency and maximum velocity), due to smaller stellar masses.
-BSCO encounters occurring in realistic GCs are capable of accelerating stars to velocities in excess of 2000 \kms, which means that this source of runaways cannot be entirely ruled out by a simple velocity cut.
-We also note that these velocities appear to pass the speed limit on star-only fewbody encounters set by \citet{1991AJ....101..562L}; further study is needed to confirm if this is cause by the inclusion of compact objects or another factor.
+BSCO encounters occurring in realistic GCs are capable of accelerating stars to velocities in excess of 2000 \kms, which complicates the identification of ejection mechanisms for HVSs when their origins are not easily recognizable.
+We also note that these velocities appear to pass the speed limit on star-only fewbody encounters found by \citet{1991AJ....101..562L}; further study is warranted to study how compact object fewbody dynamics differ from those of objects with a significant physical size.
 
-While ejected objects evolve to be largly indistinguishable from other MW stars in terms of position, they were found capable of retaining some information about the motion of their GC of origin, particularly in the case of GCs with near-circular orbits.
+While ejected objects evolve to be largely indistinguishable from other MW stars in terms of position, they were found capable of retaining some information about the motion of their GC of origin, particularly in the case of GCs with near-circular orbits.
 The overall population of ejecta was usually concentrated around the average proper motion of the GC throughout its orbit.
-It is important to realize that the present-day proper motion of a GC may not reflect this average proper motion, and that in general a better kinematic picture is possible if the orbit is back-integrated.
+It is important to recognize that the present-day proper motion of a GC may not reflect this average proper motion, and that in general a better kinematic picture is accessible through back-integration of the orbit.
 
-In the galactic context, the velocity distribution of the synthetic ejecta was found to be similar to that of HVS observations at relatively low velocities; specifically, out population was skewed towards these velocities with respect to observations.
-With galactic-center origin studies finding distributions skewed towards higher velocities in the same respect, it is possible that a mixture of the two could be used to more accurately model the real population of these objects.
-Such a calculation must be done in light of the relative rates of the two mechanisms: our study concludes that the GC BSCO runaway rate might have been a few 10\% of the overall rate in the first few Gyr of the universe, but today is no more than 10\%.
+In the galactic context, the velocity distribution of the synthetic ejecta was found to be similar to that of HVS observations at relatively low velocities; specifically, our population was skewed towards these velocities with respect to observations.
+With galactic-center origin studies finding distributions skewed towards higher velocities in the same respect \citet{2018ApJ...866...39B}, it is possible that a mixture of the two could be used to more accurately model the real population of these objects.
+Such a calculation must be done in light of the relative rates of the two mechanisms: our study concludes that while the GC BSCO runaway rate might have been a few 10\% of the overall rate in the first few Gyr of the universe, in the present day it is likely no more than 10\% of the same.
 
@@
 
+\section{Velocities in encounter rest frames versus the GC rest frame} \label{app:restframe}
+
+We justify here our claim that in neglecting the transformation from the encounter rest frame to the GC model rest frame we obtain slower - and subsequently fewer - ejections.
+
+H\'enon's Monte Carlo method tracks the dynamical state of objects by their energy and angular momentum, which makes the technique inherently spherically symmetric.
+When drawing a radial and tangential velocity from an object's orbit, the sign of the radial velocity is randomly chosen as positive or negative with equal weighting, and when setting up a fewbody encounter an angle $0 \le \phi \le 2\pi$ between the tangential velocities of the two objects is chosen from a uniform distribution.
+These two features ensure isotropy of either velocity with respect to the other, and of the center-of-mass velocity of the encounter with respect to the GC model rest frame $\vec{v}_{\rm cm|GC}$.
+Note that the speed $v_{\rm cm|GC}$ cannot be greater than the maximum speed between the two objects.
+
+If we assume that the direction of the post-encounter object velocity in the center-of-mass rest frame $\vec{v}_{\rm f|cm}$ is isotropic with respect to $\vec{v}_{\rm cm|GC}$, then the average speed after boosting back to the model rest frame is
+\begin{equation}
+    \langle v_{\rm f|GC} \rangle
+    = \int_0^{2\pi} \frac{d\phi}{2\pi} \sqrt{(v_{\rm f|cm} + v_{\rm cm} \cos \phi)^2 + (v_{\rm cm} \sin \phi)^2}.
+\end{equation}
+Naturally, for $v_{\rm cm|GC} \ll v_{\rm f|cm}$ this average post-boost speed approaches $v_{\rm f|cm}$, and in the limit $v_{\rm cm|GC} \gg v_{\rm f|cm}$ it approaches $v_{\rm cm|GC}$, which recall must be less than the initial speed of the other object in the encounter: in either of these cases, the speed augmentation caused by the boost does not favor faster or slower post-encounter velocities.
+The maximum average ``acceleration" resulting from the boost occurs at the limit $v_{\rm cm|GC} = v_{\rm f|cm}$, where $\langle v_{\rm f|GC} \rangle \sim 1.3 v_{\rm f|cm} = 1.3 v_{\rm cm|GC}$.
+
+The assumption of isotropy in calculating $\langle v_{\rm f|GC} \rangle$ is appropriate for resonant encounters wherein the dynamics are chaotic.
+For flyby encounters where the objects travel on roughly hyperbolic trajectories, there is a preference for post-encounter velocities in the same direction as the initial velocity, if the impact parameter distribution is sufficiently expansive and weighted by the square of the parameter and the final velocities are marginalized over the angle that orients the plane of the ``2-body" encounter.
+The isotropic case is therefore a conservative limit on this flyby case, and predicts a greater boost-propagated speedup than if the calculation was done in full detail.
+
+In summary, neglecting to return to the model rest frame after the \fewbody\ step for strong encounters is found to not favor faster or slower post-encounter speeds when the final speed of an object is much greater than or much less than the center-of-mass speed of the encounter.
+There is an average speedup of 30\% when the two speeds are comparable, but this latter condition means that the speeds themselves are less than the maximum initial speed between the objects, which limits the extent to which the boost itself reveals speeds in excess of the escape velocity.
+
 \section{Ejecta credible regions} \label{app:credreg}
 
-We include with this publication phase credible regions in phase space for ejecta populations from the MW GCs considered, which may be accessed at [LINK].
+We include with this publication phase credible regions in phase space for ejecta populations from the MWGCs considered, which may be accessed at [LINK].
 We intend these constructions to be used as secondary evidence for cluster membership of runaway stars, and to encourage further studies into understanding the respective phase space distributions.
@@
 
-\section{Velocities in encounter rest frames versus the GC rest frame} \label{app:restframe}
-
-We justify here our claim that in neglecting the transformation from the encounter rest frame to the GC model rest frame we obtain slower - and subsequently fewer - ejections.
-
-H\'enon's Monte Carlo method tracks the dynamical state of objects by their energy and angular momentum, which makes the technique inherently spherically symmetric.
-When drawing a radial and tangential velocity from an object's orbit, the sign of the radial velocity is randomly chosen as positive or negative with equal weighting, and when setting up a fewbody encounter an angle $0 \le \phi \le 2\pi$ between the tangential velocities of the two objects is chosen from a uniform distribution.
-These two features ensure isotropy of either velocity with respect to the other, and of the center-of-mass velocity of the encounter with respect to the GC model rest frame $\vec{v}_{\rm cm|GC}$.
-Note that the speed $v_{\rm cm|GC}$ cannot be greater than the maximum speed between the two objects.
-
-If we assume that the direction of the post-encounter object velocity in the center-of-mass rest frame $\vec{v}_{\rm f|cm}$ is isotropic with respect to $\vec{v}_{\rm cm|GC}$, then the average speed after boosting back to the model rest frame is
-\begin{equation}
-    \langle v_{\rm f|GC} \rangle
-    = \int_0^{2\pi} \frac{d\phi}{2\pi} \sqrt{(v_{\rm f|cm} + v_{\rm cm} \cos \phi)^2 + (v_{\rm cm} \sin \phi)^2}.
-\end{equation}
-Naturally, for $v_{\rm cm|GC} \ll v_{\rm f|cm}$ this average post-boost speed approaches $v_{\rm f|cm}$, and in the limit $v_{\rm cm|GC} \gg v_{\rm f|cm}$ it approaches $v_{\rm cm|GC}$, which recall must be less than the initial speed of the other object in the encounter: in either of these cases, the speed augmentation caused by the boost does not favor faster or slower post-encounter velocities.
-The maximum average ``acceleration" resulting from the boost occurs at the limit $v_{\rm cm|GC} = v_{\rm f|cm}$, where $\langle v_{\rm f|GC} \rangle \sim 1.3 v_{\rm f|cm} = 1.3 v_{\rm cm|GC}$.
-
-The assumption of isotropy in calculating $\langle v_{\rm f|GC} \rangle$ is appropriate for resonant encounters wherein the dynamics are chaotic.
-For flyby encounters where the objects travel on roughly hyperbolic trajectories, there is a preference for post-encounter velocities in the same direction as the initial velocity, if the impact parameter distribution is sufficiently expansive and weighted by the square of the parameter and the final velocities are marginalized over the angle that orients the plane of the ``2-body" encounter.
-The isotropic case is therefore a conservative limit on this flyby case, and predicts a greater boost-propagated speedup than if the calculation was done in full detail.
-
-In summary, neglecting to return to the model rest frame after the \fewbody\ step for strong encounters is found to not favor faster or slower post-encounter speeds when the final speed of an object is much greater than or much less than the center-of-mass speed of the encounter.
-There is an average speedup of 30\% when the two speeds are comparable, but this latter condition means that the speeds themselves are less than the maximum initial speed of the objects, which limits the extent to which the boost itself reveals speeds in excess of the escape velocity.
-
 \bibliography{bib}

### 2023-01-23 src/scripts/gc_orbit_ejections.py

@@ -2,6 +2,7 @@ import os
 import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
+import matplotlib.colors as mplc
 import multiprocessing as mp
 import parmap
 from tqdm import tqdm
@@ -160,15 +161,25 @@ def integrate_cmc_ejections(
             ],
             figsize=(4, 4),
         )
+        cvals = (t_ejs.value + 14000.0) / 14000.0
+        lognorm = mplc.LogNorm(vmin=0.08, vmax=19)
+        cvals = lognorm(cmc.df.mf)
+        ncmap = 256
+        cmap = np.ones((ncmap, 4))
+        cmap[:, 0] = np.linspace(1, 0, ncmap)
+        cmap[:, 1] = 0
+        cmap[:, 2] = np.linspace(0, 1, ncmap)
+        cmap = mplc.ListedColormap(cmap)
 
         ax = axd["xy"]
         # GC trajectory
         ax.plot(
             o_gc.x(ts),
             o_gc.y(ts),
-            c="gray",
+            c="k",
             alpha=0.5,
             lw=0.25,
+            zorder=-1,
             rasterized=True,
         )
         # Ejection points
@@ -176,17 +187,35 @@ def integrate_cmc_ejections(
             o_gc.x(t_ejs),
             o_gc.y(t_ejs),
             # c="k",
-            c=(t_ejs.value + 14000.0) / 14000.0,
-            # c=t_ejs,
+            c=cvals,
+            cmap=cmap,
             s=1.0,
             lw=0,
+            zorder=1,
             rasterized=True,
         )
         # Axes labels
         ax.set_xlabel(r"$x\ [{\rm kpc}]$")
         ax.set_ylabel(r"$y\ [{\rm kpc}]$")
         ax.set_aspect("equal")
-        ax.legend(title=cluster)
+        ax.legend(title=cluster, loc="upper left")
+
+        # Colorbar
+        # Add colorbar; 221019: the colorbar spans the time of the ejections, which revealed that I was determining pre- and post- present-day ejections incorrectly.  Rerunning
+        ## TODO: These two lines were copied from StackOverflow; implement later with right limits
+        ##       Note that the scale will have to be applied to the scatter function as well
+        sm = plt.cm.ScalarMappable(norm=plt.Normalize(vmin=-14, vmax=0))
[…]

### 2023-01-23 src/scripts/gcej_today.py

@@ -4,6 +4,7 @@
 import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
+import matplotlib.colors as mplc
 from astropy.coordinates import SkyCoord, Galactocentric, Galactic, ICRS
 from astropy import units as u
 from galpy.orbit import Orbit
@@ -57,7 +58,7 @@ for gc in rustics.SAMPLE_GCS:
     )
     scgc = scgc.transform_to(Galactic)
     ogc = Orbit(scgc)
-    ts = np.linspace(0,-14000,100000) * u.Myr
+    ts = np.linspace(0, -14000, 100000) * u.Myr
     ogc.integrate(ts, MWPotential2014, method="dop853_c", progressbar=False)
     scgc_orbit = ogc.SkyCoord(ts)
     scgc_orbit = scgc_orbit.transform_to(Galactic)
@@ -65,14 +66,13 @@ for gc in rustics.SAMPLE_GCS:
     # Get ejections data
     ejdf = rustics.EjectionDf(
         paths.data_mwgcs / gc / "output_N-10_ejections.txt",
-        usecols=["time", "X", "Y", "Z", "U", "V", "W"],
+        usecols=["time", "mf", "X", "Y", "Z", "U", "V", "W"],
     )
-    ejdf.df = ejdf.df[
-        (ejdf.df.X != -1)
-        & (ejdf.df.Y != -1)
-    ]
+    ejdf.df = ejdf.df[(ejdf.df.X != -1) & (ejdf.df.Y != -1)]
     # Downsample by 1/10
-    ejdf.df = ejdf.df.sample(frac=0.1, random_state=int(gcrow.X * 1e3))
+    ejdf.df = ejdf.df.sample(
+        frac=0.1, random_state=np.abs(int((gcrow.X * 1e3) % (2**32)))
+    )
 
     # Convert units
     scej = SkyCoord(
@@ -89,15 +89,22 @@ for gc in rustics.SAMPLE_GCS:
     # Set up figure
     nrows = 2
     ncols = 1
-    fig = plt.figure(figsize=(2.5*1.618 * ncols, 2.5*1 * nrows))
-    axx = fig.add_subplot(*(nrows,ncols,1), projection="aitoff")
+    fig = plt.figure(figsize=(2.5 * 1.618 * ncols, 2.5 * 1 * nrows))
+    axx = fig.add_subplot(*(nrows, ncols, 1), projection="aitoff")
[…]

### 2023-01-23 src/scripts/rustics.py

@@ -101,7 +101,7 @@ MODEL_NAMES_V2 = [
 
 # dict of sample CMC models, with values as labels
 SAMPLE_MODELS = {
-    "N8e5_rv0.5_rg8_Z0.0002": r"$(N, r_{\rm vir,pc}, Z_{Z_\odot}) = (8{\rm e}5, 0.5, 0.01)$",
+    "N8e5_rv0.5_rg8_Z0.0002": r"$N, r_{\rm vir,pc}, Z_{Z_\odot} = 8{\rm e}5, 0.5, 0.01$",
     "N4e5_rv0.5_rg8_Z0.0002": r"$N = 4{\rm e}5$",
     "N8e5_rv2_rg8_Z0.0002": r"$r_{\rm vir,pc} = 2$",
     "N8e5_rv0.5_rg8_Z0.02": r"$Z_{\rm Z_\odot} = 1$",
@@ -113,6 +113,10 @@ SAMPLE_GCS = [
     "NGC_5139",
     "NGC_6205",
     "NGC_7089",
+    # "NGC_104",
+    # "Pal_10",
+    # "NGC_6121",
+    # "NGC_5986",
 ]
 
 # Headers for realization dataframes

### 2023-02-01 src/tex/ms.tex
Fixed some figure labels; new final draft of text

@@
 \begin{abstract}
-    The dense environments in the cores of globular clusters (GCs) facilitate many fewbody encounters among stellar objects.
- 	Mass segregation ensures that the most massive stars sink into the core first, and subsequently that the core becomes populated with black holes as the same stars evolve; these compact objects are expected to enable stronger dynamics than star-only encounters.
- 	We study the capacity of these systems to produce high speed stellar ejecta through a synthetic population of binary-single encounters, the latter of which we construct from realistic $N$-body models of GCs.
+    The dense environments in the cores of globular clusters (GCs) facilitate many strong dynamical encounters among stellar objects.
+    These encounters have been shown capable of ejecting stars from the host GC, whereupon they become runaway stars, or hypervelocity stars if unbound to the galactic potential.
+ 	We study high speed stellar ejecta originating from GCs by using realistic $N$-body models, in particular focusing on binary-single encounters involving compact objects.
  	We pair our model-discriminated populations with observational catalogs of Milky Way GCs to compose a present-day galactic population of ejecta.
@@
 
-Alternate acceleration mechanisms capable of producing high-velocity stars include the binary supernova and dynamical ejection scenarios (BSS \citep{1967BOTT....4...86P} and DES \citep{1961BAN....15..265B}, respectively).
-The BSS has been predicted to accelerate stars to speeds of a few hundred \kms \citep{2019A&A...624A..66R, 2022MNRAS.tmp.3236I}, with exceptionally light companions potentially receiving velocities in excess of 1000 \kms \citep{2015MNRAS.448L...6T}.
-The DES has been associated with higher speed limits: \citet{1991AJ....101..562L} studied these encounters with numerical methods, and found that the upper limit for products of these encounters was approximately the escape speed from the surface of the most massive star involved.
+Alternate acceleration mechanisms capable of producing high-velocity stars include the binary supernova and dynamical ejection scenarios (BSS \citep{1961BAN....15..265B} and DES \citep{1967BOTT....4...86P}, respectively).
+In the BSS, the more massive primary of a stellar binary undergoes a supernova, which subsequently accelerates the companion; this scenario has been predicted to accelerate stars to speeds of a few hundred \kms \citep{2019A&A...624A..66R, 2022MNRAS.tmp.3236I}, with exceptionally light companions potentially receiving velocities in excess of 1000 \kms \citep{2015MNRAS.448L...6T}.
+The DES concerns strong gravitational interactions among 3-4 stellar objects, and has been associated with higher speed limits: \citet{1991AJ....101..562L} studied these encounters with numerical methods, and found that the upper limit for products of these encounters was approximately the escape speed from the surface of the most massive star involved.
 For a sun-like star, this escape speed is $\sim$620 \kms, while for a 60 $M_\odot$ late main-sequence star it is $\sim$1400 \kms.
+\citet{2023arXiv230111444O} recently found that for OB runaways in the Small Magellanic Cloud, the DES is expected to occur 2-3 times more frequently that the BSS.
 
-Globular clusters (GCs) are obvious candidate matrices for both of these events due to their high stellar densities, but the DES might be exceptionally amplified due to the combined effects of mass segregation and stellar evolution.
-The former process is characterized as the migration of the most massive objects to the center of a self-gravitating system due to dynamical friction \citep[e.g.,][]{2008gady.book.....B}, which in turn leads to efficient formation of binaries in the core \citep{2005MNRAS.358..572I}.
-This central population of binaries is highly influential on the evolution of the cluster, primarily serving as a heat source as binaries form and shrink through dynamical encounters, undergoing one kind of ``core collapse" in the process \citep[e.g.][]{2007ApJ...658.1047F, 2013MNRAS.429.2881C}.
-In a realistic cluster, these dynamical phases occur after stars have started collapsing into black holes (BHs), and such objects dominate the core population \citep{2020IAUS..351..357K}.
-The resulting abundance of black hole binaries (BBHs) characterizes GCs as one of the favorable progenitors of gravitational-wave sources \citep{2000ApJ...528L..17P, 2015PhRvL.115e1101R}, and in the context of this paper motivates the investigation of whether the population of GCs in the Milky Way (MW) can be considered a significant source of high-velocity stars.
+Globular clusters (GCs) are obvious candidate matrices for both of these events due to their high stellar densities, but the DES might be exceptionally amplified due to the presence of BH subsystems in the centers of GCs.
+Multi-band observations \citep{Maccarone2007a, Barnard2011, Chomiuk2013, Miller-Jones2015a} employing a variety of techniques \citep{Strader2012, Bahramian2016, Giesers2018} have been successful in finding tens of BH candidates in GCs, which are in themselves consistent with the presence of hundreds of BHs per cluster \citep{Giesers2019}.
+BHs play important roles in the macroscopic evolution of the GC \citep[e.g.][]{2020IAUS..351..357K} by dominating gravitational interactions in GC cores; this naturally places BHs in a privileged position when considering the DES in GCs, particularly when considering the maximum velocities attainable by this mechanism.
 
@@
 This work investigates the capacity of GCs to produce HVSs through the DES.
-We focus on encounter between binary and single objects, as they are the most abundant kind of fewbody encounter, and specifically those that involve compact objects (COs, meaning BHs, a white dwarfs (WDs), and neutron stars (NSs)).
+We focus on encounter between binary and single objects, as they are the most abundant kind of strong encounter, and specifically those that involve compact objects (COs, meaning BHs, a white dwarfs (WDs), and neutron stars (NSs)).
 In \S\ref{sec:methods}, we describe our method of generating binary-single compact object (BSCO) ejecta populations from realistic simulations of GCs.
@@
 Because these neighboring particles are individual stars (or binaries), the H\'enon method allows detailed stellar and strong dynamical encounters to be considered as well.
-To that end \CMC~includes prescriptions for three-body binary formation from single BHs \citep{2013ApJ...763L..15M}, binary-single and binary-binary gravitational encounters using the \texttt{Fewbody} small-$N$ scattering package \citep{2004MNRAS.352....1F,2007ApJ...658.1047F}, and galactic tidal fields \citep{2013MNRAS.429.2881C} \carl{CARL CHECK THAT}.
+To that end \CMC~includes prescriptions for three-body binary formation from single BHs \citep{2013ApJ...763L..15M}, binary-single and binary-binary gravitational encounters using the \fewbody\ small-$N$ scattering package \citep{2004MNRAS.352....1F,2007ApJ...658.1047F}, and galactic tidal fields \citep{2013MNRAS.429.2881C} \carl{CARL CHECK THAT}.
 The version of \CMC\ used to create the \CMCcat\citep[which used identical physics to the public version described in][]{Rodriguez2022} treats single and binary stellar evolution for stars with  the \texttt{COSMIC} code for population synthesis \citep{2020ApJ...898...71B}.
@@
 In general, a core collapse occurs when gravitational potential energy is rapidly liberated from the central region of a GC through dynamical encounters, causing the core to contract while energizing and potentially expanding the surrounding envelope of stars.
-Binaries play an important role in these processes, as their formation and hardening through fewbody encounters accelerate the other interacting stars, which subsequently travel to the more extended regions of the GC and potentially escape it entirely.
+Binaries play an important role in these processes, as their formation and hardening through strong encounters accelerate the other interacting stars, which subsequently travel to the more extended regions of the GC and potentially escape it entirely.
 The first core collapse of a GC tends to be propagated by these dynamics, causing the GC to puff up over the following Gyrs as the central binaries continue to shrink and the stellar density increases.
 
-Mass segregation causes the core to be populated by the most massive objects in the GC, which also are those that first evolve into BHs.
+Dynamical friction-induced mass segregation \citep[e.g.][]{2008gady.book.....B} causes the core to be populated by the most massive objects in the GC, which also are those that first evolve into BHs.
 As the core contracts, successively stronger encounters eject all but a small handful of the initially 10s-100s of BHs; this reduced subsystem is unable to support the GC to the same extent as its predecessor, and so the interior of the GC contracts until a sufficiently strong replacement is composed.
@@
 However, while the number of ejections increases as the models become more compact, increasing the number of particles/mass of the model leads to a slight \textit{decrease} in ejecta.
-The $N = 4 \times 10^5$ models consistently produce the most ejections in comparison with otherwise identical models of different population sizes, suggesting that at this mass there are not enough massive objects to prevent a severe initial core collapse through binary burning, but there are enough to facilitate a high number of BSCO encounters (the number of fewbody encounters in general is also maximized in the $N = 4 \times 10^5$ models).
+The $N = 4 \times 10^5$ models consistently produce the most ejections in comparison with otherwise identical models of different population sizes, suggesting that at this mass there are not enough massive objects to prevent a severe initial core collapse through binary burning, but there are enough to facilitate a high number of BSCO encounters (the number of strong encounters in general is also maximized in the $N = 4 \times 10^5$ models).
 
@@
 
-In this work we have studied fewbody encounters in GCs as means of producing stellar runaways.
+In this work we have studied strong 3-body encounters in GCs as means of producing stellar runaways.
 We composed a synthetic MW-like population of ejecta by matching observed GCs to realistic $N$-body models of these systems and embedding the models in the orbits of their real counterparts.
-In particular we considered binary-single encounters involving at least one compact object; this selection includes about half of all fewbody encounters in the catalog of models.
+In particular we considered binary-single encounters involving at least one compact object; this selection includes about half of all strong encounters in the catalog of models.
 
@@
 BSCO encounters occurring in realistic GCs are capable of accelerating stars to velocities in excess of 2000 \kms, which complicates the identification of ejection mechanisms for HVSs when their origins are not easily recognizable.
-We also note that these velocities appear to pass the speed limit on star-only fewbody encounters found by \citet{1991AJ....101..562L}; further study is warranted to study how compact object fewbody dynamics differ from those of objects with a significant physical size.
+We also note that these velocities appear to pass the speed limit on star-only encounters found by \citet{1991AJ....101..562L}; further study is warranted to discern the impact of compact objects on small-$N$-body dynamics.
 
@@
 
+This work was supported by NSF Grant AST-2009916 and NASA ATP Grant 80NSSC22K0722.
+CR also acknowledges support from a Charles E.~Kaufman Foundation New Investigator Research Grant, an Alfred P.~Sloan Research Fellowship, and a David and Lucile Packard Foundation Fellowship.
+
 \appendix
@@
 H\'enon's Monte Carlo method tracks the dynamical state of objects by their energy and angular momentum, which makes the technique inherently spherically symmetric.
-When drawing a radial and tangential velocity from an object's orbit, the sign of the radial velocity is randomly chosen as positive or negative with equal weighting, and when setting up a fewbody encounter an angle $0 \le \phi \le 2\pi$ between the tangential velocities of the two objects is chosen from a uniform distribution.
+When drawing a radial and tangential velocity from an object's orbit, the sign of the radial velocity is randomly chosen as positive or negative with equal weighting, and when setting up a strong interaction an angle $0 \le \phi \le 2\pi$ between the tangential velocities of the two objects is chosen from a uniform distribution.
 These two features ensure isotropy of either velocity with respect to the other, and of the center-of-mass velocity of the encounter with respect to the GC model rest frame $\vec{v}_{\rm cm|GC}$.

### 2023-02-01 src/scripts/check_credible_regions.py

@@ -200,7 +200,7 @@ hist2d_hpx_to_mollweide(
 # axcb.set_label(r"$m~(M_\odot)$")
 
 # Clean and show
-fig.suptitle(gc)
+fig.suptitle(gc.replace("_", ""))
 plt.tight_layout()
 plt.savefig(paths.figures / __file__.split("/")[-1].replace(".py", "_x.pdf"))
 plt.close()
@@ -284,7 +284,7 @@ ax.set_aspect("equal")
 ax.set_xlabel(r"$\mu_\alpha \cos \delta~[{\rm mas/yr}]$")
 
 # Clean and show
-fig.suptitle(gc)
+fig.suptitle(gc.replace("_", ""))
 plt.tight_layout()
 plt.savefig(paths.figures / __file__.split("/")[-1].replace(".py", "_v.pdf"))
 plt.close()

### 2023-02-01 src/scripts/gc_orbit_ejections.py

@@ -198,7 +198,7 @@ def integrate_cmc_ejections(
         ax.set_xlabel(r"$x\ [{\rm kpc}]$")
         ax.set_ylabel(r"$y\ [{\rm kpc}]$")
         ax.set_aspect("equal")
-        ax.legend(title=cluster, loc="upper left")
+        ax.legend(title=cluster.replace("_", " "), loc="upper left")
 
         # Colorbar
         # Add colorbar; 221019: the colorbar spans the time of the ejections, which revealed that I was determining pre- and post- present-day ejections incorrectly.  Rerunning

### 2023-02-01 src/scripts/gcej_today.py

@@ -183,6 +183,7 @@ for gc in rustics.SAMPLE_GCS:
     axv.set_ylim((-45, 15))
     axv.set_xlabel(r"$\mu_{\alpha \cos \delta}~[{\rm mas/yr}]$")
     axv.set_ylabel(r"$\mu_{\delta}~[{\rm mas/yr}]$")
+    axv.legend(title=gc.replace("_", " "), loc="upper left")
 
     ## Plot mu_l_cosb-mu_b
     # axv.scatter(

### 2023-02-06 src/tex/ms_apj.tex
Submission version

--- 2023-02-01 src/tex/ms.tex
@@
 % Define document class
-\documentclass[twocolumn]{aastex631}
-\usepackage{showyourwork}
+\documentclass[twocolumn,linenumbers]{aastex631}
+% \usepackage{showyourwork}
 \usepackage{amsmath}
@@
 \shorttitle{Runaway \& hypervelocity stars from globular clusters}
-\shortauthors{Cabrera et al.}
+\shortauthors{Cabrera \& Rodriguez}
 
@@
 }
+\affiliation{
+    Department of Physics and Astronomy,
+    University of North Carolina at Chapel Hill,
+    120 E. Cameron Ave, Chapel Hill, NC, 27599, USA
+}
 
@@
     These encounters have been shown capable of ejecting stars from the host GC, whereupon they become runaway stars, or hypervelocity stars if unbound to the galactic potential.
- 	We study high speed stellar ejecta originating from GCs by using realistic $N$-body models, in particular focusing on binary-single encounters involving compact objects.
- 	We pair our model-discriminated populations with observational catalogs of Milky Way GCs to compose a present-day galactic population of ejecta.
+ 	We study high speed stellar ejecta originating from GCs by using Monte Carlo $N$-body models, in particular focusing on binary-single encounters involving compact objects.
+ 	We pair our model-discriminated populations with observational catalogs of Milky Way GCs to compose a present-day galactic population of stellar ejecta.
  	We find that these kinds of encounters can accelerate stars to velocities in excess of 2000 \kms, to speeds beyond the previously predicted limits for ejecta from star-only encounters and in the same regime of galactic center ejections.
-	However, the same ejections can only account for 1.5-10\% of the total population of stellar runaways, and only 0.01-1\% of hypervelocity stars, with similar relative rates found for white dwarf ejections.
+	However, the same ejections can only account for 1.5-20\% of the total population of stellar runaways, and only 0.0001-1\% of hypervelocity stars, with similar relative rates found for runaway white dwarfs.
 	We also provide credible regions for ejecta from 149 Milky Way GCs, which we hope will be useful as supplementary evidence when pairing runaway stars with origin GCs.
@@
 Globular clusters (GCs) are obvious candidate matrices for both of these events due to their high stellar densities, but the DES might be exceptionally amplified due to the presence of BH subsystems in the centers of GCs.
-Multi-band observations \citep{Maccarone2007a, Barnard2011, Chomiuk2013, Miller-Jones2015a} employing a variety of techniques \citep{Strader2012, Bahramian2016, Giesers2018} have been successful in finding tens of BH candidates in GCs, which are in themselves consistent with the presence of hundreds of BHs per cluster \citep{Giesers2019}.
+Multi-band observations \citep{Maccarone2007a, Barnard2011, Chomiuk2013, Miller-Jones2015a} employing a variety of techniques \citep{Strader2012, Bahramian2016, Giesers2018} have been successful in finding tens of BH candidates in GCs, which are in themselves consistent with the presence of hundreds of BHs per cluster \citep{2018ApJ...855L..15K, Giesers2019}.
 BHs play important roles in the macroscopic evolution of the GC \citep[e.g.][]{2020IAUS..351..357K} by dominating gravitational interactions in GC cores; this naturally places BHs in a privileged position when considering the DES in GCs, particularly when considering the maximum velocities attainable by this mechanism.
 
-Several recent and ongoing studies seek investigate these phenomena and the broader question of extra-tidal stars from GCs, in part encouraged by the continual improvement of astrometric measurements through efforts such as \textit{Gaia} \citet{2022A&A...667A.148G}.
+Several recent and ongoing studies have investigated these phenomena and the broader question of extra-tidal stars from GCs, in part encouraged by the continual improvement of astrometric measurements through efforts such as \textit{Gaia} \citep{2022arXiv220800211G}.
 \citet{2023MNRAS.518.4249G} developed and used a particle spray code to model ejections from GC cores and demonstrate that kinematic cuts can be too aggressive when searching for ejecta, preferring the use of chemical abundances alone.
@@
 This work investigates the capacity of GCs to produce HVSs through the DES.
-We focus on encounter between binary and single objects, as they are the most abundant kind of strong encounter, and specifically those that involve compact objects (COs, meaning BHs, a white dwarfs (WDs), and neutron stars (NSs)).
+We focus on encounters between binary and single objects, as they are the most abundant kind of strong encounter, and specifically those that involve compact objects (COs, meaning BHs, a white dwarfs (WDs), and neutron stars (NSs)).
 In \S\ref{sec:methods}, we describe our method of generating binary-single compact object (BSCO) ejecta populations from realistic simulations of GCs.
@@
 Because these neighboring particles are individual stars (or binaries), the H\'enon method allows detailed stellar and strong dynamical encounters to be considered as well.
-To that end \CMC~includes prescriptions for three-body binary formation from single BHs \citep{2013ApJ...763L..15M}, binary-single and binary-binary gravitational encounters using the \fewbody\ small-$N$ scattering package \citep{2004MNRAS.352....1F,2007ApJ...658.1047F}, and galactic tidal fields \citep{2013MNRAS.429.2881C} \carl{CARL CHECK THAT}.
-The version of \CMC\ used to create the \CMCcat\citep[which used identical physics to the public version described in][]{Rodriguez2022} treats single and binary stellar evolution for stars with  the \texttt{COSMIC} code for population synthesis \citep{2020ApJ...898...71B}.
+To that end \CMC~includes prescriptions for three-body binary formation from single BHs \citep{2013ApJ...763L..15M}, binary-single and binary-binary gravitational encounters using the \fewbody\ package \citep{2004MNRAS.352....1F,2007ApJ...658.1047F}, and galactic tidal fields \citep{2013MNRAS.429.2881C}.
+The version of \CMC\ used to create the \CMCcat~\citep[which used identical physics to the public version described in][]{Rodriguez2022} treats single and binary stellar evolution for stars with  the \texttt{COSMIC} code for population synthesis \citep{2020ApJ...898...71B}.
 \texttt{COSMIC} is based upon the original Binary Stellar Evolution (BSE) code \citep{2000MNRAS.315..543H,2002MNRAS.329..897H}, but with updated prescriptions for compact-object formation and massive star evolution; see \citet{2020ApJ...898...71B} and \citet{Rodriguez2022} for details.
@@
 During each timestep, \CMC\ determines whether to perform a strong three-body encounter between a neighboring star and binary by computing the probability from \ref{eqn:pbs} and comparing it to a random variable drawn from [0,1], $X$.
-If $X < P_{\rm BS}$, an encounter is performed with an impact parameter, $b$, selected from a distribution proportional to $b db$ out to a maximum integrated area set by \ref{eqn:sigma}.
-All other parameters, such as the phase of the binary and the orientation of the angular momentum and Runge-Lenz vectors are randomly selected.
-Of course, this means that any encounter produced in a single \CMC\ integration is only a single realization of all the possible encounters that could have occurred in the cluster at that time.
+If $X < P_{\rm BS}$, an encounter is performed with an impact parameter, $b$, selected from a distribution proportional to $P(b) \sim b~db$ out to a maximum integrated area set by \ref{eqn:sigma}.
+
+At this point the encounter is handed off to \fewbody\ \citep{2004MNRAS.352....1F}, a small-$N$-body gravitational scattering code.
+\fewbody\ randomly selects all remaining parameters, such as the phase of the binary and the orientation of the angular momentum and Runge-Lenz vectors; of course, this means that any encounter produced in a single \CMC\ integration is only a single realization of all the possible encounters that could have occurred in the cluster at that time.
+For binary-single encounters, a hyperbolic encounter between the binary center-of-mass and the single object is initiated with infinite separation, and is analytically advanced until the tidal perturbation of the binary reaches a set threshold.
+An 8$^{\rm th}$-order Runge-Kutta Prince-Dormand integrator then evolves the encounter, and the participating objects are classified as singles or into binaries at regular timestep intervals.
+If the reduced encounter among the present single(s) and possible binary has a positive energy and the single(s)/binary are moving away from each other, then integration is terminated (termination also occurs if the encounter becomes analytic e.g.
+a merger results in a Keplerian interaction).
+
+We implement additional features into \fewbody\ pertinent to the study of compact object dynamics.
+We add additional parameters to track stellar object type, distinguishing between stars and compact objects.%, using the numbering convention of \citet{2002MNRAS.329..897H}; similarly, we implement the collision matrix presented in Table 2 of the same paper to determine the type of any post-merger products.
+We use these object types to decide whether to use \fewbody's default sticky-sphere collision criterion - which triggers a collision when the separation of the objects' centers is less than the sum of their radii - in the case of stellar interactions, and a tidal disruption criterion in the case of encounters involving NSs and BHs, which multiplies the threshold separation by a factor of $(m_{\rm CO} / m_{*})^{1/3}$ \citep[as was done in][]{Kremer2019}.
+To the utility of this collision metric, we conservatively assign BHs radii of 5 times their Schwarzschild radii to group the more extreme encounters with mergers, both of which require more careful treatment to accurately represent.
 
@@
 Over the entire catalog, our encounter sample makes up about half of all strong encounters that occur in the models, with each model contributing a few ten thousand BSCO encounters on average.
-We then realize each encounter in isolation with the same \fewbody\ package used in \CMC, computing 10 realizations of each encounter while re-drawing the randomly selected parameters (e.g.
-binary phase) to obtain a better statistical representation of the binary-single encounter population.
+We then realize each encounter in isolation with our modified \fewbody\, computing 10 realizations of each encounter while re-drawing the randomly selected parameters (e.g.~binary phase) to obtain a better statistical representation of the binary-single encounter population.
 
 The resulting objects that leave the model to become runaway stars or HVSs are identified as follows.
-To save computational resources, \fewbody\ terminates its integration once the relevant encounter products have positive energy and are moving away from one another; this means that encounters are generally terminated before the resulting objects are far from each other's gravitational influence.
-To account for this, we calculate the final velocity of an object after an encounter $v_{\rm fin}$ as the hyperbolic excess velocity
+We calculate the final velocity of an object after an encounter $v_{\rm fin}$ as the hyperbolic excess velocity
 \begin{equation}
@@
 \end{equation}
-\noindent where $v$ is the velocity of the object leaving the encounter, and $U$ and $K$ are the Keplerian potential and kinetic energies of the top-level binary-single system (all of these quantities are evaluated at the termination of integration).
+\noindent where $v$ is the velocity of the object leaving the encounter, and $U$ and $K$ are the Keplerian potential and kinetic energies of the top-level binary-single system (all of these quantities are evaluated at the termination of integration, which as noted above is a time where the potential may still have some significant magnitude).
 The local escape velocity of the star cluster $v_{\rm esc}$ is provided by \CMC\ with the other encounter parameters; any object with $v_{\rm fin} \ge v_{\rm esc}$ is considered to escape the cluster.
@@
 
-\subsection{GC core collapses} \label{subsec:cc}
+\subsection{Core collapse in GCs} \label{subsec:cc}
 
-Core collapse is a well-documented feature of GC evolution (e.g.
-\citealt{1968MNRAS.138..495L}, \citealt{2001A&A...375..711F}, \citealt{2006MNRAS.368..121F}, \citealt{2008gady.book.....B}, \citealt{2020IAUS..351..357K}), and as will be seen is a significant factor in the ejection of stars from these systems.
-In general, a core collapse occurs when gravitational potential energy is rapidly liberated from the central region of a GC through dynamical encounters, causing the core to contract while energizing and potentially expanding the surrounding envelope of stars.
-Binaries play an important role in these processes, as their formation and hardening through strong encounters accelerate the other interacting stars, which subsequently travel to the more extended regions of the GC and potentially escape it entirely.
-The first core collapse of a GC tends to be propagated by these dynamics, causing the GC to puff up over the following Gyrs as the central binaries continue to shrink and the stellar density increases.
+Core collapses are well-documented features of GC evolution \citep[e.g.][]{1968MNRAS.138..495L, 2001A&A...375..711F, 2006MNRAS.368..121F, 2008gady.book.....B, 2020IAUS..351..357K}, and the heightened densities during such phenomena makes them relevant to the present study.
+This process occurs due to the energy transport by two-body relaxation from the central regions of the cluster outwards, causing a core to develop and contract while the outer regions expand \cite{2003gmbp.book.....H}.
+The presence of massive objects (e.g.
+BHs) can significantly accelerate this process, as dynamical friction slows the most massive objects in the system, causing them to segregate into the core on a much more rapid timescale\cite{2008gady.book.....B}.
+Following \cite{2013MNRAS.432.2779B}, we refer to this initial BH-lead collapse as the ``first’’ core collapse.
+While this process can be effected substantially by the metallicity of the star cluster, with more metal-rich clusters experiencing greater mass loss due to stellar winds and producing lower-mass BHs with correspondingly longer dynamical friction timescales (fewer of which are retained due to natal kicks) \cite{2022arXiv220316547R}, core collapse typically occurs within a few 100 Myr for most GCs.
 
-Dynamical friction-induced mass segregation \citep[e.g.][]{2008gady.book.....B} causes the core to be populated by the most massive objects in the GC, which also are those that first evolve into BHs.
-As the core contracts, successively stronger encounters eject all but a small handful of the initially 10s-100s of BHs; this reduced subsystem is unable to support the GC to the same extent as its predecessor, and so the interior of the GC contracts until a sufficiently strong replacement is composed.
-After \citet{2020IAUS..351..357K}, we employ this characteristic of BH ejection as a metric of whether a GC model has undergone this second kind of core collapse: once there are less than 10 BHs remaining in the model, we label it as core collapsed from that time onward.
+% From the beginning of a GC's lifetime, dynamical friction slows the most massive objects in the system, while simultaneously accelerating the less massive objects \citep[e.g.][]{2008gady.book.....B}.
+% Globally, this leads to the expansion of the outer layers of the cluster with a contemporary contraction of the core \citep{2013MNRAS.429.2881C}, usually within 100 Myr of the birth of the system.
+
+%This first core collapse is delayed and weakened in systems with higher metallicities: the increased mass loss due to stronger stellar winds directly leads to smaller objects that experience weaker dynamical friction, and indirectly the number of ``massive" objects is reduced as any that to evolve into BHs are more easily removed from the GC by natal kicks \citep{2008MNRAS.386...65M, 2022arXiv220316547R}.
+
+First core collapse is stopped by the formation and hardening of binaries in the core (which at this point is largely composed of BHs), and the liberated energy supports the universal expansion of the GC for a time on the order of Gyr \citep{2012MNRAS.420..309B}.
+The BH population in the core is gradually depleted as strong encounters accelerate their participants beyond the local escape speed, until no more than a handful of BHs remain in the cluster \citep{2013MNRAS.432.2779B, 2020IAUS..351..357K}.
+The loss of the dynamical heat source causes the core to contract again, as the system adjusts to being supported by WDs, NSs and stars in the same mass regime.
+Unlike the first collapse, this second, permanent core collapse is observable in that the surface brightness profile of the GC becomes cuspy to the limit of the cluster center (and is what observers would classically call a ``core-collapsed cluster'').
+We follow \citet{2018ApJ...855L..15K} in pairing these demographic and observable features, marking the time of second core collapse in our models as the same time the number of BHs drops below 10.
 
@@
     \item $r_{\rm gc} = 8~{\rm kpc}$
-    \item $Z = 0.01Z_\odot$,
+    \item $Z = 0.01Z_\odot$.
 \end{itemize}
-which, except for the compact virial radius, are near the typical values for the MWGC population (the small virial radius model is chosen for its shorter relaxation time, promising a greater dynamical age for a given physical time).
 Each of the other three sample models vary one of these parameters (either $N \to 4 \times 10^5$, $r_{\rm vir} \to 2~{\rm pc}$, or $Z \to Z_\odot$) to promote understanding of the effects of each.
+The base $N$, $r_{\rm gc}$, and $Z$ were chosen as they correspond to typical values for MWGCs; the notably small $r_{\rm vir}$ is chosen for the samples because the dynamic range of cluster evolution and stellar ejections is greatest among \CMC\ models of this size, making it easier to identify the same features present in larger models.
 
-Figure \ref{fig:cmc_single_clusters} shows the ejection velocity $v_{\rm out}$ for every MS star ejected via.~a BSCO encounter in these models, plotted at the time of encounter from initialization $t$.
+Figure \ref{fig:cmc_single_clusters} shows the ejection velocity $v_{\rm out}$ for every MS star ejected through a BSCO encounter in these models, plotted at the time of encounter from initialization $t$.
 What is immediately apparent from these single cluster models is a strong correlation between BSCO encounters and the evolution of the cluster core: whenever a cluster undergoes a core collapse, the heightened densities lead to predictably high encounter rates.
@@
 \begin{figure*}
-    \script{cmc_single_clusters.py}
+    %\script{cmc_single_clusters.py}
     \gridline{
@@
 This dominance usually continues until the first core collapse after CO formation, where the heightened densities facilitate a rise in encounters involving multiple COs.
-There is a stark difference in the ejection velocities produced by these encounters in comparison to the previous mixed binary-single MS star encounters, and the fastest ejections over the cluster's lifetime are produced in the first tens of Myr after the associated ``first" core collapse.
+There is a stark difference in the ejection velocities produced by these encounters in comparison to the previous mixed binary-single MS star encounters, and the fastest ejections over the cluster's lifetime are produced in the first tens of Myr after the associated first core collapse.
 This regime lasts for a few to tens of Gyr, during which the COs in the core (predominantly BHs) preferentially form CO-CO binaries, as evidenced in the drop of mixed binary-single CO encounters during this phase.
 
-For cluster models that evolve to BH-depletion ``second" core collapse (in our sample, all but the large model), the corresponding increase in BSCO encounters is dominated by stellar binary-single CO encounters.
+For cluster models that evolve to BH-depletion second core collapse (in our sample, all but the $r_{\rm vir} = 2~{\rm pc}$ model), the corresponding increase in BSCO encounters is dominated by stellar binary-single CO encounters.
 We also find that the majority of these encounters do not involve BHs, but rather WDs (or in some cases a NSs).
@@
 
-The $r_{\rm vir} = 2 {\rm pc}$ model evolves to ``first" core collapse later than the previous two, and noticeably lacks the pre-core collapse abundance of mixed binary-single star encounters seen above.
-When ``first" core collapse does occur, the distribution of encounters is similar to the respective distributions for the base model.
+The $r_{\rm vir} = 2~{\rm pc}$ model evolves to first core collapse later than the previous two, and noticeably lacks the pre-core collapse abundance of mixed binary-single star encounters seen above.
+When first core collapse does occur, the distribution of encounters is similar to the respective distributions for the base model.
 
 The difference between the solar metallicity model and the others is striking.
-This model does not evolve to ``first" core collapse until $\sim$200 Myr (by far the latest out of the four), but still reaches ``second" core collapse near 7 Gyr.
-Furthermore, the lower stellar masses make the first core collapse much less severe, delaying the maximum ejecta production rate until the second core collapse; this rate increases roughly monotonically throughout the model's evolution.
-
-The $r_{\rm vir} = 2 pc$ model evolves slower, and so it does not reach the same core collapse phase as the previous two.
-The lower densities prevent the initial dominance of mixed binary-single star encounters, as the frequency of BSCO encounters is relatively low until the initial core collapse.
-On the other hand, this first core collapse is not associated with an abundance of BSCO encounters in the high-metallicity model, which sees a roughly monotonic rise in BSCO encounters throughout its evolution.
+This model does not evolve to first core collapse until $\sim$200 Myr (by far the latest out of the four), and leads to typical densities no more than 10\% those of the other models; this occurs due to the lower BH masses and abundances associated with the greater mass loss (c.f.
+\S\ref{subsec:cc} above, and \S5.2 in \citet{2022arXiv220316547R}).
+Also unlike the other models, here the number of ejections does not peak until the second, BH-depletion core collapse near 7 Gyr.
 
@@
 \CMC\ does not record the radius where each strong encounter occurred, but it does record the local escape velocity.
-For comparison, the escape velocity from the center of the model can be computed from the central and tidal boundary potentials, which are recorded throughout the evolution of the cluster.\footnote{These potentials can be found in the standard \CMC\ output file \texttt{initial.esc.dat}, which records data pertaining to stars that become unbound to the model for any reason.
-The escape rate is high enough that the time domain is well-resolved by these data.}
+For comparison, the escape velocity from the center of the model can be computed from the central and tidal boundary potentials, which are recorded throughout the evolution of the cluster.
 Figure \ref{fig:cmc_single_clusters_vesc} plots these data for the same sample clusters, where the distribution of encounter escape velocities is strikingly correlated to the central escape velocity, indicating the degree to which the core dominates these dynamics.
@@
 \begin{figure}
-    \script{cmc_single_clusters_vesc.py}
+    %\script{cmc_single_clusters_vesc.py}
     \centering
@@
 \begin{figure*}
-    \script{cmc_catalog.py}
+    %\script{cmc_catalog.py}
     \centering
@@
 The most noticeable distinction among models of different metallicities is the number of ejections, which decreases with increasing metallicity.
-This is understandable, as in practice the lower metallicity models have greater BH populations than the higher metallicity models; quantitatively, the 1\% solar models have about $1.2 \times$ as many BHs at the time of ``first" core collapse as the solar models, and maximum BH masses about $2 \times$ those of the same.
-This weakens BSCO dynamics before and during ``first" core collapse, as was first made visible in Figure \ref{fig:cmc_single_clusters}.
+This is understandable, as in practice the lower metallicity models have greater BH populations than the higher metallicity models; quantitatively, the 1\% solar models have about $1.2 \times$ as many BHs at the time of first core collapse as the solar models, and maximum BH masses about $2 \times$ those of the same.
+This weakens BSCO dynamics before and during first core collapse, as was first made visible in Figure \ref{fig:cmc_single_clusters}.
 Because this effect takes place in the earlier stages of model evolution - namely, when mass segregation has had less time to separate lighter objects from the strong dynamics of heavier objects - this has the most significant effect of reducing the number of ejecta with $m < M_\odot$.
-Notably, the different metallicity models have quite similar ejecta mass distributions after ``second" core collapse, as the effect of metallicity on the masses of the remaining WDs and NSs is much less pronounced than on the now-ejected BHs.
+Notably, the different metallicity models have quite similar ejecta mass distributions after second core collapse, as the effect of metallicity on the masses of the remaining WDs and NSs is much less pronounced than on the now-ejected BHs.
 
@@
 where $\bar{x}_{\rm CMC}$ and $\sigma_{\rm x,CMC}$ are respectively the mean and standard deviation of the parameter $x$ over the complete set of \CMC\ snapshots.
-The snapshot from the $r_{\rm gc}$ - [Fe/H] subset that is closest to the MWGC in the normalized $\log M$ - $r_c / r_h$ space is chosen to represent the GC; as an example, 47 Tuc ($r_{\rm gc} = 7.52$ kpc, $Z = 0.0019$; $\log M = 5.95$, $r_c / r_h,m = 0.125$) is represented by a snapshot from model \texttt{N1.6e6\_rv2\_rg8\_Z0.002}, which at the 10.8 Gyr time of the snapshot has $\log M = 5.91$ and $r_c / r_h = 0.126$.
+The snapshot from the $r_{\rm gc}$ - [Fe/H] subset that is closest to the MWGC in the normalized $\log M$ - $r_c / r_h$ space is chosen to represent the GC; as an example, 47 Tuc ($r_{\rm gc} = 7.52$ kpc, $Z = 0.0019$; $\log M = 5.95$, $r_c / r_h,m = 0.125$ \citep{2018MNRAS.478.1520B, 2010arXiv1012.3224H}) is represented by a snapshot from model \texttt{N1.6e6\_rv2\_rg8\_Z0.002}, which at the 10.8 Gyr time of the snapshot has $\log M = 5.91$ and $r_c / r_h = 0.126$.
 
 \begin{figure}
-    \script{cmcs-mwgcs_scatter.py}
+    %\script{cmcs-mwgcs_scatter.py}
     \begin{centering}
@@
 All orbit integrations in the galactic frame are done with \texttt{galpy}\footnote{http://github.com/jobovy/galpy} \citep{2015ApJS..216...29B}.
-
 Setting the snapshot to the present-day galactic orbital parameters from \citet{2018MNRAS.478.1520B}, we back-integrate the orbit of each GC in the \texttt{galpy}\texttt{MWPotential2014} potential to the initialization time of the respective model.
@@
 \begin{figure*}
-    \script{gc_orbit_ejections.py}
+    %\script{gc_orbit_ejections.py}
     \gridline{
@@
 \begin{figure*}
-    \script{gcej_today.py}
+    %\script{gcej_today.py}
     \gridline{
@@
 The distributions of distance from the galactic origin, and the local distributions of galactocentric velocity are similar when distributing over radius $r_{\rm gc}$ versus distance from the galactic plane $Z_{\rm gc}$.
-Most runaways end up at a distance on the order of 10 pc from the galactic center, and with a velocity on the order of 100-300~\kms.
-Few runaways make it past the $\sim$100 pc mark, but those that do naturally retain the highest velocities, reaching upwards of 1000~\kms.
+Most runaways end up at a distance on the order of 10 kpc from the galactic center, and with a velocity on the order of 100-300~\kms in the galactocentric rest frame.
+Few runaways make it past the 100 kpc mark, but those that do naturally retain the highest velocities, reaching upwards of 1000~\kms.
 
 \begin{figure*}
-    \script{rgc-z.py}
+    %\script{rgc-z.py}
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/rgc-z_S.pdf}
+        \includegraphics[width=0.9\linewidth]{figures/rgc-z_S.pdf}
         \caption{
-            Histograms and velocity quantiles for the synthetic ejecta.
+            Histograms (top) and velocity quantiles (bottom) for the synthetic stellar ejecta.
             The left (right) plots show the profile over radial distance from the galactic center $r_{\rm gc}$ (distance from the galactic plane $Z$).
             The quantiles in the lower plots are calculated from the present-day velocities of our population.
+            The red dots show the $r_{\rm gc}$ ($Z$) positions of the MWGCs from our composite \citet{2018MNRAS.478.1520B}+\citet{2010arXiv1012.3224H} catalog, arbitrarily spread in the vertical dimension.
         }
@@
 
-One result of note is that of the heliocentric radial velocity $v_{\rm rf}$ distribution of the synthetic population.
+\begin{figure}
+    %\script{cmc_orbits_cdf.py}
+    \begin{centering}
+        \includegraphics[width=0.99\linewidth]{figures/cmc_orbits_cdf_S.pdf}
+        \caption{
+            Velocity distributions for our synthetic and some previous observational HVS catalogs.
+            $v_{\rm rf}$ is the heliocentric radial velocity of the star as measured in the galactic rest frame.
+        }
+        \label{fig:cmc_orbits_cdf}
+    \end{centering}
+\end{figure}
+
+\begin{figure}
+    %\script{mwej_rates.py}
+    \begin{centering}
+        \includegraphics[width=0.99\linewidth]{figures/mwej_rates.pdf}
+        \caption{
+            The evolution of the ejection rate for different components of our synthetic population.
+            The blue (red) dashed line shows the estimated from observations for runaways from the galactic disc (HVSs from the galactic center), as reported by \citet{2015ARA&A..53...15B}.
+        }
+        \label{fig:mwej_rates}
+    \end{centering}
+\end{figure}
+
+One result of note is that of the heliocentric radial velocity, $v_{\rm rf}$, distribution of the synthetic population.
 \citet{2021arXiv211213864G} in part studied the galactic center origin of HVSs, and found that there is an apparent tension between the observed and predicted runaway populations; specifically, the predicted number of stars with velocities $\gtrsim 700~{\rm km~s^{-1}}$ was much higher than the observed rate from the HVS sample of \citet{2018ApJ...866...39B}.
@@
 
-\begin{figure}
-    \script{cmc_orbits_cdf.py}
-    \begin{centering}
-        \includegraphics[width=0.99\linewidth]{figures/cmc_orbits_cdf_S.pdf}
-        \caption{
-            Velocity distributions for our sythetic and some previous observational HVS catalogs.
-            $v_{\rm rf}$ is the heliocentric radial velocity of the star as measured in the galactic rest frame.
-        }
-        \label{fig:cmc_orbits_cdf}
-    \end{centering}
-\end{figure}
-
-Figure \ref{fig:mwej_rates} shows the rate of HVS/runaway production for our synthetic population, along with some base values from the literature.
-In both cases, the GC ejection rate is smaller than the observed rate, especially at the present day.
-However, runaways from GCs could make up an appreciable fraction of runaways in the early universe.
-It is also of note that GCs are able to produce any HVSs at all, at velocities previously associated entirely with the galactic center.
-
-\begin{figure}
-    \script{mwej_rates.py}
-    \begin{centering}
-        \includegraphics[width=0.99\linewidth]{figures/mwej_rates.pdf}
-        \caption{
-            The ejection rate for the synthetic MWGC population.
-            The red dashed line represents the HVS rate for the galactic center, and the blue dashed line the runaway rate for the disk proposed by \citep{2015ARA&A..53...15B}.
-        }
-        \label{fig:mwej_rates}
-    \end{centering}
-\end{figure}
+Finally, Figure \ref{fig:mwej_rates} shows the HVS/runaway rates for our synthetic population, along with observational rate estimates from \citet{2015ARA&A..53...15B}.
+At earlier times, BSCO ejecta could have made as much as 20\% (1\%) of all runaways (HVSs), during the times when GCs underwent their first core collapses.\footnote{Here, the cutoff of this phase is fairly abrupt because we constrain our models to present-day ages of 10-13.5 Gyr (\S\ref{subsec:pairing}).
+The physical rate will naturally be characterized by the evolution of the GC formation rate in the past.}
+Afterwards, the ejection rates decay to the present day, where they are closer to 1.5\% (0.0001\%) of the observational values.
+It is important to note nonetheless that GCs are able to produce HVSs with speeds high enough to make them comparable to those accelerated by mechanisms in the galactic center.
 
@@
 BSCO ejections were found to be closely linked to the evolution of the cluster core, where the closest encounters among the densest stellar objects occur.
-GCs lose mass, and generally expand as they evolve; accordingly, the majority of and the fastest BSCO ejecta were produced in the early stages of the models.
+GCs lose mass and expand as they evolve; accordingly, the majority of and the fastest BSCO ejecta were produced in the early stages of the models.
 High-metallicity models had overall weaker ejection mechanisms (in frequency and maximum velocity), due to smaller stellar masses.
@@
 
-In the galactic context, the velocity distribution of the synthetic ejecta was found to be similar to that of HVS observations at relatively low velocities; specifically, our population was skewed towards these velocities with respect to observations.
-With galactic-center origin studies finding distributions skewed towards higher velocities in the same respect \citet{2018ApJ...866...39B}, it is possible that a mixture of the two could be used to more accurately model the real population of these objects.
-Such a calculation must be done in light of the relative rates of the two mechanisms: our study concludes that while the GC BSCO runaway rate might have been a few 10\% of the overall rate in the first few Gyr of the universe, in the present day it is likely no more than 10\% of the same.
+In the galactic context, the velocity distribution of the synthetic ejecta was found to be similar to that of HVS observations for velocities $\lesssim 500~{\rm km~s^{-1}}$; specifically, our population was skewed towards these velocities with respect to observations.
+With galactic-center origin studies finding distributions skewed towards higher velocities in the same respect \citep{2018ApJ...866...39B}, it is possible that a mixture of the two could be used to more accurately model the real population of these objects.
+Such a calculation must be done in light of the relative rates of the two mechanisms: our study concludes that while the GC BSCO runaway rate might have been a few 10\% of the overall rate in the first few Gyr of the MW, in the present day it is likely no more a few 1\% of the same.
 
+\begin{acknowledgements}
 This work was supported by NSF Grant AST-2009916 and NASA ATP Grant 80NSSC22K0722.
 CR also acknowledges support from a Charles E.~Kaufman Foundation New Investigator Research Grant, an Alfred P.~Sloan Research Fellowship, and a David and Lucile Packard Foundation Fellowship.
+\end{acknowledgements}
+
+\software{\CMC\ \citep{2000ApJ...540..969J, 2013ApJS..204...15P, Rodriguez2022}, \fewbody \citep{2004MNRAS.352....1F}, \texttt{galpy} \citep{2015ApJS..216...29B}, \texttt{astropy} \citep{2013A&A...558A..33A, 2018AJ....156..123A, 2022ApJ...935..167A}, \texttt{numpy} \citep{harris2020array}, \texttt{pandas} \citep{mckinney-proc-scipy-2010, reback2020pandas}, \texttt{matplotlib} \citep{Hunter:2007}}
 
@@
 
-H\'enon's Monte Carlo method tracks the dynamical state of objects by their energy and angular momentum, which makes the technique inherently spherically symmetric.
-When drawing a radial and tangential velocity from an object's orbit, the sign of the radial velocity is randomly chosen as positive or negative with equal weighting, and when setting up a strong interaction an angle $0 \le \phi \le 2\pi$ between the tangential velocities of the two objects is chosen from a uniform distribution.
+H\'enon's Monte Carlo method assumes spherical symmetry, and subsequently the orbit of a particle is characterized by its energy, total angular momentum, and radial position; radial and tangential velocity magnitudes are drawn from the orbit by weighting by the amount of time the object spends at each point in its orbit (see \S2.5 of \citet{Rodriguez2022}).
+The sign of the radial velocity is randomly chosen as positive or negative with equal weighting, and when setting up a strong interaction an angle $0 \le \phi \le 2\pi$ between the tangential velocities of the two objects is chosen from a uniform distribution.
 These two features ensure isotropy of either velocity with respect to the other, and of the center-of-mass velocity of the encounter with respect to the GC model rest frame $\vec{v}_{\rm cm|GC}$.
-Note that the speed $v_{\rm cm|GC}$ cannot be greater than the maximum speed between the two objects.
 
@@
 The assumption of isotropy in calculating $\langle v_{\rm f|GC} \rangle$ is appropriate for resonant encounters wherein the dynamics are chaotic.
-For flyby encounters where the objects travel on roughly hyperbolic trajectories, there is a preference for post-encounter velocities in the same direction as the initial velocity, if the impact parameter distribution is sufficiently expansive and weighted by the square of the parameter and the final velocities are marginalized over the angle that orients the plane of the ``2-body" encounter.
+For flyby encounters where the objects travel on roughly hyperbolic trajectories, there is a preference for post-encounter velocities in the same direction as the initial velocity, if the impact parameter distribution is sufficiently expansive and weighted by the square of the parameter and the final velocities are marginalized over the angle that orients the plane of the 2-body encounter between the star and the binary center-of-mass.
 The isotropic case is therefore a conservative limit on this flyby case, and predicts a greater boost-propagated speedup than if the calculation was done in full detail.
 
-In summary, neglecting to return to the model rest frame after the \fewbody\ step for strong encounters is found to not favor faster or slower post-encounter speeds when the final speed of an object is much greater than or much less than the center-of-mass speed of the encounter.
-There is an average speedup of 30\% when the two speeds are comparable, but this latter condition means that the speeds themselves are less than the maximum initial speed between the objects, which limits the extent to which the boost itself reveals speeds in excess of the escape velocity.
+In summary, neglecting to return to the model rest frame after the \fewbody\ step for strong encounters does not favor faster or slower post-encounter speeds when the final speed of an object is much greater than or much less than the center-of-mass speed of the encounter in the model rest frame.
+In the case that the final speed of an object is comparable to the same center-of-mass speed, the average post-transformation boost of 30\% is unlikely to significantly increase the number of ejections, as the two speeds are generally less than the maximum initial speed among objects entering the encounter.
 
@@
 
-We include with this publication phase credible regions in phase space for ejecta populations from the MWGCs considered, which may be accessed at [LINK].
+\begin{figure}
+    %\script{check_credible_regions.py}
+    \centering
+    \includegraphics[width=0.9\textwidth]{figures/check_credible_regions_x.pdf}
+    \caption{
+        The HEALPix histogram for a sample GC (NGC 104), with the 50\% and 90\% credible regions in the right subplot.
+        Galactic coordinates are used, and the histogram weights are log scaled.
+    }
+    \label{fig:check_credible_regions_x}
+\end{figure}
+
+\begin{figure}
+    %\script{check_credible_regions.py}
+    \centering
+    \includegraphics[width=0.7\textwidth]{figures/check_credible_regions_v.pdf}
+    \caption{
+        The proper motion histogram and credible regions for the same sample GC.
+    }
+    \label{fig:check_credible_regions_v}
+\end{figure}
+
+We include with this publication phase credible regions in phase space for ejecta populations from the MWGCs considered, which may be accessed at \url{https://zenodo.org/record/7599871}.
 We intend these constructions to be used as secondary evidence for cluster membership of runaway stars, and to encourage further studies into understanding the respective phase space distributions.
@@
 
-The distribution of ejecta on the sky is quantified by discretizing the sphere with an order 4 nested HEALPix map [CITE], binning the sky into 3072 equal-area tiles.
+The distribution of ejecta on the sky is quantified by discretizing the sphere with an order 4 nested HEALPix map \citep{2005ApJ...622..759G}, binning the sky into 3072 equal-area tiles.
 We choose this resolution to enable identification of interesting credible regions while minimizing the apparent effect of isolated points whose exact location is dependent on the RNG seeds used.
@@
 The last two columns (\texttt{CR50} and \texttt{CR90}) are boolean masks of the same convection as the HEALPix probability histogram corresponding to the credible regions (50\% and 90\%, respectively), where bins with entries of 1 are included in the region.
-Figure \ref{fig:check_credible_regions_x} shows the histogram and 50\% and 90\% credible regions for E3, as an example (the script used to generate this plot is \texttt{check\_credible\_regions.py} in the GitHub repository; click on the icon by the caption to be taken directly to the file).
-
-\begin{figure}
-    \script{check_credible_regions.py}
-    \centering
-    \includegraphics[width=0.9\textwidth]{figures/check_credible_regions_x.pdf}
-    \caption{
-        The HEALPix histogram for a sample GC (E3), with the 50\% and 90\% credible regions in the right subplot.
-        Galactic coordinates are used.
-    }
-    \label{fig:check_credible_regions_x}
-\end{figure}
+Figure \ref{fig:check_credible_regions_x} shows the histogram and 50\% and 90\% credible regions for NGC 104, as an example (the script used to generate this plot is \texttt{check\_credible\_regions.py} in the GitHub repository; click on the icon by the caption to be taken directly to the file).
 
@@
 
-\begin{figure}
-    \script{check_credible_regions.py}
-    \centering
-    \includegraphics[width=0.7\textwidth]{figures/check_credible_regions_v.pdf}
-    \caption{
-        The proper motion histogram and credible regions for the same sample GC.
-    }
-    \label{fig:check_credible_regions_v}
-\end{figure}
-
 \bibliography{bib}

### 2023-02-06 src/scripts/check_credible_regions.py

@@ -90,11 +90,11 @@ def hist2d_hpx_to_mollweide(
 
 # Get ejections data
 gc = "NGC_104"
-gc = "NGC_5139"
-gc = "NGC_6205"
-gc = "NGC_7089"
-gc = "Pyxis"
-gc = "E_3"
+# gc = "NGC_5139"
+# gc = "NGC_6205"
+# gc = "NGC_7089"
+# gc = "Pyxis"
+# gc = "E_3"
 gc_path = paths.data_mwgcs / gc
 ejdf = rustics.EjectionDf(
     gc_path / "output_N-10_ejections.txt",
@@ -165,6 +165,11 @@ hist2d_hpx_to_mollweide(
     },
     kw_rotator=kw_rotator,
 )
+# sm = plt.cm.ScalarMappable(
+#     norm=plt.Normalize(vmin=np.log(ml[0]).min(), vmax=np.log(ml[0]).max()),
+#     cmap="inferno_r",
+# )
+# plt.colorbar(mappable=sm, ax=ax, orientation="horizontal")
 
 # Plot credible regions as 2D "tophat" hists
 ax = axd["cred"]
@@ -200,7 +205,7 @@ hist2d_hpx_to_mollweide(
 # axcb.set_label(r"$m~(M_\odot)$")
 
 # Clean and show
-fig.suptitle(gc.replace("_", ""))
+fig.suptitle(gc.replace("_", " "))
 plt.tight_layout()
 plt.savefig(paths.figures / __file__.split("/")[-1].replace(".py", "_x.pdf"))
 plt.close()
@@ -212,7 +217,7 @@ plt.close()
 # Set up figure
 fig, axd = plt.subplot_mosaic(
     [["hist", "cred"]],
-    sharex=True,
+    # sharex=True,
     sharey=True,
     gridspec_kw={
         "wspace": 0,
@@ -278,13 +283,14 @@ ax.hist2d(
 #     scej.pm_dec,
 #     **kw_ej,
 # )
-ax.set_xlim((-30, 30))
+axd["hist"].set_xlim((-30, 29.9))
+axd["cred"].set_xlim((-29.9, 30))
+axd["hist"].legend(title=gc.replace("_", " "), loc="upper left")
 ax.set_ylim((-45, 15))
 ax.set_aspect("equal")
 ax.set_xlabel(r"$\mu_\alpha \cos \delta~[{\rm mas/yr}]$")
 
 # Clean and show
[…]

### 2023-02-06 src/scripts/cmc_single_clusters.py

@@ -118,8 +118,6 @@ for ci, cmc_cluster in enumerate(cmc_cluster_list):
     legend_labels = []
     nbins = 30
     for ti, ti_row in type_is.iterrows():
-        # for ti, ti_row in rustics.INFO_TYPES_I.iterrows():
-        print(ti, ti_row)
         filtered = ejdf.df[
             (ejdf.df.kf >= kgroup.lo)
             & (ejdf.df.kf < kgroup.hi)

### 2023-02-06 src/scripts/cmc_single_clusters_vesc.py

@@ -17,7 +17,7 @@ import paths
 
 # Get cluster names
 cmc_cluster_list = list(rustics.SAMPLE_MODELS.keys())
-
+print("check12")
 mosaic = np.reshape(cmc_cluster_list, (4, 1))
 figwidth = rustics.textwidth
 figheight = rustics.textwidth / 4 * 1.5
@@ -88,8 +88,6 @@ for ci, cmc_cluster in enumerate(cmc_cluster_list):
     ax.set_yscale("log", subs=[2, 3, 4, 5, 6, 7, 8, 9])
 
     for ti, ti_row in type_is.iterrows():
-        # for ti, ti_row in rustics.INFO_TYPES_I.iterrows():
-        print(ti, ti_row)
         filtered = ejdf.df[
             (ejdf.df.kf >= kgroup.lo)
             & (ejdf.df.kf < kgroup.hi)

### 2023-02-06 src/scripts/mwej_rates.py

@@ -20,6 +20,7 @@ import paths
 
 ###############################################################################
 
+
 @njit
 def _rolling_window_count(data, window_centers, window_width):
     """! A function to count the number of instances in a rolling window.
@@ -33,14 +34,16 @@ def _rolling_window_count(data, window_centers, window_width):
     # Loop through windows
     window_counts = []
     for wc in window_centers:
-        wmin = wc - window_width / 2.
-        wmax = wc + window_width / 2.
+        wmin = wc - window_width / 2.0
+        wmax = wc + window_width / 2.0
         mask = (data >= wmin) & (data < wmax)
         window_counts.append(mask.sum())
     return window_counts
-        
 
-def calc_rolling_rate(mwrow, window_centers, window_width=10, vlim=(0.,np.inf)):
+
+def calc_rolling_rate(
+    mwrow, window_centers, window_width=10, vlim=(0.0, np.inf), stellartype=None
+):
     """! Function for parallelizing rolling rate calculation.
 
     @param  mwrow               mwdf row for a certain GC
@@ -52,96 +55,231 @@ def calc_rolling_rate(mwrow, window_centers, window_width=10, vlim=(0.,np.inf)):
     # Load CMC ejections
     gcdf = pd.read_csv(
         paths.data_mwgcs / mwrow.Cluster / "output_N-10_ejections.txt",
-        usecols=["time","kf","U","V","W"],
+        usecols=["time", "kf", "U", "V", "W"],
     )
 
     # Filter -1's (post-present-day ejections)
-    mask = (gcdf.U != -1) & (gcdf.V != -1) & (gcdf.W != -1) & (gcdf.kf < 10)
-    #mask = (gcdf.U != -1) & (gcdf.V != -1) & (gcdf.W != -1) & (gcdf.kf >= 10) & (gcdf.kf < 13) # white dwarfs
+    if stellartype == None or stellartype == "S":
+        mask = (gcdf.U != -1) & (gcdf.V != -1) & (gcdf.W != -1) & (gcdf.kf < 10)
+    elif stellartype == "WD":
+        mask = (
+            (gcdf.U != -1)
+            & (gcdf.V != -1)
+            & (gcdf.W != -1)
+            & (gcdf.kf >= 10)
+            & (gcdf.kf < 13)
+        )  # white dwarfs
+    elif stellartype == "NS":
+        mask = (
+            (gcdf.U != -1) & (gcdf.V != -1) & (gcdf.W != -1) & (gcdf.kf == 13)
+        )  # neutron stars
[…]

### 2023-02-06 src/scripts/rgc-z.py

@@ -12,13 +12,14 @@ import paths
 
 ###############################################################################
 
-#helio_baumgardt = {
+# helio_baumgardt = {
 #    "galcen_distance": 8.1 * u.kpc,
 #    "galcen_v_sun": np.array([11.1, 12.24 + 240, 7.25]) * u.km / u.s,
 #    "z_sun": 0.0 * u.pc,
-#}
+# }
 
 ###############################################################################
+
 
 def fetch_rgc_Zgc_vtodays(
     gc_fname,
@@ -26,28 +27,24 @@ def fetch_rgc_Zgc_vtodays(
     ej_fname="output_N-10_ejections.txt",
     kgroup=None,
 ):
-    """ Function to make a single rgc histogram, for parallelization. """
+    """Function to make a single rgc histogram, for parallelization."""
     # Define path, load ejections with relevant columns
     path = path / gc_fname / ej_fname
-    ejdf = rustics.EjectionDf(path, usecols=["X","Y","Z","U","V","W","kf"])
+    ejdf = rustics.EjectionDf(path, usecols=["X", "Y", "Z", "U", "V", "W", "kf"])
     # Filter with BSE k's if specified
     if type(kgroup) != type(None):
-        ejdf.df = ejdf.df[
-            (ejdf.df.kf >= kgroup.lo) & (ejdf.df.kf < kgroup.hi)
-        ]
+        ejdf.df = ejdf.df[(ejdf.df.kf >= kgroup.lo) & (ejdf.df.kf < kgroup.hi)]
     # Throw out -1's (after present day)
-    ejdf.df = ejdf.df[
-        (ejdf.df.X != -1)
-        & (ejdf.df.Y != -1)
-    ]
+    ejdf.df = ejdf.df[(ejdf.df.X != -1) & (ejdf.df.Y != -1)]
     # Calculate rgcs and vtodays; rename Z to Zgc to avoid overlap with metallicity settings
-    ejdf.df["rgc"] = (ejdf.df.X**2 + ejdf.df.Y**2)**0.5
-    ejdf.df["vtoday"] = (ejdf.df.U**2 + ejdf.df.V**2 + ejdf.df.W**2)**0.5
+    ejdf.df["rgc"] = (ejdf.df.X**2 + ejdf.df.Y**2) ** 0.5
[…]

### 2023-02-06 src/scripts/rustics.py

@@ -104,7 +104,11 @@ SAMPLE_MODELS = {
     "N8e5_rv0.5_rg8_Z0.0002": r"$N, r_{\rm vir,pc}, Z_{Z_\odot} = 8{\rm e}5, 0.5, 0.01$",
     "N4e5_rv0.5_rg8_Z0.0002": r"$N = 4{\rm e}5$",
     "N8e5_rv2_rg8_Z0.0002": r"$r_{\rm vir,pc} = 2$",
-    "N8e5_rv0.5_rg8_Z0.02": r"$Z_{\rm Z_\odot} = 1$",
+    "N8e5_rv0.5_rg8_Z0.02": r"$Z_{Z_\odot} = 1$",
+    # "N8e5_rv1_rg8_Z0.0002": r"$N, r_{\rm vir,pc}, Z_{Z_\odot} = 8{\rm e}5, 1, 0.01$",
+    # "N4e5_rv1_rg8_Z0.0002": r"$N = 4{\rm e}5$",
+    # "N8e5_rv2_rg8_Z0.0002": r"$r_{\rm vir,pc} = 2$",
+    # "N8e5_rv1_rg8_Z0.02": r"$Z_{Z_\odot} = 1$",
 }
 
 # List of sample GCs to use for orbit, mu-mu plots
@@ -262,7 +266,7 @@ HEADERS_TO_LABELS = {
     "dist": r"$d [{\rm kpc}]$",
     "vesc/rho_0": r"$v_{\rm esc}/\rho_0 [{\rm km~s^{-1}/something}]$",
     "v_radial": r"$v_r [{\rm km~s}^{-1}]$",
-    "vlos": r"$v_{\rm los} [{\rm km~s}^{-1}]$",
+    "vlos": r"$v_{\rm rf} [{\rm km~s}^{-1}]$",
     "mx": r"$m_{\rm max} (M_\odot)$",
     "M": r"$M~[M_\odot]$",
     "rc_spitzer/r_h": r"$r_{\rm core} / r_{h,m}$",
@@ -319,8 +323,8 @@ INFO_BSE_K_GROUPS = pd.DataFrame(
 # Dataframe of age groups info
 INFO_CC_GROUPS = pd.DataFrame(
     [
-        ["Pre-core collapse", "Y", "Pre-CC", 0.0, 1.0, "xkcd:azure", "-"],
-        ["Post-core collapse", "O", "Post-CC", 1.0, np.inf, "xkcd:orangered", "--"],
[…]

### 2023-02-06 src/previous_steps/matching_with_mywheels/aggregate.py
Added previous steps: (modified) fewbody-pn, scripts_original, matching_with_mywheels, mw_orbits

@@ -1,0 +1,158 @@
+"""! @brief A module to combine data from several catalogs """
+
+###############################################################################
+
+import numpy as np
+import pandas as pd
+
+###############################################################################
+
+
+class GCCatalog:
+    def __init__(self, paths, pd_kwargs={}):
+        """! Basic things for now."""
+
+        # If a single path is specified, assume it is a loadable csv
+        if type(paths) == str:
+            self.df = pd.read_csv(paths, **pd_kwargs)
+
+        # If a list of paths is specified, assume it they are baumgardt and harris catalogs 
+        elif type(paths) == list:
+            # Set paths
+            baumgardt_path, harris_path = paths
+
+            # Load cleaned Baumgardt data
+            df_baumgardt = pd.read_csv(
+                baumgardt_path,
+                usecols=["Cluster", "Mass", "rc", "rh,m", "R_GC"],
+                delim_whitespace=True,
+            )
+
+            # Load cleaned Harris data (for metallicities)
+            # "cleaned" = ID renamed to Cluster, names edited to match Baumgardt & Holger, Z=-100 if there's no metallicity measurement (these clusters are also the ones with wt=0 i.e. no stellar metallicities have been measured)
+            df_harris = pd.read_csv(
+                harris_path, usecols=["Cluster", "[Fe/H]"], delim_whitespace=True
+            )
+            # drop rows with [Fe/H]=-100
+            df_harris = df_harris[df_harris["[Fe/H]"] != -100.0]
+
+            # Merge the two datasets
+            self.df = pd.merge(df_baumgardt, df_harris, how="inner", on="Cluster")
+
+            # Set cluster name as index
+            self.df.set_index("Cluster", inplace=True)
+
+    def match_to_cmc_models(
+        self, cmc_path, cmc_kwargs={}, dyn_kwargs={},
+    ):
+        """! Given a path to a CMC directory, finds the matching CMC models for the GCs."""
+
+        # Save cmc_path
+        self.cmc_path = cmc_path
+
+        # Load cmc catalog, and dyn.dat data
+        import readcatalog as cmccat
+
+        cmc_models = cmccat.CMCCatalog(cmc_path, extension=".tar.gz", mp_nprocs=56, **cmc_kwargs)
+        cmc_models.add_dat_timesteps(
+            "initial.dyn.dat",
+            tmin=10000.0,
+            tmax=13500.0,
[…]

### 2023-02-06 src/previous_steps/matching_with_mywheels/match.py

@@ -1,0 +1,499 @@
+"""! @brief A module to combine data from several catalogs """
+###############################################################################
+
+import os
+import numpy as np
+import pandas as pd
+import multiprocessing as mp
+import parmap
+
+import cmctoolkit as cmctoolkit
+
+###############################################################################
+
+
+class CMCCatalog:
+    """! The class for a catalog of CMC models. """
+
+    def __init__(self, path, extension="02", mp_nprocs=1):
+        """! Initialize the catalog. 
+
+        @param  path            Path to the catalog.
+                                Should be a path to a directory that contains a folder for each of the models.
+        @param  extension       File extension on names; will be stripped, but is expected at end of all names.
+                                Note that default of "02" here a dirty way of keeping Kremer+20-like models.
+        @param  mp_nprocs       Number of processes to use for parallel tasks.
+
+        """
+
+        # Store things
+        self.path = path
+        self.mp_nprocs = mp_nprocs
+
+        # Get list of folder names
+        fnames = os.listdir(path)
+
+        # Make catalog dataframe, starting with fnames
+        self.df = pd.DataFrame(
+            [n for n in fnames if n.endswith(extension)], columns=["fname"]
+        ).set_index("fname")
+
+    def parse_names(self, replace={"_v2": ""}, cat_type="Kremer+20"):
+        """! Function to extract model parameters from names.
+        NB: The dtypes of parameter columns are reset whenever a .dat dataset is loaded.
+
+        @param  replace     Dictionary where the keys will be replaced with the values whenever they appear in the model name.
+                            Default removes any "_v2"s in the model names.
+        @param  cat_type    Name format.
+                            Default is "Kremer+20", i.e. the "N[_v2]_rv_rg_Z" convention from the respective catalog.
+
+        """
+
+        # TODO: move this to _parse_model_name
+        # Replace strings
+        fnames = self.df.index.get_level_values("fname")
+        for item in replace.items():
+            fnames = [n.replace(*item) for n in fnames]
+
+        # Extract params
+        params = [self._parse_model_name(n, cat_type=cat_type) for n in fnames]
+        params = pd.DataFrame(params, index=self.df.index)
+
+        # Join params to dataframe
+        self.df = self.df.join(params)
+
+    def _parse_model_name(self, model_name, cat_type="Kremer+20"):
+        """! Parse model names.  Currently only the base one is implemented.
+
[…]

### 2023-02-06 src/previous_steps/matching_with_mywheels/match_old.py

@@ -1,0 +1,10 @@
+import aggregate as ag
+
+mwcat = ag.GCCatalog(
+    ["/hildafs/projects/phy200025p/tcabrera/hvss_old_and_complete/holger_baumgardt_clean.txt",
+    "/hildafs/projects/phy200025p/tcabrera/hvss_old_and_complete/harris2010_II_clean.txt"],
+)
+print(mwcat.df)
+mwcat.match_to_cmc_models(
+    "/hildafs/projects/phy200025p/share/catalog_files",
+)

### 2023-02-06 src/previous_steps/matching_with_mywheels/readcatalog.py

@@ -1,0 +1,198 @@
+"""! @brief This module concerns reading data from a catalog of CMC models."""
+
+###############################################################################
+
+import os
+import numpy as np
+import pandas as pd
+import multiprocessing as mp
+import parmap
+
+import readoutput as readoutput
+
+###############################################################################
+
+
+class CMCCatalog:
+    """! The class for a catalog of CMC models. """
+
+    def __init__(self, path, extension="02", mp_nprocs=1):
+        """! Initialize the catalog. 
+
+        @param  path            Path to the catalog.
+                                Should be a path to a directory that contains a folder for each of the models.
+        @param  extension       File extension on names; will be stripped, but is expected at end of all names.
+                                Note that default of "02" here a dirty way of keeping Kremer+20-like models.
+        @param  mp_nprocs       Number of processes to use for parallel tasks.
+
+        """
+
+        # Store things
+        self.path = path
+        self.mp_nprocs = mp_nprocs
+
+        # Get list of folder names
+        fnames = os.listdir(path)
+
+        # Make catalog dataframe, starting with fnames
+        self.df = pd.DataFrame(
+            [n for n in fnames if n.endswith(extension)], columns=["fname"]
+        ).set_index("fname")
+
+    def parse_names(self, replace={"_v2": ""}, cat_type="Kremer+20"):
+        """! Function to extract model parameters from names.
+        NB: The dtypes of parameter columns are reset whenever a .dat dataset is loaded.
+
+        @param  replace     Dictionary where the keys will be replaced with the values whenever they appear in the model name.
+                            Default removes any "_v2"s in the model names.
+        @param  cat_type    Name format.
+                            Default is "Kremer+20", i.e. the "N[_v2]_rv_rg_Z" convention from the respective catalog.
+
+        """
+
+        # TODO: move this to _parse_model_name
+        # Replace strings
+        fnames = self.df.index.get_level_values("fname")
+        for item in replace.items():
+            fnames = [n.replace(*item) for n in fnames]
+
+        # Extract params
+        params = [self._parse_model_name(n, cat_type=cat_type) for n in fnames]
+        params = pd.DataFrame(params, index=self.df.index)
+
+        # Join params to dataframe
+        self.df = self.df.join(params)
+
+    def _parse_model_name(self, model_name, cat_type="Kremer+20"):
[…]

### 2023-02-06 src/previous_steps/matching_with_mywheels/readoutput.py

@@ -1,0 +1,148 @@
+"""! @brief This module loads the standard CMC output files into a pandas DataFrame."""
+
+###############################################################################
+
+import numpy as np
+import pandas as pd
+
+import cmctoolkit as cmctoolkit
+
+###############################################################################
+
+
+class _dat_file:
+    """! The parent class for the individual files. """
+
+    def __init__(
+        self, path, header_line_no=0, colon_aliases=[], pd_kwargs={}, convert_units={},
+    ):
+        """! Read the data.
+
+        @param  path            The path to the output file.
+        @param  header_line_no  The line to read the columns from.
+        @param  colon_aliases   List-like of character to replace with colons (e.g. ["."] for dyn.dat files)
+        @param  pd_kwargs       Dictionary of keyword arguments to pass to pd.read_csv when loading data.
+                                Merges the specified dict with the default to preserve defaults.
+        @param  convert_units   Dictionary of units to convert (see _dat_file.convert_units)
+
+        """
+
+        # Save path
+        self.path = path
+
+        # Get the column names
+        names = self._get_column_names(path, header_line_no, colon_aliases)
+
+        # Merge specified pd_kwargs dist with default
+        pd_kwarg_defaults = {
+            "names": names,
+            "delimiter": " ",
+            "skiprows": header_line_no + 1,
+            "low_memory": False,
+        }
+        pd_kwargs = {**pd_kwarg_defaults, **pd_kwargs}
+
+        # Load data, passing usecols to select particular columns
+        self.df = pd.read_csv(path, **pd_kwargs,)
+
+        # Note that units are not converted from original values
+        self.units_converted = {n: False for n in self.df.columns}
+
+        # Convert any specified units on load
+        self.convert_units(convert_units)
+
+    def _get_column_names(self, path, header_line_no, colon_aliases=[]):
+        """! Parses the specified line in the file to get the header names.
+
+        @return columns     The column names.
+
+        """
+
+        # Read the header line
+        with open(path) as file:
+            for li, l in enumerate(file):
+                if li == header_line_no:
+                    names = l
+                    break
+
+        # Split at whitespace
+        names = names.split()
+
+        # Keep everything after the colon (using aliases if needed
+        for ca in colon_aliases:
+            names = [c.replace(ca, ":") for c in names]
+        names = [c.split(":")[1] for c in names]
+
+        return names
+
[…]

### 2023-02-06 src/previous_steps/matching_with_mywheels/submit.sh

@@ -1,0 +1,11 @@
+#!/bin/bash
+#SBATCH -n 56 
+#SBATCH -t 720:00:00
+#SBATCH -J match 
+#SBATCH -o match.slurm
+#SBATCH -A phy200025p
+#SBATCH -p HENON
+# use the bash shell
+set -x 
+time python match.py
+

### 2023-02-06 src/previous_steps/mw_orbits/aggregate.py

@@ -1,0 +1,149 @@
+"""! @brief A module to combine data from several catalogs """
+
+###############################################################################
+
+import numpy as np
+import pandas as pd
+
+###############################################################################
+
+
+class GCCatalog:
+    def __init__(self, paths, pd_kwargs={}):
+        """! Basic things for now."""
+
+        # If a single path is specified, assume it is a loadable csv
+        if type(paths) == str:
+            self.df = pd.read_csv(paths, **pd_kwargs)
+
+        # If a list of paths is specified, assume it they are baumgardt and harris catalogs 
+        elif type(paths) == list:
+            # Set paths
+            baumgardt_path, harris_path = paths
+
+            # Load cleaned Baumgardt data
+            df_baumgardt = pd.read_csv(
+                baumgardt_path,
+                usecols=["Cluster", "Mass", "rc", "rh,m", "R_GC"],
+                delim_whitespace=True,
+            )
+
+            # Load cleaned Harris data (for metallicities)
+            # "cleaned" = ID renamed to Cluster, names edited to match Baumgardt & Holger, Z=-100 if there's no metallicity measurement (these clusters are also the ones with wt=0 i.e. no stellar metallicities have been measured)
+            df_harris = pd.read_csv(
+                harris_path, usecols=["Cluster", "[Fe/H]"], delim_whitespace=True
+            )
+            # drop rows with [Fe/H]=-100
+            df_harris = df_harris[df_harris["[Fe/H]"] != -100.0]
+
+            # Merge the two datasets
+            self.df = pd.merge(df_baumgardt, df_harris, how="inner", on="Cluster")
+
+            # Set cluster name as index
+            self.df.set_index("Cluster", inplace=True)
+
+    def match_to_cmc_models(
+        self, cmc_path, cmc_kwargs={}, dyn_kwargs={},
+    ):
+        """! Given a path to a CMC directory, finds the matching CMC models for the GCs."""
+
+        # Save cmc_path
+        self.cmc_path = cmc_path
+
+        # Load cmc catalog, and dyn.dat data
+        import mywheels.cmcutils.readcatalog as cmccat
+
+        cmc_models = cmccat.CMCCatalog(cmc_path, extension=".tar.gz", mp_nprocs=128, **cmc_kwargs)
+        cmc_models.add_dat_timesteps(
+            "initial.dyn.dat",
+            tmin=10000.0,
+            tmax=13500.0,
[…]

### 2023-02-06 src/previous_steps/mw_orbits/cmctoolkit.py

@@ -1,0 +1,2478 @@
+import numpy as np
+import pandas as pd
+import h5py
+import scipy.optimize
+import scipy.interpolate
+import gzip
+import time
+import os
+
+################################################################################
+# DEFINE CGS CONSTANTS
+################################################################################
+
+#Universal constants
+h, c, k, hbar = 6.6260755e-27, 2.99792458e10, 1.380658e-16, 1.05457266e-27
+G, sigma = 6.67259e-8, 5.67051e-5
+
+# Subsets
+startype_all = np.array([0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15])
+startype_star = np.array([0, 1, 2, 3, 4, 5, 6, 7, 8, 9])
+startype_ms = np.array([0, 1])
+startype_giant = np.array([2, 3, 4, 5, 6, 7, 8, 9])
+startype_wd = np.array([10, 11, 12])
+startype_other = np.array([7])
+startype_remnant = np.array([10, 11, 12, 13, 14])
+startype_bh = np.array([14])
+
+# Define column dictionaries; Snapshot class will pick the right column dictionary
+# depending on the format of the CMC output
+coldict_h5 = {'binflag': 'binflag',
+               'm_MSUN': 'm_MSUN',
+              'm0_MSUN': 'm0_MSUN',
+              'm1_MSUN': 'm1_MSUN',
+      'luminosity_LSUN': 'luminosity_LSUN',
+   'bin_star_lum0_LSUN': 'bin_star_lum0_LSUN',
+   'bin_star_lum1_LSUN': 'bin_star_lum1_LSUN',
+             'startype': 'startype',
+        'bin_startype0': 'bin_startype0',
+        'bin_startype1': 'bin_startype1',
+          'radius_RSUN': 'radius_RSUN',
+'bin_star_radius0_RSUN': 'bin_star_radius0_RSUN',
+'bin_star_radius1_RSUN': 'bin_star_radius1_RSUN',
+                    'r': 'r',
+                   'vr': 'vr',
+                   'vt': 'vt',
+                'ospin': 'ospin',
+               'ospin0': 'ospin0',
+               'ospin1': 'ospin1',
+                'dmdt0': 'dmdt0',
+                'dmdt1': 'dmdt1',
+             }
+
+coldict_datgz = {'binflag': 'binflag',
+                  'm_MSUN': 'm[MSUN]',
[…]

### 2023-02-06 src/previous_steps/mw_orbits/ejection_orbits.py

@@ -1,0 +1,229 @@
+import os
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import multiprocessing as mp
+import parmap
+from tqdm import tqdm
+from galpy.orbit import Orbit
+from galpy.potential import MWPotential2014
+from astropy.coordinates import SkyCoord, Galactocentric
+from astropy import units as u
+
+import rustics
+import readoutput as ro
+import aggregate as ag
+
+###############################################################################
+
+helio_baumgardt = {
+    "galcen_distance": 8.1 * u.kpc,
+    "galcen_v_sun": np.array([11.1, 12.24 + 240, 7.25]) * u.km / u.s,
+    "z_sun": 0.0 * u.pc,
+}
+
+###############################################################################
+
+
+def integrate_cmc_ejections(
+    cmc_fnames,
+    mwgc_catalog,
+    cmc_path=rustics.PATH_TO_PROJECT + "/data",
+    ejections_fname="output_N-10_ejections.txt",
+    nprocs=128,
+):
+    """! A function to parallelize the integration of encounters."""
+
+    # Iterate over the cmc models first, so their data only have to be loaded once each
+    for ci, cmc_fname in enumerate(cmc_fnames):
+        print("[%d/%d] %s" % (ci+1, len(cmc_fnames), cmc_fname))
+
+        ##############################
+        ###   Load CMC ejections   ###
+        ##############################
+        # Make path to and load CMC ejections
+        path = "/".join((cmc_path, cmc_fname, ejections_fname))
+        cmc = rustics.EjectionDf(path)
+        cmc.convert_from_fewbody()
+        cmc.df["vout"] = cmc.calc_vout()
+        #cmc.df = cmc.df[-100:]
+
+        ##############################
+        ###    Loop through GCs    ###
+        ##############################
+        # Preliminary things
+        # NOTE: There are three time coordiate systems:
+        #       ts: ranges from present (t=0) to beginning of universe (t=-t_int)
+        #       cmc.df.time: ranges from beginning of universe (time=0) to present (time=t_int); t_ejs is in this convention
+        #       tfes: time from ejection, ranges from time of ejection (tfe=0) to t_int past that (tfe=t_int)
+        t0 = 0.0
+        t_int = 14000.0
+        Nt = 10000
[…]

### 2023-02-06 src/previous_steps/mw_orbits/ejection_orbits_old.py

@@ -1,0 +1,264 @@
+import os
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+import multiprocessing as mp
+import parmap
+from tqdm import tqdm
+from galpy.orbit import Orbit
+from galpy.potential import MWPotential2014
+from astropy.coordinates import SkyCoord, Galactocentric
+from astropy import units as u
+
+import rustics
+import readoutput as ro
+import aggregate as ag
+
+###############################################################################
+
+helio_baumgardt = {
+    "galcen_distance": 8.1 * u.kpc,
+    "galcen_v_sun": np.array([11.1, 12.24 + 240, 7.25]) * u.km / u.s,
+    "z_sun": 0.0 * u.pc,
+}
+
+###############################################################################
+
+
+def integrate_cmc_ejections(
+    cmc_fname,
+    mwgc_catalog,
+    cmc_path="/hildafs/projects/phy200025p/tcabrera/hvss/data",
+    ejections_fname="output_N-10_ejections.txt",
+):
+    """! A function to parallelize the integration of encounters, s.t. the CMC data only have to be loaded once."""
+
+    print(cmc_fname)
+
+    ##############################
+    ###   Load CMC ejections   ###
+    ##############################
+    # Make path to and load CMC ejections
+    path = "/".join((cmc_path, cmc_fname, ejections_fname))
+    cmc = rustics.EjectionDf(path)
+    cmc.convert_from_fewbody()
+    cmc.df["vout"] = cmc.calc_vout()
+    #cmc.df = cmc.df[-100:]
+
+    ##############################
+    ###    Loop through GCs    ###
+    ##############################
+    # Preliminary things
+    # NOTE: There are three time coordiate systems:
+    #       ts: ranges from present (t=0) to beginning of universe (t=-t_int)
+    #       cmc.df.time: ranges from beginning of universe (time=0) to present (time=t_int); t_ejs is in this convention
+    #       tfes: time from ejection, ranges from time of ejection (tfe=0) to t_int past that (tfe=t_int)
+    t0 = 0.0
+    t_int = 14000.0
+    Nt = 10000
+    ts = np.linspace(t0, -t_int, Nt) * u.Myr
+    t_ejs = (cmc.df.time.to_numpy() - t_int) * u.Myr
+
[…]

### 2023-02-06 src/previous_steps/mw_orbits/readoutput.py

@@ -1,0 +1,148 @@
+"""! @brief This module loads the standard CMC output files into a pandas DataFrame."""
+
+###############################################################################
+
+import numpy as np
+import pandas as pd
+
+import cmctoolkit
+
+###############################################################################
+
+
+class _dat_file:
+    """! The parent class for the individual files. """
+
+    def __init__(
+        self, path, header_line_no=0, colon_aliases=[], pd_kwargs={}, convert_units={},
+    ):
+        """! Read the data.
+
+        @param  path            The path to the output file.
+        @param  header_line_no  The line to read the columns from.
+        @param  colon_aliases   List-like of character to replace with colons (e.g. ["."] for dyn.dat files)
+        @param  pd_kwargs       Dictionary of keyword arguments to pass to pd.read_csv when loading data.
+                                Merges the specified dict with the default to preserve defaults.
+        @param  convert_units   Dictionary of units to convert (see _dat_file.convert_units)
+
+        """
+
+        # Save path
+        self.path = path
+
+        # Get the column names
+        names = self._get_column_names(path, header_line_no, colon_aliases)
+
+        # Merge specified pd_kwargs dist with default
+        pd_kwarg_defaults = {
+            "names": names,
+            "delimiter": " ",
+            "skiprows": header_line_no + 1,
+            "low_memory": False,
+        }
+        pd_kwargs = {**pd_kwarg_defaults, **pd_kwargs}
+
+        # Load data, passing usecols to select particular columns
+        self.df = pd.read_csv(path, **pd_kwargs,)
+
+        # Note that units are not converted from original values
+        self.units_converted = {n: False for n in self.df.columns}
+
+        # Convert any specified units on load
+        self.convert_units(convert_units)
+
+    def _get_column_names(self, path, header_line_no, colon_aliases=[]):
+        """! Parses the specified line in the file to get the header names.
+
+        @return columns     The column names.
+
+        """
+
+        # Read the header line
+        with open(path) as file:
+            for li, l in enumerate(file):
+                if li == header_line_no:
+                    names = l
+                    break
+
+        # Split at whitespace
+        names = names.split()
+
+        # Keep everything after the colon (using aliases if needed
+        for ca in colon_aliases:
+            names = [c.replace(ca, ":") for c in names]
+        names = [c.split(":")[1] for c in names]
+
+        return names
+
[…]

### 2023-02-06 src/previous_steps/mw_orbits/rustics.py

@@ -1,0 +1,1 @@
+../rustics/rustics.py

### 2023-02-06 src/previous_steps/mw_orbits/submit.sh

@@ -1,0 +1,11 @@
+#!/bin/bash
+#SBATCH -n 56 
+#SBATCH -t 720:00:00
+#SBATCH -J bsco_orbits 
+#SBATCH -o bsco_orbits.slurm
+#SBATCH -A phy200025p
+#SBATCH -p HENON
+# use the bash shell
+set -x 
+time python ejection_orbits.py
+

### 2023-02-06 src/previous_steps/scripts_original/hvss_hbin_cmc.py

@@ -1,0 +1,149 @@
+import sys
+import os
+import numpy as np
+import pandas as pd
+from tqdm import tqdm
+
+import hvss_utils
+
+################################################################################
+
+
+N = 10
+vbins = hvss_utils.VBINS
+binsingle_types = hvss_utils.BINSINGLE_TYPES_CMC_I
+bse_k_groups = hvss_utils.BSE_K_GROUPS
+age_groups = hvss_utils.AGE_GROUPS
+
+# Get CATALOG_MODELS et al. (note: different from other files!)
+catalog_models = hvss_utils.CATALOG_MODELS
+N_list = hvss_utils.N_LIST
+rv_list = hvss_utils.RV_LIST
+
+# Get cmc_core_collapsed.dat (file w/ cc times)
+core_collapsed = pd.read_csv("cmc_core_collapsed.dat")
+
+# initialize full catalog array (n_N, n_rv, n_age_groups, n_binsingle_types, n_bse_k_groups, n_vbins)
+catalog = np.zeros(
+    hvss_utils.CATALOG_SHAPE,
+    dtype=np.int32,
+)
+
+for mi, model in catalog_models.iterrows():
+
+    cmc_cluster = (
+        "N{}_".format(hvss_utils.ns_to_str(model.loc["N"] * 100000))
+        + "rv{:n}_".format(model.loc["rv"])
+        + "rg{:n}_".format(model.loc["rg"])
+        + "Z{}".format(model.loc["Z"])
+    )
+    print("\n{}, N={} ({}/{})".format(cmc_cluster, N, mi + 1, len(catalog_models)))
+
+    # Particular shorthands
+    data_file_path = (
+        hvss_utils.DATA_PATH
+        + cmc_cluster
+        + "/{}_N-{}".format(hvss_utils.FB_OUTPUT_FILENAME, N)
+    )
+
+    # Read saved data file
+    print("\tLoading data...")
+    try:
+        singles = pd.read_csv(
+            data_file_path + "_singles.txt",
+            names=hvss_utils.SINGLES_HEADERS,
+            dtype=np.float64,
+        )
+    except Exception as e:
+        print("\tError in loading singles data:".format(cmc_cluster, N))
+        print("\t\t", e)
+        print("\tContinuing...")
+        continue
+
+    # Get specific core_collapsed row
+    cc_row = core_collapsed[
+        (core_collapsed.N == model.loc["N"])
[…]

### 2023-02-06 src/previous_steps/scripts_original/hvss_hbin_isolated.py

@@ -1,0 +1,70 @@
+import sys
+import os
+import numpy as np
+import pandas as pd
+from tqdm import tqdm
+
+import hvss_utils
+
+################################################################################
+
+
+N = 1000000
+vbins = hvss_utils.VBINS
+binsingle_types = hvss_utils.BINSINGLE_TYPES_ISOLATED
+bse_k_groups = hvss_utils.BSE_K_GROUPS
+age_groups = hvss_utils.AGE_GROUPS
+
+# Particular shorthands
+data_file_path = hvss_utils.DATA_PATH + "isolated/{}_N-{}".format(
+    hvss_utils.FB_OUTPUT_FILENAME, N
+)
+
+# Read saved data file
+print("\tLoading data...")
+try:
+    singles = pd.read_csv(
+        data_file_path + "_singles.txt",
+        names=hvss_utils.SINGLES_HEADERS,
+        dtype=np.float64,
+    )
+except Exception as e:
+    print("\tError in loading singles data:".format(cmc_cluster, N))
+    print("\t\t", e)
+
+# remove outliers, filter out mergers
+# TODO: change to energy conservation criterion?
+singles = singles[(singles.type_f != 5)]
+
+# initialize binned array (n_age_groups, n_binsingle_types, n_bse_k_groups, n_vbins)
+data_binned = np.zeros(
+    hvss_utils.BINNED_SHAPE,
+    dtype=np.int32,
+)
+
+# print filtered dataframes
+# print('    dat.shape: ', dat.shape, '\n')
+print("\tsingles.shape: ", singles.shape)
+
+# vout histogram data
+print("\tBinning data...")
+for bti, binsingle_type in enumerate(binsingle_types):
+    for kgi, bse_k_group in enumerate(bse_k_groups):
+        for agi, age_group in enumerate(age_groups):
+            filtered = singles[
+                (singles.time >= age_group.lo)
+                & (singles.time < age_group.hi)
+                & (singles.kf >= bse_k_group.lo)
+                & (singles.kf < bse_k_group.hi)
+                & (singles.type_i == binsingle_type.id)
+            ]
+            filtered = filtered.dropna(subset=["vout"])
+            hist = [0] * (len(vbins) - 1)
+            if not filtered.empty:
+                hist, _ = np.histogram(filtered["vout"], bins=vbins)
+            data_binned[bti, kgi, agi, :] += hist
+np.savetxt(
+    "{}_binned.txt".format(data_file_path),
+    data_binned.flatten(),
+    fmt="%d",
+)

### 2023-02-06 src/previous_steps/scripts_original/hvss_realize_cmc.py

@@ -1,0 +1,280 @@
+import sys
+import os
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+from matplotlib.colors import ListedColormap
+from matplotlib import cm
+import subprocess
+import parmap
+import multiprocessing as mp
+from tqdm import tqdm
+
+import hvss_utils
+
+
+################################################################################
+
+
+def bin_log_lin(mn, mx, nb_log, nb_lin):
+    """Takes an interval and splits it into layered bins.
+    First layer is split logarithmically, second is linearly.
+    Arguments:
+        mn = lower bound of interval
+        mx = upper bound of interval
+        nb_log = number of logarithmic bins
+        nb_lin = numer of linear bins
+    Returns:
+        bins = returns list of bin intervals
+    """
+
+    # create logarithmic bins
+    log_bins = np.logspace(np.log10(mn), np.log10(mx), nb_log)
+
+    # create linear bins
+    bins = np.linspace(log_bins[:-1], log_bins[1:], nb_lin)
+
+    # transpose and flatten
+    bins = bins.transpose().flatten()
+
+    return bins
+
+
+def gen_fb_input(
+    path_to_cluster, N, seed_max, cmc_input_filename="full_initial.encounters.dat"
+):
+    """
+    Generates data for high-velocity star analysis with fewbody.
+        Arguments:
+            path_to_cluster = path specifying one CMC cluster
+            N = number of realizations per scattering
+            seed_max = maximum seed for fb_randorient
+            cmc_input_filename = file in zipped cluster to use
+        Returns:
+            fb_input = array of N*N_scatterings inputs for fewbody
+    """
+
+    # load cmc scatterings
+    scats = np.loadtxt(path_to_cluster + "/" + cmc_input_filename)
+
+    # check if there are no encounters
+    if not scats.any():
+        return scats
+
+    # filter out any with e1>=1.0
+    scats = scats[scats[:, 4] < 1.0]
+
+    # initialize fb_input array by repeating scattering array N times
+    fb_input = np.zeros((N * scats.shape[0], scats.shape[1] + 1))
+    fb_input[:, :-1] = np.repeat(scats, N, axis=0)
+
[…]

### 2023-02-06 src/previous_steps/scripts_original/hvss_utils.py

@@ -1,0 +1,638 @@
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+
+
+################################################################################
+
+
+class binsingle_type:
+    def __init__(self, id, id_string, color):
+        self.id = id
+        self.id_string = id_string
+        self.color = color
+
+    def print_self(self):
+        print(
+            (
+                f"threebody_type; id={self.id}; "
+                f"id_string={self.id_string}; color={self.color}"
+            )
+        )
+
+
+# Class for consolidating data groupings
+class data_group:
+    def __init__(self, name, short_name, label, lo, hi, color):
+        self.name = name
+        self.short_name = short_name
+        self.label = label
+        self.lo = lo
+        self.hi = hi
+        self.color = color
+
+
+################################################################################
+
+
+def ns_to_str(N):
+    """
+    Converts N from 10**5 value to string format.
+    """
+    return "{:.1e}".format(N).replace(".0", "").replace("+0", "")
+
+
+def sort_binsingle_types(bs_types, data):
+    """
+    Given a set of BSE k-type groups,
+    returns list of groups sorted by size in given dataset.
+    """
+    counts = []
+    for bs_type in bs_types:
+        counts.append(data[data.type_i == bs_type.id].shape[0])
+    bs_types_sorted = []
+    for ci in np.argsort(counts)[::-1]:
+        if counts[ci] > 0:
+            bs_types_sorted.append(bs_types[ci])
+    return bs_types_sorted
+
+
+def load_flattened(file_path, shape):
+    """
+    Loads flattened data files.
+    For hvss_bin_cmc.py data:
+        Binned data are stored as flattened 4D arrays:
+            (n_binsingle_types x n_bse_k_groups x n_agebins x n_vbins)
[…]

### 2023-02-06 src/previous_steps/matching_with_mywheels/aggregate.py
Updated readme; added binsingle_extractor notebook

@@ -1,158 +1,0 @@
-"""! @brief A module to combine data from several catalogs """
-
-###############################################################################
-
-import numpy as np
-import pandas as pd
-
-###############################################################################
-
-
-class GCCatalog:
-    def __init__(self, paths, pd_kwargs={}):
-        """! Basic things for now."""
-
-        # If a single path is specified, assume it is a loadable csv
-        if type(paths) == str:
-            self.df = pd.read_csv(paths, **pd_kwargs)
-
-        # If a list of paths is specified, assume it they are baumgardt and harris catalogs 
-        elif type(paths) == list:
-            # Set paths
-            baumgardt_path, harris_path = paths
-
-            # Load cleaned Baumgardt data
-            df_baumgardt = pd.read_csv(
-                baumgardt_path,
-                usecols=["Cluster", "Mass", "rc", "rh,m", "R_GC"],
-                delim_whitespace=True,
-            )
-
-            # Load cleaned Harris data (for metallicities)
-            # "cleaned" = ID renamed to Cluster, names edited to match Baumgardt & Holger, Z=-100 if there's no metallicity measurement (these clusters are also the ones with wt=0 i.e. no stellar metallicities have been measured)
-            df_harris = pd.read_csv(
-                harris_path, usecols=["Cluster", "[Fe/H]"], delim_whitespace=True
-            )
-            # drop rows with [Fe/H]=-100
-            df_harris = df_harris[df_harris["[Fe/H]"] != -100.0]
-
-            # Merge the two datasets
-            self.df = pd.merge(df_baumgardt, df_harris, how="inner", on="Cluster")
-
-            # Set cluster name as index
-            self.df.set_index("Cluster", inplace=True)
-
-    def match_to_cmc_models(
-        self, cmc_path, cmc_kwargs={}, dyn_kwargs={},
-    ):
-        """! Given a path to a CMC directory, finds the matching CMC models for the GCs."""
-
-        # Save cmc_path
-        self.cmc_path = cmc_path
-
-        # Load cmc catalog, and dyn.dat data
-        import readcatalog as cmccat
-
-        cmc_models = cmccat.CMCCatalog(cmc_path, extension=".tar.gz", mp_nprocs=56, **cmc_kwargs)
-        cmc_models.add_dat_timesteps(
-            "initial.dyn.dat",
-            tmin=10000.0,
-            tmax=13500.0,
[…]

### 2023-02-06 src/previous_steps/matching_with_mywheels/cmctoolkit.py

@@ -1,2478 +1,0 @@
-import numpy as np
-import pandas as pd
-import h5py
-import scipy.optimize
-import scipy.interpolate
-import gzip
-import time
-import os
-
-################################################################################
-# DEFINE CGS CONSTANTS
-################################################################################
-
-#Universal constants
-h, c, k, hbar = 6.6260755e-27, 2.99792458e10, 1.380658e-16, 1.05457266e-27
-G, sigma = 6.67259e-8, 5.67051e-5
-
-# Subsets
-startype_all = np.array([0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15])
-startype_star = np.array([0, 1, 2, 3, 4, 5, 6, 7, 8, 9])
-startype_ms = np.array([0, 1])
-startype_giant = np.array([2, 3, 4, 5, 6, 7, 8, 9])
-startype_wd = np.array([10, 11, 12])
-startype_other = np.array([7])
-startype_remnant = np.array([10, 11, 12, 13, 14])
-startype_bh = np.array([14])
-
-# Define column dictionaries; Snapshot class will pick the right column dictionary
-# depending on the format of the CMC output
-coldict_h5 = {'binflag': 'binflag',
-               'm_MSUN': 'm_MSUN',
-              'm0_MSUN': 'm0_MSUN',
-              'm1_MSUN': 'm1_MSUN',
-      'luminosity_LSUN': 'luminosity_LSUN',
-   'bin_star_lum0_LSUN': 'bin_star_lum0_LSUN',
-   'bin_star_lum1_LSUN': 'bin_star_lum1_LSUN',
-             'startype': 'startype',
-        'bin_startype0': 'bin_startype0',
-        'bin_startype1': 'bin_startype1',
-          'radius_RSUN': 'radius_RSUN',
-'bin_star_radius0_RSUN': 'bin_star_radius0_RSUN',
-'bin_star_radius1_RSUN': 'bin_star_radius1_RSUN',
-                    'r': 'r',
-                   'vr': 'vr',
-                   'vt': 'vt',
-                'ospin': 'ospin',
-               'ospin0': 'ospin0',
-               'ospin1': 'ospin1',
-                'dmdt0': 'dmdt0',
-                'dmdt1': 'dmdt1',
-             }
-
-coldict_datgz = {'binflag': 'binflag',
-                  'm_MSUN': 'm[MSUN]',
[…]

### 2023-02-06 src/previous_steps/matching_with_mywheels/match.py

@@ -1,499 +1,0 @@
-"""! @brief A module to combine data from several catalogs """
-###############################################################################
-
-import os
-import numpy as np
-import pandas as pd
-import multiprocessing as mp
-import parmap
-
-import cmctoolkit as cmctoolkit
-
-###############################################################################
-
-
-class CMCCatalog:
-    """! The class for a catalog of CMC models. """
-
-    def __init__(self, path, extension="02", mp_nprocs=1):
-        """! Initialize the catalog. 
-
-        @param  path            Path to the catalog.
-                                Should be a path to a directory that contains a folder for each of the models.
-        @param  extension       File extension on names; will be stripped, but is expected at end of all names.
-                                Note that default of "02" here a dirty way of keeping Kremer+20-like models.
-        @param  mp_nprocs       Number of processes to use for parallel tasks.
-
-        """
-
-        # Store things
-        self.path = path
-        self.mp_nprocs = mp_nprocs
-
-        # Get list of folder names
-        fnames = os.listdir(path)
-
-        # Make catalog dataframe, starting with fnames
-        self.df = pd.DataFrame(
-            [n for n in fnames if n.endswith(extension)], columns=["fname"]
-        ).set_index("fname")
-
-    def parse_names(self, replace={"_v2": ""}, cat_type="Kremer+20"):
-        """! Function to extract model parameters from names.
-        NB: The dtypes of parameter columns are reset whenever a .dat dataset is loaded.
-
-        @param  replace     Dictionary where the keys will be replaced with the values whenever they appear in the model name.
-                            Default removes any "_v2"s in the model names.
-        @param  cat_type    Name format.
-                            Default is "Kremer+20", i.e. the "N[_v2]_rv_rg_Z" convention from the respective catalog.
-
-        """
-
-        # TODO: move this to _parse_model_name
-        # Replace strings
-        fnames = self.df.index.get_level_values("fname")
-        for item in replace.items():
-            fnames = [n.replace(*item) for n in fnames]
-
-        # Extract params
-        params = [self._parse_model_name(n, cat_type=cat_type) for n in fnames]
-        params = pd.DataFrame(params, index=self.df.index)
-
-        # Join params to dataframe
-        self.df = self.df.join(params)
-
-    def _parse_model_name(self, model_name, cat_type="Kremer+20"):
-        """! Parse model names.  Currently only the base one is implemented.
-
[…]

### 2023-02-06 src/previous_steps/matching_with_mywheels/match_old.py

@@ -1,10 +1,0 @@
-import aggregate as ag
-
-mwcat = ag.GCCatalog(
-    ["/hildafs/projects/phy200025p/tcabrera/hvss_old_and_complete/holger_baumgardt_clean.txt",
-    "/hildafs/projects/phy200025p/tcabrera/hvss_old_and_complete/harris2010_II_clean.txt"],
-)
-print(mwcat.df)
-mwcat.match_to_cmc_models(
-    "/hildafs/projects/phy200025p/share/catalog_files",
-)

### 2023-02-06 src/previous_steps/matching_with_mywheels/readcatalog.py

@@ -1,198 +1,0 @@
-"""! @brief This module concerns reading data from a catalog of CMC models."""
-
-###############################################################################
-
-import os
-import numpy as np
-import pandas as pd
-import multiprocessing as mp
-import parmap
-
-import readoutput as readoutput
-
-###############################################################################
-
-
-class CMCCatalog:
-    """! The class for a catalog of CMC models. """
-
-    def __init__(self, path, extension="02", mp_nprocs=1):
-        """! Initialize the catalog. 
-
-        @param  path            Path to the catalog.
-                                Should be a path to a directory that contains a folder for each of the models.
-        @param  extension       File extension on names; will be stripped, but is expected at end of all names.
-                                Note that default of "02" here a dirty way of keeping Kremer+20-like models.
-        @param  mp_nprocs       Number of processes to use for parallel tasks.
-
-        """
-
-        # Store things
-        self.path = path
-        self.mp_nprocs = mp_nprocs
-
-        # Get list of folder names
-        fnames = os.listdir(path)
-
-        # Make catalog dataframe, starting with fnames
-        self.df = pd.DataFrame(
-            [n for n in fnames if n.endswith(extension)], columns=["fname"]
-        ).set_index("fname")
-
-    def parse_names(self, replace={"_v2": ""}, cat_type="Kremer+20"):
-        """! Function to extract model parameters from names.
-        NB: The dtypes of parameter columns are reset whenever a .dat dataset is loaded.
-
-        @param  replace     Dictionary where the keys will be replaced with the values whenever they appear in the model name.
-                            Default removes any "_v2"s in the model names.
-        @param  cat_type    Name format.
-                            Default is "Kremer+20", i.e. the "N[_v2]_rv_rg_Z" convention from the respective catalog.
-
-        """
-
-        # TODO: move this to _parse_model_name
-        # Replace strings
-        fnames = self.df.index.get_level_values("fname")
-        for item in replace.items():
-            fnames = [n.replace(*item) for n in fnames]
-
-        # Extract params
-        params = [self._parse_model_name(n, cat_type=cat_type) for n in fnames]
-        params = pd.DataFrame(params, index=self.df.index)
-
-        # Join params to dataframe
-        self.df = self.df.join(params)
-
-    def _parse_model_name(self, model_name, cat_type="Kremer+20"):
[…]

### 2023-02-06 src/previous_steps/matching_with_mywheels/readoutput.py

@@ -1,148 +1,0 @@
-"""! @brief This module loads the standard CMC output files into a pandas DataFrame."""
-
-###############################################################################
-
-import numpy as np
-import pandas as pd
-
-import cmctoolkit as cmctoolkit
-
-###############################################################################
-
-
-class _dat_file:
-    """! The parent class for the individual files. """
-
-    def __init__(
-        self, path, header_line_no=0, colon_aliases=[], pd_kwargs={}, convert_units={},
-    ):
-        """! Read the data.
-
-        @param  path            The path to the output file.
-        @param  header_line_no  The line to read the columns from.
-        @param  colon_aliases   List-like of character to replace with colons (e.g. ["."] for dyn.dat files)
-        @param  pd_kwargs       Dictionary of keyword arguments to pass to pd.read_csv when loading data.
-                                Merges the specified dict with the default to preserve defaults.
-        @param  convert_units   Dictionary of units to convert (see _dat_file.convert_units)
-
-        """
-
-        # Save path
-        self.path = path
-
-        # Get the column names
-        names = self._get_column_names(path, header_line_no, colon_aliases)
-
-        # Merge specified pd_kwargs dist with default
-        pd_kwarg_defaults = {
-            "names": names,
-            "delimiter": " ",
-            "skiprows": header_line_no + 1,
-            "low_memory": False,
-        }
-        pd_kwargs = {**pd_kwarg_defaults, **pd_kwargs}
-
-        # Load data, passing usecols to select particular columns
-        self.df = pd.read_csv(path, **pd_kwargs,)
-
-        # Note that units are not converted from original values
-        self.units_converted = {n: False for n in self.df.columns}
-
-        # Convert any specified units on load
-        self.convert_units(convert_units)
-
-    def _get_column_names(self, path, header_line_no, colon_aliases=[]):
-        """! Parses the specified line in the file to get the header names.
-
-        @return columns     The column names.
-
-        """
-
-        # Read the header line
-        with open(path) as file:
-            for li, l in enumerate(file):
-                if li == header_line_no:
-                    names = l
-                    break
-
-        # Split at whitespace
-        names = names.split()
-
-        # Keep everything after the colon (using aliases if needed
-        for ca in colon_aliases:
-            names = [c.replace(ca, ":") for c in names]
-        names = [c.split(":")[1] for c in names]
-
-        return names
-
[…]

### 2023-02-06 src/previous_steps/matching_with_mywheels/submit.sh

@@ -1,11 +1,0 @@
-#!/bin/bash
-#SBATCH -n 56 
-#SBATCH -t 720:00:00
-#SBATCH -J match 
-#SBATCH -o match.slurm
-#SBATCH -A phy200025p
-#SBATCH -p HENON
-# use the bash shell
-set -x 
-time python match.py
-

### 2023-02-06 src/previous_steps/mw_orbits/aggregate.py
Removed mw_orbits

@@ -1,149 +1,0 @@
-"""! @brief A module to combine data from several catalogs """
-
-###############################################################################
-
-import numpy as np
-import pandas as pd
-
-###############################################################################
-
-
-class GCCatalog:
-    def __init__(self, paths, pd_kwargs={}):
-        """! Basic things for now."""
-
-        # If a single path is specified, assume it is a loadable csv
-        if type(paths) == str:
-            self.df = pd.read_csv(paths, **pd_kwargs)
-
-        # If a list of paths is specified, assume it they are baumgardt and harris catalogs 
-        elif type(paths) == list:
-            # Set paths
-            baumgardt_path, harris_path = paths
-
-            # Load cleaned Baumgardt data
-            df_baumgardt = pd.read_csv(
-                baumgardt_path,
-                usecols=["Cluster", "Mass", "rc", "rh,m", "R_GC"],
-                delim_whitespace=True,
-            )
-
-            # Load cleaned Harris data (for metallicities)
-            # "cleaned" = ID renamed to Cluster, names edited to match Baumgardt & Holger, Z=-100 if there's no metallicity measurement (these clusters are also the ones with wt=0 i.e. no stellar metallicities have been measured)
-            df_harris = pd.read_csv(
-                harris_path, usecols=["Cluster", "[Fe/H]"], delim_whitespace=True
-            )
-            # drop rows with [Fe/H]=-100
-            df_harris = df_harris[df_harris["[Fe/H]"] != -100.0]
-
-            # Merge the two datasets
-            self.df = pd.merge(df_baumgardt, df_harris, how="inner", on="Cluster")
-
-            # Set cluster name as index
-            self.df.set_index("Cluster", inplace=True)
-
-    def match_to_cmc_models(
-        self, cmc_path, cmc_kwargs={}, dyn_kwargs={},
-    ):
-        """! Given a path to a CMC directory, finds the matching CMC models for the GCs."""
-
-        # Save cmc_path
-        self.cmc_path = cmc_path
-
-        # Load cmc catalog, and dyn.dat data
-        import mywheels.cmcutils.readcatalog as cmccat
-
-        cmc_models = cmccat.CMCCatalog(cmc_path, extension=".tar.gz", mp_nprocs=128, **cmc_kwargs)
-        cmc_models.add_dat_timesteps(
-            "initial.dyn.dat",
-            tmin=10000.0,
-            tmax=13500.0,
[…]

### 2023-02-06 src/previous_steps/mw_orbits/ejection_orbits.py

@@ -1,229 +1,0 @@
-import os
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as plt
-import multiprocessing as mp
-import parmap
-from tqdm import tqdm
-from galpy.orbit import Orbit
-from galpy.potential import MWPotential2014
-from astropy.coordinates import SkyCoord, Galactocentric
-from astropy import units as u
-
-import rustics
-import readoutput as ro
-import aggregate as ag
-
-###############################################################################
-
-helio_baumgardt = {
-    "galcen_distance": 8.1 * u.kpc,
-    "galcen_v_sun": np.array([11.1, 12.24 + 240, 7.25]) * u.km / u.s,
-    "z_sun": 0.0 * u.pc,
-}
-
-###############################################################################
-
-
-def integrate_cmc_ejections(
-    cmc_fnames,
-    mwgc_catalog,
-    cmc_path=rustics.PATH_TO_PROJECT + "/data",
-    ejections_fname="output_N-10_ejections.txt",
-    nprocs=128,
-):
-    """! A function to parallelize the integration of encounters."""
-
-    # Iterate over the cmc models first, so their data only have to be loaded once each
-    for ci, cmc_fname in enumerate(cmc_fnames):
-        print("[%d/%d] %s" % (ci+1, len(cmc_fnames), cmc_fname))
-
-        ##############################
-        ###   Load CMC ejections   ###
-        ##############################
-        # Make path to and load CMC ejections
-        path = "/".join((cmc_path, cmc_fname, ejections_fname))
-        cmc = rustics.EjectionDf(path)
-        cmc.convert_from_fewbody()
-        cmc.df["vout"] = cmc.calc_vout()
-        #cmc.df = cmc.df[-100:]
-
-        ##############################
-        ###    Loop through GCs    ###
-        ##############################
-        # Preliminary things
-        # NOTE: There are three time coordiate systems:
-        #       ts: ranges from present (t=0) to beginning of universe (t=-t_int)
-        #       cmc.df.time: ranges from beginning of universe (time=0) to present (time=t_int); t_ejs is in this convention
-        #       tfes: time from ejection, ranges from time of ejection (tfe=0) to t_int past that (tfe=t_int)
-        t0 = 0.0
-        t_int = 14000.0
-        Nt = 10000
[…]

### 2023-02-06 src/previous_steps/mw_orbits/ejection_orbits_old.py

@@ -1,264 +1,0 @@
-import os
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as plt
-import multiprocessing as mp
-import parmap
-from tqdm import tqdm
-from galpy.orbit import Orbit
-from galpy.potential import MWPotential2014
-from astropy.coordinates import SkyCoord, Galactocentric
-from astropy import units as u
-
-import rustics
-import readoutput as ro
-import aggregate as ag
-
-###############################################################################
-
-helio_baumgardt = {
-    "galcen_distance": 8.1 * u.kpc,
-    "galcen_v_sun": np.array([11.1, 12.24 + 240, 7.25]) * u.km / u.s,
-    "z_sun": 0.0 * u.pc,
-}
-
-###############################################################################
-
-
-def integrate_cmc_ejections(
-    cmc_fname,
-    mwgc_catalog,
-    cmc_path="/hildafs/projects/phy200025p/tcabrera/hvss/data",
-    ejections_fname="output_N-10_ejections.txt",
-):
-    """! A function to parallelize the integration of encounters, s.t. the CMC data only have to be loaded once."""
-
-    print(cmc_fname)
-
-    ##############################
-    ###   Load CMC ejections   ###
-    ##############################
-    # Make path to and load CMC ejections
-    path = "/".join((cmc_path, cmc_fname, ejections_fname))
-    cmc = rustics.EjectionDf(path)
-    cmc.convert_from_fewbody()
-    cmc.df["vout"] = cmc.calc_vout()
-    #cmc.df = cmc.df[-100:]
-
-    ##############################
-    ###    Loop through GCs    ###
-    ##############################
-    # Preliminary things
-    # NOTE: There are three time coordiate systems:
-    #       ts: ranges from present (t=0) to beginning of universe (t=-t_int)
-    #       cmc.df.time: ranges from beginning of universe (time=0) to present (time=t_int); t_ejs is in this convention
-    #       tfes: time from ejection, ranges from time of ejection (tfe=0) to t_int past that (tfe=t_int)
-    t0 = 0.0
-    t_int = 14000.0
-    Nt = 10000
-    ts = np.linspace(t0, -t_int, Nt) * u.Myr
-    t_ejs = (cmc.df.time.to_numpy() - t_int) * u.Myr
-
[…]

### 2023-02-06 src/previous_steps/mw_orbits/readoutput.py

@@ -1,148 +1,0 @@
-"""! @brief This module loads the standard CMC output files into a pandas DataFrame."""
-
-###############################################################################
-
-import numpy as np
-import pandas as pd
-
-import cmctoolkit
-
-###############################################################################
-
-
-class _dat_file:
-    """! The parent class for the individual files. """
-
-    def __init__(
-        self, path, header_line_no=0, colon_aliases=[], pd_kwargs={}, convert_units={},
-    ):
-        """! Read the data.
-
-        @param  path            The path to the output file.
-        @param  header_line_no  The line to read the columns from.
-        @param  colon_aliases   List-like of character to replace with colons (e.g. ["."] for dyn.dat files)
-        @param  pd_kwargs       Dictionary of keyword arguments to pass to pd.read_csv when loading data.
-                                Merges the specified dict with the default to preserve defaults.
-        @param  convert_units   Dictionary of units to convert (see _dat_file.convert_units)
-
-        """
-
-        # Save path
-        self.path = path
-
-        # Get the column names
-        names = self._get_column_names(path, header_line_no, colon_aliases)
-
-        # Merge specified pd_kwargs dist with default
-        pd_kwarg_defaults = {
-            "names": names,
-            "delimiter": " ",
-            "skiprows": header_line_no + 1,
-            "low_memory": False,
-        }
-        pd_kwargs = {**pd_kwarg_defaults, **pd_kwargs}
-
-        # Load data, passing usecols to select particular columns
-        self.df = pd.read_csv(path, **pd_kwargs,)
-
-        # Note that units are not converted from original values
-        self.units_converted = {n: False for n in self.df.columns}
-
-        # Convert any specified units on load
-        self.convert_units(convert_units)
-
-    def _get_column_names(self, path, header_line_no, colon_aliases=[]):
-        """! Parses the specified line in the file to get the header names.
-
-        @return columns     The column names.
-
-        """
-
-        # Read the header line
-        with open(path) as file:
-            for li, l in enumerate(file):
-                if li == header_line_no:
-                    names = l
-                    break
-
-        # Split at whitespace
-        names = names.split()
-
-        # Keep everything after the colon (using aliases if needed
-        for ca in colon_aliases:
-            names = [c.replace(ca, ":") for c in names]
-        names = [c.split(":")[1] for c in names]
-
-        return names
-
[…]

### 2023-02-06 src/previous_steps/mw_orbits/rustics.py

@@ -1,1 +1,0 @@
-../rustics/rustics.py

### 2023-02-06 src/previous_steps/mw_orbits/submit.sh

@@ -1,11 +1,0 @@
-#!/bin/bash
-#SBATCH -n 56 
-#SBATCH -t 720:00:00
-#SBATCH -J bsco_orbits 
-#SBATCH -o bsco_orbits.slurm
-#SBATCH -A phy200025p
-#SBATCH -p HENON
-# use the bash shell
-set -x 
-time python ejection_orbits.py
-

### 2023-02-08 src/tex/ms.tex
Fixed some references

@@
 For a sun-like star, this escape speed is $\sim$620 \kms, while for a 60 $M_\odot$ late main-sequence star it is $\sim$1400 \kms.
-\citet{2023arXiv230111444O} recently found that for OB runaways in the Small Magellanic Cloud, the DES is expected to occur 2-3 times more frequently that the BSS.
+\citet{2020ApJ...903...43D} found that for OB runaways in the Small Magellanic Cloud, the DES is expected to occur 2-3 times more frequently that the BSS.
 
 Globular clusters (GCs) are obvious candidate matrices for both of these events due to their high stellar densities, but the DES might be exceptionally amplified due to the presence of BH subsystems in the centers of GCs.
-Multi-band observations \citep{Maccarone2007a, Barnard2011, Chomiuk2013, Miller-Jones2015a} employing a variety of techniques \citep{Strader2012, Bahramian2016, Giesers2018} have been successful in finding tens of BH candidates in GCs, which are in themselves consistent with the presence of hundreds of BHs per cluster \citep{Giesers2019}.
+Multi-band observations \citep{Maccarone2007a, Barnard2011, Chomiuk2013, Miller-Jones2015a} employing a variety of techniques \citep{Strader2012, Bahramian2016, Giesers2018} have been successful in finding tens of BH candidates in GCs, which are in themselves consistent with the presence of hundreds of BHs per cluster \citep{2018ApJ...855L..15K, Giesers2019}.
 BHs play important roles in the macroscopic evolution of the GC \citep[e.g.][]{2020IAUS..351..357K} by dominating gravitational interactions in GC cores; this naturally places BHs in a privileged position when considering the DES in GCs, particularly when considering the maximum velocities attainable by this mechanism.
 
-Several recent and ongoing studies seek investigate these phenomena and the broader question of extra-tidal stars from GCs, in part encouraged by the continual improvement of astrometric measurements through efforts such as \textit{Gaia} \citet{2022A&A...667A.148G}.
+Several recent and ongoing studies have investigated these phenomena and the broader question of extra-tidal stars from GCs, in part encouraged by the continual improvement of astrometric measurements through efforts such as \textit{Gaia} \citep{2022arXiv220800211G}.
 \citet{2023MNRAS.518.4249G} developed and used a particle spray code to model ejections from GC cores and demonstrate that kinematic cuts can be too aggressive when searching for ejecta, preferring the use of chemical abundances alone.
@@
 
-\subsection{GC core collapses} \label{subsec:cc}
+\subsection{Core collapse in GCs} \label{subsec:cc}
 
-Core collapse is a well-documented feature of GC evolution (e.g.
-\citealt{1968MNRAS.138..495L}, \citealt{2001A&A...375..711F}, \citealt{2006MNRAS.368..121F}, \citealt{2008gady.book.....B}, \citealt{2020IAUS..351..357K}), and as will be seen is a significant factor in the ejection of stars from these systems.
-In general, a core collapse occurs when gravitational potential energy is rapidly liberated from the central region of a GC through dynamical encounters, causing the core to contract while energizing and potentially expanding the surrounding envelope of stars.
-Binaries play an important role in these processes, as their formation and hardening through strong encounters accelerate the other interacting stars, which subsequently travel to the more extended regions of the GC and potentially escape it entirely.
-The first core collapse of a GC tends to be propagated by these dynamics, causing the GC to puff up over the following Gyrs as the central binaries continue to shrink and the stellar density increases.
+Core collapses are well-documented features of GC evolution \citep[e.g.][]{1968MNRAS.138..495L, 2001A&A...375..711F, 2006MNRAS.368..121F, 2008gady.book.....B, 2020IAUS..351..357K}, and the heightened densities during such phenomena makes them relevant to the present study.
+This process occurs due to the energy transport by two-body relaxation from the central regions of the cluster outwards, causing a core to develop and contract while the outer regions expand \citep{2003gmbp.book.....H}.
+The presence of massive objects (e.g.
+BHs) can significantly accelerate this process, as dynamical friction slows the most massive objects in the system, causing them to segregate into the core on a much more rapid timescale \citep{2008gady.book.....B}.
+Following \cite{2013MNRAS.432.2779B}, we refer to this initial BH-lead collapse as the ``first’’ core collapse.
+While this process can be effected substantially by the metallicity of the star cluster, with more metal-rich clusters experiencing greater mass loss due to stellar winds and producing lower-mass BHs with correspondingly longer dynamical friction timescales (fewer of which are retained due to natal kicks) \citep{2022arXiv220316547R}, core collapse typically occurs within a few 100 Myr for most GCs.
 
-Dynamical friction-induced mass segregation \citep[e.g.][]{2008gady.book.....B} causes the core to be populated by the most massive objects in the GC, which also are those that first evolve into BHs.
-As the core contracts, successively stronger encounters eject all but a small handful of the initially 10s-100s of BHs; this reduced subsystem is unable to support the GC to the same extent as its predecessor, and so the interior of the GC contracts until a sufficiently strong replacement is composed.
-After \citet{2020IAUS..351..357K}, we employ this characteristic of BH ejection as a metric of whether a GC model has undergone this second kind of core collapse: once there are less than 10 BHs remaining in the model, we label it as core collapsed from that time onward.
+% From the beginning of a GC's lifetime, dynamical friction slows the most massive objects in the system, while simultaneously accelerating the less massive objects \citep[e.g.][]{2008gady.book.....B}.
+% Globally, this leads to the expansion of the outer layers of the cluster with a contemporary contraction of the core \citep{2013MNRAS.429.2881C}, usually within 100 Myr of the birth of the system.
+
+%This first core collapse is delayed and weakened in systems with higher metallicities: the increased mass loss due to stronger stellar winds directly leads to smaller objects that experience weaker dynamical friction, and indirectly the number of ``massive" objects is reduced as any that to evolve into BHs are more easily removed from the GC by natal kicks \citep{2008MNRAS.386...65M, 2022arXiv220316547R}.
+
+First core collapse is stopped by the formation and hardening of binaries in the core (which at this point is largely composed of BHs), and the liberated energy supports the universal expansion of the GC for a time on the order of Gyr \citep{2012MNRAS.420..309B}.
+The BH population in the core is gradually depleted as strong encounters accelerate their participants beyond the local escape speed, until no more than a handful of BHs remain in the cluster \citep{2013MNRAS.432.2779B, 2020IAUS..351..357K}.
+The loss of the dynamical heat source causes the core to contract again, as the system adjusts to being supported by WDs, NSs and stars in the same mass regime.
+Unlike the first collapse, this second, permanent core collapse is observable in that the surface brightness profile of the GC becomes cuspy to the limit of the cluster center (and is what observers would classically call a ``core-collapsed cluster'').
+We follow \citet{2018ApJ...855L..15K} in pairing these demographic and observable features, marking the time of second core collapse in our models as the same time the number of BHs drops below 10.
 
@@
 where $\bar{x}_{\rm CMC}$ and $\sigma_{\rm x,CMC}$ are respectively the mean and standard deviation of the parameter $x$ over the complete set of \CMC\ snapshots.
-The snapshot from the $r_{\rm gc}$ - [Fe/H] subset that is closest to the MWGC in the normalized $\log M$ - $r_c / r_h$ space is chosen to represent the GC; as an example, 47 Tuc ($r_{\rm gc} = 7.52$ kpc, $Z = 0.0019$; $\log M = 5.95$, $r_c / r_h,m = 0.125$) is represented by a snapshot from model \texttt{N1.6e6\_rv2\_rg8\_Z0.002}, which at the 10.8 Gyr time of the snapshot has $\log M = 5.91$ and $r_c / r_h = 0.126$.
+The snapshot from the $r_{\rm gc}$ - [Fe/H] subset that is closest to the MWGC in the normalized $\log M$ - $r_c / r_h$ space is chosen to represent the GC; as an example, 47 Tuc ($r_{\rm gc} = 7.52$ kpc, $Z = 0.0019$; $\log M = 5.95$, $r_c / r_h,m = 0.125$ \citep{2018MNRAS.478.1520B, 2010arXiv1012.3224H}) is represented by a snapshot from model \texttt{N1.6e6\_rv2\_rg8\_Z0.002}, which at the 10.8 Gyr time of the snapshot has $\log M = 5.91$ and $r_c / r_h = 0.126$.
 
@@
 The distributions of distance from the galactic origin, and the local distributions of galactocentric velocity are similar when distributing over radius $r_{\rm gc}$ versus distance from the galactic plane $Z_{\rm gc}$.
-Most runaways end up at a distance on the order of 10 pc from the galactic center, and with a velocity on the order of 100-300~\kms.
-Few runaways make it past the $\sim$100 pc mark, but those that do naturally retain the highest velocities, reaching upwards of 1000~\kms.
+Most runaways end up at a distance on the order of 10 kpc from the galactic center, and with a velocity on the order of 100-300~\kms in the galactocentric rest frame.
+Few runaways make it past the 100 kpc mark, but those that do naturally retain the highest velocities, reaching upwards of 1000~\kms.
 
@@
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/rgc-z_S.pdf}
+        \includegraphics[width=0.9\linewidth]{figures/rgc-z_S.pdf}
         \caption{
-            Histograms and velocity quantiles for the synthetic ejecta.
+            Histograms (top) and velocity quantiles (bottom) for the synthetic stellar ejecta.
             The left (right) plots show the profile over radial distance from the galactic center $r_{\rm gc}$ (distance from the galactic plane $Z$).
             The quantiles in the lower plots are calculated from the present-day velocities of our population.
+            The red dots show the $r_{\rm gc}$ ($Z$) positions of the MWGCs from our composite \citet{2018MNRAS.478.1520B}+\citet{2010arXiv1012.3224H} catalog, arbitrarily spread in the vertical dimension.
         }
@@
 
-One result of note is that of the heliocentric radial velocity $v_{\rm rf}$ distribution of the synthetic population.
+\begin{figure}
+    \script{cmc_orbits_cdf.py}
+    \begin{centering}
+        \includegraphics[width=0.99\linewidth]{figures/cmc_orbits_cdf_S.pdf}
+        \caption{
+            Velocity distributions for our synthetic and some previous observational HVS catalogs.
+            $v_{\rm rf}$ is the heliocentric radial velocity of the star as measured in the galactic rest frame.
+        }
+        \label{fig:cmc_orbits_cdf}
+    \end{centering}
+\end{figure}
+
+\begin{figure}
+    \script{mwej_rates.py}
+    \begin{centering}
+        \includegraphics[width=0.99\linewidth]{figures/mwej_rates.pdf}
+        \caption{
+            The evolution of the ejection rate for different components of our synthetic population.
+            The blue (red) dashed line shows the estimated from observations for runaways from the galactic disc (HVSs from the galactic center), as reported by \citet{2015ARA&A..53...15B}.
+        }
+        \label{fig:mwej_rates}
+    \end{centering}
+\end{figure}
+
+One result of note is that of the heliocentric radial velocity, $v_{\rm rf}$, distribution of the synthetic population.
 \citet{2021arXiv211213864G} in part studied the galactic center origin of HVSs, and found that there is an apparent tension between the observed and predicted runaway populations; specifically, the predicted number of stars with velocities $\gtrsim 700~{\rm km~s^{-1}}$ was much higher than the observed rate from the HVS sample of \citet{2018ApJ...866...39B}.
@@
 The assumption of isotropy in calculating $\langle v_{\rm f|GC} \rangle$ is appropriate for resonant encounters wherein the dynamics are chaotic.
-For flyby encounters where the objects travel on roughly hyperbolic trajectories, there is a preference for post-encounter velocities in the same direction as the initial velocity, if the impact parameter distribution is sufficiently expansive and weighted by the square of the parameter and the final velocities are marginalized over the angle that orients the plane of the ``2-body" encounter.
+For flyby encounters where the objects travel on roughly hyperbolic trajectories, there is a preference for post-encounter velocities in the same direction as the initial velocity, if the impact parameter distribution is sufficiently expansive and weighted by the square of the parameter and the final velocities are marginalized over the angle that orients the plane of the 2-body encounter between the star and the binary center-of-mass.
 The isotropic case is therefore a conservative limit on this flyby case, and predicts a greater boost-propagated speedup than if the calculation was done in full detail.
 
-In summary, neglecting to return to the model rest frame after the \fewbody\ step for strong encounters is found to not favor faster or slower post-encounter speeds when the final speed of an object is much greater than or much less than the center-of-mass speed of the encounter.
-There is an average speedup of 30\% when the two speeds are comparable, but this latter condition means that the speeds themselves are less than the maximum initial speed between the objects, which limits the extent to which the boost itself reveals speeds in excess of the escape velocity.
+In summary, neglecting to return to the model rest frame after the \fewbody\ step for strong encounters does not favor faster or slower post-encounter speeds when the final speed of an object is much greater than or much less than the center-of-mass speed of the encounter in the model rest frame.
+In the case that the final speed of an object is comparable to the same center-of-mass speed, the average post-transformation boost of 30\% is unlikely to significantly increase the number of ejections, as the two speeds are generally less than the maximum initial speed among objects entering the encounter.
 
 \section{Ejecta credible regions} \label{app:credreg}
-
-We include with this publication phase credible regions in phase space for ejecta populations from the MWGCs considered, which may be accessed at [LINK].
-We intend these constructions to be used as secondary evidence for cluster membership of runaway stars, and to encourage further studies into understanding the respective phase space distributions.
-The 2D position and proper motion distributions are separated into two different files, the conventions of which are described below.
-
-The distribution of ejecta on the sky is quantified by discretizing the sphere with an order 4 nested HEALPix map [CITE], binning the sky into 3072 equal-area tiles.
-We choose this resolution to enable identification of interesting credible regions while minimizing the apparent effect of isolated points whose exact location is dependent on the RNG seeds used.
-We create the respective histogram by counting the number of synthetic ejecta that are found in each tile in the present day, and normalize by the total number of ejecta for the GC.
-The resulting probability histogram is stored in the first column (\texttt{PROBS}) of the \texttt{hp\_probs.fits} file for each GC; the \texttt{NEJECT} field in the header of the same file contains the number of ejections for the GC.
-We calculate our credible regions by cumulatively adding the highest probability bins until the target percentage is reached.
-The last two columns (\texttt{CR50} and \texttt{CR90}) are boolean masks of the same convection as the HEALPix probability histogram corresponding to the credible regions (50\% and 90\%, respectively), where bins with entries of 1 are included in the region.
-Figure \ref{fig:check_credible_regions_x} shows the histogram and 50\% and 90\% credible regions for E3, as an example (the script used to generate this plot is \texttt{check\_credible\_regions.py} in the GitHub repository; click on the icon by the caption to be taken directly to the file).
 
@@
     \caption{
-        The HEALPix histogram for a sample GC (E3), with the 50\% and 90\% credible regions in the right subplot.
-        Galactic coordinates are used.
+        The HEALPix histogram for a sample GC (NGC 104), with the 50\% and 90\% credible regions in the right subplot.
+        Galactic coordinates are used, and the histogram weights are log scaled.
     }
@@
 \end{figure}
-
-We construct proper motion histograms and credible regions in a similar manner.
-We use a domain of $-30 \le \mu_\alpha \cos \delta~{\rm [km~s^{-1}]} \le 30$, $-45 \le \mu_\delta~{\rm [km~s^{-1}]} \le 15$ divided into a 50 $\times$ 50 grid.
-These bounds and resolution are included in the headers of the \texttt{pm\_prob.fits} files for each GC, where calling \texttt{np.linspace(PM[D/RCD]MIN, PM[D/RCD]MAX, PMNUM)} will return the bin edges used for the appropriate dimension.
-The header also includes a \texttt{COVERAGE} field containing the fraction of ejecta that lie in the specified domain; for all GCs this fraction is at least 0.98, and in most cases is greater than 0.999.
-The total number of ejected objects (including those outside of the domain) is stored in the \texttt{NEJECT} field, as for the HEALPix histograms.
-The proper motion histogram and respective masks for the 50\% and 90\% credible regions are stored in the \texttt{pm\_prob.fits} files as separate HDUs; these items for the same example GC as the HEALPix plot is show in Figure \ref{fig:check_credible_regions_v}, and the same \texttt{check\_credible\_regions.py} script contains the generating code.
 
@@
 
+We include with this publication phase credible regions in phase space for ejecta populations from the MWGCs considered, which may be accessed at \url{https://zenodo.org/record/7599871}.
+We intend these constructions to be used as secondary evidence for cluster membership of runaway stars, and to encourage further studies into understanding the respective phase space distributions.
+The 2D position and proper motion distributions are separated into two different files, the conventions of which are described below.
+
+The distribution of ejecta on the sky is quantified by discretizing the sphere with an order 4 nested HEALPix map \citep{2005ApJ...622..759G}, binning the sky into 3072 equal-area tiles.
+We choose this resolution to enable identification of interesting credible regions while minimizing the apparent effect of isolated points whose exact location is dependent on the RNG seeds used.
+We create the respective histogram by counting the number of synthetic ejecta that are found in each tile in the present day, and normalize by the total number of ejecta for the GC.
+The resulting probability histogram is stored in the first column (\texttt{PROBS}) of the \texttt{hp\_probs.fits} file for each GC; the \texttt{NEJECT} field in the header of the same file contains the number of ejections for the GC.
+We calculate our credible regions by cumulatively adding the highest probability bins until the target percentage is reached.
+The last two columns (\texttt{CR50} and \texttt{CR90}) are boolean masks of the same convection as the HEALPix probability histogram corresponding to the credible regions (50\% and 90\%, respectively), where bins with entries of 1 are included in the region.
+Figure \ref{fig:check_credible_regions_x} shows the histogram and 50\% and 90\% credible regions for NGC 104, as an example (the script used to generate this plot is \texttt{check\_credible\_regions.py} in the GitHub repository; click on the icon by the caption to be taken directly to the file).
+
+We construct proper motion histograms and credible regions in a similar manner.
+We use a domain of $-30 \le \mu_\alpha \cos \delta~{\rm [km~s^{-1}]} \le 30$, $-45 \le \mu_\delta~{\rm [km~s^{-1}]} \le 15$ divided into a 50 $\times$ 50 grid.
+These bounds and resolution are included in the headers of the \texttt{pm\_prob.fits} files for each GC, where calling \texttt{np.linspace(PM[D/RCD]MIN, PM[D/RCD]MAX, PMNUM)} will return the bin edges used for the appropriate dimension.
+The header also includes a \texttt{COVERAGE} field containing the fraction of ejecta that lie in the specified domain; for all GCs this fraction is at least 0.98, and in most cases is greater than 0.999.
+The total number of ejected objects (including those outside of the domain) is stored in the \texttt{NEJECT} field, as for the HEALPix histograms.
+The proper motion histogram and respective masks for the 50\% and 90\% credible regions are stored in the \texttt{pm\_prob.fits} files as separate HDUs; these items for the same example GC as the HEALPix plot is show in Figure \ref{fig:check_credible_regions_v}, and the same \texttt{check\_credible\_regions.py} script contains the generating code.
+
 \bibliography{bib}

### 2023-04-20 src/tex/ms.tex
Comment responses, inc. DOI links

@@
 
-Figure \ref{fig:cmc_single_clusters} shows the ejection velocity $v_{\rm out}$ for every MS star ejected through a BSCO encounter in these models, plotted at the time of encounter from initialization $t$.
+Figure \ref{fig:cmc_single_clusters} shows the ejection velocity $v_{\rm out}$ for every MS star ejected through a BSCO encounter in these models, plotted at the time of encounter from initialization $t$; \textbf{generally, these ejecta account for $\sim$1-6\% of all stellar escapers from a model over its lifetime}.
 What is immediately apparent from these single cluster models is a strong correlation between BSCO encounters and the evolution of the cluster core: whenever a cluster undergoes a core collapse, the heightened densities lead to predictably high encounter rates.
@@
 An interplay between stellar evolution and cluster dynamics is revealed in the kinds of BSCO encounters that occur at certain times.
-The most massive stars in a cluster are both the first to form binaries and the first to evolve into COs; hence, encounters between a mixed binary (composed of a MS star and a CO) and a single MS star tend to dominate the first generations of BSCO encounters.
-This dominance usually continues until the first core collapse after CO formation, where the heightened densities facilitate a rise in encounters involving multiple COs.
-There is a stark difference in the ejection velocities produced by these encounters in comparison to the previous mixed binary-single MS star encounters, and the fastest ejections over the cluster's lifetime are produced in the first tens of Myr after the associated first core collapse.
+The most massive stars in a cluster are both the first to form binaries and the first to evolve into COs.
+hence, encounters between a mixed binary (composed of a MS star and a CO) and a single MS star \textbf{have the first opportunity to contribute significantly to the overall BSCO encounter population; in the densest models, this primacy leads to a majority of BSCO encounters being of this type over the 14 Gyr evolution.
+Multiple-CO encounters first become major players at first core collapse after CO formation, and can take over as the majority in the case of models with weak or nonexistent pre-core collapse BSCO encounter phases.}
+There is a stark difference in the ejection velocities produced by these multiple-CO encounters in comparison to the previous mixed binary-single MS star encounters, and the fastest ejections over the cluster's lifetime are produced in the first tens of Myr after the associated first core collapse.
 This regime lasts for a few to tens of Gyr, during which the COs in the core (predominantly BHs) preferentially form CO-CO binaries, as evidenced in the drop of mixed binary-single CO encounters during this phase.
@@
 For comparison, the escape velocity from the center of the model can be computed from the central and tidal boundary potentials, which are recorded throughout the evolution of the cluster.
-Figure \ref{fig:cmc_single_clusters_vesc} plots these data for the same sample clusters, where the distribution of encounter escape velocities is strikingly correlated to the central escape velocity, indicating the degree to which the core dominates these dynamics.
+\textbf{
+    Figure \ref{fig:cmc_single_clusters_vesc} plots these data for the first sample cluster, where the distribution of encounter escape velocities is strikingly correlated to the central escape velocity, indicating the degree to which the core dominates these dynamics.
+    Throughout the evolution of the model, most BSCO ejections occur at or near the central escape velocity, and this feature is common to the counterpart plots for the other sample models.
+    There is a small fraction of points that lie above the core velocity line, which we attribute to the difference in methods employed to calculate escape velocities in the ejection and core contexts.
+}
 
@@
     \caption{
-        The local escape velocities $v_{\rm esc}$ of all BSCO encounters generated from the four sample \CMC\ models (colored points), plotted alongside the central escape velocity of the model (maroon).
+        \textbf{
+        The local escape velocities $v_{\rm esc}$ at the locations of all BSCO encounters generated from the first sample \CMC\ model (colored points), plotted alongside the central escape velocity of the model (navy).
+        The top plot shows the data in units of ${\rm km~s^{-1}}$, while the lower plot shows the same data normalized to the continuum of the core escape velocity (navy line in the upper plot).
+        }
         See Figure \ref{fig:cmc_single_clusters} for an explanation of the color scheme.
@@
 All orbit integrations in the galactic frame are done with \texttt{galpy}\footnote{http://github.com/jobovy/galpy} \citep{2015ApJS..216...29B}.
-Setting the snapshot to the present-day galactic orbital parameters from \citet{2018MNRAS.478.1520B}, we back-integrate the orbit of each GC in the \texttt{galpy}\texttt{MWPotential2014} potential to the initialization time of the respective model.
+Setting the snapshot to the present-day galactic orbital parameters from \citet{2018MNRAS.478.1520B}, we back-integrate the orbit of each GC in the \texttt{galpy} \texttt{MWPotential2014} potential to the initialization time of the respective model.
 We then locate each ejected object at the appropriate place in the GC orbit, using the time of BSCO encounter (naturally ignoring any ejections that occurred after the time of the chosen snapshot).
@@
 \begin{figure*}
-    %\script{gc_orbit_ejections.py}
+    \script{gc_orbit_ejections.py}
     \gridline{
@@
     \gridline{
-        \fig{figures/gcej_today_NGC_104.pdf}{0.45\textwidth}{}
-        \fig{figures/gcej_today_NGC_5139.pdf}{0.45\textwidth}{}
+        \fig{figures/gcej_today_NGC_104.pdf}{0.425\textwidth}{}
+        \fig{figures/gcej_today_NGC_5139.pdf}{0.425\textwidth}{}
     }
     \gridline{
-        \fig{figures/gcej_today_NGC_6205.pdf}{0.45\textwidth}{}
-        \fig{figures/gcej_today_NGC_7089.pdf}{0.45\textwidth}{}
+        \fig{figures/gcej_today_NGC_6205.pdf}{0.425\textwidth}{}
+        \fig{figures/gcej_today_NGC_7089.pdf}{0.425\textwidth}{}
     }
@@
             The blue (red) dashed line shows the estimated from observations for runaways from the galactic disc (HVSs from the galactic center), as reported by \citet{2015ARA&A..53...15B}.
+            \textbf{The threshold times by which 50\% and 90\% of the runaway ejections have occured are indicated along the bottom of the figure.}
         }
@@
 Finally, Figure \ref{fig:mwej_rates} shows the HVS/runaway rates for our synthetic population, along with observational rate estimates from \citet{2015ARA&A..53...15B}.
-At earlier times, BSCO ejecta could have made as much as 20\% (1\%) of all runaways (HVSs), during the times when GCs underwent their first core collapses.\footnote{Here, the cutoff of this phase is fairly abrupt because we constrain our models to present-day ages of 10-13.5 Gyr (\S\ref{subsec:pairing}).
+\textbf{We note that 50(90)\% of ejections occur before our synthetic population is \variable{output/mwej_rates.txt}old, and that naturally the earliest ejections are most dependent on any time variability in the MW potential.}
+At these earlier times, BSCO ejecta could have made as much as 20\% (1\%) of all runaways (HVSs), during the times when GCs underwent their first core collapses.\footnote{Here, the cutoff of this phase is fairly abrupt because we constrain our models to present-day ages of 10-13.5 Gyr (\S\ref{subsec:pairing}).
 The physical rate will naturally be characterized by the evolution of the GC formation rate in the past.}
@@
 \software{\CMC\ \citep{2000ApJ...540..969J, 2013ApJS..204...15P, Rodriguez2022}, \fewbody \citep{2004MNRAS.352....1F}, \texttt{galpy} \citep{2015ApJS..216...29B}, \texttt{astropy} \citep{2013A&A...558A..33A, 2018AJ....156..123A, 2022ApJ...935..167A}, \texttt{numpy} \citep{harris2020array}, \texttt{pandas} \citep{mckinney-proc-scipy-2010, reback2020pandas}, \texttt{matplotlib} \citep{Hunter:2007}}
+
+This work was prepared in part with the reproducibility software \href{https://github.com/showyourwork/showyourwork}{\showyourwork}\citep{2021arXiv211006271L}, which leverages continuous integration to transparently connect the paper to the publicly-available dataset and relevant code.
+The GitHub repository for this project can be found at \url{https://github.com/tomas-cabrera/hvss-bsco}; the icons next to paper content link to the particular scripts used to generate that content.
+The dataset is stored at \url{https://doi.org/10.5281/zenodo.7599870}, which also includes copies of the simulation and figure scripts from the GitHub for insurance of future access.
 
@@
 
-We include with this publication phase credible regions in phase space for ejecta populations from the MWGCs considered, which may be accessed at \url{https://zenodo.org/record/7599871}.
+We include with this publication phase credible regions in phase space for ejecta populations from the MWGCs considered, which may be accessed at \url{https://doi.org/10.5281/zenodo.7599870}.
 We intend these constructions to be used as secondary evidence for cluster membership of runaway stars, and to encourage further studies into understanding the respective phase space distributions.

### 2023-04-20 src/scripts/cmc_single_clusters.py

@@ -107,7 +107,7 @@ for ci, cmc_cluster in enumerate(cmc_cluster_list):
     axr.plot(
         df_dyn.loc[tsample, "t"] / 1000.0,
         df_dyn.loc[tsample, "rho_0"],
-        color="xkcd:crimson",
+        color="xkcd:navy",
         alpha=0.7,
         lw=0.5,
         rasterized=True,

### 2023-04-20 src/scripts/cmc_single_clusters_types.py

@@ -1,0 +1,79 @@
+import sys
+import os
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+from matplotlib.colors import ListedColormap
+from matplotlib import cm
+from matplotlib.legend_handler import HandlerTuple
+import matplotlib.ticker as mplticker
+
+import rustics
+import paths
+
+################################################################################
+
+# plt.style.use(rustics.PATH_TO_MPLRC)
+
+# Get cluster names
+cmc_cluster_list = list(rustics.SAMPLE_MODELS.keys())
+for ci, cmc_cluster in enumerate(cmc_cluster_list):
+    print("{}, N_REALZ={}".format(cmc_cluster, rustics.N_REALZ))
+
+    # File names and directory creation
+    path_to_ejections = paths.data_cmc / cmc_cluster / rustics.FILE_EJECTIONS
+
+    # Read saved data file
+    ejdf = rustics.EjectionDf(path_to_ejections)
+    ejdf.df = ejdf.df
+
+    # Convert to physical units
+    ejdf.convert_from_fewbody()
+
+    # Filter out mergers
+    ejdf.df = ejdf.df[ejdf.df["type_f"] > 0]
+
+    # Load times and core radii from initial.dyn.dat
+    df_esc = pd.read_csv(
+        paths.data_cmc / cmc_cluster / "initial.esc.dat",
+        names=["t", "phi_rtidal", "phi_zero"],
+        usecols=[1, 9, 10],  # 1 for t, 9 for phi_rtidal, 10 for phi_zero
+        skiprows=1,
+        delim_whitespace=True,
+    )
+
+    # Load initial.conv.sh (for converting TotalTime to Myr and core vesc to km/s)
+    # Copied from cmctools/cmctoolkit.py
+    conv_path = paths.data_cmc / cmc_cluster / "initial.conv.sh"
+    f = open(conv_path, "r")
+    convfile = f.read().split("\n")
+    f.close()
+    lengthunitcgs = float(convfile[13][14:])
+    timeunitsmyr = float(convfile[19][13:])
+    nbtimeunitcgs = float(convfile[21][14:])
+    nb_kms = 1e-5 * lengthunitcgs / nbtimeunitcgs
+    df_esc["t"] *= timeunitsmyr
+    df_esc["phi_rtidal"] *= nb_kms**2
[…]

### 2023-04-20 src/scripts/cmc_single_clusters_vesc.py

@@ -1,15 +1,17 @@
-import sys
 import os
+import sys
+
+import matplotlib.pyplot as plt
+import matplotlib.ticker as mplticker
 import numpy as np
 import pandas as pd
-import matplotlib.pyplot as plt
-from matplotlib.colors import ListedColormap
-from matplotlib import cm
-from matplotlib.legend_handler import HandlerTuple
-import matplotlib.ticker as mplticker
-
-import rustics
 import paths
+import rustics
+import scipy.interpolate
+from matplotlib import cm
+from matplotlib.colors import ListedColormap
+from matplotlib.legend_handler import HandlerTuple
+from matplotlib.lines import Line2D
 
 ################################################################################
 
@@ -17,20 +19,36 @@ import paths
 
 # Get cluster names
 cmc_cluster_list = list(rustics.SAMPLE_MODELS.keys())
-print("check12")
 mosaic = np.reshape(cmc_cluster_list, (4, 1))
+# Redefine for single-cluster plots
+cmc_cluster_list = cmc_cluster_list[:1]
+mosaic = np.array([[c + "_standard", c + "_flattened"] for c in cmc_cluster_list]).T
 figwidth = rustics.textwidth
-figheight = rustics.textwidth / 4 * 1.5
+figheight = rustics.textwidth / 4 * 1.75
 fig, axd = plt.subplot_mosaic(
     mosaic,
     figsize=(mosaic.shape[1] * figwidth, mosaic.shape[0] * figheight),
     sharex=True,
-    sharey=True,
+    # sharey=True,
     gridspec_kw={
         "hspace": 0,
         "wspace": 0,
     },
 )
+ms = 0.25
+kw_scatter = {
+    "linestyle": "None",
+    # label=ti_row.label,
+    "marker": "+",
+    "markersize": 0.25,  # irrelevant for marker="," (pixels)
+    "alpha": ms,
+    "rasterized": True,
+}
+kw_vesccore = {
+    "color": "xkcd:navy",
+    "lw": 1,
+    "rasterized": True,
+}
 for ci, cmc_cluster in enumerate(cmc_cluster_list):
     print("{}, N_REALZ={}".format(cmc_cluster, rustics.N_REALZ))
 
@@ -74,37 +92,34 @@ for ci, cmc_cluster in enumerate(cmc_cluster_list):
     type_is = ejdf.df.value_counts("type_i").index
[…]

### 2023-04-20 src/scripts/cmc_single_clusters_vesc_old.py

@@ -1,0 +1,170 @@
+import sys
+import os
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+from matplotlib.colors import ListedColormap
+from matplotlib import cm
+from matplotlib.legend_handler import HandlerTuple
+import matplotlib.ticker as mplticker
+
+import rustics
+import paths
+
+################################################################################
+
+# plt.style.use(rustics.PATH_TO_MPLRC)
+
+# Get cluster names
+cmc_cluster_list = list(rustics.SAMPLE_MODELS.keys())
+print("check12")
+mosaic = np.reshape(cmc_cluster_list, (4, 1))
+figwidth = rustics.textwidth
+figheight = rustics.textwidth / 4 * 1.75
+fig, axd = plt.subplot_mosaic(
+    mosaic,
+    figsize=(mosaic.shape[1] * figwidth, mosaic.shape[0] * figheight),
+    sharex=True,
+    # sharey=True,
+    gridspec_kw={
+        "hspace": 0,
+        "wspace": 0,
+    },
+)
+for ci, cmc_cluster in enumerate(cmc_cluster_list):
+    print("{}, N_REALZ={}".format(cmc_cluster, rustics.N_REALZ))
+
+    # File names and directory creation
+    path_to_ejections = paths.data_cmc / cmc_cluster / rustics.FILE_EJECTIONS
+
+    # Read saved data file
+    ejdf = rustics.EjectionDf(path_to_ejections)
+    ejdf.df = ejdf.df
+
+    # Convert to physical units
+    ejdf.convert_from_fewbody()
+
+    # Filter out mergers
+    ejdf.df = ejdf.df[ejdf.df["type_f"] > 0]
+
+    # Load times and core radii from initial.dyn.dat
+    df_esc = pd.read_csv(
+        paths.data_cmc / cmc_cluster / "initial.esc.dat",
+        names=["t", "phi_rtidal", "phi_zero"],
+        usecols=[1, 9, 10],  # 1 for t, 9 for phi_rtidal, 10 for phi_zero
+        skiprows=1,
+        delim_whitespace=True,
+    )
+
+    # Load intial.conv.sh (for converting TotalTime to Myr and core vesc to km/s)
+    # Copied from cmctools/cmctoolkit.py
+    conv_path = paths.data_cmc / cmc_cluster / "initial.conv.sh"
[…]

### 2023-04-20 src/scripts/mwej_rates.py

@@ -18,6 +18,8 @@ import paths
 #  time w/o @njit |  85s  |  37s
 #  time w/ @njit  |  50s  |  24s
 
+plt.style.use("./src/scripts/matplotlibrc")
+
 ###############################################################################
 
 
@@ -86,9 +88,8 @@ def calc_rolling_rate(
 
     # Calculate rolling rate
     # Note: gcdf.time - mwrow.t sets the time 0 to the present day
-    return _rolling_window_count(
-        gcdf.time.to_numpy() - mwrow.t, window_centers, window_width
-    )
+    times = gcdf.time.to_numpy() - mwrow.t
+    return times, _rolling_window_count(times, window_centers, window_width)
 
 
 ###############################################################################
@@ -146,7 +147,34 @@ for st in np.array(mosaic).flatten():
             pm_pool=pool,
             pm_pbar=True,
         )
-    full_counts = np.array(output).sum(axis=0)
+    # Extract outputs
+    times = np.concatenate([o[0] for o in output])
+    full_counts = np.array([o[1] for o in output]).sum(axis=0)
+
+    ##############################
+    ###  Calc. ej. quantiles   ###
+    ##############################
+
+    # Cut out "future" ejections, and move present day from 0 to 14000
+    times /= 1000
+    times_forward = times[times < 0]
+    times_forward += 14000
+
+    # Calculate quantiles
+    quants5090 = np.quantile(times, [0.5, 0.9])
+    quants5090_forward = np.quantile(times_forward, [0.5, 0.9])
+    print("quants5090 (Myr):", quants5090)
+
+    # Print to output file
+    with open(
+        __file__.replace("scripts", "tex/output").replace(".py", ".txt"), "w"
+    ) as f:
+        f.write("%.2f(%.2f) Gyr" % (14 + quants5090[0], 14 + quants5090[1]))
+
+    ##############################
+    ###          Plot          ###
+    ##############################
+
     # Calculate rate for HV[Ss]
     if nprocs == 1:
         # Don't run in parallel
@@ -175,68 +203,68 @@ for st in np.array(mosaic).flatten():
             pm_pool=pool,
             pm_pbar=True,
         )
-    hvs_counts = np.array(output).sum(axis=0)
-    # Calc WD rate, if one plot
-    if np.array(mosaic).flatten().shape[0] == 1:
-        if nprocs == 1:
-            # Don't run in parallel
-            mp_input = [x for _, x in mwdf.iterrows()]
[…]

### 2023-08-25 src/tex/ms.tex
Updated links, removed ApJ formatting.

@@
 We implement additional features into \fewbody\ pertinent to the study of compact object dynamics.
-We add additional parameters to track stellar object type, distinguishing between stars and compact objects.%, using the numbering convention of \citet{2002MNRAS.329..897H}; similarly, we implement the collision matrix presented in Table 2 of the same paper to determine the type of any post-merger products.
-We use these object types to decide whether to use \fewbody's default sticky-sphere collision criterion - which triggers a collision when the separation of the objects' centers is less than the sum of their radii - in the case of stellar interactions, and a tidal disruption criterion in the case of encounters involving NSs and BHs, which multiplies the threshold separation by a factor of $(m_{\rm CO} / m_{*})^{1/3}$ \citep[as was done in][]{Kremer2019}.
-To the utility of this collision metric, we conservatively assign BHs radii of 5 times their Schwarzschild radii to group the more extreme encounters with mergers, both of which require more careful treatment to accurately represent.
+We add additional parameters to track stellar object type, distinguishing between stars and compact objects.
+We use these object types to decide whether to use \fewbody's default sticky-sphere collision criterion (which triggers a collision when the separation of the objects' centers is less than the sum of their radii) in the case of stellar interactions, or a tidal disruption criterion in the case of encounters involving NSs and BHs, which multiplies the threshold separation by a factor of $(m_{\rm CO} / m_{*})^{1/3}$ \citep[as was done in][]{Kremer2019}.
+To the utility of this collision metric, we conservatively assign BHs radii of 5 times their Schwarzschild radii to group the more extreme encounters with mergers, both of which require more careful treatment to accurately compute.
 
@@
 Over the entire catalog, our encounter sample makes up about half of all strong encounters that occur in the models, with each model contributing a few ten thousand BSCO encounters on average.
-We then realize each encounter in isolation with our modified \fewbody\, computing 10 realizations of each encounter while re-drawing the randomly selected parameters (e.g.~binary phase) to obtain a better statistical representation of the binary-single encounter population.
+We realize each encounter in isolation with our modified \fewbody\, computing 10 realizations of each encounter while re-drawing the randomly selected parameters (e.g.~binary phase) to obtain a better statistical representation of the binary-single encounter population.
 
@@
 they do not contain information about the center-of-mass velocity of the encounter in the frame of the GC model.
-We do not attempt to correct for this, which leads to a minor underestimation of final velocities for encountering objects and subsequently ejection rates; we justify this in Appendix \ref{app:restframe}.
+We do not attempt to correct for this, which leads to a minor underestimation of final velocities for encountering objects and subsequently ejection rates (we justify this in Appendix \ref{app:restframe}).
 
@@
 Unlike the first collapse, this second, permanent core collapse is observable in that the surface brightness profile of the GC becomes cuspy to the limit of the cluster center (and is what observers would classically call a ``core-collapsed cluster'').
-We follow \citet{2018ApJ...855L..15K} in pairing these demographic and observable features, marking the time of second core collapse in our models as the same time the number of BHs drops below 10.
+We follow \citet{2018ApJ...855L..15K} in pairing these demographic and observable features, marking the time of second core collapse in our models as the time when the number of BHs drops below 10.
 
@@
 
-Figure \ref{fig:cmc_single_clusters} shows the ejection velocity $v_{\rm out}$ for every MS star ejected through a BSCO encounter in these models, plotted at the time of encounter from initialization $t$; \textbf{generally, these ejecta account for $\sim$1-6\% of all stellar escapers from a model over its lifetime}.
+Figure \ref{fig:cmc_single_clusters} shows the ejection velocity $v_{\rm out}$ for every MS star ejected through a BSCO encounter in these models, plotted at the time of encounter from initialization $t$; generally, these ejecta account for $\sim$1-6\% of all stellar escapers from a model over its lifetime.
 What is immediately apparent from these single cluster models is a strong correlation between BSCO encounters and the evolution of the cluster core: whenever a cluster undergoes a core collapse, the heightened densities lead to predictably high encounter rates.
@@
 The most massive stars in a cluster are both the first to form binaries and the first to evolve into COs.
-hence, encounters between a mixed binary (composed of a MS star and a CO) and a single MS star \textbf{have the first opportunity to contribute significantly to the overall BSCO encounter population; in the densest models, this primacy leads to a majority of BSCO encounters being of this type over the 14 Gyr evolution.
-Multiple-CO encounters first become major players at first core collapse after CO formation, and can take over as the majority in the case of models with weak or nonexistent pre-core collapse BSCO encounter phases.}
+Hence, encounters between a mixed binary (composed of a MS star and a CO) and a single MS star have the first opportunity to contribute significantly to the overall BSCO encounter population; in the densest models, this primacy leads to a majority of BSCO encounters being of this type over the 14 Gyr evolution.
+Multiple-CO encounters first become major players at first core collapse after CO formation, and can take over as the majority in the case of models with weak or nonexistent pre-core collapse BSCO encounter phases.
 There is a stark difference in the ejection velocities produced by these multiple-CO encounters in comparison to the previous mixed binary-single MS star encounters, and the fastest ejections over the cluster's lifetime are produced in the first tens of Myr after the associated first core collapse.
@@
 For comparison, the escape velocity from the center of the model can be computed from the central and tidal boundary potentials, which are recorded throughout the evolution of the cluster.
-\textbf{
 Figure \ref{fig:cmc_single_clusters_vesc} plots these data for the first sample cluster, where the distribution of encounter escape velocities is strikingly correlated to the central escape velocity, indicating the degree to which the core dominates these dynamics.
-    Throughout the evolution of the model, most BSCO ejections occur at or near the central escape velocity, and this feature is common to the counterpart plots for the other sample models.
+Throughout the evolution of the model, most BSCO ejections occur at or near the central escape velocity (the same plots for the other sample models also display this feature).
 There is a small fraction of points that lie above the core velocity line, which we attribute to the difference in methods employed to calculate escape velocities in the ejection and core contexts.
-}
 
@@
     \caption{
-        \textbf{
-        The local escape velocities $v_{\rm esc}$ at the locations of all BSCO encounters generated from the first sample \CMC\ model (colored points), plotted alongside the central escape velocity of the model (navy).
-        The top plot shows the data in units of ${\rm km~s^{-1}}$, while the lower plot shows the same data normalized to the continuum of the core escape velocity (navy line in the upper plot).
-        }
+        The local escape velocities $v_{\rm esc}$ at the locations of all BSCO encounters generated from the first sample \CMC\ model (colored points), plotted alongside the central escape velocity of the model (dark blue).
+        The top plot shows the data in units of ${\rm km~s^{-1}}$, while the lower plot shows the same data normalized to the continuum of the core escape velocity (dark blue line in the upper plot).
         See Figure \ref{fig:cmc_single_clusters} for an explanation of the color scheme.
@@
             The blue (red) dashed line shows the estimated from observations for runaways from the galactic disc (HVSs from the galactic center), as reported by \citet{2015ARA&A..53...15B}.
-            \textbf{The threshold times by which 50\% and 90\% of the runaway ejections have occured are indicated along the bottom of the figure.}
+            The threshold times by which 50\% and 90\% of the runaway ejections have occured are indicated along the bottom of the figure.
         }
@@
 Finally, Figure \ref{fig:mwej_rates} shows the HVS/runaway rates for our synthetic population, along with observational rate estimates from \citet{2015ARA&A..53...15B}.
-\textbf{We note that 50(90)\% of ejections occur before our synthetic population is \variable{output/mwej_rates.txt}old, and that naturally the earliest ejections are most dependent on any time variability in the MW potential.}
+We note that 50(90)\% of ejections occur before our synthetic population is 3.21(8.59) Gyr old, and that naturally the earliest ejections are most dependent on any time variability in the MW potential.
 At these earlier times, BSCO ejecta could have made as much as 20\% (1\%) of all runaways (HVSs), during the times when GCs underwent their first core collapses.\footnote{Here, the cutoff of this phase is fairly abrupt because we constrain our models to present-day ages of 10-13.5 Gyr (\S\ref{subsec:pairing}).
@@
 
-This work was prepared in part with the reproducibility software \href{https://github.com/showyourwork/showyourwork}{\showyourwork}\citep{2021arXiv211006271L}, which leverages continuous integration to transparently connect the paper to the publicly-available dataset and relevant code.
+This work was prepared in part with the reproducibility software \href{https://github.com/showyourwork/showyourwork}{showyourwork} \citep{2021arXiv211006271L}, which leverages continuous integration to transparently connect the paper to the publicly-available dataset and relevant code.
 The GitHub repository for this project can be found at \url{https://github.com/tomas-cabrera/hvss-bsco}; the icons next to paper content link to the particular scripts used to generate that content.
@@
 
-We include with this publication phase credible regions in phase space for ejecta populations from the MWGCs considered, which may be accessed at \url{https://doi.org/10.5281/zenodo.7599870}.
+We include with this publication phase credible regions in phase space for ejecta populations from the MWGCs considered, which may be accessed at \url{https://doi.org/10.5281/zenodo.7852916}.
 We intend these constructions to be used as secondary evidence for cluster membership of runaway stars, and to encourage further studies into understanding the respective phase space distributions.
@@
 The last two columns (\texttt{CR50} and \texttt{CR90}) are boolean masks of the same convection as the HEALPix probability histogram corresponding to the credible regions (50\% and 90\%, respectively), where bins with entries of 1 are included in the region.
-Figure \ref{fig:check_credible_regions_x} shows the histogram and 50\% and 90\% credible regions for NGC 104, as an example (the script used to generate this plot is \texttt{check\_credible\_regions.py} in the GitHub repository; click on the icon by the caption to be taken directly to the file).
+Figure \ref{fig:check_credible_regions_x} shows the histogram and 50\% and 90\% credible regions for NGC 104, as an example (the script used to generate this plot is \texttt{check\_credible\_regions.py}, which may be found in the GitHub/Zenodo repositories).
 

### 2023-08-25 src/scripts/cmc_single_clusters.py

@@ -107,8 +107,8 @@ for ci, cmc_cluster in enumerate(cmc_cluster_list):
     axr.plot(
         df_dyn.loc[tsample, "t"] / 1000.0,
         df_dyn.loc[tsample, "rho_0"],
-        color="xkcd:navy",
-        alpha=0.7,
+        color="xkcd:dark blue",
+        # alpha=0.7,
         lw=0.5,
         rasterized=True,
     )

### 2023-08-25 src/scripts/cmc_single_clusters_vesc.py

@@ -45,7 +45,7 @@ kw_scatter = {
     "rasterized": True,
 }
 kw_vesccore = {
-    "color": "xkcd:navy",
+    "color": "xkcd:dark blue",
     "lw": 1,
     "rasterized": True,
 }

### 2023-08-25 src/scripts/gcej_today_credreg.py

@@ -1,0 +1,358 @@
+#! For generating ra-dec and mu-mu plots of GCs and their ejecta
+###############################################################################
+
+import healpy as hp
+from astropy.io import fits
+import matplotlib.colors as mplc
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import paths
+import rustics
+from astropy import units as u
+from astropy.coordinates import ICRS, Galactic, Galactocentric, SkyCoord
+from galpy.orbit import Orbit
+from galpy.potential import MWPotential2014
+
+plt.style.use("src/scripts/matplotlibrc")
+
+###############################################################################
+
+def hist2d_hpx_to_mollweide(
+    axes,
+    m,
+    nest=False,
+    xsize=1000,
+    longitude_grid_spacing=60,
+    latitude_grid_spacing=30,
+    graticule_labels=True,
+    kw_rotator={},
+    kw_pcolormesh={},
+):
+    """! Add a HEALPix map as a 2D histogram to an existing Mollweide axes.
+    Largely inspired by hp.newvisufunc.projview.
+
+    axes: axes to add histogram to
+
+    m: HEALPix map
+
+    xsize: number of pixels to use in longitude space
+
+    kw_rotator: dict, keyword args to build rotator for HEALPix map
+
+    kw_pcolormesh: keywords args for pcolormesh call
+    """
+
+    # Make the theta, phi meshgrid
+    ysize = xsize // 2
+    phi = np.linspace(-np.pi, np.pi, xsize)
+    theta = np.linspace(np.pi, 0, ysize)
+    phi, theta = np.meshgrid(phi, theta)
+
+    # Rotate meshgrid if needed
+    if kw_rotator:
+        r = hp.rotator.Rotator(**kw_rotator)
+        theta, phi = r(theta.flatten(), phi.flatten())
+        theta = theta.reshape(ysize, xsize)
+        phi = phi.reshape(ysize, xsize)
+
+    # Get map values at grid points
+    nside = hp.pixelfunc.npix2nside(len(m))
+    grid_pix = hp.pixelfunc.ang2pix(nside, theta, phi, nest=nest)
[…]

### 2024-02-14 src/tex/ms.tex
Updated Zenodo link, fixed figure caption.

@@
             The quantiles in the lower plots are calculated from the present-day velocities of our population.
-            The red dots show the $r_{\rm gc}$ ($Z$) positions of the MWGCs from our composite \citet{2018MNRAS.478.1520B}+\citet{2010arXiv1012.3224H} catalog, arbitrarily spread in the vertical dimension.
+            The red dots show the MWGCs from our composite \citet{2018MNRAS.478.1520B}+\citet{2010arXiv1012.3224H} catalog.
         }

### 2024-02-22 src/tex/ms.tex
Updated Zenodo DOI

@@
 
-We include with this publication phase credible regions in phase space for ejecta populations from the MWGCs considered, which may be accessed at \url{https://doi.org/10.5281/zenodo.7852916}.
+We include with this publication phase credible regions in phase space for ejecta populations from the MWGCs considered, which may be accessed at \url{https://doi.org/10.5281/zenodo.7599870}.
 We intend these constructions to be used as secondary evidence for cluster membership of runaway stars, and to encourage further studies into understanding the respective phase space distributions.
